### 2013-03-26 TCAD2013/overclocking_tcad.tex
CSA Equations1

%% bare_jrnl.tex
%% V1.4
%% 2012/12/27
%% by Michael Shell
%% see http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8 or later) with an IEEE journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
%% and
%% http://www.ieee.org/

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. IEEE's font choices can trigger bugs that do  ***
% *** not appear when using other class files.                            ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%
%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
%%                    bare_jrnl_transmag.tex
%%*************************************************************************

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[journal]{IEEEtran}
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[journal]{../sty/IEEEtran}

% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)

% *** MISC UTILITY PACKAGES ***
%
%\usepackage{ifpdf}
% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
% compilation based on whether the output is pdf or dvi.
% usage:
% \ifpdf
%   % pdf code
% \else
%   % dvi code
% \fi
% The latest version of ifpdf.sty can be obtained from:
% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
% Also, note that IEEEtran.cls V1.7 and later provides a builtin
% \ifCLASSINFOpdf conditional that works the same way.
% When switching from latex to pdflatex and vice-versa, the compiler may
% have to be run twice to clear warning/error messages.

% *** CITATION PACKAGES ***
%
%\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
% not currently provide for hyperlinked citations.
% The latest version can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
% The documentation is contained in the cite.sty file itself.

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi
% graphicx was written by David Carlisle and Sebastian Rahtz. It is
% required if you want graphics, photos, etc. graphicx.sty is already
% installed on most LaTeX systems. The latest version and documentation
% can be obtained at: 
% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
% Another good source of documentation is "Using Imported Graphics in
% LaTeX2e" by Keith Reckdahl which can be found at:
% http://www.ctan.org/tex-archive/info/epslatex/
%
% latex, and pdflatex in dvi mode, support graphics in encapsulated
% postscript (.eps) format. pdflatex in pdf mode supports graphics
% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
% which can result in "jaggedy"/blurry rendering of lines and letters as
% well as large increases in file sizes.
%
% You can find documentation about the pdfTeX application at:
% http://www.tug.org/applications/pdftex

% *** MATH PACKAGES ***
%
%\usepackage[cmex10]{amsmath}
% A popular package from the American Mathematical Society that provides
% many useful and powerful commands for dealing with mathematics. If using
% it, be sure to load this package with the cmex10 option to ensure that
% only type 1 fonts will utilized at all point sizes. Without this option,
% it is possible that some math symbols, particularly those within
% footnotes, will be rendered in bitmap form which will result in a
% document that can not be IEEE Xplore compliant!
%
% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
% thus preventing page breaks from occurring within multiline equations. Use:
%\interdisplaylinepenalty=2500
% after loading amsmath to restore such page breaks as IEEEtran.cls normally
% does. amsmath.sty is already installed on most LaTeX systems. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/

% *** SPECIALIZED LIST PACKAGES ***
%
%\usepackage{algorithmic}
% algorithmic.sty was written by Peter Williams and Rogerio Brito.
% This package provides an algorithmic environment fo describing algorithms.
% You can use the algorithmic environment in-text or within a figure
% environment to provide for a floating algorithm. Do NOT use the algorithm
% floating environment provided by algorithm.sty (by the same authors) or
% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
% algorithm float types and packages that provide these will not provide
% correct IEEE style captions. The latest version and documentation of
% algorithmic.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
% There is also a support site at:
% http://algorithms.berlios.de/index.html
% Also of interest may be the (relatively newer and more customizable)
% algorithmicx.sty package by Szasz Janos:
% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/

% *** ALIGNMENT PACKAGES ***
%
%\usepackage{array}
% Frank Mittelbach's and David Carlisle's array.sty patches and improves
% the standard LaTeX2e array and tabular environments to provide better
% appearance and additional user controls. As the default LaTeX2e table
% generation code is lacking to the point of almost being broken with
% respect to the quality of the end results, all users are strongly
% advised to use an enhanced (at the very least that provided by array.sty)
% set of table tools. array.sty is already installed on most systems. The
% latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/required/tools/

% IEEEtran contains the IEEEeqnarray family of commands that can be used to
% generate multiline equations as well as matrices, tables, etc., of high
% quality.

% *** SUBFIGURE PACKAGES ***
%\ifCLASSOPTIONcompsoc
%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
%\else
%  \usepackage[caption=false,font=footnotesize]{subfig}
%\fi
% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
% for subfigure.sty, the latter of which is no longer maintained and is
% incompatible with some LaTeX packages including fixltx2e. However,
% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
% which will override IEEEtran.cls' handling of captions and this will result
% in non-IEEE style figure/table captions. To prevent this problem, be sure
% and invoke subfig.sty's "caption=false" package option (available since
% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
% handling of captions.
% Note that the Computer Society format requires a larger sans serif font
% than the serif footnote size font used in traditional IEEE formatting
% and thus the need to invoke different subfig.sty package options depending
% on whether compsoc mode has been enabled.
%
% The latest version and documentation of subfig.sty can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/

% *** FLOAT PACKAGES ***
%
%\usepackage{fixltx2e}
% fixltx2e, the successor to the earlier fix2col.sty, was written by
% Frank Mittelbach and David Carlisle. This package corrects a few problems
% in the LaTeX2e kernel, the most notable of which is that in current
% LaTeX2e releases, the ordering of single and double column floats is not
% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
% single column figure to be placed prior to an earlier double column
% figure. The latest version and documentation can be found at:
% http://www.ctan.org/tex-archive/macros/latex/base/

%\usepackage{stfloats}
% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
% the ability to do double column floats at the bottom of the page as well
% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
% LaTeX2e). It also provides a command:
%\fnbelowfloat
% to enable the placement of footnotes below bottom floats (the standard
% LaTeX2e kernel puts them above bottom floats). This is an invasive package
% which rewrites many portions of the LaTeX2e float routines. It may not work
% with other packages that modify the LaTeX2e float routines. The latest
% version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
% Do not use the stfloats baselinefloat ability as IEEE does not allow
% \baselineskip to stretch. Authors submitting work to the IEEE should note
% that IEEE rarely uses double column equations and that authors should try
% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
% such ways.
% Do not attempt to use stfloats with fixltx2e as they are incompatible.
% Instead, use Morten Hogholm'a dblfloatfix which combines the features
% of both fixltx2e and stfloats:
%
% \usepackage{dblfloatfix}
% The latest version can be found at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/

%\ifCLASSOPTIONcaptionsoff
%  \usepackage[nomarkers]{endfloat}
% \let\MYoriglatexcaption\caption
% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
%\fi
% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
% Axel Sommerfeldt. This package may be useful when used in conjunction with 
% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
% submissions have lists of figures/tables at the end of the paper and that
% figures/tables without any captions are placed on a page by themselves at
% the end of the document. If needed, the draftcls IEEEtran class option or
% \CLASSINPUTbaselinestretch interface can be used to increase the line
% spacing as well. Be sure and use the nomarkers option of endfloat to
% prevent endfloat from "marking" where the figures would have been placed
% in the text. The two hack lines of code above are a slight modification of
% that suggested by in the endfloat docs (section 8.4.1) to ensure that
% the full captions always appear in the list of figures/tables - even if
% the user used the short optional argument of \caption[]{}.
% IEEE papers do not typically make use of \caption[]'s optional argument,
% so this should not be an issue. A similar trick can be used to disable
% captions of packages such as subfig.sty that lack options to turn off
% the subcaptions:
% For subfig.sty:
% \let\MYorigsubfloat\subfloat
% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
% However, the above trick will not work if both optional arguments of
% the \subfloat command are used. Furthermore, there needs to be a
% description of each subfigure *somewhere* and endfloat does not add
% subfigure captions to its list of figures. Thus, the best approach is to
% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
% and instead reference/explain all the subfigures within the main caption.
% The latest version of endfloat.sty and its documentation can obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
%
% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
% later in the document, say, to conditionally put the References on a 
% page by themselves.

% *** PDF, URL AND HYPERLINK PACKAGES ***
%
%\usepackage{url}
% url.sty was written by Donald Arseneau. It provides better support for
% handling and breaking URLs. url.sty is already installed on most LaTeX
% systems. The latest version and documentation can be obtained at:
% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
% Basically, \url{my_url_here}.

% *** Do not adjust lengths that control margins, column widths, etc. ***
% *** Do not use packages that alter fonts (such as pslatex).         ***
% There should be no need to do such things with IEEEtran.cls V1.6 and later.
% (Unless specifically asked to do so by the journal or conference you plan
% to submit to, of course. )

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls for Journals}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
        John~Doe,~\IEEEmembership{Fellow,~OSA,}
        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
\thanks{M. Shell is with the Department
of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
% 
% *** Note that you probably will NOT want to include the author's ***
% *** name in the headers of peer review papers.                   ***
% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
% you desire.

% If you want to put a publisher's ID mark on the page you can do it like
% this:
%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
% Remember, if you use this you must call \IEEEpubidadjcol in the second
% column for its text to clear the IEEEpubid mark.

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
The abstract goes here.
\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}

\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% The very first letter is a 2 line initial drop letter followed
% by the rest of the first word in caps.
% 
% form to use if the first word consists of a single letter:
% \IEEEPARstart{A}{demo} file is ....
% 
% form to use if you need the single drop letter followed by
% normal text (unknown if ever used by IEEE):
% \IEEEPARstart{A}{}demo file is ....
% 
% Some journals put the first two words in caps:
% \IEEEPARstart{T}{his demo} file is ....
% 
% Here we have the typical use of a "T" for an initial drop letter
% and "HIS" in caps to complete the first word.
\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
for IEEE journal papers produced under \LaTeX\ using
IEEEtran.cls version 1.8 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill December 27, 2012

\subsection{Subsection Heading Here}
Subsection text here.

% needed in second column of first page if using \IEEEpubid
%\IEEEpubidadjcol

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{Carry Select Adder}
\subsection{Introduction}

\subsection{Timing Models for $n$-bit Carry Selct Adder}
In this section, we describe the modeling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA. This information can be employed to determine the truncation error based on the models presented in Section.xxx.

In an $n$-stage CSA, let the stage delay be denoted as $d_{0}\dots d_{n-1}$, where $d_{0}$ and $d_{n-1}$ represent the delay of MSB stage and LSB stage, respectively. In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing. Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ detnoes the delay of multiplexer.
\begin{eqnarray}\label{CSA_SingleStageDelay}
  d_i=n_i\cdot \mu_{c}+xxx\cdot\mu_{mux} 
 % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
\end{eqnarray}

Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform to lead to the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
\begin{eqnarray}\label{CSA_DelayEqual}
  d_0=d_1=\cdots=d_{n-1}
\end{eqnarray}

Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (), which denotes the word-length of stage $i$.
\begin{eqnarray}\label{CSA_DelayRep}
  n_i=n_0-xxx\cdot\frac{\mu_{mux}}{\mu_{c}}
\end{eqnarray}

Therefore the word-length of CSA is given by (\ref{CSA_WL}).
\begin{eqnarray}\label{CSA_WL}
  n_{CSA}=\sum_{i=0}^{n-1}n_{i}=cn_{0}-\frac{\mu_{mux}}{\mu_{carry}}\cdot\frac{(c+1)(c-2)}{2}
\end{eqnarray}

In the conventional situation, the word-length of both RCA and CSA should be truncated in order to meet timing. Hence we obtain~(\ref{CSA_RCA}), where $n_{RCA}$ is determined through (xxx).
\begin{eqnarray}\label{CSA_RCA}
  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
\end{eqnarray}

Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}) we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
\begin{eqnarray}\label{CSA_Timing}
  n_{CSA}=cn_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
\end{eqnarray}

%In addition, the word-length of the least significant stage should be greater than 0. Therefore
In addition, combining (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure that $n_{c-1}>0$. Therefore the stage number is bounded by (\ref{CSA_StageNumber}).
\begin{eqnarray}\label{CSA_StageNumber}
  c<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
\end{eqnarray}
%the word-length of each CSA stage is allocated to ensure that

\subsection{Model Verification}

\subsection{Comparison between CSA and RCA}

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results.}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals use top floats exclusively.
% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
% floats. This can be corrected via the \fnbelowfloat command of the
% stfloats package.

\section{Conclusion}
The conclusion goes here.

% if have a single appendix:
%\appendix[Proof of the Zonklar Equations]
% or
%\appendix  % for no appendix heading
% do not use \section anymore after \appendix, only \section*
% is possibly needed

% use appendices with more than one appendix
% then use \section to start each appendix
% you must declare a \section before using any
% \subsection or using \label (\appendices by itself
% starts a section numbered zero.)
%

\appendices
\section{Proof of the First Zonklar Equation}
Appendix one text goes here.

% you can choose not to have a title for an appendix
% if you want by leaving the argument blank
\section{}
Appendix two text goes here.

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

\begin{IEEEbiography}{Michael Shell}
Biography text here.
\end{IEEEbiography}

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{John Doe}
Biography text here.
\end{IEEEbiographynophoto}

% insert where needed to balance the two columns on the last page with
% biographies
%\newpage

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

% that's all folks
\end{document}

### 2013-03-27 TCAD2013/overclocking_tcad.tex
CSA_equations2

@@
 
+\usepackage{multirow}
+\usepackage{amssymb}
+
 % *** MATH PACKAGES ***
 %
-%\usepackage[cmex10]{amsmath}
+\usepackage[cmex10]{amsmath}
 % A popular package from the American Mathematical Society that provides
@@
 \begin{eqnarray}\label{CSA_SingleStageDelay}
-  d_i=n_i\cdot \mu_{c}+xxx\cdot\mu_{mux} 
+  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
  % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
@@
 
-Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (), which denotes the word-length of stage $i$.
+Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), which denotes the CSA word-length of stage $i$.
+Note that the word-length of stage $c-1$ and $c-2$ are identical, since the least significant stage is composed of RCA.
 \begin{eqnarray}\label{CSA_DelayRep}
-  n_i=n_0-xxx\cdot\frac{\mu_{mux}}{\mu_{c}}
+ % n_i=n_0-xxx\cdot\frac{\mu_{mux}}{\mu_{c}}
+ n_i=\left\{
+	\begin{matrix}
+	  n_0-i\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in(2,c-2]$ and $c>2$}\\
+	  n_0-(c-2)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i=c-1$ and $c\geqslant2$}
+	\end{matrix}
+    \right.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{CSA_Timing}
-  n_{CSA}=cn_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
+  n_{CSA}=c\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
 \end{eqnarray}
@@
 %In addition, the word-length of the least significant stage should be greater than 0. Therefore
-In addition, combining (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure that $n_{c-1}>0$. Therefore the stage number is bounded by (\ref{CSA_StageNumber}).
+It can be seen that $c=1$ leads to $n_{CSA}=n_{RCA}$.
+This is because the least significant stage of CSA is built by RCA.
+In addition, combining (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure that $n_{c-1}>0$.
+Therefore the stage number is bounded by (\ref{CSA_StageNumber}).
 \begin{eqnarray}\label{CSA_StageNumber}
@@
 \subsection{Model Verification}
+As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
+This is achieved by keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$.
+The corresponding $d_0$ is recorded through the timing analysis tool.
+Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Figure.xxx.
+Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
 
-\subsection{Comparison between CSA and RCA}
+Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA.
+Figure.xxx demonstrates both the modeled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency.
+Note that tht maximum input word-length is 16-bit, hence the modeled value is set to 16 if it expires.
+
+% Figure goes here!
+It can be seen that our model provide slight conservative outcomes than the experimental data, especially at higher operating frequency.
+This is because the model coefficients are obtained based on timing analysis, which is designed to ensure correct functionality across a range of operating conditions.
+In addition, routing delay might be introduced to enlarge the overall delay, while our models consider logic delay only.
+
+\subsection{Area Overhead}
+Figure.xxx demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies.
+We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
+It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is intially increased.
+This means smaller truncation error can be obtained by CSA for a given frequency.
+RCA outperforms than CSA when very high frequency is applied, which in turn leads to small word-length for both structures.
+In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.
+
+%CSA achieves greater word-length than RCA when frequency is initially increased
+
+However, the accuracy benefits brought by CSA comes with the cost of large area overhead.
+Figure.xxx depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures.
+It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+
+the 3-stage CSA costs
+
+The stage number is determined by (\ref{CSA_StageNumber})
 

### 2013-03-28 TCAD2013/overclocking_tcad.tex
Add Figures for CSA section

@@
 %
+%\usepackage{graphicx}
 \ifCLASSINFOpdf
-  % \usepackage[pdftex]{graphicx}
+  \usepackage[pdftex]{graphicx}
   % declare the path(s) where your graphic files are
@@
   % driver is specified.
-  % \usepackage[dvips]{graphicx}
+  \usepackage[dvips]{graphicx}
   % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
+  \graphicspath{{../Figures/}}
   % and their extensions so you won't have to specify these with
   % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
+  \DeclareGraphicsExtensions{.eps}
 \fi
+\usepackage{epstopdf}
 % graphicx was written by David Carlisle and Sebastian Rahtz. It is
@@
 % *** SUBFIGURE PACKAGES ***
+\usepackage[tight,footnotesize]{subfigure}
 %\ifCLASSOPTIONcompsoc
@@
 
-%\usepackage{stfloats}
+\usepackage{stfloats}
 % stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
@@
 % Do not put math or special symbols in the title.
-\title{Bare Demo of IEEEtran.cls for Journals}
+\title{Title}
 %
@@
 
-\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
-        John~Doe,~\IEEEmembership{Fellow,~OSA,}
-        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
-\thanks{M. Shell is with the Department
-of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,
-GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
+\author{Kan~Shi,
+        David~Boland,~\IEEEmembership{Member,~IEEE,}
+        and~George~A.~Constantinides,~\IEEEmembership{Senior~Memberellow,~IEEE}% <-this % stops a space
+	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, UK}%
+	%\thanks{M.
+Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
+%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
 \thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}
@@
 \begin{abstract}
-The abstract goes here.
+The abstract.
 \end{abstract}
@@
 
-\subsection{Timing Models for $n$-bit Carry Selct Adder}
-In this section, we describe the modeling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
+\subsection{Timing Models for $n$-bit Carry Select Adder}
+In this section, we describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
 This information can be employed to determine the truncation error based on the models presented in Section.xxx.
@@
 In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing.
-Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ detnoes the delay of multiplexer.
+Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexer.
 \begin{eqnarray}\label{CSA_SingleStageDelay}
@@
 Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA.
-Figure.xxx demonstrates both the modeled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency.
-Note that tht maximum input word-length is 16-bit, hence the modeled value is set to 16 if it expires.
+Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency.
+Note that the maximum input word-length is 16-bit, hence the modelled value is set to 16 if it expires.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3in]{./Figures/Model.eps}
+  \caption{Model Verification.}
+  \label{CSA Model Verification}
+\end{figure}
 
@@
 \subsection{Area Overhead}
-Figure.xxx demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies.
+Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies.
 We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
-It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is intially increased.
+It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
 This means smaller truncation error can be obtained by CSA for a given frequency.
@@
 In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.
-
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
+  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
+  \label{CSA3stage Timing}
+\end{figure}
 %CSA achieves greater word-length than RCA when frequency is initially increased
@@
 However, the accuracy benefits brought by CSA comes with the cost of large area overhead.
-Figure.xxx depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures.
+Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures.
 It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
+  \caption{Area overhead for RCA and CSA.}
+  \label{CSA3stage Area}
+\end{figure}
+%the 3-stage CSA costs
 
-the 3-stage CSA costs
+\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
+Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead.
+In the following experiments, the trade-offs between accuracy, performance as well as area are explored.
+If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
+Therefore truncation errors would be generated.
+For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively.
+The corresponding error expectations of RCA and CSA are demonstrated in Fig.xxx.
+The optimal design method which achieves the minimum error expectation is labelled.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
+	\caption{LUT=45}
+\end{figure}
 
-The stage number is determined by (\ref{CSA_StageNumber})
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
+	\caption{LUT=35}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
+	\caption{LUT=25}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
+	\caption{LUT=15}
+\end{figure}
+
+%\begin{figure*}[htbp]
+%  \centering
+%  \subfigure[LUTs=45]{
+%  \begin{minipage}[c]{0.45\textwidth}
+%    \centering
+%    \includegraphics[width=2in]{./Figures/Error_LUT45.eps}
+%  \end{minipage}%
+%  }%
+%  \subfigure[LUT=35]{
+%  \begin{minipage}[c]{0.45\textwidth}
+%    \centering
+%    \includegraphics[width=2in]{./Figures/Error_LUT35.eps}
+%  \end{minipage}
+%  }
+%  \subfigure[LUT=25]{
+%  \begin{minipage}[c]{0.45\textwidth}
+%    \centering
+%    \includegraphics[width=2in]{./Figures/Error_LUT25.eps}
+%  \end{minipage}
+%  }%
+%  \subfigure[LUT=15]{
+%  \begin{minipage}[c]{0.45\textwidth}
+%    \centering
+%    \includegraphics[width=2in]{./Figures/Error_LUT15.eps}
+%  \end{minipage}
+%  }
+%  \caption{Accuracy-performance trade-offs under fixed area constraints.}
+%  \label{Fig Tradeoffs}
+%\end{figure*}
+%the maximum word-lengths of RCA and CSA under given area constraints are listed in Table.xxx
+
+It can be seen that if area is not limited, CSA with higher stage numbers serve as the optimal design choice for most frequency values, as we discussed in Section.xxx.
+While overclocking the RCA achieves better accuracy at higher frequencies, d
+%According to
 
@@
 
-\appendices
-\section{Proof of the First Zonklar Equation}
-Appendix one text goes here.
+%\appendices
+%\section{Proof of the First Zonklar Equation}
+%Appendix one text goes here.
 
@@
 % if you want by leaving the argument blank
-\section{}
-Appendix two text goes here.
+%\section{}
+%Appendix two text goes here.
 

### 2013-03-31 TCAD2013/overclocking_tcad.tex
Describe tradeoffs

@@
 %% by Michael Shell
-%% see http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.8 or later) with an IEEE journal paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
 
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex,
-%%                    bare_jrnl_transmag.tex
-%%*************************************************************************
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
-%
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
-%
 \documentclass[journal]{IEEEtran}
@@
 % \documentclass[journal]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
 
@@
 \usepackage[cmex10]{amsmath}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-%\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
 
@@
 
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
 \hyphenation{op-tical net-works semi-conduc-tor}
@@
 \begin{document}
-%
-% paper title
-% can use linebreaks \\ within to get better formatting as desired
-% Do not put math or special symbols in the title.
+
 \title{Title}
@@
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2012 IEEE}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark.
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
 
@@
 The corresponding $d_0$ is recorded through the timing analysis tool.
-Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Figure.xxx.
+Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}).
 Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
+  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the delay value obtained through the Xilinx Timing Analyzer.}
+  \label{DelayFitting}
+\end{figure}
 
@@
 If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
-Therefore truncation errors would be generated.
-For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively.
-The corresponding error expectations of RCA and CSA are demonstrated in Fig.xxx.
+This potentially generate truncation errors.
+For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture.
+In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking.
+The corresponding error expectations of these scenarios are depicted in Fig.xxx.
 The optimal design method which achieves the minimum error expectation is labelled.
@@
 %\end{figure*}
-%the maximum word-lengths of RCA and CSA under given area constraints are listed in Table.xxx
 
-It can be seen that if area is not limited, CSA with higher stage numbers serve as the optimal design choice for most frequency values, as we discussed in Section.xxx.
-While overclocking the RCA achieves better accuracy at higher frequencies, d
-%According to
+If there is no area limitation, CSA with higher stage numbers will be the optimal design choice unless very high frequencies are applied.
+This is because a long carry chain is divided into multiple overlapped sections in comparison to RCA, and the higher stage number the shorter the carry chain length of each stage.
+When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA.
+It can be seen that the overclocked RCA outperforms at higher frequencies.
+
+For a tighter area budget, only part of the complex structures can be implemented, while the simple structure still keep full precision.
+As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes dominate when the frequency is initially increased.
+This lead to the truncation of word-length of both 2-stage and 3-stage CSA.
+For an even stringent area constraint, the word-length of RCA is limited, meanwhile CSA with high stage numbers could not be implemented, as shown in Fig.xxx.
+In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.
+
+In general, the error expectations at the output of all four design method for a variety of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3.3in]{./Figures/Tradeoff.eps}
+  \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
+  \label{Tradeoff}
+\end{figure}
 
@@
 
-% if have a single appendix:
-%\appendix[Proof of the Zonklar Equations]
-% or
-%\appendix  % for no appendix heading
-% do not use \section anymore after \appendix, only \section*
-% is possibly needed
-
-% use appendices with more than one appendix
-% then use \section to start each appendix
-% you must declare a \section before using any
-% \subsection or using \label (\appendices by itself
-% starts a section numbered zero.)
-%
-
-%\appendices
-%\section{Proof of the First Zonklar Equation}
-%Appendix one text goes here.
-
-% you can choose not to have a title for an appendix
-% if you want by leaving the argument blank
-%\section{}
-%Appendix two text goes here.
-
 % use section* for acknowledgement

### 2013-03-31 TCAD2013/overclocking_tcad.tex
modified v1

@@
-%% bare_jrnl.tex
-%% V1.4
-%% 2012/12/27
-%% by Michael Shell
+%% overclocking_tcad.tex
+%% by Kan Shi
+
+%\usepackage{times,epsfig,amsfonts,bm}
+%\usepackage{pdflscape}
+%\usepackage{afterpage}
+%\usepackage{algorithm}
+%\usepackage{algorithmic}
+%\usepackage{fmtcount,threeparttable, setspace, nicefrac}
+%\usepackage[dvips]{color}
+%\usepackage{amsthm}
 
 \documentclass[journal]{IEEEtran}
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[journal]{../sty/IEEEtran}
+\usepackage{cite}
 
-% *** MISC UTILITY PACKAGES ***
-%
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-% *** CITATION PACKAGES ***
-%
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off
-% such as if a citation ever needs to be enclosed in parenthesis.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
-%
-%\usepackage{graphicx}
 \ifCLASSINFOpdf
@@
 \usepackage{epstopdf}
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation
-% can be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found at:
-% http://www.ctan.org/tex-archive/info/epslatex/
-%
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
 
@@
 \usepackage{amssymb}
-
-% *** MATH PACKAGES ***
-%
 \usepackage[cmex10]{amsmath}
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
 %\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
 %\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-% *** SUBFIGURE PACKAGES ***
 \usepackage[tight,footnotesize]{subfigure}
-%\ifCLASSOPTIONcompsoc
-%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
-%\else
-%  \usepackage[caption=false,font=footnotesize]{subfig}
-%\fi
-% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
-% for subfigure.sty, the latter of which is no longer maintained and is
-% incompatible with some LaTeX packages including fixltx2e. However,
-% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
-% which will override IEEEtran.cls' handling of captions and this will result
-% in non-IEEE style figure/table captions. To prevent this problem, be sure
-% and invoke subfig.sty's "caption=false" package option (available since
-% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
-% handling of captions.
-% Note that the Computer Society format requires a larger sans serif font
-% than the serif footnote size font used in traditional IEEE formatting
-% and thus the need to invoke different subfig.sty package options depending
-% on whether compsoc mode has been enabled.
-%
-% The latest version and documentation of subfig.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
 \usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Do not use the stfloats baselinefloat ability as IEEE does not allow
-% \baselineskip to stretch. Authors submitting work to the IEEE should note
-% that IEEE rarely uses double column equations and that authors should try
-% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
-% packages (also by Sigitas Tolusis) as IEEE does not format its papers in
-% such ways.
-% Do not attempt to use stfloats with fixltx2e as they are incompatible.
-% Instead, use Morten Hogholm'a dblfloatfix which combines the features
-% of both fixltx2e and stfloats:
-%
-% \usepackage{dblfloatfix}
-% The latest version can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/dblfloatfix/
-
-%\ifCLASSOPTIONcaptionsoff
-%  \usepackage[nomarkers]{endfloat}
-% \let\MYoriglatexcaption\caption
-% \renewcommand{\caption}[2][\relax]{\MYoriglatexcaption[#2]{#2}}
-%\fi
-% endfloat.sty was written by James Darrell McCauley, Jeff Goldberg and 
-% Axel Sommerfeldt. This package may be useful when used in conjunction with 
-% IEEEtran.cls'  captionsoff option. Some IEEE journals/societies require that
-% submissions have lists of figures/tables at the end of the paper and that
-% figures/tables without any captions are placed on a page by themselves at
-% the end of the document. If needed, the draftcls IEEEtran class option or
-% \CLASSINPUTbaselinestretch interface can be used to increase the line
-% spacing as well. Be sure and use the nomarkers option of endfloat to
-% prevent endfloat from "marking" where the figures would have been placed
-% in the text. The two hack lines of code above are a slight modification of
-% that suggested by in the endfloat docs (section 8.4.1) to ensure that
-% the full captions always appear in the list of figures/tables - even if
-% the user used the short optional argument of \caption[]{}.
-% IEEE papers do not typically make use of \caption[]'s optional argument,
-% so this should not be an issue. A similar trick can be used to disable
-% captions of packages such as subfig.sty that lack options to turn off
-% the subcaptions:
-% For subfig.sty:
-% \let\MYorigsubfloat\subfloat
-% \renewcommand{\subfloat}[2][\relax]{\MYorigsubfloat[]{#2}}
-% However, the above trick will not work if both optional arguments of
-% the \subfloat command are used. Furthermore, there needs to be a
-% description of each subfigure *somewhere* and endfloat does not add
-% subfigure captions to its list of figures. Thus, the best approach is to
-% avoid the use of subfigure captions (many IEEE journals avoid them anyway)
-% and instead reference/explain all the subfigures within the main caption.
-% The latest version of endfloat.sty and its documentation can obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/endfloat/
-%
-% The IEEEtran \ifCLASSOPTIONcaptionsoff conditional can also be used
-% later in the document, say, to conditionally put the References on a 
-% page by themselves.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/url/
-% Basically, \url{my_url_here}.
-
-\hyphenation{op-tical net-works semi-conduc-tor}
 
@@
 \title{Title}
-%
-%
-% author names and IEEE memberships
-% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
-% a structure at a ~ so this keeps an author's name from being broken across
-% two lines.
-% use \thanks{} to gain access to the first footnote area
-% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
-% was not built to handle multiple paragraphs
-%
 
@@
         David~Boland,~\IEEEmembership{Member,~IEEE,}
-        and~George~A.~Constantinides,~\IEEEmembership{Senior~Memberellow,~IEEE}% <-this % stops a space
-	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, UK}%
+        and~George~A.~Constantinides,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
+	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, SW7 2BT, U.K. (email: {}@imperial.ac.uk)}%
 	%\thanks{M.
@@
 
-% make the title area
 \maketitle
@@
 
-% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
@@
 
-% needed in second column of first page if using \IEEEpubid
-%\IEEEpubidadjcol
-
 \subsubsection{Subsubsection Heading Here}
@@
 \subsection{Introduction}
+Since the delay of RCA is determined by the length of carry chain, there are several alternative adder architectures proposed to shorten the carry chain.
+For instance, the carry select adder (CSA) is designed to overlap carry propagation in sections such that the operating speed can be boosted.
+In a CSA, the carry chain is divided into multiple stages.
+Each stage contains two RCAs and two multiplexers.
+For a given input, computations are performed twice simultaneously, with the carry input as zero and one respectively.
+The results are then selected according to the actual carry input.
+Although this structure brings timing benefits, it costs extra hardware resources than RCA as the carry chain is duplicated and multiplexers are expensive especially in the FPGA technology.
+In this section, silicon area is incorporated as the third metric besides accuracy and performance.
+We explore the trade-offs between these three factors for both adder structures.
+The objective is to demonstrate the best design choice for a given set of design constraints.
+
+%In addition to RCA, there are several
 
 \subsection{Timing Models for $n$-bit Carry Select Adder}
-In this section, we describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
+We initially describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
 This information can be employed to determine the truncation error based on the models presented in Section.xxx.
 
-In an $n$-stage CSA, let the stage delay be denoted as $d_{0}\dots d_{n-1}$, where $d_{0}$ and $d_{n-1}$ represent the delay of MSB stage and LSB stage, respectively.
-In our analysis, we follow the previous assumption that delay is caused due to carry propagation and, in this case, multiplexing.
-Thus the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{carry}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexer.
+In a CSA with $c$ stages, let the stage delay be denoted by $d_{0}\dots d_{c-1}$, where $d_{0}$ and $d_{c-1}$ represent the delay of the most significant stage and the least significant stage, respectively.
+Unlike other stages, the least significant stage is built by one RCA only, since it is directly driven by the carry input.
+In our analysis, we follow the previous assumption that delay is due to carry propagation as well as, in this case, multiplexing the carry output.
+Therefore the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
 \begin{eqnarray}\label{CSA_SingleStageDelay}
@@
 
-Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform to lead to the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
+Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform for the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
 \begin{eqnarray}\label{CSA_DelayEqual}
@@
 
-Therefore the word-length of CSA is given by (\ref{CSA_WL}).
+The word-length of CSA is then given by (\ref{CSA_WL}).
 \begin{eqnarray}\label{CSA_WL}
@@
 
-In the conventional situation, the word-length of both RCA and CSA should be truncated in order to meet timing. Hence we obtain~(\ref{CSA_RCA}), where $n_{RCA}$ is determined through (xxx).
+In the conventional situation, the word-length of both RCA and CSA should be properly selected in order to meet timing.
+In this case,~(\ref{CSA_RCA}) can be obtained, where $n_{RCA}$ is determined by current timing information through (xxx).
 \begin{eqnarray}\label{CSA_RCA}
@@
 
-Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}) we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
+Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}), we may obtain the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
+% we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
 \begin{eqnarray}\label{CSA_Timing}
@@
 
-%In addition, the word-length of the least significant stage should be greater than 0. Therefore
 It can be seen that $c=1$ leads to $n_{CSA}=n_{RCA}$.
-This is because the least significant stage of CSA is built by RCA.
-In addition, combining (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure that $n_{c-1}>0$.
-Therefore the stage number is bounded by (\ref{CSA_StageNumber}).
+This is because RCA forms the least significant stage of CSA.
+In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure $n_{c-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
 \begin{eqnarray}\label{CSA_StageNumber}
@@
 As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
-This is achieved by keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$.
-The corresponding $d_0$ is recorded through the timing analysis tool.
+This ratio can be obtained through timing analysis.
+Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ through the timing analysis tool.
+According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials, as presented in Fig.~(\ref{DelayFitting}).
+Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
+%keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$.
+The corresponding delay value $d_0$ is recorded through the timing analysis tool.
 Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}).
@@
   \includegraphics[width=3.3in]{./Figures/Fitting.eps}
-  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the delay value obtained through the Xilinx Timing Analyzer.}
+  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the given input word-length and the corresponding delay value obtained through the Xilinx Timing Analyzer.}
   \label{DelayFitting}
@@
 
-Using this information, we verify our model with the results obtained through post place and route simulations of Xilinx Virtex-6 FPGA.
-Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, under a given operating frequency.
-Note that the maximum input word-length is 16-bit, hence the modelled value is set to 16 if it expires.
+Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
+Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, across a range of operating frequencies.
+The maximum input word-length in our experiments is 16-bit, hence the modelled value is set to 16 if it expires.
 \begin{figure}[htbp]
@@
   \includegraphics[width=3in]{./Figures/Model.eps}
-  \caption{Model Verification.}
+  \caption{Comparison of the maximum word-length for a given operating frequency between the modelled value and the experimental results from FPGA simulations.}
   \label{CSA Model Verification}
@@
 % Figure goes here!
-It can be seen that our model provide slight conservative outcomes than the experimental data, especially at higher operating frequency.
-This is because the model coefficients are obtained based on timing analysis, which is designed to ensure correct functionality across a range of operating conditions.
-In addition, routing delay might be introduced to enlarge the overall delay, while our models consider logic delay only.
+It can be seen that our timing models match well the experimental results for both RCA and CSA, except that the modelled outcomes are slight conservative, especially at higher operating frequencies.
+This is because the model coefficients are obtained based on timing analysis, which is designed with safety margins to ensure correct functionality for diverse operating conditions.
+In addition, routing delay might be introduced during timing analysis such that the overall delay is enlarged, while our models consider logic delay only.
+
+% provide slight conservative outcomes than the experimental data, especially at higher operating frequencies. 
+.
 
 \subsection{Area Overhead}
-Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-length for RCA and CSA with 2 stages and 3 stages respectively under a range of operating frequencies.
-We only investigate 3 stages since the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
+Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies.
+We only investigate 3 stages as the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
 It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
-This means smaller truncation error can be obtained by CSA for a given frequency.
-RCA outperforms than CSA when very high frequency is applied, which in turn leads to small word-length for both structures.
+This corresponds to smaller truncation errors.
+RCA only outperforms than CSA when very high frequency is applied.
 In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.
@@
 However, the accuracy benefits brought by CSA comes with the cost of large area overhead.
-Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs)) used for all three structures.
-It can be seen that the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs) in the FPGA) used for all three structures.
+It can be seen that for a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
 \begin{figure}[htbp]
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead.
-In the following experiments, the trade-offs between accuracy, performance as well as area are explored.
+%Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, 
+To answer this question, we explore the trade-offs between accuracy, performance as well as area in this section.
 If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
-This potentially generate truncation errors.
-For instance, the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture.
+The precision lose might generates large errors even at low frequencies.
+This is demonstrated by experiments where an area constraint is applied besides the timing requirement.
+Both of the constraints are met by reducing the word-length of the input signal.
+The errors at the outputs are recorded with the reference to the original word-length.
+In addition, another designing method is adopted where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
+For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
+The optimal design metric with the minimum error expectation is labelled for each area constraint.
+%
+% the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture.
 In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking.
@@
 
-If there is no area limitation, CSA with higher stage numbers will be the optimal design choice unless very high frequencies are applied.
-This is because a long carry chain is divided into multiple overlapped sections in comparison to RCA, and the higher stage number the shorter the carry chain length of each stage.
+If the available area is large enough, as shown in Fig.xxx, CSA with higher stage numbers can be implemented with full precision and it is the optimal design choice unless very high frequencies are applied.
+This is because at lower frequencies, the long carry chain is divided into multiple overlapped sections, and the higher stage number the shorter the carry chain length of each stage.
 When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA.
-It can be seen that the overclocked RCA outperforms at higher frequencies.
+It can be seen that the overclocked RCA achieves best accuracy at higher frequencies.
 
-For a tighter area budget, only part of the complex structures can be implemented, while the simple structure still keep full precision.
-As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes dominate when the frequency is initially increased.
-This lead to the truncation of word-length of both 2-stage and 3-stage CSA.
-For an even stringent area constraint, the word-length of RCA is limited, meanwhile CSA with high stage numbers could not be implemented, as shown in Fig.xxx.
+For a tighter area budget, only part of the complex structures can be implemented, whilst the simple structure still keeps full precision.
+As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes the dominate factor when frequency is initially increased.
+This lead to a large truncation error for both 2-stage and 3-stage CSA.
+In this situation, overclocking RCA serves as the optimum choice with respect to accuracy.
+
+For an even stringent area constraint, the word-length of RCA is also limited.
+This results in truncation error initially for all design scenarios, as shown in Fig.xxx.
+Meanwhile, CSA with high stage numbers could not be implemented at all.
 In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.
 
-In general, the error expectations at the output of all four design method for a variety of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
+In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
 \begin{figure}[htbp]

### 2013-04-04 TCAD2013/overclocking_tcad.tex
add RCA and CCM

@@
         and~George~A.~Constantinides,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
-	\thanks{K. Shi, D. Boland and G. A. Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, SW7 2BT, U.K. (email: {}@imperial.ac.uk)}%
+	\thanks{K.
+Shi, D.
+Boland and G.
+A.
+Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, SW7 2BT, U.K.
+(email: \{k.shi11, david.boland03, g.constantinides\}@imperial.ac.uk)}%
 	%\thanks{M.
@@
 Subsubsection text here.
+\section{Ripple Carry Adder}\label{section_RCA}
+\subsection{Adder Structures in FPGAs}
+%something about fast carry logic in FPGA and pictures
+Adders serve as a key building block for arithmetic operations.
+Generally speaking, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
+As such, the philosophy of our approach is first exemplified with the analysis of a RCA.
+We later describe how this methodology can be extended to other arithmetic operators in Section~\ref{section_CCM} by discussing  the CCM that is commonly used in DSP applications and numerical algorithms.
+
+Typically the maximum frequency of a RCA is determined by the longest carry propagation.
+Consequently, modern FPGAs offer built-in architectures for very fast ripple carry addition.
+For instance, the Altera Cyclone series uses fast tables~\cite{AlteraCyclone} while the Xilinx Virtex series employs dedicated multiplexers and encoders for the fast carry logic~\cite{Virtex6}.
+Figure~\ref{FPGA adder} illustrates the structure of an $n$-bit RCA, which is composed of $n$ serial-connected full adders (FAs) and utilizes the internal fast carry logic of the Virtex-6 FPGA.
+
+While the fast carry logic reduces the time of each individual carry-propagation delay, the overall delay of carry-propagation will eventually overwhelm the delay of sum generation of each LUT with increasing operand word-lengths.
+For our initial analysis, we assume that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay, and hence the critical path delay of the RCA is $\mu_{RCA}=n\mu$, as shown in~Figure~\ref{FPGA adder}.
+For an $n$-bit RCA, it follows that if the sampling period $T_S$ is greater than $\mu_{RCA}$, correct results will be sampled.
+If, however, $T_S<\mu_{RCA}$, intermediate results will be sampled, potentially generating errors.
+%
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=3in]{./Figures/FastCarryLogic3.eps}
+%  \vspace{-2ex}
+  \caption{An $n$-bit ripple carry adder in Virtex-6 FPGA.}
+  \label{FPGA adder}
+  %\vspace{-3.5ex}
+\end{figure}
+
+In the following sections, we consider two methods that would allow the circuit to run at a frequency higher than $1/{T_S}$.
+The first is a traditional circuit design approach where operations occur without timing violations.
+To this end, the operand word-length is truncated in order to meet the timing requirement.
+This process results in truncation or roundoff error.
+In our proposed new scenario, circuits are implemented with greater word-length, but are clocked beyond the safe region so that timing violations sometimes occur.
+This process generates ``overclocking error''.
+
+ %We note that it may be possible to operate at a higher clock frequency than $1/T_{S}$ by using alternative adder structures, such as carry-select adder and carry lookahead adder.
+However, the effectiveness of these techniques is limited in FPGAs due to the build-in structures for the acceleration of carry propagation.
+In addition, such techniques will require substantial extra silicon area.
+
+\subsection{Probabilistic Model of Truncation Error}
+For ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
+For our initial analysis, we assume every bit of each input is uniformly and independently generated.
+However, this assumption will be relaxed in Section~\ref{Section_Experiments} where the predictions are verified using real image data.
+The errors at the output are evaluated in terms of the absolute value and the probability of their occurring.
+These two metrics are combined as the error expectation.
+
+If the input signal of a circuit is $k$ bits, truncation error occurs when the input signal is truncated from $k$ bits to $n$ bits.
+Under this premise, the mean value of the truncated bits at signal input ($E_{Tin}$) is given by (\ref{ET at single input}).
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{ET at single input}
+%\small
+%\footnotesize
+%\scriptsize
+  E_{Tin}=\frac{1}{2}\sum_{i=n+1}^{k}2^{-i}=2^{-n-1}-2^{-k-1}
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+Since we assume there are two mutually independent inputs to the RCA, the overall expectation of truncation error for the RCA is given by (\ref{TruncationError}).
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{TruncationError}
+%\small
+%\footnotesize
+  E_T=\left\{
+    \begin{matrix}
+        2^{-n}-2^{-k}, & \textrm{if $n<k$}\\
+        0, & \textrm{otherwise}
+    \end{matrix}
+  \right.
+\end{eqnarray}
+%\normalsize
+
+\subsection{Probabilistic Model of Overclocking Error}
+\subsubsection{Generation of Overclocking Error}\label{subsub:Generation of Overclocking Error}
+For a given $T_S$, the maximum length of error-free carry propagation is described by~(\ref{Max.length of carry chain}), where $f_S$ denotes the sampling frequency.
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{Max.length of carry chain}
+%\small
+%\footnotesize
+%\scriptsize
+    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
+\end{eqnarray}
+%\normalsize
+
+However, since the length of an actual carry chain during execution is dependent upon input patterns, in general, the worst case may occur rarely.
+To determine when this timing constraint is not met and the size of the error in this case, we expand standard results~\cite{DigitalICDesign} to the following statements, which examine carry generation, propagation and annihilation, as well as the corresponding summation results of a single bit $i$, according to the relationship between its input patterns $A_i$ and $B_i$:
+%
+ \begin{itemize}
+   \item If $\!A_i\!=\!B_i\!=1$, a new carry chain is generated at bit $i$, and $S_i\!=\!C_{i-1}$;
+   \item If $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i\!=\!0$;
+   \item If $\!A_i\!=\!B_i$, the current carry chain annihilates at bit $i$, and $S_i\!\!=\!\!1$.
+ \end{itemize}
+
+\subsubsection{Absolute Value of Overclocking Error}
+For an $n$-bit RCA, let $C_{tm}$ denote the carry chain generated at bit $S_t$ with the length of $m$ bits.
+For a certain $f_S$, the maximum length of error-free carry propagation, $b$, is determined through (\ref{Max.length of carry chain}).
+The presence of overclocking error requires $m>b$.
+Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{t_RCA}) and (\ref{m_RCA}):
+%
+%\vspace{-1ex}
+\begin{align}
+%\small
+%\footnotesize
+%\scriptsize
+  \label{t_RCA}  0&\leq t \leq n-b\\
+    b&<m\leq n+1-t      \label{m_RCA}
+%    \vspace{-1ex}
+\end{align}
+%\normalsize
+
+For $C_{tm}$, correct results will be generated from bit $S_t$ to bit $S_{t+b-1}$.
+Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Output Error}), where $\hat{S_i}$ and $S_i$ denote the actual and error-free output of bit $i$ respectively.
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{Output Error}
+%\small
+%\footnotesize
+    e_{tm}=\frac{\left|\sum_{i=t+b}^{n}(S_i-\hat{S_i})\cdot 2^i\right|}{2^n}
+%    \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+$S_i$ and $\hat{S_i}$ can be determined using the equations from the previous statements in Section~\ref{subsub:Generation of Overclocking Error}.
+In the error-free case, the carry will propagate from bit $S_t$ to bit $S_{t+m-1}$, and we will obtain $S_{t+b}=S_{t+b+1}=\cdots=S_{t+m-2}=0$ for carry propagation, and $S_{t+m-1}=1$ for carry annihilation.
+However, when a timing violation occurs, the carry will not propagate through all these bits.
+Substituting these values into (\ref{Output Error}) yields (\ref{etm}).
+Interestingly, the value of overclocking error has no dependence on the length of carry chain $m$.
+%
+%Instead, $\hat{S}_{t+b}=\hat{S}_{t+b+1}=\cdots=\hat{S}_{t+m-2}=1$ and $\hat{S}_{t+m-1}=0$.
+It is worth noting that these expressions are obtained based on the assumption that all the internal bits are initialized to zero.
+%
+\begin{eqnarray}\label{etm}
+%\small
+%\footnotesize
+  e_{tm}=\frac{\left|2^{t+m-1}-2^{t+m-2}-\dots-2^{t+b}\right|}{2^n}=2^{t+b-n}
+\end{eqnarray}
+%\normalsize
+
+\subsubsection{Probability of Overclocking Error}
+The carry chain $C_{tm}$ occurs when there is a carry generated at bit $t$, a carry annihilated at bit $t+m-1$ and the carry propagates in between.
+Consequently, its probability $P_{tm}$ is given by (\ref{Ptm_RCA}).
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{Ptm_RCA}
+%\small
+%\footnotesize
+  P_{tm}=P_{(A_t=B_t=1)}P_{(A_{t+m-1}=B_{t+m-1})}\cdot \prod_{i=t+1}^{t+m-2}P_{(A_i\neq B_i)}
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$, so $P_{tm}$ can be obtained by~(\ref{Ptm2}).
+Note that~(\ref{Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
+%\vspace{-1ex}
+%
+\begin{eqnarray}\label{Ptm2}
+%\small
+%\footnotesize
+    P_{tm}=\left\{\begin{array}{ll}
+      (1/2)^{m+1} & \textrm{if $t+m-1<n$}\\
+      (1/2)^{m} & \textrm{if $t+m-1=n$}
+    \end{array} \right.
+%    \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+\subsubsection{Expectation of Overclocking Error}
+Expectation of overclocking error can be expressed by (\ref{Eo_exp}).
+%
+%\vspace{-1ex}
+\begin{eqnarray}\label{Eo_exp}
+%\small
+%\footnotesize
+%\scriptsize
+    %E_O=\sum_{t=0}^{n-b}\sum_{m=b+1}^{n-t+1}P_{tm}\cdot e_{tm}
+    E_O=\sum_{t}\sum_{m}P_{tm}\cdot e_{tm}
+%    \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+%
+Using $P_{tm}$ and $e_{tm}$ from (\ref{etm}) and (\ref{Ptm2}) respectively, $E_O$ can be obtained by (\ref{Eo}).
+%\vspace{-1ex}
+\begin{eqnarray}\label{Eo}
+%\small
+%\footnotesize
+      E_O=\left\{
+        \begin{matrix}
+            2^{-b}-2^{-n-1}, & \textrm{if $b\leq n$}\\
+            0, & \textrm{otherwise}
+        \end{matrix}
+      \right.
+%      \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+\subsection{Comparison between Two Scenarios}
+In the traditional scenario, the word-length of RCA must be truncated, using $n=b-1$ bits, in order to meet a given $f_S$. The error expectation is then given by (\ref{Eo_trad_RCA}).
+%
+\begin{eqnarray}\label{Eo_trad_RCA}
+%\small
+%\vspace{-1ex}
+%\footnotesize
+%\scriptsize
+  E_{trad}=2^{-b+1}-2^{-k}
+  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+Overclocking errors are allowed to happen in the second scenario, therefore the word-length of RCA is set to be equal to the input word-length, that is, $n=k$.
+Hence we obtain (\ref{Eo_new_RCA}) according to (\ref{Eo}).
+%
+\begin{eqnarray}\label{Eo_new_RCA}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+%\scriptsize
+  E_{new}=2^{-b}-2^{-k-1}
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+%
+Comparing (\ref{Eo_new_RCA}) and (\ref{Eo_trad_RCA}), we have (\ref{Comparison RCA}).
+This equation indicates that by allowing timing violations, the overall error expectation of RCA outputs drops by a factor of 2 in comparison to traditional scenario.
+This provides the first hint that our approach is useful in practice.
+%
+\begin{eqnarray}\label{Comparison RCA}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+%\scriptsize
+  \frac{E_{new}}{E_{trad}}=\frac{2^{-b}-2^{-k-1}}{2^{-b+1}-2^{-k}}=\frac{1}{2}
+\end{eqnarray}
+
+\section{Constant Coefficient Multiplier}\label{section_CCM}
+
+As another key primitive of arithmetic operations, CCM can be implemented using RCA and shifters.
+For example, operation $B=9A$ is equivalent to $B=A+8A=A+(A<<3)$, which can be built using one RCA and one shifter.
+We first focus on a single RCA and single shifter structure.
+We describe how more complex structures consisting of multiple RCAs and multiple shifters can be built in accordance with this baseline structure in Section~\ref{CCM_Multi}.
+
+In this CCM structure, let the two inputs of the RCA be denoted by $A_S$ and $A_O$ respectively, which are both two's complement numbers.
+$A_S$ denotes the ``shifted signal", with zeros padded after LSB, while $A_O$ denotes the ``original signal" with MSB sign extension.
+For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Figure~\ref{CCM_fig}.
+\begin{figure}[htbp]
+  \centering
+%  \vspace{-2ex}
+  %\includegraphics[width=3.5in]{./Figures/CCM_DataFlow3.pdf}
+  \includegraphics[width=3.3in]{./Figures/CCM_DataFlow3.eps}
+%  \vspace{-2ex}
+  \caption{Different types of carry chain in constant coefficient multiplier. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
+  \label{CCM_fig}
+%  \vspace{-1.5ex}
+\end{figure}
+
+\subsection{Probabilistic Model of Truncation Error}
+Let $E_{Tin}$ and $E_{Tout}$ denote the expectation of truncation error at the input and output of CCM respectively.
+We then have (\ref{Et_CCM}), where $coe$ denotes the coefficient value of the CCM, and $E_{Tin}$ can be obtained according to~(\ref{TruncationError}).
+%
+\begin{eqnarray}\label{Et_CCM}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+%\scriptsize
+  E_{Tout}=|coe|\cdot E_{Tin}
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+\subsection{Probabilistic Model of Overclocking Error}
+\subsubsection{Absolute Value of Overclocking Error}
+The absolute value of overclocking error of carry chain $C_{tm}$ is increased by a factor of $2^s$ due to shifting, compared to RCA.
+Hence $e_{tm}$ in CCM can be modified from (\ref{etm}) to give (\ref{etm_CCM}).
+%
+\begin{eqnarray}\label{etm_CCM}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+  e_{tm}=2^{t+b-n+s}
+%  \vspace{-1.5ex}
+\end{eqnarray}
+%\normalsize
+
+\subsubsection{Probability of Overclocking Error}
+Due to the dependencies in a CCM, carry generation requires $a_t=a_{t-s}=1$, propagation and annihilation of a carry chain is best considered separately for four types of carry chain generated at bit~$t$.
+We label these by $C_{tm}1$ to $C_{tm}4$ in Figure~\ref{CCM_fig}, defined by the end region of the carry chain.
+For $C_{tm}1$, we have:
+\begin{itemize}
+  \item Carry propagation: $\!a_i\neq\!a_{i+s}\!$ where $\!i\!\in[t+1,n-s-2]\!$;
+  \item Carry annihilation: $\!a_j\!=\!a_{j+s}\!$ where $\!j\!\in[t+1,n-s-1]\!$.
+\end{itemize}
+Similarly for $C_{tm}2$, we have:
+\begin{itemize}
+  \item Carry propagation: $a_i\neq a_{n-1}$ where $i\in[n-s-1,n-3]$; or $a_i\neq a_{i+s}$ where $i\in[t+1,n-s-2]$;
+  \item Carry annihilation: $\!a_j\!=a_{n-1}\!$ where $j\!\in\![n-s-1,n-2]$.
+\end{itemize}
+
+For the first two types of carry chain $C_{tm}1$ and $C_{tm}2$, the probability of carry propagation and annihilation is $1/2$ and the probability of carry generation is $1/4$, under the premise that all bits of input signal are mutually independent.
+Therefore (\ref{Ptm_CCM1}) can be obtained by substituting this into~(\ref{Ptm_RCA}).
+%
+\begin{eqnarray}\label{Ptm_CCM1}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+  P_{tm}=\left(1/2\right)^{m+1}, & \textrm{if $t+m-1\leqslant n-2$}
+\end{eqnarray}
+%\normalsize
+
+For carry annihilation of $C_{tm}3$, $a_{n-1}=a_{n-1}$, which is always true. Thus the probability of $C_{tm}3$ is given by (\ref{Ptm_CCM2}).
+%
+\begin{eqnarray}\label{Ptm_CCM2}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+  P_{tm}=\left(1/2\right)^m, & \textrm{if $t+m-1=n-1$}
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+$C_{tm}4$ represents carry chain annihilates over $a_{n-1}$, therefore carry propagation requires $a_{n-1}\neq a_{n-1}$. This means $C_{tm}4$ never occurs in a CCM.
+
+Altogether, $P_{tm}$ for a CCM is given by (\ref{Ptm_CCM}).
+\begin{eqnarray}\label{Ptm_CCM}
+%\small
+  P_{tm}=\left\{\begin{array}{ll}
+      (1/2)^{m+1} & \textrm{if $t+m-1<n-1$}\\
+      (1/2)^{m} & \textrm{if $t+m-1=n-1$}
+    \end{array} \right.
+    %\vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+\subsubsection{Expectation of Overclocking Error}
+Since the carry chain of a CCM will not propagate over $a_{n-1}$, the upper bound of parameter $t$ and $m$ should be modified from (\ref{t_RCA}) and (\ref{m_RCA}) to give (\ref{t_CCM}) and (\ref{m_CCM}).
+%
+\begin{eqnarray}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+%\scriptsize
+  \label{t_CCM} 0\leqslant t\leqslant n-b-1\\
+  \label{m_CCM} b<m\leqslant n-t
+%  \vspace{-1ex}
+\end{eqnarray}
+%\normalsize
+
+Finally, by substituting (\ref{Ptm_CCM}) and (\ref{etm_CCM}) with modified bounds of $t$ and $m$ into (\ref{Eo_exp}), we obtain the expectation of overclocking error for a CCM to be given by (\ref{Eo_CCM}).
+%
+\begin{eqnarray}\label{Eo_CCM}
+%\vspace{-1ex}
+%\small
+%\footnotesize
+      E_O=\left\{
+        \begin{matrix}
+            2^{s-b-1}-2^{s-n-1}, & \textrm{if $b\leq n-1$}\\
+            0, & \textrm{otherwise}
+        \end{matrix}
+      \right.
+%      \vspace{1ex}
+\end{eqnarray}
+%\normalsize
+
+\subsection{CCM with Multiple RCAs and Shifters}\label{CCM_Multi}
+In the case where a CCM is composed of two shifters and one RCA, such as operation $\!B\!=\!20A\!=\!(\!A<<2)+(\!A<<4)$, let the shifted bits be denoted as $s_1$ and $s_2$ respectively.
+Hence the equivalent $s$ in (\ref{Eo_CCM}) can be obtained through~(\ref{ShiftNo}).
+%
+%\vspace{-3ex}
+\begin{eqnarray}\label{ShiftNo}
+%\footnotesize
+%\scriptsize
+  s=\left|s_1-s_2\right|
+%  \vspace{-1ex}
+\end{eqnarray}
+
+For those operations such as $B=37A=(A<<5)+(A<<2)+(A<<1)$, the CCM can be built using a tree structure.
+Each root node is the baseline CCM and the errors are propagated through an adder tree, of which the error can be determined based on our previous RCA model.
 
@@
 
-In a CSA with $c$ stages, let the stage delay be denoted by $d_{0}\dots d_{c-1}$, where $d_{0}$ and $d_{c-1}$ represent the delay of the most significant stage and the least significant stage, respectively.
+In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{0}\dots d_{s-1}$, where $d_{0}$ and $d_{s-1}$ represent the delay of the most significant stage and the least significant stage, respectively.
 Unlike other stages, the least significant stage is built by one RCA only, since it is directly driven by the carry input.
@@
 Therefore the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
+%Note that the delay of the ${(s-1)}^{th}$ and ${(s-2)}^{th}$ stages are identical, because the least significant stage of CSA is built by RCA.
 \begin{eqnarray}\label{CSA_SingleStageDelay}
-  d_i=n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux} 
- % d_0=n_0\cdot \mu_{carry}+\mu_{mux}
+  d_i=\left\{
+    \begin{matrix}
+      n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux}, &\textrm{if $i\in\left[0,s-2\right]$}\\
+      d_{i-1}, & \textrm{if $i=s-1$}
+    \end{matrix}
+  \right.
 \end{eqnarray}
@@
 \begin{eqnarray}\label{CSA_DelayEqual}
-  d_0=d_1=\cdots=d_{n-1}
+  d_0=d_1=\cdots=d_{s-1}
 \end{eqnarray}
@@
 Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), which denotes the CSA word-length of stage $i$.
-Note that the word-length of stage $c-1$ and $c-2$ are identical, since the least significant stage is composed of RCA.
+%Note that the word-length of stage $s-1$ and $s-2$ are identical, since the least significant stage is composed of RCA.
 \begin{eqnarray}\label{CSA_DelayRep}
- % n_i=n_0-xxx\cdot\frac{\mu_{mux}}{\mu_{c}}
  n_i=\left\{
 	\begin{matrix}
-	  n_0-i\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in(2,c-2]$ and $c>2$}\\
-	  n_0-(c-2)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i=c-1$ and $c\geqslant2$}
+	  n_0-i\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[0,s-2\right]$}\\
+	  n_{i-1}, &\textrm{if $i=s-1$}
+      %n_0-(c-2)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i=c-1$ and $c\geqslant2$}
 	\end{matrix}
@@
 \begin{eqnarray}\label{CSA_WL}
-  n_{CSA}=\sum_{i=0}^{n-1}n_{i}=cn_{0}-\frac{\mu_{mux}}{\mu_{carry}}\cdot\frac{(c+1)(c-2)}{2}
+  n_{CSA}=\sum_{i=0}^{s-1}n_{i}=s\cdot n_{0}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
 \end{eqnarray}
@@
 \begin{eqnarray}\label{CSA_Timing}
-  n_{CSA}=c\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(c+2)(c-1)}{2}
+  n_{CSA}=s\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
 \end{eqnarray}
 
-It can be seen that $c=1$ leads to $n_{CSA}=n_{RCA}$.
+It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
 This is because RCA forms the least significant stage of CSA.
-In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure $n_{c-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
+In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
 \begin{eqnarray}\label{CSA_StageNumber}
-  c<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
+  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
 \end{eqnarray}
@@
 Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ through the timing analysis tool.
-According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials, as presented in Fig.~(\ref{DelayFitting}).
-Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
-%keeping $i=0$ in (\ref{CSA_SingleStageDelay}) while varying the value of $n_0$.
-The corresponding delay value $d_0$ is recorded through the timing analysis tool.
-Hence $\mu_{mux}/\mu_c$ can be obtained by fitting those values, as presented in Fig.~(\ref{DelayFitting}).
-Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
-  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the given input word-length and the corresponding delay value obtained through the Xilinx Timing Analyzer.}
-  \label{DelayFitting}
-\end{figure}
+According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials.
+%, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
+%
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
+%  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the given input word-length and the corresponding delay value obtained through the Xilinx Timing Analyzer.}
+%  \label{DelayFitting}
+%\end{figure}
 
 Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
-Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of RCA and 2-stage CSA, respectively, across a range of operating frequencies.
-The maximum input word-length in our experiments is 16-bit, hence the modelled value is set to 16 if it expires.
+Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
+In this experiment, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
+It can be seen that the the modelled value match well with the experimental results.
+%The maximum input word-length in our experiments is 16-bit, hence the modelled value is set to 16 if it expires.
 \begin{figure}[htbp]
@@
 
-% Figure goes here!
-It can be seen that our timing models match well the experimental results for both RCA and CSA, except that the modelled outcomes are slight conservative, especially at higher operating frequencies.
+%It can be seen that our timing models match well the experimental results for both RCA and CSA, except that the modelled outcomes are slight conservative, especially at higher operating frequencies.
 This is because the model coefficients are obtained based on timing analysis, which is designed with safety margins to ensure correct functionality for diverse operating conditions.
 In addition, routing delay might be introduced during timing analysis such that the overall delay is enlarged, while our models consider logic delay only.
-
-% provide slight conservative outcomes than the experimental data, especially at higher operating frequencies. 
-.
 
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-%Although advanced architectures such as CSA inheritly offer better performance than the basic structure, this would generate a large area overhead. In the following experiments, 
+%Although advanced architectures such as CSA inherently offer better performance than the basic structure, this would generate a large area overhead. In the following experiments,
 To answer this question, we explore the trade-offs between accuracy, performance as well as area in this section.
@@
 The optimal design metric with the minimum error expectation is labelled for each area constraint.
+For a given frequency and area constraint, the optimum design is chosen based on the following metrics:
+\begin{itemize}
+  \item Design with the minimum error expectation is the optimum design;
+  \item If multiple designs achieve the same error expectation, then the design with minimum area is the optimum design;
+  \item If the error expectation and area are identical for multiple designs, they are all treated as the optimum design.
+\end{itemize}
 %
-% the number of available LUTs is set to 45, 35, 25 and 15 respectively, while timing requirements are met by reducing the input word-length of each architecture.
-In addition, we also investigate the scenario where RCA is implemented with the maximum possible word-length under the given area constraint, while meeting timing by overclocking.
-The corresponding error expectations of these scenarios are depicted in Fig.xxx.
-The optimal design method which achieves the minimum error expectation is labelled.
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
-	\caption{LUT=45}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
-	\caption{LUT=35}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
-	\caption{LUT=25}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
-	\caption{LUT=15}
-\end{figure}
-
-%\begin{figure*}[htbp]
+%\begin{figure}[htbp]
 %	\centering
-%  \subfigure[LUTs=45]{
-%  \begin{minipage}[c]{0.45\textwidth}
+%	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
+%	\caption{LUT=45}
+%\end{figure}
+%
+%\begin{figure}[htbp]
 %	\centering
-%    \includegraphics[width=2in]{./Figures/Error_LUT45.eps}
-%  \end{minipage}%
-%  }%
-%  \subfigure[LUT=35]{
-%  \begin{minipage}[c]{0.45\textwidth}
+%	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
+%	\caption{LUT=35}
+%\end{figure}
+%
+%\begin{figure}[htbp]
 %	\centering
-%    \includegraphics[width=2in]{./Figures/Error_LUT35.eps}
-%  \end{minipage}
-%  }
-%  \subfigure[LUT=25]{
-%  \begin{minipage}[c]{0.45\textwidth}
+%	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
+%	\caption{LUT=25}
+%\end{figure}
+%
+%\begin{figure}[htbp]
 %	\centering
-%    \includegraphics[width=2in]{./Figures/Error_LUT25.eps}
-%  \end{minipage}
-%  }%
-%  \subfigure[LUT=15]{
-%  \begin{minipage}[c]{0.45\textwidth}
-%    \centering
-%    \includegraphics[width=2in]{./Figures/Error_LUT15.eps}
-%  \end{minipage}
-%  }
-%  \caption{Accuracy-performance trade-offs under fixed area constraints.}
-%  \label{Fig Tradeoffs}
-%\end{figure*}
+%	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
+%	\caption{LUT=15}
+%\end{figure}
 
@@
 
-In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}.
+In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
 \begin{figure}[htbp]
   \centering
-  \includegraphics[width=3.3in]{./Figures/Tradeoff.eps}
+  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
   \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
@@
 
-\begin{IEEEbiography}{Michael Shell}
+\begin{IEEEbiography}{Author}
 Biography text here.
@@
 % if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
+\begin{IEEEbiographynophoto}{Author}
 Biography text here.
@@
 
-\begin{IEEEbiographynophoto}{Jane Doe}
+\begin{IEEEbiographynophoto}{Author}
 Biography text here.
@@
 
-% that's all folks
 \end{document}

### 2013-04-04 TCAD2013/overclocking_tcad.tex
Shrink the size of CSA section

@@
 
+%\begin{figure*}[t]
+%  \centering
+%  \includegraphics[width=\textwidth]{./Figures/CSAstructure.pdf}
+%  \caption{Structure of an $s$-stage CSA.}
+%\end{figure*}
+
 %In addition to RCA, there are several
 
-\subsection{Timing Models for $n$-bit Carry Select Adder}
+\subsection{Timing Models for Carry Select Adder}
 We initially describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
@@
 In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
+%  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
+%  \label{CSA3stage Timing}
+%\end{figure}
+
 \begin{figure}[htbp]
+    \begin{minipage}[b]{.48\textwidth}
         \centering
+        \subfigure[Maximum word-length.]{
             \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
-  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
             \label{CSA3stage Timing}
+        }
+        \subfigure[Hardware resource usage.]{
+            \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
+            \label{CSA3stage Area}
+        }
+    \end{minipage}
+    \centering
+    \caption{Comparison between RCA and CSA across a variety of frequency values in terms of the maximum word-length of input signal and the area consumption.}
 \end{figure}
-%CSA achieves greater word-length than RCA when frequency is initially increased
 
@@
 This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
-  \caption{Area overhead for RCA and CSA.}
-  \label{CSA3stage Area}
-\end{figure}
-%the 3-stage CSA costs
+%\begin{figure}[htbp]
+%  \centering
+%  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
+%  \caption{Area overhead for RCA and CSA.}
+%  \label{CSA3stage Area}
+%\end{figure}
 
@@
 The precision lose might generates large errors even at low frequencies.
-This is demonstrated by experiments where an area constraint is applied besides the timing requirement.
-Both of the constraints are met by reducing the word-length of the input signal.
-The errors at the outputs are recorded with the reference to the original word-length.
-In addition, another designing method is adopted where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
-For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
+This is demonstrated by experiments where area constraints are applied besides the timing requirement.
+Conventionally, both of the constraints are met by reducing the word-length of the input signal.
+The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
+In addition, we propose another designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
+For a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
+%For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
 The optimal design metric with the minimum error expectation is labelled for each area constraint.
@@
 \end{itemize}
-%
+
+The optimum design method for a variety of frequency and area constraints is demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
+If the available area is large enough, CSA serves as the optimum design option because it inherently operates faster than RCA, and it can be implemented with full precision in this situation.
+The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
+For a tighter area budget, only part of the CSA can be implemented, whilst RCA still keeps full precision.
+In this case, area instead of timing becomes the dominate factor for small frequency values.
+This leads to precision loss for CSA initially.
+Therefore we see RCA with overclocking is the best design across almost the whole frequency domain.
+For an even stringent area constraint, the word-length of RCA is also limited.
+This results in truncation error initially for all design scenarios.
+Meanwhile, CSA with high stage numbers could not even be implemented at all.
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
+  \caption{Demonstration of the optimum design methodology for a variety frequency and area constraints.}
+  \label{Tradeoff}
+\end{figure}
+
+%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
+
 %\begin{figure}[htbp]
@@
 %\end{figure}
-
-If the available area is large enough, as shown in Fig.xxx, CSA with higher stage numbers can be implemented with full precision and it is the optimal design choice unless very high frequencies are applied.
+%
+%If the available area is large enough, as shown in Fig.xxx, CSA with higher stage numbers can be implemented with full precision and it is the optimal design choice unless very high frequencies are applied.
 This is because at lower frequencies, the long carry chain is divided into multiple overlapped sections, and the higher stage number the shorter the carry chain length of each stage.
@@
 
-For a tighter area budget, only part of the complex structures can be implemented, whilst the simple structure still keeps full precision.
+%For a tighter area budget, only part of the complex structures can be implemented, whilst the simple structure still keeps full precision.
 As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes the dominate factor when frequency is initially increased.
@@
 
-For an even stringent area constraint, the word-length of RCA is also limited.
-This results in truncation error initially for all design scenarios, as shown in Fig.xxx.
-Meanwhile, CSA with high stage numbers could not be implemented at all.
-In this situation the overclocked RCA achieves best accuracy across the whole frequency domain.
-
-In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
-  \caption{Trade-offs between accuracy, performance and area for 4 design methodologies.}
-  \label{Tradeoff}
-\end{figure}
+%In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
 

### 2013-04-05 TCAD2013/overclocking_tcad.tex
CSA overall check v2

@@
 We initially describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
-This information can be employed to determine the truncation error based on the models presented in Section.xxx.
+This information can then be employed to determine the truncation error based on the models presented in Section.xxx.
 
@@
 Unlike other stages, the least significant stage is built by one RCA only, since it is directly driven by the carry input.
-In our analysis, we follow the previous assumption that delay is due to carry propagation as well as, in this case, multiplexing the carry output.
-Therefore the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
+In our analysis, we follow the previous assumption that the critical path delay is due to carry propagation as well as, in this case, multiplexing the carry output.
+Therefore, the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
 %Note that the delay of the ${(s-1)}^{th}$ and ${(s-2)}^{th}$ stages are identical, because the least significant stage of CSA is built by RCA.
@@
       n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux}, &\textrm{if $i\in\left[0,s-2\right]$}\\
-      d_{i-1}, & \textrm{if $i=s-1$}
+      d_{s-2}, & \textrm{if $i=s-1$}
     \end{matrix}
@@
 
-Under the timing-driven design environment, the delay of each stage of CSA is set to be approximately uniform for the fastest operation. In this case we obtain~(\ref{CSA_DelayEqual}).
+Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation. That is,~(\ref{CSA_DelayEqual}) can be obtained.
 \begin{eqnarray}\label{CSA_DelayEqual}
@@
 
-Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), which denotes the CSA word-length of stage $i$.
+This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
+Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), where $n_i$ denotes the CSA word-length of stage $i$.
 %Note that the word-length of stage $s-1$ and $s-2$ are identical, since the least significant stage is composed of RCA.
@@
 	  n_0-i\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[0,s-2\right]$}\\
-	  n_{i-1}, &\textrm{if $i=s-1$}
+	  n_{s-2}, &\textrm{if $i=s-1$}
       %n_0-(c-2)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i=c-1$ and $c\geqslant2$}
@@
 \begin{eqnarray}\label{CSA_WL}
-  n_{CSA}=\sum_{i=0}^{s-1}n_{i}=s\cdot n_{0}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
+  \begin{split}
+    n_{CSA} &=\sum_{i=0}^{s-1}n_{i} \\
+    &= s\cdot n_{0}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
+  \end{split}
 \end{eqnarray}
 
-In the conventional situation, the word-length of both RCA and CSA should be properly selected in order to meet timing.
+Conventionally for a given frequency constraint, the word-length of both RCA and CSA should be properly selected to avoid timing violation, as presented in~(\ref{CSA_RCA}), where $n_{RCA}$ is determined by current timing information through (xxx).
+%In the conventional situation, the word-length of both RCA and CSA should be properly selected in order to meet timing.
 In this case,~(\ref{CSA_RCA}) can be obtained, where $n_{RCA}$ is determined by current timing information through (xxx).
 \begin{eqnarray}\label{CSA_RCA}
-  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
+%  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
+  \mu_{c}\cdot n_{RCA}=d_i
 \end{eqnarray}
 
-Based on~(\ref{CSA_WL}) and~(\ref{CSA_RCA}), we may obtain the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
+Combining~(\ref{CSA_WL}) and~(\ref{CSA_RCA}), we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
 % we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
@@
 As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
-This ratio can be obtained through timing analysis.
-Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ through the timing analysis tool.
+This ratio can be obtained through timing analysis instead of experiments.
+Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ from the timing analysis tool.
 According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials.
-%, as presented in Fig.~(\ref{DelayFitting}). Out experimental results show that $\mu_{mux}/\mu_c\approx8$.
-%
-%\begin{figure}[htbp]
-%  \centering
-%  \includegraphics[width=3.3in]{./Figures/Fitting.eps}
-%  \caption{Fitted curve of (\ref{CSA_SingleStageDelay}) for the most significant stage ($i=0$), based on the given input word-length and the corresponding delay value obtained through the Xilinx Timing Analyzer.}
-%  \label{DelayFitting}
-%\end{figure}
 
 Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
-Fig.~\ref{CSA Model Verification} demonstrates both the modelled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
-In this experiment, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
-It can be seen that the the modelled value match well with the experimental results.
-%The maximum input word-length in our experiments is 16-bit, hence the modelled value is set to 16 if it expires.
+Fig.~\ref{CSA Model Verification} illustrates both the modeled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
+In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
+It can be seen that the the modeled value match well with the experimental results.
 \begin{figure}[htbp]
@@
   \includegraphics[width=3in]{./Figures/Model.eps}
-  \caption{Comparison of the maximum word-length for a given operating frequency between the modelled value and the experimental results from FPGA simulations.}
+  \caption{Comparison of the maximum word-length for given operating frequencies between the modeled value and the experimental results from FPGA simulations.}
   \label{CSA Model Verification}
@@
 \subsection{Area Overhead}
-Fig.~\ref{CSA3stage Timing} demonstrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies.
+We then compare different adder structures in terms of the maximum word-length for a given operating frequency and the corresponding area consumption.
+Fig.~\ref{CSA3stage Timing} illustrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies.
 We only investigate 3 stages as the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
-It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
+However, similar analysis can be performed on CSA with any stage numbers and the overall conclusion will still hold.
+It can be seen from Fig.~\ref{CSA3stage Timing} that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
 This corresponds to smaller truncation errors.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
     \begin{minipage}[b]{.48\textwidth}
@@
 However, the accuracy benefits brought by CSA comes with the cost of large area overhead.
-Fig.~\ref{CSA3stage Area} depicts the resource usage (in terms of the number of Look-Up Tables (LUTs) in the FPGA) used for all three structures.
-It can be seen that for a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
+It can be seen that for all frequency values, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
 This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-%Although advanced architectures such as CSA inherently offer better performance than the basic structure, this would generate a large area overhead. In the following experiments,
-To answer this question, we explore the trade-offs between accuracy, performance as well as area in this section.
+To answer this question, the silicon area is incorporated into the trade-offs between accuracy and performance.
 If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
-The precision lose might generates large errors even at low frequencies.
+The precision loss might results in large errors even at low frequencies.
 This is demonstrated by experiments where area constraints are applied besides the timing requirement.
-Conventionally, both of the constraints are met by reducing the word-length of the input signal.
+In the conventional design scenario, both of the constraints are met by reducing the word-length of the input signal.
 The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
@@
 The optimum design method for a variety of frequency and area constraints is demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
-If the available area is large enough, CSA serves as the optimum design option because it inherently operates faster than RCA, and it can be implemented with full precision in this situation.
+If the available area is large enough, CSA serves as the optimum design option because it inherently operates faster than RCA, and it can be implemented with full precision with unlimited hardware resources.
 The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
 For a tighter area budget, only part of the CSA can be implemented, whilst RCA still keeps full precision.
-In this case, area instead of timing becomes the dominate factor for small frequency values.
+In this case, area instead of timing becomes the dominate factor.
 This leads to precision loss for CSA initially.
-Therefore we see RCA with overclocking is the best design across almost the whole frequency domain.
+Therefore we see RCA with overclocking is the optimum design method across almost the whole frequency domain.
 For an even stringent area constraint, the word-length of RCA is also limited.
 This results in truncation error initially for all design scenarios.
-Meanwhile, CSA with high stage numbers could not even be implemented at all.
+Meanwhile, CSA with high stage numbers might not even be implemented at all.
 \begin{figure}[htbp]

### 2013-04-07 TCAD2013/overclocking_tcad.tex
Modified CSA v3

@@
 %\scriptsize
-  E_{Tin}=\frac{1}{2}\sum_{i=n+1}^{k}2^{-i}=2^{-n-1}-2^{-k-1}
+  \begin{split}
+    E_{Tin} &= \frac{1}{2}\sum_{i=n+1}^{k}2^{-i}\\
+    &= 2^{-n-1}-2^{-k-1}
 %  \vspace{-1ex}
+  \end{split}
 \end{eqnarray}
@@
 %\scriptsize
-    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
+    b := \left\lceil \frac{T_S}{\mu} \right\rceil= \left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
 \end{eqnarray}
@@
 %\footnotesize
-  e_{tm}=\frac{\left|2^{t+m-1}-2^{t+m-2}-\dots-2^{t+b}\right|}{2^n}=2^{t+b-n}
+  \begin{split}
+    e_{tm} &= \frac{\left|2^{t+m-1}-2^{t+m-2}-\dots-2^{t+b}\right|}{2^n}\\
+    &= 2^{t+b-n}
+  \end{split}
 \end{eqnarray}
@@
 \subsection{Area Overhead}
-We then compare different adder structures in terms of the maximum word-length for a given operating frequency and the corresponding area consumption.
+We then compare different adder structures in terms of the maximum word-length with respect to different operating frequencies and the corresponding area consumption.
 Fig.~\ref{CSA3stage Timing} illustrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies.
@@
 Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
-It can be seen that for all frequency values, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
+It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
 This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-To answer this question, the silicon area is incorporated into the trade-offs between accuracy and performance.
+To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
 If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
@@
 The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
-In addition, we propose another designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
-For a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
+In addition, we propose another circuit designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
+
+Our results could be of interest to a circuit designer in two aspects.
+On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated.
+We select the optimum design methodology for both situations.
+
+In the first case, for a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
 %For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
@@
 \begin{itemize}
-  \item Design with the minimum error expectation is the optimum design;
-  \item If multiple designs achieve the same error expectation, then the design with minimum area is the optimum design;
-  \item If the error expectation and area are identical for multiple designs, they are all treated as the optimum design.
+  \item Design with the best accuracy at outputs is the optimum design;
+  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
+  \item If the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
 \end{itemize}
 
-The optimum design method for a variety of frequency and area constraints is demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
+The accuracy here is assessed in terms of the mean error at outputs.
+The optimum design method with respect to a variety of operating frequencies and area consumptions is demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
 If the available area is large enough, CSA serves as the optimum design option because it inherently operates faster than RCA, and it can be implemented with full precision with unlimited hardware resources.
@@
 In this case, area instead of timing becomes the dominate factor.
-This leads to precision loss for CSA initially.
+This leads to precision loss for CSA from the start.
 Therefore we see RCA with overclocking is the optimum design method across almost the whole frequency domain.
@@
   \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
-  \caption{Demonstration of the optimum design methodology for a variety frequency and area constraints.}
+  \caption{Demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
   \label{Tradeoff}
@@
 
+Similarly in the second case where a pair of $\{Area, Accuracy\}$ constraint is applied, a certain amount of error can be tolerated when designing circuits.
+The error specifications are evaluated in terms of mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+\begin{eqnarray}\label{MRE}
+  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
+\end{eqnarray}
+
+In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
+For a certain MRE, design with the maximum operating frequencies is labeled as the optimum design.
+Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area.
+Based on these criteria, the decision graph is depicted in Fig.~(\ref{Tradeoff_Error}).
 %We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
+\begin{figure}[htbp]
+    \centering
+    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
+    \caption{Demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
+    \label{Tradeoff_Error}
+\end{figure}
+
+For a tight accuracy requirement, i.e.
+$MRE<0.005\%$, CSA serves as the optimum design choice with respect to large accessible area, as it intrinsically operates faster than RCA.
+When the area budget shrinks, RCA exceeds because the precision is CSA is limited.
+Similarly the precision of RCA is reduced when critical area requirement is applied.
+
+However, if the tolerable error increases, i.e. $MRE>1\%$, the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
 

### 2013-04-09 TCAD2013/overclocking_tcad.tex
Modified CSA, revised by David, v1

@@
 \subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, there are several alternative adder architectures proposed to shorten the carry chain.
-For instance, the carry select adder (CSA) is designed to overlap carry propagation in sections such that the operating speed can be boosted.
-In a CSA, the carry chain is divided into multiple stages.
+Since the delay of RCA is determined by the length of carry chain, the carry select adder (CSA) is designed to shorten the carry chain by overlapping carry propagation in sections such that the operating speed can be boosted.
+In a CSA, the carry chain is divided into multiple stages, as seen in Fig.~xxx.
 Each stage contains two RCAs and two multiplexers.
-For a given input, computations are performed twice simultaneously, with the carry input as zero and one respectively.
-The results are then selected according to the actual carry input.
-Although this structure brings timing benefits, it costs extra hardware resources than RCA as the carry chain is duplicated and multiplexers are expensive especially in the FPGA technology.
-In this section, silicon area is incorporated as the third metric besides accuracy and performance.
+For a given input, two computations are performed simultaneously where the carry input is zero and one respectively.
+One of these two results is then selected according to the actual carry input.
+Although this structure brings timing benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
+Furthermore, in FPGA technology, multiplexers are expensive.
+Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of these two adder structures in this section.
+
+%, silicon area is incorporated as the third metric besides accuracy and performance.
 We explore the trade-offs between these three factors for both adder structures.
@@
 \subsection{Timing Models for Carry Select Adder}
-We initially describe the modelling method for the CSA timing, with the aim of forming the relationship between the operating frequency and the corresponding maximum word-length of CSA.
+We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
 This information can then be employed to determine the truncation error based on the models presented in Section.xxx.
 
-In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{0}\dots d_{s-1}$, where $d_{0}$ and $d_{s-1}$ represent the delay of the most significant stage and the least significant stage, respectively.
-Unlike other stages, the least significant stage is built by one RCA only, since it is directly driven by the carry input.
-In our analysis, we follow the previous assumption that the critical path delay is due to carry propagation as well as, in this case, multiplexing the carry output.
-Therefore, the delay of the $i^{th}$ stage can be obtained through~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$ denotes the delay of $1$-bit carry propagation and $\mu_{mux}$ denotes the delay of multiplexing.
-%Note that the delay of the ${(s-1)}^{th}$ and ${(s-2)}^{th}$ stages are identical, because the least significant stage of CSA is built by RCA.
+In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
+In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output.
+Note that unlike other stages, the least significant stage is only built by one RCA without multiplexers, since it is directly driven by the carry input.
+Hence we obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
 \begin{eqnarray}\label{CSA_SingleStageDelay}
@@
     \begin{matrix}
-      n_i\cdot \mu_{c}+(i+1)\cdot\mu_{mux}, &\textrm{if $i\in\left[0,s-2\right]$}\\
-      d_{s-2}, & \textrm{if $i=s-1$}
+      n_i\cdot \mu_{c}+(s-i)\cdot\mu_{mux}, &\textrm{if $i\in\left[1,s-1\right]$}\\
+      n_0\cdot \mu_c + (s-1)\cdot\mu_{mux}, & \textrm{if $i=0$}
     \end{matrix}
@@
 
-Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation. That is,~(\ref{CSA_DelayEqual}) can be obtained.
+Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{CSA_DelayEqual}).
 \begin{eqnarray}\label{CSA_DelayEqual}
-  d_0=d_1=\cdots=d_{s-1}
+  d_{s-1}=d_{s-2}=\cdots=d_{0}
 \end{eqnarray}
 
-This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
+In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
+%This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
 Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), where $n_i$ denotes the CSA word-length of stage $i$.
-%Note that the word-length of stage $s-1$ and $s-2$ are identical, since the least significant stage is composed of RCA.
 \begin{eqnarray}\label{CSA_DelayRep}
@@
 	\begin{matrix}
-	  n_0-i\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[0,s-2\right]$}\\
-	  n_{s-2}, &\textrm{if $i=s-1$}
-      %n_0-(c-2)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i=c-1$ and $c\geqslant2$}
+	  n_{s-1}-(s-1-i)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[1,s-1\right]$}\\
+	  n_{s-1}-(s-2)\cdot\frac{\mu_{mux}}{\mu_c}, &\textrm{if $i=0$}
 	\end{matrix}
@@
 
-The word-length of CSA is then given by (\ref{CSA_WL}).
+Summing up $n_i$ gives the total word-length of the CSA in (\ref{CSA_WL}).
+%The total word-length of the CSA is the sum of every stage, as given by (\ref{CSA_WL}).
 \begin{eqnarray}\label{CSA_WL}
@@
     n_{CSA} &=\sum_{i=0}^{s-1}n_{i} \\
-    &= s\cdot n_{0}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
+    &= s\cdot n_{s-1}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
   \end{split}
@@
 
-Conventionally for a given frequency constraint, the word-length of both RCA and CSA should be properly selected to avoid timing violation, as presented in~(\ref{CSA_RCA}), where $n_{RCA}$ is determined by current timing information through (xxx).
-%In the conventional situation, the word-length of both RCA and CSA should be properly selected in order to meet timing.
-In this case,~(\ref{CSA_RCA}) can be obtained, where $n_{RCA}$ is determined by current timing information through (xxx).
-\begin{eqnarray}\label{CSA_RCA}
-%  \mu_{c}\cdot n_{RCA}=\mu_{c}n_0+\mu_{mux}
-  \mu_{c}\cdot n_{RCA}=d_i
+Conventionally a given frequency constraint is met by selecting word-lengths of each stage of the CSA in order to satisfy~(\ref{TimingConstraint_CSA}).
+\begin{eqnarray}\label{TimingConstraint_CSA}
+  \begin{matrix}
+    d_i\leqslant\frac{1}{f_s} &, & \forall i\in[0,s-1]
+  \end{matrix}
+\end{eqnarray}
+Under this situation, the maximum word-length of the most significant stage $n_{s-1}$ is given by~(\ref{WL_MSB_CSA}), where $b$ is determined by~(\ref{Max.length of carry chain}).
+\begin{eqnarray}\label{WL_MSB_CSA}
+  n_{s-1}\cdot\mu_c+\mu_{mux}=b\cdot\mu_c
 \end{eqnarray}
 
-Combining~(\ref{CSA_WL}) and~(\ref{CSA_RCA}), we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
+%, the word-lengths of RCAs and CSAs are selected to avoid timing violation, as presented in~(\ref{CSA_RCA}).
+
+Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}), we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
 % we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
 \begin{eqnarray}\label{CSA_Timing}
-  n_{CSA}=s\cdot n_{RCA}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
+  n_{CSA}=s\cdot b-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
 \end{eqnarray}
 
-It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
+%It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
 This is because RCA forms the least significant stage of CSA.
-In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_RCA}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
-\begin{eqnarray}\label{CSA_StageNumber}
-  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
-\end{eqnarray}
-%the word-length of each CSA stage is allocated to ensure that
+In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_WL}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
+%\begin{eqnarray}\label{CSA_StageNumber}
+%  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
+%\end{eqnarray}
 
 \subsection{Model Verification}
-As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
+%As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
 This ratio can be obtained through timing analysis instead of experiments.
@@
 
-Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
+%Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
 Fig.~\ref{CSA Model Verification} illustrates both the modeled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
@@
 It can be seen that the the modeled value match well with the experimental results.
+The ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
+We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
+The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$).
+Then the total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
+In addition, the maximum word-length of the 2-stage CSA is obtained experimentally by increasing $n_{CSA}$ until errors are observed at the output.
+The comparison between the modeled value and the empirical results of $n_{CSA}$ is illustrated in Fig.~(\ref{CSA Model Verification}).
+It can be seen that our model match well with the experimental results.
+%
+%experimentally and compare our model with the empirical results of the maximum word-length of the 2stage CSA for various operating frequencies.
+It can be seen that the modeled value match well with the experimental results.
 \begin{figure}[htbp]
@@
   \includegraphics[width=3in]{./Figures/Model.eps}
-  \caption{Comparison of the maximum word-length for given operating frequencies between the modeled value and the experimental results from FPGA simulations.}
+  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
   \label{CSA Model Verification}
@@
 
-\subsection{Area Overhead}
-We then compare different adder structures in terms of the maximum word-length with respect to different operating frequencies and the corresponding area consumption.
-Fig.~\ref{CSA3stage Timing} illustrates the maximum word-lengths for RCA and CSA with 2 stages and 3 stages under a range of operating frequencies.
-We only investigate 3 stages as the maximum stages number predicted in (\ref{CSA_StageNumber}) is 3.
-However, similar analysis can be performed on CSA with any stage numbers and the overall conclusion will still hold.
+\subsection{Accuracy Benefits and Area Overhead in CSA}
+As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{CSA3stage Timing}.
 It can be seen from Fig.~\ref{CSA3stage Timing} that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
-This corresponds to smaller truncation errors.
 RCA only outperforms than CSA when very high frequency is applied.
-In addition, the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain, as expected.
-%\begin{figure}[htbp]
-%  \centering
-%  \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
-%  \caption{Maximum word-length for RCA and CSA across a variety of frequencies.}
-%  \label{CSA3stage Timing}
-%\end{figure}
-
+This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
+However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
+In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
 \begin{figure}[tbp]
@@
 
-However, the accuracy benefits brought by CSA comes with the cost of large area overhead.
+However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
 Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
-It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the number of the 2-stage CSA is $1.7\times\sim3.1\times$.
-This finding poses a question of whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
+It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
+This finding poses a question of which is the best adder structure for a specific area budget.
+%whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
 %\begin{figure}[htbp]
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
+In the conventional design scenario, the word-length of the RCA and CSA are limited by the following two factors:
+\begin{itemize}
+  \item The critical path of the adder;
+  \item The available silicon area.
+\end{itemize}
+We compare the accuracy, performance and area trade-offs to an RCA where the maximum possible word-length is limited by the given area budget, and the timing constraints are allowed to be violated.
+%To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
 If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
@@
 
-Our results could be of interest to a circuit designer in two aspects.
+%Our results could be of interest to a circuit designer in two aspects.
 On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
@@
 
-In the first case, for a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
+Suppose an algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+In this case, for a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
 %For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
@@
 
-The accuracy here is assessed in terms of the mean error at outputs.
-The optimum design method with respect to a variety of operating frequencies and area consumptions is demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
-If the available area is large enough, CSA serves as the optimum design option because it inherently operates faster than RCA, and it can be implemented with full precision with unlimited hardware resources.
+If we define the accuracy in terms of the error expectation at the output.
+The optimum design method with respect to a variety of operating frequencies and area consumptions is demonstrated in Fig.~\ref{Tradeoff}.
+From this figure several observations can be made.
+If the available area is large enough to implement a CSA in full precision, it will be the optimum design.
+This is expected from our earlier analysis in Fig~(\ref{CSA3stage Timing}).
 The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
-For a tighter area budget, only part of the CSA can be implemented, whilst RCA still keeps full precision.
-In this case, area instead of timing becomes the dominate factor.
-This leads to precision loss for CSA from the start.
-Therefore we see RCA with overclocking is the optimum design method across almost the whole frequency domain.
-For an even stringent area constraint, the word-length of RCA is also limited.
+For a tighter area budget, only part of the CSA can be implemented, whereas the RCA still keeps full precision.
+In this case, area becomes the dominate factor and precision is lost for the CSA.
+In this case we see the RCA with overclocking is the optimum design method across almost the whole frequency domain.
+For more stringent area constraints, the word-length of RCA is also limited.
 This results in truncation error initially for all design scenarios.
-Meanwhile, CSA with high stage numbers might not even be implemented at all.
+However, the RCA with overclocking is still .......
+%Meanwhile, CSA with high stage numbers might not even be implemented at all.
 \begin{figure}[htbp]
@@
 
-Similarly in the second case where a pair of $\{Area, Accuracy\}$ constraint is applied, a certain amount of error can be tolerated when designing circuits.
-The error specifications are evaluated in terms of mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+Similarly if the algorithm designer would expect the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~(\ref{Tradeoff_Error}).
+In this situation, the error specifications are evaluated in terms of mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
 \begin{eqnarray}\label{MRE}
@@
 In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
-For a certain MRE, design with the maximum operating frequencies is labeled as the optimum design.
+For a certain MRE, the design with the maximum operating frequencies is labeled as the optimum design.
 Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area.
@@
 $MRE<0.005\%$, CSA serves as the optimum design choice with respect to large accessible area, as it intrinsically operates faster than RCA.
-When the area budget shrinks, RCA exceeds because the precision is CSA is limited.
-Similarly the precision of RCA is reduced when critical area requirement is applied.
+Once again, when the area budget shrinks, the RCA performs best because the precision of the CSA is limited.
+Similarly to the previous section, we see that the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
 
-However, if the tolerable error increases, i.e. $MRE>1\%$, the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
+%the precision of RCA is reduced when critical area requirement is applied.
+%
+%However, if the tolerable error increases, i.e. $MRE>1\%$, the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
 

### 2013-04-10 TCAD2013/overclocking_tcad.tex
Modified CSA v4

@@
 
-\title{Title}
+\title{Imprecise Computing in Datapath Design: Precision Loss or Timing Violations}
+%Imprecise Datapath Design: An Overclocking Approach
+%Imprecise Computation Through Overclocking
 
@@
 
+\section{Carry Select Adder}
+\subsection{Introduction}
+Since the delay of RCA is determined by the length of carry chain, the carry select adder (CSA) is designed to shorten the carry chain by overlapping carry propagation in sections such that the operating speed can be boosted.
+In a CSA, the carry chain is divided into multiple stages, as seen in Fig.~xxx.
+Each stage contains two RCAs and two multiplexers.
+For a given input, two computations are performed simultaneously where the carry input is zero and one respectively.
+One of these two results is then selected according to the actual carry input.
+Although this structure brings timing benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
+Furthermore, in FPGA technology, multiplexers are expensive.
+Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of these two adder structures in this section.
+
+%, silicon area is incorporated as the third metric besides accuracy and performance.
+We explore the trade-offs between these three factors for both adder structures.
+The objective is to demonstrate the best design choice for a given set of design constraints.
+
+%\begin{figure*}[t]
+%  \centering
+%  \includegraphics[width=\textwidth]{./Figures/CSAstructure.pdf}
+%  \caption{Structure of an $s$-stage CSA.}
+%\end{figure*}
+
+%In addition to RCA, there are several
+
+\subsection{Timing Models for Carry Select Adder}
+We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
+This information can then be employed to determine the truncation error based on the models presented in Section.xxx.
+
+In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
+In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output.
+Note that unlike other stages, the least significant stage is only built by one RCA without multiplexers, since it is directly driven by the carry input.
+Hence we obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
+\begin{eqnarray}\label{CSA_SingleStageDelay}
+  d_i=\left\{
+    \begin{matrix}
+      n_i\cdot \mu_{c}+(s-i)\cdot\mu_{mux}, &\textrm{if $i\in\left[1,s-1\right]$}\\
+      n_0\cdot \mu_c + (s-1)\cdot\mu_{mux}, & \textrm{if $i=0$}
+    \end{matrix}
+  \right.
+\end{eqnarray}
+
+Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{CSA_DelayEqual}).
+\begin{eqnarray}\label{CSA_DelayEqual}
+  d_{s-1}=d_{s-2}=\cdots=d_{0}
+\end{eqnarray}
+
+In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
+%This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
+Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), where $n_i$ denotes the CSA word-length of stage $i$.
+\begin{eqnarray}\label{CSA_DelayRep}
+ n_i=\left\{
+	\begin{matrix}
+	  n_{s-1}-(s-1-i)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[1,s-1\right]$}\\
+	  n_{s-1}-(s-2)\cdot\frac{\mu_{mux}}{\mu_c}, &\textrm{if $i=0$}
+	\end{matrix}
+    \right.
+\end{eqnarray}
+
+Summing up $n_i$ gives the total word-length of the CSA in (\ref{CSA_WL}).
+%The total word-length of the CSA is the sum of every stage, as given by (\ref{CSA_WL}).
+\begin{eqnarray}\label{CSA_WL}
+  \begin{split}
+    n_{CSA} &=\sum_{i=0}^{s-1}n_{i} \\
+    &= s\cdot n_{s-1}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
+  \end{split}
+\end{eqnarray}
+
+Conventionally under a given frequency constraint, the word-length of RCA is truncated by using $n_{RCA}=b-1$ bits, where $b$ is determined by~(\ref{Max.length of carry chain}).
+Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{TimingConstraint_CSA}).
+\begin{eqnarray}\label{TimingConstraint_CSA}
+  \begin{matrix}
+    d_i\leqslant\frac{1}{f_s} &, & \forall i\in[0,s-1]
+  \end{matrix}
+\end{eqnarray}
+
+Hence for the same frequency requirement, we can form the relationship between the delay of the most significant stage of CSA and the delay of RCA, as given by~(\ref{WL_MSB_CSA}),
+\begin{eqnarray}\label{WL_MSB_CSA}
+    \mu_c\cdot (b-1) = n_{s-1}\cdot\mu_c+\mu_{mux}
+\end{eqnarray}
+
+%, the word-lengths of RCAs and CSAs are selected to avoid timing violation, as presented in~(\ref{CSA_RCA}).
+
+Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
+% we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
+\begin{eqnarray}\label{CSA_Timing}
+  n_{CSA}=s\cdot (b-1)-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
+\end{eqnarray}
+
+%It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
+This is because RCA forms the least significant stage of CSA.
+In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_WL}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
+%\begin{eqnarray}\label{CSA_StageNumber}
+%  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
+%\end{eqnarray}
+
+\subsection{Model Verification}
+%As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
+This ratio can be obtained through timing analysis instead of experiments.
+Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ from the timing analysis tool.
+According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials.
+
+%Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
+Fig.~\ref{CSA Model Verification} illustrates both the modeled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
+In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
+It can be seen that the the modeled value match well with the experimental results.
+The ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
+We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
+The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$).
+Then the total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
+In addition, the maximum word-length of the 2-stage CSA is obtained experimentally by increasing $n_{CSA}$ until errors are observed at the output.
+The comparison between the modeled value and the empirical results of $n_{CSA}$ is illustrated in Fig.~(\ref{CSA Model Verification}).
+It can be seen that our model match well with the experimental results.
+%
+\begin{figure}[htbp]
+  \centering
+  \includegraphics[width=3in]{./Figures/Model.eps}
+  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
+  \label{CSA Model Verification}
+\end{figure}
+
+\subsection{Accuracy Benefits and Area Overhead in CSA}
+As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{CSA3stage Timing}.
+It can be seen from Fig.~\ref{CSA3stage Timing} that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
+RCA only outperforms than CSA when very high frequency is applied.
+This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
+However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
+In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
+\begin{figure}[tbp]
+    \begin{minipage}[b]{.48\textwidth}
+        \centering
+        \subfigure[Maximum word-length.]{
+            \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
+            \label{CSA3stage Timing}
+        }
+        \subfigure[Hardware resource usage.]{
+            \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
+            \label{CSA3stage Area}
+        }
+    \end{minipage}
+    \centering
+    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
+\end{figure}
+
+However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
+Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
+It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
+This finding poses a question of which is the best adder structure for a specific area budget.
+
+\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
+In Section xxx, we have discussed two design scenarios when considering timing constraints.
+In this section, we expand our analysis by incorporating the silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures.
+In the conventional design scenario, the word-length of RCA and CSA is limited by the given frequency constraint, or/and the available hardware resources.
+The precision loss potentially generates large errors even without timing violations.
+However in the new design scenario, we use RCA with the maximum possible word-length under the given area budget, and the timing constraints are allowed to be violated.
+This process might result in timing errors as well as truncation errors due to area limitation.
+We compare these two scenarios with different design goals, with the aim of targeting the optimum design methodology under each situation.
+
+%To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
+If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
+The precision loss might results in large errors even at low frequencies.
+This is demonstrated by experiments where area constraints are applied besides the timing requirement.
+In the conventional design scenario, both of the constraints are met by reducing the word-length of the input signal.
+The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
+In addition, we propose another circuit designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
+
+%Our results could be of interest to a circuit designer in two aspects.
+On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated.
+We select the optimum design methodology for both situations.
+
+First, suppose the designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+That is, a pair of $\{Area, Frequency\}$ constraint is applied.
+In this case, the optimum design method is selected based on the following criteria:
+%For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
+The optimal design metric with the minimum error expectation is labelled for each area constraint.
+For a given frequency and area constraint, the optimum design is chosen based on the following metrics:
+\begin{itemize}
+  \item Design with the best accuracy at outputs is the optimum design;
+  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
+  \item If the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
+\end{itemize}
+
+For instance let the available LUTs number be 25, the accuracy with respect to different operating frequencies for both design scenarios are presented in Fig.~(\ref{CSA_LUT25}), on which the optimum design metric is labeled.
+Note that the accuracy is defined in terms of the error expectation at the output.
+\begin{figure}[ht]
+  \centering
+  \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
+  \caption{A comparison between two design scenarios when the number of LUT is set to 25.
+The RCA and CSA are investigated in the conventional scenario, while the RCA is explored in the proposed new scenario.
+The results are obtained from post place-and-route simulations on Xilinx Virtex FPGAs.}
+  \label{CSA_LUT25}
+\end{figure}
+
+We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models in Section xxx.
+It can also be observed that CSA cannot be implemented with full word-length due to the limited area budget, and this leads to large truncation errors initially for CSA.
+
+We then perform the similar experiments with a variety of area constraints.
+The optimum design method with respect to different operating frequencies and area consumptions is demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}.
+From this figure, several observations can be made.
+If the available area is large enough to implement a CSA in full precision, it will be the optimum design.
+This is expected from our earlier analysis in Fig.~\ref{CSA3stage Timing}.
+The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
+For a tighter area budget, only part of the CSA can be implemented, whereas the RCA still keeps full precision.
+In this case, area becomes the dominate factor and precision is lost for the CSA.
+We see the RCA with overclocking is the optimum design method across almost the whole frequency domain.
+For a more stringent area constraint, the word-length of RCA is also limited.
+This results in truncation errors initially for all design scenarios.
+However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than CSA under the same area constraint.
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
+  \caption{A demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
+  \label{Fig_CSA_Tradeoff}
+\end{figure}
+
+Similarly if the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
+In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+\begin{eqnarray}\label{MRE}
+  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
+\end{eqnarray}
+
+In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
+For a certain MRE, the design with the maximum operating frequencies is selected as the optimum design.
+Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement.
+Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
+%Based on these criteria, the decision graph is depicted in
+%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
+    \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
+    \label{Fig_CSA_Tradeoff_Error}
+\end{figure}
+
+For a tight accuracy requirement, i.e.
+$MRE<0.005\%$, CSA serves as the optimum design choice with respect to large accessible area, as it intrinsically operates faster than RCA.
+Once again, when the area budget shrinks, the RCA performs best because the precision of the CSA is limited.
+Similarly to the previous section, we see that the overclocked RCA achieves the fastest operating frequencies under most area constraints when the accuracy requirement is released.
+
+To sum up, it can be seen that for both design goals, CSA is the best option only when there is enough hardware resources.
+However this circumstance is unlikely to happen, especially with the continued technology scaling nowadays.
+Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.
+
 \section{Constant Coefficient Multiplier}\label{section_CCM}
@@
 Each root node is the baseline CCM and the errors are propagated through an adder tree, of which the error can be determined based on our previous RCA model.
-
-\section{Carry Select Adder}
-\subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, the carry select adder (CSA) is designed to shorten the carry chain by overlapping carry propagation in sections such that the operating speed can be boosted.
-In a CSA, the carry chain is divided into multiple stages, as seen in Fig.~xxx.
-Each stage contains two RCAs and two multiplexers.
-For a given input, two computations are performed simultaneously where the carry input is zero and one respectively.
-One of these two results is then selected according to the actual carry input.
-Although this structure brings timing benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
-Furthermore, in FPGA technology, multiplexers are expensive.
-Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of these two adder structures in this section.
-
-%, silicon area is incorporated as the third metric besides accuracy and performance.
-We explore the trade-offs between these three factors for both adder structures.
-The objective is to demonstrate the best design choice for a given set of design constraints.
-
-%\begin{figure*}[t]
-%  \centering
-%  \includegraphics[width=\textwidth]{./Figures/CSAstructure.pdf}
-%  \caption{Structure of an $s$-stage CSA.}
-%\end{figure*}
-
-%In addition to RCA, there are several
-
-\subsection{Timing Models for Carry Select Adder}
-We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
-This information can then be employed to determine the truncation error based on the models presented in Section.xxx.
-
-In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
-In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output.
-Note that unlike other stages, the least significant stage is only built by one RCA without multiplexers, since it is directly driven by the carry input.
-Hence we obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
-\begin{eqnarray}\label{CSA_SingleStageDelay}
-  d_i=\left\{
-    \begin{matrix}
-      n_i\cdot \mu_{c}+(s-i)\cdot\mu_{mux}, &\textrm{if $i\in\left[1,s-1\right]$}\\
-      n_0\cdot \mu_c + (s-1)\cdot\mu_{mux}, & \textrm{if $i=0$}
-    \end{matrix}
-  \right.
-\end{eqnarray}
-
-Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{CSA_DelayEqual}).
-\begin{eqnarray}\label{CSA_DelayEqual}
-  d_{s-1}=d_{s-2}=\cdots=d_{0}
-\end{eqnarray}
-
-In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
-%This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
-Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), where $n_i$ denotes the CSA word-length of stage $i$.
-\begin{eqnarray}\label{CSA_DelayRep}
- n_i=\left\{
-	\begin{matrix}
-	  n_{s-1}-(s-1-i)\cdot\frac{\mu_{mux}}{\mu_c}, & \textrm{if $i\in\left[1,s-1\right]$}\\
-	  n_{s-1}-(s-2)\cdot\frac{\mu_{mux}}{\mu_c}, &\textrm{if $i=0$}
-	\end{matrix}
-    \right.
-\end{eqnarray}
-
-Summing up $n_i$ gives the total word-length of the CSA in (\ref{CSA_WL}).
-%The total word-length of the CSA is the sum of every stage, as given by (\ref{CSA_WL}).
-\begin{eqnarray}\label{CSA_WL}
-  \begin{split}
-    n_{CSA} &=\sum_{i=0}^{s-1}n_{i} \\
-    &= s\cdot n_{s-1}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
-  \end{split}
-\end{eqnarray}
-
-Conventionally a given frequency constraint is met by selecting word-lengths of each stage of the CSA in order to satisfy~(\ref{TimingConstraint_CSA}).
-\begin{eqnarray}\label{TimingConstraint_CSA}
-  \begin{matrix}
-    d_i\leqslant\frac{1}{f_s} &, & \forall i\in[0,s-1]
-  \end{matrix}
-\end{eqnarray}
-Under this situation, the maximum word-length of the most significant stage $n_{s-1}$ is given by~(\ref{WL_MSB_CSA}), where $b$ is determined by~(\ref{Max.length of carry chain}).
-\begin{eqnarray}\label{WL_MSB_CSA}
-  n_{s-1}\cdot\mu_c+\mu_{mux}=b\cdot\mu_c
-\end{eqnarray}
-
-%, the word-lengths of RCAs and CSAs are selected to avoid timing violation, as presented in~(\ref{CSA_RCA}).
-
-Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}), we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
-% we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
-\begin{eqnarray}\label{CSA_Timing}
-  n_{CSA}=s\cdot b-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
-\end{eqnarray}
-
-%It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
-This is because RCA forms the least significant stage of CSA.
-In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_WL}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
-%\begin{eqnarray}\label{CSA_StageNumber}
-%  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
-%\end{eqnarray}
-
-\subsection{Model Verification}
-%As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
-This ratio can be obtained through timing analysis instead of experiments.
-Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ from the timing analysis tool.
-According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials.
-
-%Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
-Fig.~\ref{CSA Model Verification} illustrates both the modeled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
-In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
-It can be seen that the the modeled value match well with the experimental results.
-The ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
-We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
-The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$).
-Then the total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
-In addition, the maximum word-length of the 2-stage CSA is obtained experimentally by increasing $n_{CSA}$ until errors are observed at the output.
-The comparison between the modeled value and the empirical results of $n_{CSA}$ is illustrated in Fig.~(\ref{CSA Model Verification}).
-It can be seen that our model match well with the experimental results.
-%
-%experimentally and compare our model with the empirical results of the maximum word-length of the 2stage CSA for various operating frequencies.
-It can be seen that the modeled value match well with the experimental results.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3in]{./Figures/Model.eps}
-  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
-  \label{CSA Model Verification}
-\end{figure}
-
-%It can be seen that our timing models match well the experimental results for both RCA and CSA, except that the modelled outcomes are slight conservative, especially at higher operating frequencies.
-This is because the model coefficients are obtained based on timing analysis, which is designed with safety margins to ensure correct functionality for diverse operating conditions.
-In addition, routing delay might be introduced during timing analysis such that the overall delay is enlarged, while our models consider logic delay only.
-
-\subsection{Accuracy Benefits and Area Overhead in CSA}
-As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{CSA3stage Timing}.
-It can be seen from Fig.~\ref{CSA3stage Timing} that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
-RCA only outperforms than CSA when very high frequency is applied.
-This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
-However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
-In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
-\begin{figure}[tbp]
-    \begin{minipage}[b]{.48\textwidth}
-        \centering
-        \subfigure[Maximum word-length.]{
-            \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
-            \label{CSA3stage Timing}
-        }
-        \subfigure[Hardware resource usage.]{
-            \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
-            \label{CSA3stage Area}
-        }
-    \end{minipage}
-    \centering
-    \caption{Comparison between RCA and CSA across a variety of frequency values in terms of the maximum word-length of input signal and the area consumption.}
-\end{figure}
-
-However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
-Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
-It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
-This finding poses a question of which is the best adder structure for a specific area budget.
-%whether CSA with higher stage numbers still offer better accuracy than RCA under a limited area budget.
-%\begin{figure}[htbp]
-%  \centering
-%  \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
-%  \caption{Area overhead for RCA and CSA.}
-%  \label{CSA3stage Area}
-%\end{figure}
-
-\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-In the conventional design scenario, the word-length of the RCA and CSA are limited by the following two factors:
-\begin{itemize}
-  \item The critical path of the adder;
-  \item The available silicon area.
-\end{itemize}
-We compare the accuracy, performance and area trade-offs to an RCA where the maximum possible word-length is limited by the given area budget, and the timing constraints are allowed to be violated.
-%To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
-If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
-The precision loss might results in large errors even at low frequencies.
-This is demonstrated by experiments where area constraints are applied besides the timing requirement.
-In the conventional design scenario, both of the constraints are met by reducing the word-length of the input signal.
-The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
-In addition, we propose another circuit designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
-
-%Our results could be of interest to a circuit designer in two aspects.
-On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
-On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated.
-We select the optimum design methodology for both situations.
-
-Suppose an algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
-In this case, for a certain pair of $\{Area, Frequency\}$ constraint, the optimum design method is selected based on the following criteria:
-%For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
-The optimal design metric with the minimum error expectation is labelled for each area constraint.
-For a given frequency and area constraint, the optimum design is chosen based on the following metrics:
-\begin{itemize}
-  \item Design with the best accuracy at outputs is the optimum design;
-  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
-  \item If the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
-\end{itemize}
-
-If we define the accuracy in terms of the error expectation at the output.
-The optimum design method with respect to a variety of operating frequencies and area consumptions is demonstrated in Fig.~\ref{Tradeoff}.
-From this figure several observations can be made.
-If the available area is large enough to implement a CSA in full precision, it will be the optimum design.
-This is expected from our earlier analysis in Fig~(\ref{CSA3stage Timing}).
-The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
-For a tighter area budget, only part of the CSA can be implemented, whereas the RCA still keeps full precision.
-In this case, area becomes the dominate factor and precision is lost for the CSA.
-In this case we see the RCA with overclocking is the optimum design method across almost the whole frequency domain.
-For more stringent area constraints, the word-length of RCA is also limited.
-This results in truncation error initially for all design scenarios.
-However, the RCA with overclocking is still .......
-%Meanwhile, CSA with high stage numbers might not even be implemented at all.
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
-  \caption{Demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
-  \label{Tradeoff}
-\end{figure}
-
-Similarly if the algorithm designer would expect the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~(\ref{Tradeoff_Error}).
-In this situation, the error specifications are evaluated in terms of mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
-\begin{eqnarray}\label{MRE}
-  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
-\end{eqnarray}
-
-In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
-For a certain MRE, the design with the maximum operating frequencies is labeled as the optimum design.
-Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area.
-Based on these criteria, the decision graph is depicted in Fig.~(\ref{Tradeoff_Error}).
-%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
-\begin{figure}[htbp]
-    \centering
-    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
-    \caption{Demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
-    \label{Tradeoff_Error}
-\end{figure}
-
-For a tight accuracy requirement, i.e.
-$MRE<0.005\%$, CSA serves as the optimum design choice with respect to large accessible area, as it intrinsically operates faster than RCA.
-Once again, when the area budget shrinks, the RCA performs best because the precision of the CSA is limited.
-Similarly to the previous section, we see that the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
 

### 2013-04-10 TCAD2013/overclocking_tcad.tex
Add FCCM experiments

@@
 \usepackage{stfloats}
+\usepackage{threeparttable}
 
@@
 
-\subsection{Probabilistic Model of Truncation Error}
+\subsection{Probabilistic Model of Truncation Error}\label{section_RCA_TruncationError}
 For ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
@@
 
-\subsection{Comparison between Two Scenarios}
+\subsection{Comparison between Two Scenarios}\label{section_RCA_Comparison}
 In the traditional scenario, the word-length of RCA must be truncated, using $n=b-1$ bits, in order to meet a given $f_S$. The error expectation is then given by (\ref{Eo_trad_RCA}).
@@
 Since the delay of RCA is determined by the length of carry chain, the carry select adder (CSA) is designed to shorten the carry chain by overlapping carry propagation in sections such that the operating speed can be boosted.
-In a CSA, the carry chain is divided into multiple stages, as seen in Fig.~xxx.
-Each stage contains two RCAs and two multiplexers.
+The structure of a CSA is presented in Fig.~\ref{Fig_CSA_Structure}.
+In a CSA, the carry chain is divided into multiple stages.
+Each stage contains two RCAs and two multiplexers, as seen in Fig.~\ref{Fig_CSA_SingleStage}.
 For a given input, two computations are performed simultaneously where the carry input is zero and one respectively.
@@
 
+\begin{figure}[htbp]
+    \begin{minipage}[b]{.49\textwidth}
+        \centering
+        \subfigure[The structure diagram of a CSA with $s$ stages.]{
+            \includegraphics[width=\textwidth]{./Figures/CSA_structure.pdf}
+            \label{Fig_CSA_Structure}
+        }\vspace{-3ex}
+        \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
+        %\centering
+            \includegraphics[width=2.4in]{./Figures/CSA_SingleStage.pdf}
+            \label{Fig_CSA_SingleStage}
+        }
+    \end{minipage}
+    \centering
+    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
+\end{figure}
+
 %, silicon area is incorporated as the third metric besides accuracy and performance.
@@
 We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
-This information can then be employed to determine the truncation error based on the models presented in Section.xxx.
-
-In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
+This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.
+
+In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1}~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
 In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output.
@@
 \subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-In Section xxx, we have discussed two design scenarios when considering timing constraints.
+In Section~\ref{section_RCA}, we have discussed two design scenarios when considering timing constraints.
 In this section, we expand our analysis by incorporating the silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures.
@@
 In this case, the optimum design method is selected based on the following criteria:
-%For instance, Fig.xxx to Fig.xxx illustrate error expectations of all the described design scenarios when setting the LUTs number to 45, 35, 25 and 15 respectively.
-The optimal design metric with the minimum error expectation is labelled for each area constraint.
-For a given frequency and area constraint, the optimum design is chosen based on the following metrics:
 \begin{itemize}
@@
 
-We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models in Section xxx.
+We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models in Section~\ref{section_RCA_Comparison}.
 It can also be observed that CSA cannot be implemented with full word-length due to the limited area budget, and this leads to large truncation errors initially for CSA.
@@
 
-%the precision of RCA is reduced when critical area requirement is applied.
-%
-%However, if the tolerable error increases, i.e. $MRE>1\%$, the overclocked RCA achieves the fastest operating frequencies with respect to most area constraints.
+\section{Test Platform}\label{Experiment}
+In our experiments, we compare two design perspectives.
+In the first scenario, the word-length of the input signal is truncated before propagating through the datapath in order to meet a given latency.
+In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length.
+The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA XC6VLX240T-1FFG1156.
+
+\subsection{Experimental Setup} % (fold)
+\label{sub:experimental_setup}
+We initially build up a test framework on an FPGA.
+The general architecture is depicted in Fig.~\ref{Test Framework}.
+The main body of the test framework consists of the circuit under test (CUT), the test frequency generator and the control logic, as shown in the dotted box in Fig.~\ref{Test Framework}.
+The I/Os of the CUT are registered by the launch registers (LRs) and the sample registers (SRs), which are all triggered by the test clock.
+Input test vectors are stored in the on-chip memory during initialization.
+The results are sampled using Xilinx ChipScope.
+Finally, we perform an offline comparison of the output of the original circuit at the rated frequency with the output of the overclocked as well as the truncated designs using the same input vectors.
+%
+\begin{figure}[htbp]
+  \centering
+  %\vspace{-3.5ex}
+  \includegraphics[width=3.3in]{./Figures/TestFramework2.eps}
+  %\vspace{-4.5ex}
+  \caption{FPGA Test framework, which is composed of a measurement architecture (the dotted box) and an off-line comparator.}
+  \label{Test Framework}
+  %\vspace{-1ex}
+\end{figure}
+
+The test frequency generator is implemented using two cascaded mixed-mode clock managers (MMCMs), created using Xilinx Core Generator~\cite{Virtex6Clocking}.
+Besides the outputs, the corresponding input vectors and memory addresses are also recorded into the comparator, as can be seen in Fig.~\ref{Test Framework}, in order to ensure that the recorded errors arise from overclocking the CUT rather than the surrounding circuitry when high test frequencies are applied.
+
+%the potential timing errors generated from the test framework instead of CUT, when high test frequencies are applied.
+Comparisons are performed between the sampled results and the expected values.
+If mismatch is found, the results will be discarded.
+
+%.
+In this test framework, two cascaded MMCMs are employed in order to provide a wide range of frequency values.
+In addition, the output frequency of the MMCM can be dynamically reconfigured without re-implementing the whole design~\cite{Virtex6Clocking,MMCM}.
+This reconfiguration process is controlled by a finite state machine within the control logic.
+Before actual measurements on FPGA, the rated frequency of CUT is examined through Xilinx Timing Analyzer.
+This frequency is then utilized as the starting value when generating test frequencies.
+The new frequency will increase with a step of 10MHz and stop when the comparator shows that output errors are stabilized.
+The control logic also generates address and read enable signal for the on-chip memory.
+
+%In our experiments, the test clock frequency starts from the rated operating frequency of CUT, and increases with a step of 10MHz until the output error expectation stabilizes.
+
+%In order to avoid the potential timing errors generated from the test framework instead of CUT under high test frequencies, several methods are adopted.
+Firstly, the control signals for the test frequency generator is triggered by the system clock, which is 33.33MHz in our experiments.
+This will guarantee that the test clock generation will not be affected by high frequencies.
+Secondly, since the address counter for the on-chip memory is driven by the test frequency, a deeply pipelined counter structure with initial delay of 258 cycles is used to ensure the correct sample of each address bit.
+Thirdly, the key internal control signals such as memory address and corresponding operands are recorded together with the outputs to the comparator.
+Comparisons are performed between these values and the corresponding original values.
+The results will be discarded if mismatch is found.
+% without reimplement the whole design.
+% subsection experimental_setup (end)
+% \subsection{Experimental Results} % (fold)
+% \label{sub:subsubsection_name}
+
+\subsection{Benchmark Circuits}
+Three types of DSP designs are tested: digital filters (FIR, IIR and Butterworth), a Sobel edge detector and a direct implementation of a Discrete Cosine Transformation (DCT).
+The filter parameters are generated through MATLAB filter design toolbox, and they are normalized to integers for implementation.
+Table~\ref{Rated_Frequency_table} summarizes the operating frequency of each implemented design in Xilinx ISE14.1 when the word-length of input signal is 8-bit.
+\vspace{-0.5ex}
+\begin{table}[htbp]
+%% increase table row spacing, adjust to taste
+\renewcommand{\arraystretch}{1.2}
+%\setlength{\tabcolsep}{2}
+\caption{Rated Frequencies of Example Designs.}
+\label{Rated_Frequency_table}
+\begin{center}
+\footnotesize
+%\vspace{-4ex}
+\begin{tabular}{ccc}
+\hline
+\hline
+Design & Frequency (MHz) & Description\\
+\hline
+FIR Filter & 126.2 & $5^{th}$ order\\
+Sobel Edge Detector & 196.7 & $3\times 3$\\
+IIR Filter & 140.3 & $7^{th}$ order\\
+Butterworth Filter & 117.1 & $9^{th}$ order\\
+DCT & 176.7 & 4-point\\
+\hline
+\hline
+\end{tabular}
+\normalsize
+\end{center}
+%\vspace{-2.5ex}
+\end{table}
+
+The input data are generated from two sources.
+One is called ``uniform independent inputs'', which are randomly sampled from a uniform distribution of 8-bit numbers.
+The other is referred to as ``real inputs'', which denote 8-bit pixel values of the $512\!
+\times\!
+512$ Lena image.
+
+\subsection{Exploring the Conservative Timing Margin} % (fold)
+\label{sub:exploring_the_conservative_timing_margin}
+
+Generally, the operating frequency provided by EDA tools tends to be conservative to ensure the correct functionality under a wide range of operating environments and workloads.
+In a practical situation, this may result in a large gap between the predicted frequency and the actual frequency under which the correct operation is maintained~\cite{gojman2013FPGA}.
+
+For example, the predicted frequencies and the actual frequencies of a $5^{th}$~order FIR filter using different word-lengths are depicted in Fig.~\ref{TimingMargin}.
+The ``actual'' maximum frequencies are computed by increasing the operating frequency from the rated value until errors are observed at the output; the maximum operating frequency with correct output is recorded for the current word-length.
+As can be seen in Fig.~\ref{TimingMargin}, the circuit can operate without errors at a much higher frequency in practice than predicted according to our experiments.
+A maximum speed differential of $3.2\times$ is obtained when the input signal is 5-bit.
+
+\begin{figure}[t]
+  \centering
+  \includegraphics[width=3.2in]{./Figures/Exp/FIR/RatedFrequency3.eps}
+  %\vspace{-1.5ex}
+  \caption{The maximum operating frequencies for different input word-lengths of an FIR filter.
+The dotted line depicts the rated frequency reported by the Xilinx Timing Analyzer.
+The solid line is obtained through real FPGA tests using our platform.}
+  \label{TimingMargin}
+  %\vspace{-3.5ex}
+\end{figure}
+
+In our experiments in Section~\ref{Section_Experiments}, the conservative timing margin is removed in the traditional scenario for a fairer comparison to the overclocking scenario.
+To do this, for each truncated word-length, we select the maximum frequency at which we see no overclocking error on the FPGA board in our lab.
+For example, in Fig.~\ref{TimingMargin}, the operating frequency of the design when the word-lengths are truncated to 8,~5 and 2 bits are 400MHz,~450MHz and 500MHz respectively.
+
+Fig.~\ref{TimingMargin} also demonstrates that when the circuit is truncated, it allows the circuit to operate at a higher frequency than the frequency of full precision implementation.
+However, a non-uniform period change can be observed for both results.
+For instance, the maximum operating frequency keeps almost constant when the operand word-length reduces from 8 to 6 or from 5 to 3 in both the experimental results and those of timing analyzer.
+This will cause a slight deviation between our analytical model which assumes that the single bit carry propagation delay to be a constant value, as discussed in (\ref{Eo_trad_RCA}) with expression $n=b-1$.
+This deviation will be influenced by many factors including how the architecture has been packed onto LUTs and CLBs and process variation causing non-uniform interconnection delays~\cite{FPGAPV}.
+However, we shall see that our model remains close to the true empirical results in Section~\ref{Section_Experiments}.
+
+\subsection{Evaluation Metric of Outputs}
+The results are evaluated in terms of mean relative error (MRE), which represents the percentage of error at outputs.
+MRE is given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the correct output respectively.
+%
+\begin{eqnarray}\label{MRE}
+%\small
+\scriptsize
+  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
+\end{eqnarray}
+\normalsize
+
+\subsection{Computing Model Parameters}
+The accuracy of our proposed models is examined with practical results on Virtex-6 FPGA.
+We first determine the model parameters.
+There are two types of parameters in the models of overclocking error.
+The first is based on the circuit architecture.
+For example, the word-length of RCAs and CCMs ($n$), the shifted bits of the shifters in CCM ($s$), and the word-length of the input signal ($k$).
+This is determined through static analysis.
+The second depends on timing information, such as the single bit carry propagation delay $\mu$.
+In order to keep consistency with the assumption made in models that $\mu$ is a fixed value, it is obtained according to the actual FPGA measurement results.
+
+Initially the maximum error-free frequency $f_0$ is applied.
+In this case we have~(\ref{Eq_decideMu_0}) where $d_c$ is a constant value which denotes the interconnection delay.
+The frequency is then increased such that~(\ref{Eq_decideMu_1}) is obtained.
+This process repeats until the maximum frequency $f_{n-1}$ is applied in~(\ref{Eq_decideMu_2}).
+Based on these frequency values, $\mu$ can be determined.
+\begin{eqnarray}\label{Eq_decideMu_0}
+\vspace{-1ex}
+%\small
+%\footnotesize
+\scriptsize
+  f_0 &= n\mu+d_c
+  \vspace{-12ex}
+\end{eqnarray}
+\vspace{-5ex}
+\begin{align}\label{Eq_decideMu_1}
+  f_1 &= (n-1)\mu+d_c    \\
+  &\cdots               \notag
+  \vspace{-3ex}
+\end{align}
+\vspace{-5.5ex}
+\begin{eqnarray}\label{Eq_decideMu_2}
+  f_{n-1} &= \mu+d_c
+%  \vspace{-2ex}
+\end{eqnarray}
+\normalsize
+
+\section{Results and Discussion}\label{Section_Experiments}
+\subsection{Case study: FIR filter}
+We first assess the accuracy of our proposed models of error.
+The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data.
+The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
+% FIR
+\begin{figure}[htbp]
+  \centering
+%  \vspace{-2.5ex}
+  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New2.eps}
+%  \vspace{-5ex}
+  \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA.
+The modeled values of both overclocking errors and truncation errors are presented as dotted lines.
+The actual FPGA measurements are depicted using solid lines.
+Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
+  \label{FIR}
+%  \vspace{-1ex}
+\end{figure}
+
+%Lena image
+\begin{figure*}[htbp]
+  %\vspace{-2ex}
+  \centering
+  \subfigure[425MHz,~n=8~,~no errors observed]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
+  \end{minipage}%
+  }% This is important! use % to indicate same line, otherwise new line
+  \subfigure[430MHz,~n=8,~SNR=47.15dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
+  \end{minipage}
+  }%
+  \subfigure[480MHz,~n=8,~SNR=24.1dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
+  \end{minipage}
+  }%
+  \subfigure[520MHz,~n=8,~SNR=10.86dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
+  \end{minipage}
+  }\vspace{-1ex}
+  \subfigure[425MHz,~n=7,~SNR=26.06dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
+  \end{minipage}%
+  }% This is important! use % to indicate same line, otherwise new line
+  \subfigure[430MHz,~n=5,~SNR=24.85dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
+  \end{minipage}
+  }%
+  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
+  \end{minipage}
+  }%
+  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
+  \end{minipage}
+  }
+%\vspace{-2ex}
+\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
+\label{FIR_Lena}
+%\vspace{-2ex}
+\end{figure*}
+
+According to Fig.~\ref{FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as expected by our models.
+In addition, we see that using real data, more significant reduction of MRE are achieved, and that no errors are observed when frequency is initially increased.
+This is because for real data, long carry chains are typically generated with even smaller probabilities, and the longest carry chain rarely occurs.
+
+The output images of the FIR filter for both of the two scenarios with increasing frequencies are presented in Fig.~\ref{FIR_Lena}, from which we can clearly see the differences between the errors generated in these two scenarios.
+In the overclocking scenario, we observe errors in the MSBs for certain input patterns.
+This leads to ``salt and pepper noise'', as shown on the images in the top row of Fig.~\ref{FIR_Lena}.
+In the traditional scenario, truncation causes an overall degradation of the whole image, as can be seen in the bottom row of Fig.~\ref{FIR_Lena}.
+Furthermore, it is difficult to recover from the latter type of error, since it is generated due to precision loss.
+
+\subsection{Potential Benefits in Circuit Design}
+%The results can be interpreted in two folds.
+Our results could be of interest to a circuit designer in two ways.
+Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
+In the first case, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
+\begin{eqnarray}\label{Relative Reduction MRE}
+%\small
+\scriptsize
+  \frac{MRE_{Trad}-MRE_{ovrc}}{MRE_{Trad}}\times 100\%
+\end{eqnarray}
+\normalsize
+%\vspace{-2ex}
+
+In this table, the frequency is normalized to the maximum error-free frequency for each design when the input signal is 8-bit.
+The N/A in Table~\ref{Ratio_MRE} refers to the situations where a certain frequency simply cannot be achieved using the traditional scenario.
+It can be seen that a significant reduction of MRE can be achieved using the proposed overclocking scenario, and the geometric mean reduction varies from $67.9\%$ to $95.4\%$ using uniform input data.
+Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{FIR}.
+%Table goes here
+
+\begin{table*}[htbp]
+ %\vspace{-2ex}
+ %% increase table row spacing, adjust to taste
+   \renewcommand{\arraystretch}{1.05}
+   \setlength{\tabcolsep}{3.5pt}
+   \caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
+%   \vspace{-2ex}
+   \centering
+   \footnotesize
+   %\vspace{-4mm}
+   \begin{threeparttable}
+   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
+     \hline
+     \hline
+     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
+     \multicolumn{2}{c|}{\textbf{FIR}} &
+     \multicolumn{2}{c|}{\textbf{Sobel}} &
+     \multicolumn{2}{c|}{\textbf{IIR}} &
+     \multicolumn{2}{c|}{\textbf{Butterworth}} &
+     \multicolumn{2}{c||}{\textbf{DCT4}} &
+     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
+     &  {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena  }
+     &  {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena}\\
+     \hline
+     1.04 & 99.85\%	& 100.00\%  & 99.51\% &	99.74\% &	 72.28\% &	90.09\% &	 79.03\% &	 100.00\% &	 83.58\% &	 98.06\% & 86.14\% & 97.50\%\\
+     1.08 & 98.93\%	& 99.97\%	& 96.26\% &	93.75\% &	 71.64\% &	90.50\% &	 78.81\% &	 100.00\% &	 83.26\% &	 98.45\% & 85.15\% & 96.46\%\\
+     1.12 & 94.27\%	& 98.82\%   & 96.25\% &	93.62\% &	 73.63\% &   88.25\% &	 81.88\% &	 84.87\%  &	 89.44\% &	 99.56\% & 86.68\% & 92.84\%\\
+     1.16 & 99.66\%	& 99.91\%   & 73.73\% &	93.62\% &	 73.10\% &   89.92\% &	 79.30\% &	 84.23\%  &	 79.07\% &	 99.44\% & 80.44\% & 93.23\%\\
+     1.20 & 96.03\%	& 99.90\%   & 81.55\% &	81.52\% &	 70.76\% &	75.67\% &	 64.96\% &	 84.50\%  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.46\% & 84.95\% \\
+     1.24 & 98.46\%	& 99.32\%   & 81.43\% &	81.67\% &	 70.47\% &	76.12\% &	 63.66\% &	 84.23\%  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.44\% & 84.92\%\\
+     1.28 & 95.39\%	& 99.29\%   & 60.41\% &	78.24\% &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	54.38\% &	 75.15\%  &	N/A\tnote{*}	  & N/A\tnote{*} & 67.92\% & 83.58\%\\
+     1.32 & 95.37\%	& 98.75\%   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 95.37\%	& 98.75\% \\
+     \hline
+     \hline
+   \end{tabular}
+   \normalsize
+   \begin{tablenotes}
+   \footnotesize
+    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
+   \end{tablenotes}
+   \end{threeparttable}
+   \label{Ratio_MRE}
+% \vspace{-1ex}
+ \end{table*}
+
+\begin{table*}[htbp]
+ %\vspace{-2ex}
+ %% increase table row spacing, adjust to taste
+   \renewcommand{\arraystretch}{1.05}
+   \setlength{\tabcolsep}{3.5pt}
+   \caption{Frequency Speedups in Overclocking Scenario Under Various Error Budgets.}
+%   \vspace{-2ex}
+   \label{Exp_Real_Inputs}
+   \centering
+   \footnotesize
+   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
+     \hline
+     \hline
+     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
+     \multicolumn{2}{c|}{\textbf{FIR}} &
+     \multicolumn{2}{c|}{\textbf{Sobel}} &
+     \multicolumn{2}{c|}{\textbf{IIR}} &
+     \multicolumn{2}{c|}{\textbf{Butterworth}} &
+     \multicolumn{2}{c||}{\textbf{DCT4}} &
+     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
+     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
+     & {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena  }
+     & {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena }\\
+     \hline
+     0.05 & 4.76\%&	21.43\%&	 6.82\%&	6.82\%&	0.95\%&	 1.26\%&	12.40\%&	 24.03\%&	 0.72\%&	 0.96\%  &3.07\%    &5.32\%\\
+     0.5  & 19.05\%&	21.43\%&	 13.64\%&	6.82\%&	0.63\%&	 10.06\%&	24.03\%&	 24.03\%&	0.48\%&	 12.44\%   &4.52\% &13.45\%\\
+     1    & 19.05\%&	28.57\%&	 13.64\%&	18.18\%&	 10.06\%&	16.35\%&	 24.03\%&	 24.03\%&	 0.48\%&	 12.44\%    &7.86\% &19.10\%\\
+     5    & 19.15\%&	25.53\%&	 18.18\%&	18.18\%&	 0.54\%&	0.82\%&	 0.63\%&	 0.94\%&	 7.66\%&	 12.44\%    &3.91\%    &5.36\%\\
+     10   & 19.15\%&	25.53\%&	 10.64\%&	10.64\%&	 0.54\%&	1.09\%&	 6.92\%&	 13.21\%&	 4.91\%&	 4.911\%    &5.19\%    &7.19\%\\
+     20   & 19.15\%&	25.53\%&	 5.77\%&	15.39\%&	 8.70\%&	8.70\%&	 3.26\%&	 3.26\%&	 6.70\%&	 10.88\%    &7.32\%    &10.39\%\\
+     50   & 15.69\%&	15.69\%&	 10.53\%&	19.30\%&	 42.50\%&	50.00\%&	 46.74\%&	 54.89\%&	 15.06\%&	 19.25\%    &21.8\% &27.59\%\\
+     \hline
+     \hline
+   \end{tabular}
+   \normalsize
+   \label{Max_Frequency}
+%   \vspace{-3ex}
+ \end{table*}
+
+Table~\ref{Max_Frequency} illustrates the frequency speedups for each design when the specified error tolerance varies from 0.05\% to 50\%.
+For all designs, we see that the overclocking scenario still outperforms the traditional scenario for each MRE budget in terms of operating frequency.
+Likewise, the frequency speedup is higher for real image inputs than uniform inputs.
+The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
+
+\section{Conclusion}
+The conclusion goes here.
+
+\section*{Acknowledgment}
+The authors would like to acknowledge the support of the EPSRC (Grants EP/I020557/1 and EP/I012036/1).
 
@@
 %
-%If the available area is large enough, as shown in Fig.xxx, CSA with higher stage numbers can be implemented with full precision and it is the optimal design choice unless very high frequencies are applied.
-This is because at lower frequencies, the long carry chain is divided into multiple overlapped sections, and the higher stage number the shorter the carry chain length of each stage.
-When the frequency increases, however, the multiplexer delay becomes comparable to the carry chain delay, and this will limit the maximum word-length of CSA.
-It can be seen that the overclocked RCA achieves best accuracy at higher frequencies.
-
-%For a tighter area budget, only part of the complex structures can be implemented, whilst the simple structure still keeps full precision.
-As can be seen in Fig.xxx and Fig.xxx, area instead of timing becomes the dominate factor when frequency is initially increased.
-This lead to a large truncation error for both 2-stage and 3-stage CSA.
-In this situation, overclocking RCA serves as the optimum choice with respect to accuracy.
-
-%In general, the error expectations at the output of all four design method for a set of timing and area constraints are demonstrated in Fig.~\ref{Tradeoff}, from which several observations can be made.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
+
 %\begin{figure}[!t]
@@
 %\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
 
@@
 %
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
 
@@
 
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals use top floats exclusively.
-% Note that, LaTeX2e, unlike IEEE journals, places footnotes above bottom
-% floats. This can be corrected via the \fnbelowfloat command of the
-% stfloats package.
-
-\section{Conclusion}
-The conclusion goes here.
-
-% use section* for acknowledgement
-\section*{Acknowledgment}
-
-The authors would like to thank...
-
-% Can use something like this to put references on a page
-% by themselves when using endfloat and the captionsoff option.
-\ifCLASSOPTIONcaptionsoff
-  \newpage
-\fi
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
 % references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-\begin{thebibliography}{1}
-
-\bibitem{IEEEhowto:kopka}
-H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-\end{thebibliography}
+\bibliographystyle{./IEEEtran}
+\bibliography{./IEEEabrv,./Reference}
 

### 2013-04-21 TCAD2013/overclocking_tcad.tex
Add Area Tables

@@
 \subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, the carry select adder (CSA) is designed to shorten the carry chain by overlapping carry propagation in sections such that the operating speed can be boosted.
-The structure of a CSA is presented in Fig.~\ref{Fig_CSA_Structure}.
-In a CSA, the carry chain is divided into multiple stages.
+Since the delay of RCA is determined by the length of carry chain, the parallel adder architectures, such as carry select, carry look-ahead and Kogge-Stone adders, are proposed to boost the performance.
+For instance, the carry select adder (CSA) is designed with a carry chain being divided and overlapped in sections such that the operating speed can be largely increased.
+The structure of a CSA is shown in Fig.~\ref{Fig_CSA_Structure}.
+There are multiple stages within a CSA.
 Each stage contains two RCAs and two multiplexers, as seen in Fig.~\ref{Fig_CSA_SingleStage}.
-For a given input, two computations are performed simultaneously where the carry input is zero and one respectively.
+For a given input, two additions are performed simultaneously where the carry input is zero and one respectively.
 One of these two results is then selected according to the actual carry input.
-Although this structure brings timing benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
+Although this structure brings performance benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
 Furthermore, in FPGA technology, multiplexers are expensive.
@@
         \subfigure[The structure diagram of a CSA with $s$ stages.]{
-            \includegraphics[width=\textwidth]{./Figures/CSA_structure.pdf}
+            \includegraphics[width=0.95\textwidth]{./Figures/CSA_structure.pdf}
             \label{Fig_CSA_Structure}
-        }\vspace{-3ex}
+        }\vspace{-2ex}
         \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
@@
 
-\subsection{Model Verification}
-%As seen in (\ref{CSA_Timing}), the value of $\mu_{mux}/\mu_c$ should be determined before applying the timing model.
-This ratio can be obtained through timing analysis instead of experiments.
-Specifically, varying the word-length of a single stage $n_i$ and recording the corresponding delay value $d_i$ from the timing analysis tool.
-According to~(\ref{CSA_SingleStageDelay}), the ratio can be obtained by fitting those values using linear polynomials.
-
+%\subsection{Model Verification}
 %Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
@@
 It can be seen that the the modeled value match well with the experimental results.
-The ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
+
+%
+%\begin{figure}[thbp]
+%  \centering
+%  \includegraphics[width=3in]{./Figures/Model.eps}
+%  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
+%  \label{CSA Model Verification}
+%\end{figure}
+
+\subsection{Accuracy Benefits and Area Overhead in CSA}
+We first verify the models for RCA and CSA in terms of the maximum word-length under the given operating frequencies.
+For the CSA, the ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
 We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
 The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$).
-Then the total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
-In addition, the maximum word-length of the 2-stage CSA is obtained experimentally by increasing $n_{CSA}$ until errors are observed at the output.
-The comparison between the modeled value and the empirical results of $n_{CSA}$ is illustrated in Fig.~(\ref{CSA Model Verification}).
-It can be seen that our model match well with the experimental results.
-%
-\begin{figure}[htbp]
-  \centering
-  \includegraphics[width=3in]{./Figures/Model.eps}
-  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
-  \label{CSA Model Verification}
+The total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
+In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output.
+The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA3stage_Timing} with dotted lines.
+It can be seen that our models for both RCA and CSA match well with the experimental results.
+
+\begin{figure}[tbp]
+    \begin{minipage}[b]{0.48\textwidth}
+        \centering
+        \subfigure[The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
+            \centering
+            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Model_Timing.eps}
+            \label{Fig_CSA3stage Timing}
+        }
+        \subfigure[Hardware resource usage for RCA and CSA with 2 and 3 stages.]{
+            \centering
+            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Area.eps}
+            \label{CSA3stage Area}
+        }
+    \end{minipage}
+    \centering
+    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
 \end{figure}
 
-\subsection{Accuracy Benefits and Area Overhead in CSA}
 As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{CSA3stage Timing}.
@@
 In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
-\begin{figure}[tbp]
-    \begin{minipage}[b]{.48\textwidth}
-        \centering
-        \subfigure[Maximum word-length.]{
-            \includegraphics[width=3.3in]{./Figures/CSA3stage_Timing.eps}
-            \label{CSA3stage Timing}
-        }
-        \subfigure[Hardware resource usage.]{
-            \includegraphics[width=3.3in]{./Figures/CSA3stage_Area.eps}
-            \label{CSA3stage Area}
-        }
-    \end{minipage}
-    \centering
-    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
-\end{figure}
 
@@
 
-First, suppose the designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+First, suppose the algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
 That is, a pair of $\{Area, Frequency\}$ constraint is applied.
-In this case, the optimum design method is selected based on the following criteria:
+In this case, the optimum design method can be selected based on the following criteria:
 \begin{itemize}
@@
 
-For instance let the available LUTs number be 25, the accuracy with respect to different operating frequencies for both design scenarios are presented in Fig.~(\ref{CSA_LUT25}), on which the optimum design metric is labeled.
+For instance let the available LUTs number be 25, then the accuracy with respect to different operating frequencies for both design scenarios are presented in Fig.~\ref{CSA_LUT25}, on which the optimum design metric is labeled.
 Note that the accuracy is defined in terms of the error expectation at the output.
-\begin{figure}[ht]
+In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which is uniformly distributed.
+\begin{figure}[th]
   \centering
   \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
-  \caption{A comparison between two design scenarios when the number of LUT is set to 25.
+  \caption{A comparison between two design scenarios when the number of available LUT is 25.
 The RCA and CSA are investigated in the conventional scenario, while the RCA is explored in the proposed new scenario.
-The results are obtained from post place-and-route simulations on Xilinx Virtex FPGAs.}
+The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
   \label{CSA_LUT25}
@@
 
-To sum up, it can be seen that for both design goals, CSA is the best option only when there is enough hardware resources.
+To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources.
 However this circumstance is unlikely to happen, especially with the continued technology scaling nowadays.
@@
 
-According to Fig.~\ref{FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as expected by our models.
+According to Fig.~\ref{FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as the analytical model validates.
 In addition, we see that using real data, more significant reduction of MRE are achieved, and that no errors are observed when frequency is initially increased.
@@
 The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
+
+\subsection{Area Overhead}
+\begin{table*}[htbp]
+ %\vspace{-2ex}
+ %% increase table row spacing, adjust to taste
+   \renewcommand{\arraystretch}{1.05}
+   \setlength{\tabcolsep}{3.5pt}
+   %\caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
+   \caption{Area Overhead of Out Approach with respect to Given Frequency Requirements}
+%   \vspace{-2ex}
+   \centering
+   \footnotesize
+   %\vspace{-4mm}
+   \begin{threeparttable}
+   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
+     \hline
+     \hline
+     \multirow{2}*{\begin{tabular}{c}\textbf{Normalized}\\\textbf{Frequency}\end{tabular}} &
+     \multicolumn{2}{c|}{\textbf{FIR}} &
+     \multicolumn{2}{c|}{\textbf{Sobel}} &
+     \multicolumn{2}{c|}{\textbf{IIR}} &
+     \multicolumn{2}{c|}{\textbf{Butterworth}} &
+     \multicolumn{2}{c||}{\textbf{DCT4}} &
+     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
+     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
+     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
+     \hline
+     1.04 & 1.24	& 1.05  & 1.12 &	1.22 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.13 &	 1.00 & 1.18 & 1.15\\
+     1.08 & 1.24	& 1.05	& 1.03 &	1.08 &	 1.26 &	1.42 &	 1.16 &	 1.11 &	 1.11 &	 1.15 & 1.16 & 1.16\\
+     1.12 & 1.24	& 1.05   & 1.03 &	1.08 &	 1.26 & 1.42 &	 1.37 &	1.54  &	 2.30 &	 2.17 & 1.38 & 1.40\\
+     1.16 & 2.95	& 2.56   & 1.03 &	1.08 &	 1.61 & 1.71 &	 1.99 &	 2.03  &	 4.60 &	 2.89 &2.14 & 1.95\\
+     1.20 & 2.95	& 2.56   & 1.66 &	1.39 &	 2.77 &	3.48 &	3.17 &	 3.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 2.56 & 2.57 \\
+     1.24 & 4.42	& 3.15  & 4.00 &	3.55 &	 7.87 &	6.73 &	6.92 &	 5.25  &	 N/A\tnote{*}	  & N/A\tnote{*} & 5.57 & 4.46\\
+     1.28 & 4.42	& 3.15   & 4.00 &	3.55 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	6.92 &	 5.25  &	N/A\tnote{*}	  & N/A\tnote{*} & 4.97& 3.89\\
+     1.32 & 4.42	& 3.15   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 4.42	& 3.15 \\
+     \hline
+     \hline
+   \end{tabular}
+   \normalsize
+   \begin{tablenotes}
+   \footnotesize
+    \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
+   \end{tablenotes}
+   \end{threeparttable}
+   \label{Ratio_MRE}
+% \vspace{-1ex}
+ \end{table*}
+
+ \begin{table*}[htbp]
+ %\vspace{-2ex}
+ %% increase table row spacing, adjust to taste
+   \renewcommand{\arraystretch}{1.05}
+   \setlength{\tabcolsep}{3.5pt}
+   %\caption{Frequency Speedups in Overclocking Scenario Under Various Error Budgets.}
+   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
+%   \vspace{-2ex}
+   \label{Exp_Real_Inputs}
+   \centering
+   \footnotesize
+   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
+     \hline
+     \hline
+     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
+     \multicolumn{2}{c|}{\textbf{FIR}} &
+     \multicolumn{2}{c|}{\textbf{Sobel}} &
+     \multicolumn{2}{c|}{\textbf{IIR}} &
+     \multicolumn{2}{c|}{\textbf{Butterworth}} &
+     \multicolumn{2}{c||}{\textbf{DCT4}} &
+     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
+     %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
+     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
+     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
+     \hline
+     0.05 & 1.00&	1.00& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00  &1.00  &  1.00\\
+     0.5  & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
+     1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
+     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.18    &1.18\\
+     10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
+     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &11.78\\
+     50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\
+     \hline
+     \hline
+   \end{tabular}
+   \normalsize
+   \label{Max_Frequency}
+%   \vspace{-3ex}
+ \end{table*}
 

### 2013-04-23 TCAD2013/overclocking_tcad.tex
Modified CSA v5

@@
 
-Summing up $n_i$ gives the total word-length of the CSA in (\ref{CSA_WL}).
+Sum up $n_i$ to give the total word-length of the CSA in (\ref{CSA_WL}).
 %The total word-length of the CSA is the sum of every stage, as given by (\ref{CSA_WL}).
@@
 
-Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of a given timing constraint, as presented in~(\ref{CSA_Timing}).
+Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of $b$, as presented in~(\ref{CSA_Timing}).
 % we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
@@
             \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Model_Timing.eps}
-            \label{Fig_CSA3stage Timing}
+            \label{Fig_CSA3stage_Timing}
         }
@@
             \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Area.eps}
-            \label{CSA3stage Area}
+            \label{Fig_CSA3stage_Area}
         }
@@
 
-As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{CSA3stage Timing}.
-It can be seen from Fig.~\ref{CSA3stage Timing} that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
+As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{Fig_CSA3stage_Timing}.
+It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
 RCA only outperforms than CSA when very high frequency is applied.
@@
 However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
-Fig.~\ref{CSA3stage Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
+Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
 It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
@@
 
-\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-In Section~\ref{section_RCA}, we have discussed two design scenarios when considering timing constraints.
+%\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
+\section{The Optimum Adder Structure}
+In Section~\ref{section_RCA}, we have discussed two design scenarios in RCA when considering timing constraints.
 In this section, we expand our analysis by incorporating the silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures.
@@
 We select the optimum design methodology for both situations.
-
-First, suppose the algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
+\subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
+First, suppose the algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage.
 That is, a pair of $\{Area, Frequency\}$ constraint is applied.
@@
 \begin{itemize}
-  \item Design with the best accuracy at outputs is the optimum design;
+  \item Design with the minimum value of errors at outputs is the optimum design;
   \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
-  \item If the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
+  \item If both the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
 \end{itemize}
 
-For instance let the available LUTs number be 25, then the accuracy with respect to different operating frequencies for both design scenarios are presented in Fig.~\ref{CSA_LUT25}, on which the optimum design metric is labeled.
-Note that the accuracy is defined in terms of the error expectation at the output.
-In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which is uniformly distributed.
+For instance, we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios, when the number of the available LUTs is set to 25.
+The experimental results are shown in Fig.~\ref{CSA_LUT25}, on which the optimum adder structure is labeled.
+In the following experiments within this section, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.
+% sampled from a 16-bit data set, which is uniformly distributed.
 \begin{figure}[th]
@@
 
-We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models in Section~\ref{section_RCA_Comparison}.
-It can also be observed that CSA cannot be implemented with full word-length due to the limited area budget, and this leads to large truncation errors initially for CSA.
+We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for RCA in Section~\ref{section_RCA_Comparison}.
+It can also be observed that CSA cannot be implemented with the original word-length due to the limited area budget, and this leads to large truncation errors initially.
 
 We then perform the similar experiments with a variety of area constraints.
-The optimum design method with respect to different operating frequencies and area consumptions is demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}.
+The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}.
 From this figure, several observations can be made.
-If the available area is large enough to implement a CSA in full precision, it will be the optimum design.
-This is expected from our earlier analysis in Fig.~\ref{CSA3stage Timing}.
-The 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
-For a tighter area budget, only part of the CSA can be implemented, whereas the RCA still keeps full precision.
+Firstly, if the available area is large enough to implement a CSA in full precision, it will be the optimum design.
+This is expected from our earlier analysis in Fig.~\ref{Fig_CSA3stage_Timing}.
+Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
+Thirdly, only part of the CSA can be implemented if under a tighter area budget, whereas the RCA still keeps full precision.
 In this case, area becomes the dominate factor and precision is lost for the CSA.
-We see the RCA with overclocking is the optimum design method across almost the whole frequency domain.
-For a more stringent area constraint, the word-length of RCA is also limited.
+We see the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
+Last but not the least, for a more stringent area constraint, the word-length of RCA is also limited.
 This results in truncation errors initially for all design scenarios.
@@
 
-Similarly if the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
-In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as presented in~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+\subsection{Determination of the Optimum Adder Structure for Given Accuracy Requirements}
+If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
+In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as fiben by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
 \begin{eqnarray}\label{MRE}
@@
 In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
-For a certain MRE, the design with the maximum operating frequencies is selected as the optimum design.
+For a certain value of MRE, the design with the maximum operating frequencies is selected as the optimum design.
 Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement.
@@
 Once again, when the area budget shrinks, the RCA performs best because the precision of the CSA is limited.
-Similarly to the previous section, we see that the overclocked RCA achieves the fastest operating frequencies under most area constraints when the accuracy requirement is released.
-
+Similarly to the results in Fig.~\ref{Fig_CSA_Tradeoff}, we see that the overclocked RCA achieves the fastest operating frequencies under most area constraints when the accuracy requirement is released.
+
+\subsection{Design Guidance}
 To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources.
-However this circumstance is unlikely to happen, especially with the continued technology scaling nowadays.
+However this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays.
 Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.
@@
 
-\subsection{Evaluation Metric of Outputs}
-The results are evaluated in terms of mean relative error (MRE), which represents the percentage of error at outputs.
+%\subsection{Evaluation Metric of Outputs}
+%The results are evaluated in terms of mean relative error (MRE), which represents the percentage of error at outputs.
 MRE is given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the correct output respectively.
-%
-\begin{eqnarray}\label{MRE}
-%\small
-\scriptsize
-  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
-\end{eqnarray}
-\normalsize
+%%
+%\begin{eqnarray}\label{MRE}
+%%\small
+%\scriptsize
+%  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
+%\end{eqnarray}
+%\normalsize
 
@@
    %\caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
-   \caption{Area Overhead of Out Approach with respect to Given Frequency Requirements}
+   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
 %   \vspace{-2ex}
@@
      1    & 1.02&	1.15& 1.00&	1.00& 1.00&	 1.00&	1.00&	 1.00&	1.00&	 1.00   &1.00 &1.03\\
-     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.18    &1.18\\
+     5    & 1.24&	1.05& 1.00&	1.00& 1.26&   1.42&   1.65&   1.11&	 1.00&    1.00   &1.13    &1.11\\
      10   & 1.24&	1.05& 1.12&	1.22& 1.26&	1.42& 1.65&	1.11& 1.11&	 1.15&    1.18    &1.18\\
-     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &11.78\\
+     20   & 1.24&	1.05& 1.03&	1.08& 1.26&	1.42& 6.92&	 5.25&   3.45&	 2.17   &2.07    &1.79\\
      50   & 2.95&	2.56& 4.00&	3.55& 7.87&	6.73& 6.92&	 5.25&   3.45&	 2.12	&4.67 &3.70\\

### 2013-04-24 TCAD2013/overclocking_tcad.tex
Modified CSA, revised by David v2

@@
 \subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, the parallel adder architectures, such as carry select, carry look-ahead and Kogge-Stone adders, are proposed to boost the performance.
-For instance, the carry select adder (CSA) is designed with a carry chain being divided and overlapped in sections such that the operating speed can be largely increased.
-The structure of a CSA is shown in Fig.~\ref{Fig_CSA_Structure}.
+Since the delay of RCA is determined by the length of carry chain, alternative adder architectures, such as carry select adder (CSA) have been proposed to boost performance.
+For CSA, the carry chain is divided into multiple overlapped sections to increase the operating speed, as shown in Fig.~\ref{Fig_CSA_Structure}.
 There are multiple stages within a CSA.
@@
 Furthermore, in FPGA technology, multiplexers are expensive.
-Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of these two adder structures in this section.
+Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of RCA and CSA in this section.
 
@@
     \centering
-    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
+    \caption{The structure diagram of CSA.}
 \end{figure}
@@
 \subsection{Timing Models for Carry Select Adder}
-We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
+We initially model the CSA in order to understand the relationship between the operating frequency and maximum word-length of the CSA.
 This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.
 
-In a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1}~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
-In our analysis, we follow the assumption that the critical path delay is due to carry propagation and multiplexing the carry output.
-Note that unlike other stages, the least significant stage is only built by one RCA without multiplexers, since it is directly driven by the carry input.
-Hence we obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
+%In a CSA, the stage delay refers to the combination of the carry propagation delay and the delay of multiplexing the carry output of the giv stage.
+
+In our analysis, the stage delay of stage $i$ in the CSA refers to the combination of the $i$-bit carry propagation delay and the delay of multiplexing the carry output.
+For a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
+We still follow the aforementioned assumption that the critical path delay of the CSA is due to carry propagation and multiplexing the carry output, instead of generating the sum outputs.
+It should be noted that unlike other stages, the least significant stage of the CSA is only built by one RCA without multiplexers, since it is directly driven by the carry input.
+Hence we can obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
 \begin{eqnarray}\label{CSA_SingleStageDelay}
@@
   \begin{matrix}
-    d_i\leqslant\frac{1}{f_s} &, & \forall i\in[0,s-1]
+    \forall i\in[0,s-1] &, & d_i\leqslant\frac{1}{f_s}
   \end{matrix}
@@
 \subsection{Accuracy Benefits and Area Overhead in CSA}
-We first verify the models for RCA and CSA in terms of the maximum word-length under the given operating frequencies.
-For the CSA, the ratio $\mu_{mux}/\mu_c$ can be computed from experiments.
+We first verify the models for the RCA and CSA in terms of the maximum word-length under the given operating frequencies.
+For the CSA, the ratio $\mu_{mux}/\mu_c$ can be computed experimentally.
 We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
-The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths of this given stage ($n_i$).
+The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths.
 The total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
 In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output.
-The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA3stage_Timing} with dotted lines.
+The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA2stage_Timing} with dotted lines.
 It can be seen that our models for both RCA and CSA match well with the experimental results.
@@
             \centering
-            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Model_Timing.eps}
-            \label{Fig_CSA3stage_Timing}
+            \includegraphics[width=0.95\textwidth]{./Figures/CSA2stage_Model_Timing.eps}
+            \label{Fig_CSA2stage_Timing}
         }
@@
 
-As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in Fig.~\ref{Fig_CSA3stage_Timing}.
-It can be seen that in comparison to RCA, CSA achieves greater word-length when frequency is initially increased.
-RCA only outperforms than CSA when very high frequency is applied.
+%As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in
+
+Fig.~\ref{Fig_CSA2stage_Timing} also highlight that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
+The RCA only outperforms than the CSA when very high frequency is applied.
 This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
 However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
-In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
+%In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
 
 However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
-Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for all three structures.
+Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for a RCA, a 2-stage CSA and a 3-stage CSA.
 It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
@@
 %\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-\section{The Optimum Adder Structure}
-In Section~\ref{section_RCA}, we have discussed two design scenarios in RCA when considering timing constraints.
-In this section, we expand our analysis by incorporating the silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures.
+\section{Choosing the Optimum Adder Structure}
+In Section~\ref{section_RCA}, we discussed two design scenarios for the RCA when considering timing constraints.
+In this section, we expand our analysis by incorporating silicon area as another evaluation metric, and investigate the accuracy, performance and area trade-offs for different adder structures.
 In the conventional design scenario, the word-length of RCA and CSA is limited by the given frequency constraint, or/and the available hardware resources.
 The precision loss potentially generates large errors even without timing violations.
-However in the new design scenario, we use RCA with the maximum possible word-length under the given area budget, and the timing constraints are allowed to be violated.
+However in the new design scenario, we use the RCA with the maximum possible word-length under the given area budget, and the timing constraints are allowed to be violated.
 This process might result in timing errors as well as truncation errors due to area limitation.
-We compare these two scenarios with different design goals, with the aim of targeting the optimum design methodology under each situation.
+We compare these two scenarios with different design goals with the aim of finding the optimum design methodology under each situation.
 
@@
 \subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
-First, suppose the algorithm designer would wish to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage.
-That is, a pair of $\{Area, Frequency\}$ constraint is applied.
-In this case, the optimum design method can be selected based on the following criteria:
+First, suppose the algorithm designer wished to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage, i.e.
+a pair of $\{Area, Frequency\}$ constraint is applied.
+In this case, the optimum design method is selected according to the following criteria:
 \begin{itemize}
-  \item Design with the minimum value of errors at outputs is the optimum design;
+  \item Design with the minimum mean value of errors at the output is the optimum design;
   \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
@@
 
-For instance, we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios, when the number of the available LUTs is set to 25.
-The experimental results are shown in Fig.~\ref{CSA_LUT25}, on which the optimum adder structure is labeled.
-In the following experiments within this section, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.
-% sampled from a 16-bit data set, which is uniformly distributed.
+For instance, in Fig.~\ref{Fig_CSA_LUT25} we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios when the number of the available LUTs is set to 25.
+In this graph, we have labeled the optimum adder structure.
+Note that in this and all the following experiments within this section, in order to apply our models the input data is randomly generated following the uniform distribution.
+
+%, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.
+
 \begin{figure}[th]
@@
 The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
-  \label{CSA_LUT25}
+  \label{Fig_CSA_LUT25}
 \end{figure}
 
-We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for RCA in Section~\ref{section_RCA_Comparison}.
-It can also be observed that CSA cannot be implemented with the original word-length due to the limited area budget, and this leads to large truncation errors initially.
-
-We then perform the similar experiments with a variety of area constraints.
+We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}.
+It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
+Although CSA with 3 stages outperforms temporarily when frequency is further increased, the overclocked RCA is still the optimum design when high operating frequencies are applied.
+
+We then perform similar experiments with a variety of area constraints.
 The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}.
@@
 Firstly, if the available area is large enough to implement a CSA in full precision, it will be the optimum design.
-This is expected from our earlier analysis in Fig.~\ref{Fig_CSA3stage_Timing}.
-Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both of them achieve the same error expectation.
-Thirdly, only part of the CSA can be implemented if under a tighter area budget, whereas the RCA still keeps full precision.
-In this case, area becomes the dominate factor and precision is lost for the CSA.
-We see the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
+This is expected from our earlier analysis in Fig.~\ref{Fig_CSA2stage_Timing}.
+Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both achieve the same error expectation.
+Thirdly, only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision.
+In this case, area becomes the dominate factor and precision is lost for the CSA, meaning the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
 Last but not the least, for a more stringent area constraint, the word-length of RCA is also limited.
 This results in truncation errors initially for all design scenarios.
-However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than CSA under the same area constraint.
+However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than the CSA under the same area constraint.
+
 \begin{figure}[t]
@@
 If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
-In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as fiben by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
 \begin{eqnarray}\label{MRE}
@@
 In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
-For a certain value of MRE, the design with the maximum operating frequencies is selected as the optimum design.
+For a certain value of MRE, the design with the maximum operating frequency is selected as the optimum design.
 Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement.
@@
 To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources.
-However this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays.
+However for the remainder of this paper, we are interested in cases where there is a limited area budget, as may be the case in the embedded applications.
+Due to this reason, we will focus on the RCA in our following analysis and experiments.
+
+%this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays.
 Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.

### 2013-05-09 TCAD2013/overclocking_tcad.tex
Introduction&Background Section v1

@@
 
-\title{Imprecise Computing in Datapath Design: Precision Loss or Timing Violations}
+\title{Imprecise Computing in Datapath Design: An Overclocking Approach}
+%Imprecise Computing in Datapath Design: Precision Loss or Timing Violations}
 %Imprecise Datapath Design: An Overclocking Approach
@@
 % and "HIS" in caps to complete the first word.
-\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-for IEEE journal papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8 and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
-
-\hfill mds
-
-\hfill December 27, 2012
-
-\subsection{Subsection Heading Here}
-Subsection text here.
-
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
+%for IEEE journal papers produced under \LaTeX\ using
+%IEEEtran.cls version 1.8 and later.
+%% You must have at least 2 lines in the paragraph with the drop letter
+%I wish you the best of success.
+
+\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, as CMOS technology continues to shrink to the nanometer regime.
+However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
+Traditionally, hardware designers employ safety margins to ensure a uniform functionality across a variety of possible working environments.
+However, there are two major problems if we keep using this approach.
+One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic behavior.
+The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss.
+
+In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
+In this case, designers tend to employ multi-core systems, heterogeneous platforms and massive parallel accelerators (such as FPGAs) to sustain the performance scaling.
+
+Specifically, large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications.
+However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs.
+Furthermore, timing analysis tools typically report a very conservative clock frequency for ``safe'' operations.
+This substantially limits the potential performance of the device to a further extent.
+
+In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath.
+For the former method, pipelining will not tend to reduce the circuit latency.
+Actually the latency in terms of clock cycles will increase.
+As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in datapath containing feedback where C-slow retiming is inappropriate.
+For the second approach, reducing the datapath precision would subtract out the latency, but at the cost of introducing quantization errors into the design.
+For hardware platforms such as FPGAs or ASICs, research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification has been an extensive topic~\cite{GeorgeDT11}, as it is possible to use a number system with customized precisions on these platforms.
+A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.
+
+Unfortunately, neither of the conventional approaches tends to remove the conservative safety margin.
+In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}.
+The detailed review of this research area will be presented in Section~\ref{Section_Background_Imprecise}.
+
+In this paper, we describe an alternative circuit design methodology when considering performance-accuracy-area tradeoffs.
+We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
+Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
+This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric for the trade-offs.
+Based on this premise, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e.
+binary adders) under various design constraints.
+A summary of the main contributions of this work are as follows:
+
+The rest of this paper is organized as follows.
+It first reviews in detail the current literature regarding the existing approaches that are used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
+The analytical error models for two different adder structures: RCA and CSA, are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively.
+The decision of the optimum adder structure under the accuracy-performance-area trade-offs, is then put forward in Section~\ref{Section_OptimumAdder}.
+It is followed by a description of the probabilistic error models for CCM in Section~\ref{section_CCM}.
+Section.xxx discusses a practical experimental setup to verify our models and test the proposed design methodology.
+The demonstration of the benefits of our proposed approach is then demonstrated in Section.xxx.
+Finally, Section.xxx discusses the conclusions of this work and the possible research directions in the future.
+
+\section{Background}\label{Section_Background}
+\subsection{Word-length Optimization}\label{Section_Background_WL}
+There exists a significant amount of work demonstrating that optimizing the precision used throughout the datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
+As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification.
+Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach including interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
+A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.
+
+\subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
+However, the choice of precision is not the only source of errors when designing a datapath.
+Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for performance or energy efficiency.
+This strand of research is motivated by the fact that it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.
+
+To address this problem, the international technology roadmap for semiconductors (ITRS07) pointed out that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects~\cite{semiconductor2007international}.
+This topic is expected to be of growing importance in the future, because we will face new challenges as the technology scales further.
+
+According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases.
+Research in this area is based on the observations that in practice, the worst case happens rarely.
+A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}.
+In general, a BTWC design is composed of cores and checkers.
+The cores are operated with high performance by eliminating the conservative guard-bands, while the possible timing errors are diagnosed by the checkers.
+Optionally the system can be recovered at the observation of errors.
+As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit.
+This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors.
+For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively.
+Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA} or xxx.
+
+Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns.
+Meanwhile, many studies have shown that errors can be potentially tolerated in various applications, e.g.
+DSP applications concerning human perceptions.
+In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
+Current research in this area is focusing on designing ``probabilistic circuits'' that employ techniques from either software level or hardware level.
+For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into precise part and approximate part, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
+This technique enables a relatively high service quality, in the meantime energy reduction can be obtained due to approximation.
+Similar ideas have also been applied on hardware directly.
+As an example, Palem et~al.~\cite{NonUniformScaling} described a non-uniform voltage scaling technique for the ripple carry adder.
+In this study, multiple voltage regions are employed for different bits along a carry chain.
+That is, higher voltage would be applied for computations generating most significant bits, and vice versa.
+
+While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further to design a simplified circuit for peformance/energy efficiency.
+For example, Lu et~al.
+proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}.
+Kulkarni et.al.
+described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}.
+In this case, reduction of area and power consumption can be achieved with the cost of accuracy.
+In addition, Gupta et.al.
+developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.
+
+However, the limitations of the existing work cannot be neglected.
+Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed.
+Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms.
+Thirdly, the link between the probability of output correctness and energy savings or performance improvements are not analyzed.
+
+In this work, we propose an alternative methodology to remove these limitations.
+It is argued in this paper that our method can be easily applied onto existing hardware arithmetic operators such as RCAs and CCMs with almost no hardware overhead.
+We support this hypothesis experimentally and analytically by presenting theoretical probabilistic error models.
+
+%, by simply allowing timing violations to happen.
+We compare to the situation where a specific timing requirement is met by reducing datapath precisions.
+Instead of simply performing experiments, we also present analytical models of errors generated due to both timing violation and precision loss.
+
+%In addition, a variety of research aimed at designing imprecise architectures to get rid of the worst cases.
+
+%such as non-uniform voltage scaling or imprecise architectures for computations.
+
+%achieving a uniform circuit performance and 100\% accuracy becomes increasingly difficult and expensive, especially when technology shrinks to the nanometer regime.
+
 \section{Ripple Carry Adder}\label{section_RCA}
@@
   %  \vspace{-2ex}
-  \caption{An $n$-bit ripple carry adder in Virtex-6 FPGA.}
+  \caption{An $n$-bit ripple carry adder in the Xilinx Virtex-6 FPGA.}
   \label{FPGA adder}
@@
 
-\section{Carry Select Adder}
+\section{Carry Select Adder}\label{Section_CSA}
 \subsection{Introduction}
@@
 In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output.
-The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA2stage_Timing} with dotted lines.
+The comparison between the modeled value and the empirical results is illustrated in Fig.~\ref{Fig_CSA2stage_Timing}.
 It can be seen that our models for both RCA and CSA match well with the experimental results.
@@
         }
-        \subfigure[Hardware resource usage for RCA and CSA with 2 and 3 stages.]{
+        \subfigure[Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
             \centering
@@
 
-Fig.~\ref{Fig_CSA2stage_Timing} also highlight that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
+Fig.~\ref{Fig_CSA2stage_Timing} also highlights that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
 The RCA only outperforms than the CSA when very high frequency is applied.
@@
 However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
-Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for a RCA, a 2-stage CSA and a 3-stage CSA.
+Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for an RCA, a 2-stage CSA and a 3-stage CSA.
 It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
@@
 
-%\subsection{Exploring Trade-offs Between Accuracy, Performance and Area}
-\section{Choosing the Optimum Adder Structure}
+\section{Choosing the Optimum Adder Structure}\label{Section_OptimumAdder}
 In Section~\ref{section_RCA}, we discussed two design scenarios for the RCA when considering timing constraints.
@@
 It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
-Although CSA with 3 stages outperforms temporarily when frequency is further increased, the overclocked RCA is still the optimum design when high operating frequencies are applied.
+Although the CSA with 3 stages outperforms temporarily when frequency is further increased, the overclocked RCA is still the optimum design when high operating frequencies are applied.
 
@@
 Furthermore, it is difficult to recover from the latter type of error, since it is generated due to precision loss.
+
+\begin{figure}[tbp]
+    \begin{minipage}[b]{0.48\textwidth}
+        \centering
+        \subfigure[The cumulative distribution function with respect to both type of input data.]{
+            \centering
+            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
+            \label{Fig_CSA2stage_Timing}
+        }
+        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
+            \centering
+            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
+            \label{Fig_CSA3stage_Area}
+        }
+    \end{minipage}
+    \centering
+    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
+\end{figure}
 

### 2013-05-09 TCAD2013/overclocking_tcad.tex
Modified several Figures: CSA and FIR

@@
 \section{Introduction}
-% The very first letter is a 2 line initial drop letter followed
-% by the rest of the first word in caps.
-%
-% form to use if the first word consists of a single letter:
-% \IEEEPARstart{A}{demo} file is ....
-%
-% form to use if you need the single drop letter followed by
-% normal text (unknown if ever used by IEEE):
-% \IEEEPARstart{A}{}demo file is ....
-%
-% Some journals put the first two words in caps:
-% \IEEEPARstart{T}{his demo} file is ....
-%
-% Here we have the typical use of a "T" for an initial drop letter
-% and "HIS" in caps to complete the first word.
-%\IEEEPARstart{T}{his} demo file is intended to serve as a ``starter file''
-%for IEEE journal papers produced under \LaTeX\ using
-%IEEEtran.cls version 1.8 and later.
-%% You must have at least 2 lines in the paragraph with the drop letter
-%I wish you the best of success.
-
-\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, as CMOS technology continues to shrink to the nanometer regime.
+\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, with the continuous scaling of CMOS technology to the nanometer regime.
 However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
-Traditionally, hardware designers employ safety margins to ensure a uniform functionality across a variety of possible working environments.
-However, there are two major problems if we keep using this approach.
-One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic behavior.
-The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss.
-
-In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
-In this case, designers tend to employ multi-core systems, heterogeneous platforms and massive parallel accelerators (such as FPGAs) to sustain the performance scaling.
+Although hardware designers traditionally employ safety margins to ensure a uniform functionality across a variety of possible working environments, there are two major problems if we keep using this approach nowadays.
+One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior.
+The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation.
+
+In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for performance improvement in embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
+In this case, designers tend to employ multi-core processors, heterogeneous systems and massive parallel accelerators to sustain the performance scaling.
 
@@
 However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs.
-Furthermore, timing analysis tools typically report a very conservative clock frequency for ``safe'' operations.
+Furthermore, timing analysis tools typically report a very conservative clock frequency to guarantee ``safe'' operations.
 This substantially limits the potential performance of the device to a further extent.
@@
 In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath.
-For the former method, pipelining will not tend to reduce the circuit latency.
+For the former method, it should be noted that pipelining will not tend to reduce the circuit latency.
 Actually the latency in terms of clock cycles will increase.
@@
 In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}.
-The detailed review of this research area will be presented in Section~\ref{Section_Background_Imprecise}.
-
-In this paper, we describe an alternative circuit design methodology when considering performance-accuracy-area tradeoffs.
+The detailed review of this research field will be presented in Section~\ref{Section_Background_Imprecise}.
+
+In this paper, we describe an alternative circuit design methodology when considering tradeoffs between accuracy, performance and area.
 We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
 Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
-This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric for the trade-offs.
-Based on this premise, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e.
+This paper elaborates on the prior work [xxx], with a further enrichment by incorporating silicon area as another evaluation metric for the trade-offs.
+In this work, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e.
 binary adders) under various design constraints.
@@
 As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification.
-Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach including interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
+Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
 A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.
@@
 \subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
-However, the choice of precision is not the only source of errors when designing a datapath.
-Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for performance or energy efficiency.
-This strand of research is motivated by the fact that it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.
+Note that, however, the choice of precision is not the only source of errors when designing a datapath.
+Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
+This strand of research is motivated by the drastic performance variations introduced by process scaling.
+
+%it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.
 
@@
 In general, a BTWC design is composed of cores and checkers.
-The cores are operated with high performance by eliminating the conservative guard-bands, while the possible timing errors are diagnosed by the checkers.
+The cores are operated with high performance by eliminating the guard-bands, meanwhile the possible timing errors are diagnosed by the checkers.
 Optionally the system can be recovered at the observation of errors.
@@
 In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
-Current research in this area is focusing on designing ``probabilistic circuits'' that employ techniques from either software level or hardware level.
-For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into precise part and approximate part, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
+Current research in this area is focusing on designing probabilistic or imprecise circuits that employ techniques from either software level or hardware level.
+For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
 This technique enables a relatively high service quality, in the meantime energy reduction can be obtained due to approximation.
@@
 
-While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further to design a simplified circuit for peformance/energy efficiency.
+While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance/energy efficiency.
 For example, Lu et~al.
@@
 described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}.
-In this case, reduction of area and power consumption can be achieved with the cost of accuracy.
+In both cases, reduction of area and power consumption can be achieved with the cost of accuracy.
 In addition, Gupta et.al.
@@
 
-However, the limitations of the existing work cannot be neglected.
+However, the limitations of the existing work should not be neglected.
 Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed.
 Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms.
-Thirdly, the link between the probability of output correctness and energy savings or performance improvements are not analyzed.
+More importantly, correct results would never be obtained by using approximate architectures.
+Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
 
@@
     \centering
-    \includegraphics[width=3.5in]{./Figures/Tradeoff_Error.eps}
+    \includegraphics[width=3.7in]{./Figures/Tradeoff_Error.eps}
     \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
@@
 $A_S$ denotes the ``shifted signal", with zeros padded after LSB, while $A_O$ denotes the ``original signal" with MSB sign extension.
-For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Figure~\ref{CCM_fig}.
-\begin{figure}[htbp]
-  \centering
-%  \vspace{-2ex}
-  %\includegraphics[width=3.5in]{./Figures/CCM_DataFlow3.pdf}
-  \includegraphics[width=3.3in]{./Figures/CCM_DataFlow3.eps}
-%  \vspace{-2ex}
-  \caption{Different types of carry chain in constant coefficient multiplier. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
+For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Fig.~\ref{CCM_fig}.
+\begin{figure*}[htbp]
+  \centering
+  \includegraphics[width=0.99\textwidth]{./Figures/CCM_CarryChain.pdf}
+  \caption{Four possible carry chain types in a constant coefficient multiplier with $n$-bit inputs. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
   \label{CCM_fig}
-%  \vspace{-1.5ex}
-\end{figure}
+\end{figure*}
 
@@
 In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length.
-The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA XC6VLX240T-1FFG1156.
+The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA.
+%XC6VLX240T-1FFG1156.
 
@@
 %  \vspace{-2.5ex}
-  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New2.eps}
+  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
 %  \vspace{-5ex}
@@
   \centering
-  \subfigure[425MHz,~n=8~,~no errors observed]{
+  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
   \begin{minipage}[c]{0.24\textwidth}
@@
   }% This is important! use % to indicate same line, otherwise new line
-  \subfigure[430MHz,~n=8,~SNR=47.15dB]{
+  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
   \begin{minipage}[c]{0.24\textwidth}
@@
   }%
-  \subfigure[480MHz,~n=8,~SNR=24.1dB]{
+  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
   \begin{minipage}[c]{0.24\textwidth}
@@
   }%
-  \subfigure[520MHz,~n=8,~SNR=10.86dB]{
+  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
   \begin{minipage}[c]{0.24\textwidth}
@@
   }\vspace{-1ex}
-  \subfigure[425MHz,~n=7,~SNR=26.06dB]{
+  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
   \begin{minipage}[c]{0.24\textwidth}
@@
   }% This is important! use % to indicate same line, otherwise new line
-  \subfigure[430MHz,~n=5,~SNR=24.85dB]{
+  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
   \begin{minipage}[c]{0.24\textwidth}

### 2013-05-10 TCAD2013/overclocking_tcad.tex
Add Section: Area Overhead

@@
 For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively.
-Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA} or xxx.
+Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
 
@@
 Kulkarni et.al.
-described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh Map analysis~\cite{Undersigned2x2multiplier}.
+described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
 In both cases, reduction of area and power consumption can be achieved with the cost of accuracy.
-In addition, Gupta et.al.
+In addition, Gupta et~al.
 developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.
@@
 Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms.
-More importantly, correct results would never be obtained by using approximate architectures.
+More importantly, correct results would never be obtained as long as the approximate architectures were employed.
 Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
@@
   \end{minipage}
-  }\vspace{-1ex}
+  }
   \subfigure[425MHz,~n=7,~SNR=26.02dB]{
@@
 %The results can be interpreted in two folds.
-Our results could be of interest to a circuit designer in two ways.
+As we mentioned in Section~xxx, our results could be of interest to a circuit designer in two ways.
 Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
-In the first case, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
+For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
+
 \begin{eqnarray}\label{Relative Reduction MRE}
-%\small
-\scriptsize
   \frac{MRE_{Trad}-MRE_{ovrc}}{MRE_{Trad}}\times 100\%
 \end{eqnarray}
-\normalsize
-%\vspace{-2ex}
 
@@
 \subsection{Area Overhead}
+For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario.
+Consequently, the area overheads of our approach are summarized in Table xxx and Table xxx for both design goals.
+In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms.
+It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
+
+An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies.
+As seen in Table xxx, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
+Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Tablexxx, because a specific error budget can be tolerated.
+
+In general, we can observe a relatively small area overhead of our approach, especially when frequency is initially increased or with a small error budget (i.e. $\sim10\%$).
+
 \begin{table*}[htbp]
- %\vspace{-2ex}
  %% increase table row spacing, adjust to taste
@@
    \setlength{\tabcolsep}{3.5pt}
-   %\caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
    \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
-%   \vspace{-2ex}
    \centering
    \footnotesize
-   %\vspace{-4mm}
    \begin{threeparttable}
@@
    \label{Ratio_MRE}
-% \vspace{-1ex}
  \end{table*}
@@
  \begin{table*}[htbp]
- %\vspace{-2ex}
  %% increase table row spacing, adjust to taste
@@
    \setlength{\tabcolsep}{3.5pt}
-   %\caption{Frequency Speedups in Overclocking Scenario Under Various Error Budgets.}
    \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
-%   \vspace{-2ex}
    \label{Exp_Real_Inputs}
@@
    \label{Max_Frequency}
-%   \vspace{-3ex}
  \end{table*}
@@
 The authors would like to acknowledge the support of the EPSRC (Grants EP/I020557/1 and EP/I012036/1).
-
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[width=3.3in]{./Figures/Error_LUT45.eps}
-%	\caption{LUT=45}
-%\end{figure}
-%
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[width=3.3in]{./Figures/Error_LUT35.eps}
-%	\caption{LUT=35}
-%\end{figure}
-%
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
-%	\caption{LUT=25}
-%\end{figure}
-%
-%\begin{figure}[htbp]
-%	\centering
-%	\includegraphics[width=3.3in]{./Figures/Error_LUT15.eps}
-%	\caption{LUT=15}
-%\end{figure}
-%
 

### 2013-05-13 TCAD2013/overclocking_tcad.tex
Add Abstract, Modified Figure for Test Framework

@@
 \begin{abstract}
-The abstract.
+As process scaling introduces significant performance variations, releasing the tight accuracy requirement rather than covering all possible worst cases would potentially offer the greater freedom to create a design with better performance or energy efficiency.
+In this paper, we compare two different approaches that could trade accuracy for performance.
+One is the traditional approach where the precision used in the datapath is limited to meet a target latency.
+The other is a proposed new approach to boost the clock frequency by simply allowing the datapath to operate without timing closure.
+We demonstrate analytically and experimentally that on average, our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach, since the worst case caused by timing violations only happens rarely, while the precision loss results in errors to all data.
+We also show that for embedded applications where silicon area is also a limited factor, using the proposed approach on simple arithmetic primitives could achieve better accuracy or performance than using the traditional method on advanced operators.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-
+Overclocking, Imprecise Computing, Numerical Analysis.
 \end{IEEEkeywords}
@@
 It is followed by a description of the probabilistic error models for CCM in Section~\ref{section_CCM}.
-Section.xxx discusses a practical experimental setup to verify our models and test the proposed design methodology.
-The demonstration of the benefits of our proposed approach is then demonstrated in Section.xxx.
-Finally, Section.xxx discusses the conclusions of this work and the possible research directions in the future.
+Section~\ref{Section_ExpSetup} discusses a practical experimental setup to verify our models and test the proposed design methodology.
+The demonstration of the benefits of our proposed approach is then demonstrated in Section~\ref{Section_Experiments}.
+Finally, Section~\ref{Section_Conclusion} discusses the conclusions of this work and the possible research directions in the future.
 
@@
 
-\section{Test Platform}\label{Experiment}
+\section{Test Platform}\label{Section_ExpSetup}
 In our experiments, we compare two design perspectives.
@@
 
-\subsection{Experimental Setup} % (fold)
-\label{sub:experimental_setup}
+\subsection{Experimental Setup} \label{sub:experimental_setup}
 We initially build up a test framework on an FPGA.
@@
   %\vspace{-3.5ex}
-  \includegraphics[width=3.3in]{./Figures/TestFramework2.eps}
+  \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
   %\vspace{-4.5ex}
-  \caption{FPGA Test framework, which is composed of a measurement architecture (the dotted box) and an off-line comparator.}
+  \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software.
+Note that the error-free data are obtained by either pre-computation or initial run with low frequencies.}
   \label{Test Framework}
@@
 %In order to avoid the potential timing errors generated from the test framework instead of CUT under high test frequencies, several methods are adopted.
-Firstly, the control signals for the test frequency generator is triggered by the system clock, which is 33.33MHz in our experiments.
-This will guarantee that the test clock generation will not be affected by high frequencies.
+Firstly, the control signals for the test frequency generator is triggered by the system clock, which is much lower than the test frequency.
+This will guarantee a correct generation of the test clock.
 Secondly, since the address counter for the on-chip memory is driven by the test frequency, a deeply pipelined counter structure with initial delay of 258 cycles is used to ensure the correct sample of each address bit.
@@
 The results will be discarded if mismatch is found.
-% without reimplement the whole design.
-% subsection experimental_setup (end)
-% \subsection{Experimental Results} % (fold)
-% \label{sub:subsubsection_name}
 
@@
   \caption{The maximum operating frequencies for different input word-lengths of an FIR filter.
-The dotted line depicts the rated frequency reported by the Xilinx Timing Analyzer.
+The dotted line depicts the rated frequency reported by the timing analysis tool.
 The solid line is obtained through real FPGA tests using our platform.}
@@
 Initially the maximum error-free frequency $f_0$ is applied.
-In this case we have~(\ref{Eq_decideMu_0}) where $d_c$ is a constant value which denotes the interconnection delay.
+In this case we have~(\ref{Eq_decideMu_0}) where $d_c$ is a constant value which denotes the interconnection delay, and $d_0=1/f_0$.
 The frequency is then increased such that~(\ref{Eq_decideMu_1}) is obtained.
@@
 Based on these frequency values, $\mu$ can be determined.
+
 \begin{eqnarray}\label{Eq_decideMu_0}
-\vspace{-1ex}
-%\small
-%\footnotesize
-\scriptsize
-  f_0 &= n\mu+d_c
-  \vspace{-12ex}
-\end{eqnarray}
-\vspace{-5ex}
+  %\frac{1}{f_0} &= n\mu+d_c
+  d_0 &= n\mu+d_c
+  \vspace{-13ex}
+\end{eqnarray}
+\vspace{-4ex}
 \begin{align}\label{Eq_decideMu_1}
-  f_1 &= (n-1)\mu+d_c    \\
+  d_1 &= (n-1)\mu+d_c    \\
   &\cdots               \notag
@@
 \end{align}
-\vspace{-5.5ex}
+\vspace{-4ex}
 \begin{eqnarray}\label{Eq_decideMu_2}
-  f_{n-1} &= \mu+d_c
-%  \vspace{-2ex}
-\end{eqnarray}
-\normalsize
+  {d_{n-1}} &= \mu+d_c
+\end{eqnarray}
 
@@
 % FIR
-\begin{figure}[htbp]
+\begin{figure}[tbp]
   \centering
@@
   \label{FIR}
-%  \vspace{-1ex}
 \end{figure}
@@
 \label{FIR_Lena}
-%\vspace{-2ex}
 \end{figure*}
@@
 
+In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.xxx.
+As the input data is 8-bit, the longest possible carry chain length is 9-bit.
+It can be observed that when using Lena data,  the probability is only higher for carry chain with a length of 3-bit.
+While in other situations, using uniform data leads to higher probability, especially for long carry chain length.
+This finding explicitly demonstrates that longer carry chains happens with an even smaller probability when utilizing real data.
+
+% for short carry chains (i.e. carry chain length of 2-bit or 3-bit),
+
+%In detail, the difference between the two types of data is explicitly
+
 \begin{figure}[tbp]
-    \begin{minipage}[b]{0.48\textwidth}
-        \centering
-        \subfigure[The cumulative distribution function with respect to both type of input data.]{
-            \centering
-            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
-            \label{Fig_CSA2stage_Timing}
-        }
-        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
-            \centering
-            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
-            \label{Fig_CSA3stage_Area}
-        }
-    \end{minipage}
-    \centering
-    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
+  \centering
+  \includegraphics[width=3.5in]{./Figures/CC_length2.eps}
+  \caption{Probability distribution of different length of carry chains in a 8-bit RCA.
+For the uniform data, two inputs of RCA are randomly sampled from a uniform distribution.
+For the image data Lena, one input of RCA uses the original data and the other uses the delayed original data for several clock cycles.}
+  \label{CarryDistribution}
 \end{figure}
 
-\subsection{Potential Benefits in Circuit Design}
+%\begin{figure}[tbp]
+%    \begin{minipage}[b]{0.48\textwidth}
+%        \centering
+%        \subfigure[The cumulative distribution function with respect to both type of input data.]{
+%            \centering
+%            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
+%            \label{Fig_CSA2stage_Timing}
+%        }
+%        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
+%            \centering
+%            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
+%            \label{Fig_CSA3stage_Area}
+%        }
+%    \end{minipage}
+%    \centering
+%    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
+%\end{figure}
+
+\subsection{Potential Benefits in Datapath Design}
 %The results can be interpreted in two folds.
-As we mentioned in Section~xxx, our results could be of interest to a circuit designer in two ways.
+As we mentioned in Section~\ref{Section_OptimumAdder}, our results could be of interest to a circuit designer in two ways.
 Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
@@
 
-\subsection{Area Overhead}
+\subsection{Area Overhead of Our Approach}
 For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario.
-Consequently, the area overheads of our approach are summarized in Table xxx and Table xxx for both design goals.
+Consequently, the area overheads of our approach are summarized in Table~\ref{Table_AreaFrequency} and Table~\ref{Table_AreaError} for both design goals.
 In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms.
@@
 An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies.
-As seen in Table xxx, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
-Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Tablexxx, because a specific error budget can be tolerated.
+As seen in Table~\ref{Table_AreaFrequency}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
+Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Table~\ref{Table_AreaError}, because a specific error budget can be tolerated.
 
@@
    \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
+   \label{Table_AreaFrequency}
    \centering
@@
    \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
-   \label{Exp_Real_Inputs}
+   \label{Table_AreaError}
    \centering
@@
 
-\section{Conclusion}
+\section{Conclusion}  \label{Section_Conclusion}
 The conclusion goes here.

### 2013-05-17 TRETS2013/TRETS_overclocking.tex
TRETS13: Merge all stuff from TCAD13 here, no format checks!

--- 2013-05-13 TCAD2013/overclocking_tcad.tex
@@
-%% overclocking_tcad.tex
-%% by Kan Shi
-
-%\usepackage{times,epsfig,amsfonts,bm}
-%\usepackage{pdflscape}
-%\usepackage{afterpage}
-%\usepackage{algorithm}
-%\usepackage{algorithmic}
-%\usepackage{fmtcount,threeparttable, setspace, nicefrac}
-%\usepackage[dvips]{color}
-%\usepackage{amsthm}
-
-\documentclass[journal]{IEEEtran}
-\usepackage{cite}
-
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  \graphicspath{{../Figures/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  \DeclareGraphicsExtensions{.eps}
-\fi
+% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
+% Steps to compile: latex, bibtex, latex latex
+
+\documentclass[prodmode,acmtrets]{acmsmall} % Aptara syntax
+
+% Package to generate and customize Algorithm as per ACM style
+\usepackage[ruled]{algorithm2e}
+%\usepackage{amsmath,epsfig}
+%\usepackage[table]{xcolor}
+%\usepackage{amsmath,amsfonts,epsfig}
+%\usepackage{fancyhdr}
+%\usepackage{mathdots,colortbl,dcolumn,rotating,subfigure,appendix}
+%\usepackage[scriptsize,it]{caption}
+\usepackage{graphicx}
 \usepackage{epstopdf}
-
 \usepackage{multirow}
@@
 \usepackage[cmex10]{amsmath}
-%\usepackage{algorithmic}
-%\usepackage{array}
 \usepackage[tight,footnotesize]{subfigure}
@@
 
+%\renewcommand{\algorithmcfname}{ALGORITHM}
+\SetAlFnt{\small}
+\SetAlCapFnt{\small}
+\SetAlCapNameFnt{\small}
+\SetAlCapHSkip{0pt}
+\IncMargin{-\parindent}
+
+% Metadata Information for publication
+\acmVolume{0}
+\acmNumber{0}
+\acmArticle{0}
+\acmYear{2014}
+\acmMonth{0}
+
+% Document starts
 \begin{document}
 
-\title{Imprecise Computing in Datapath Design: An Overclocking Approach}
-%Imprecise Computing in Datapath Design: Precision Loss or Timing Violations}
-%Imprecise Datapath Design: An Overclocking Approach
-%Imprecise Computation Through Overclocking
-
-\author{Kan~Shi,
-        David~Boland,~\IEEEmembership{Member,~IEEE,}
-        and~George~A.~Constantinides,~\IEEEmembership{Senior~Member,~IEEE}% <-this % stops a space
-	\thanks{K.
-Shi, D.
-Boland and G.
-A.
-Constantinides are with the Department of Electrical and Electronic Engineering, Imperial College London, London, SW7 2BT, U.K.
-(email: \{k.shi11, david.boland03, g.constantinides\}@imperial.ac.uk)}%
-	%\thanks{M.
-Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta,GA, 30332 USA e-mail: (see http://www.michaelshell.org/contact.html).}% <-this % stops a space
-%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
-\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}
-
-% note the % following the last \IEEEmembership and also \thanks -
-% these prevent an unwanted space from occurring between the last author name
-% and the end of the author line. i.e., if you had this:
-%
-% \author{....lastname \thanks{...} \thanks{...} }
-%                     ^------------^------------^----Do not want these spaces!
-%
-% a space would be appended to the last name and could cause every name on that
-% line to be shifted left slightly. This is one of those "LaTeX things". For
-% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
-% "AB" then you have to do: "\textbf{A}\textbf{B}"
-% \thanks is no different in this regard, so shield the last } of each \thanks
-% that ends a line with a % and do not let a space in before the next \thanks.
-% Spaces after \IEEEmembership other than the last one are OK (and needed) as
-% you are supposed to have spaces between the names. For what it is worth,
-% this is a minor point as most people would not even notice if the said evil
-% space somehow managed to creep in.
-
-% The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-
-\maketitle
-
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
+% Page heads
+\markboth{K. Shi et al.}{Imprecise Datapath Design: An Overclocking Approach}
+
+% Title portion
+\title{Imprecise Datapath Design: An Overclocking Approach}
+\author{KAN SHI, DAVID BOLAND\\
+and GEORGE A CONSTANTINIDES
+\affil{Imperial College London}
+}
+
 \begin{abstract}
-As process scaling introduces significant performance variations, releasing the tight accuracy requirement rather than covering all possible worst cases would potentially offer the greater freedom to create a design with better performance or energy efficiency.
+As process scaling introduces significant performance variations, much more conservative timing margins will have to be applied to avoid timing violations.
+Potentially, releasing the tight accuracy requirement would offer greater freedom to create a design with better performance or energy efficiency.
 In this paper, we compare two different approaches that could trade accuracy for performance.
 One is the traditional approach where the precision used in the datapath is limited to meet a target latency.
-The other is a proposed new approach to boost the clock frequency by simply allowing the datapath to operate without timing closure.
-We demonstrate analytically and experimentally that on average, our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach, since the worst case caused by timing violations only happens rarely, while the precision loss results in errors to all data.
-We also show that for embedded applications where silicon area is also a limited factor, using the proposed approach on simple arithmetic primitives could achieve better accuracy or performance than using the traditional method on advanced operators.
+The other is a proposed new approach which simply allows the datapath to operate without timing closure.
+We demonstrate analytically and experimentally that on average our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach.
+This is because the worst case caused by timing violations only happens rarely, while the precision loss results in errors to most data.
+We also show that for basic arithmetic operations such as addition, applying our approach to simple operators (i.e.
+ripple carry adders) can achieve better accuracy or performance than using the traditional method to both original operators and intrinsically faster operators (i.e.
+carry select adders) which consumes the same silicon area.
 \end{abstract}
 
-\begin{IEEEkeywords}
-Overclocking, Imprecise Computing, Numerical Analysis.
-\end{IEEEkeywords}
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+\category{C.2.2}{Computer-Communication Networks}{Network Protocols}
+
+\terms{Design, Algorithms, Performance}
+
+\keywords{A,B}
+
+\acmformat{Kan Shi, David Boland,
+and George A. Constantinides, 2013. Imprecise Datapath Design: An Overclocking Approach.}
+
+\begin{bottomstuff}
+This work is supported by the EPSRC, under
+grant EP/I020557/1 and grand EP/I012036/1.
+
+Author's addresses: K. Shi, D. Boland {and} G. A. Contantinides,
+Department of Electrical and Electronic Engineering,
+Imperial College London.
+\end{bottomstuff}
+
+\maketitle
 
 \section{Introduction}
-\IEEEPARstart{C}{ircuit} performance has increased tremendously over the past decades, with the continuous scaling of CMOS technology to the nanometer regime.
+Circuit performance has increased tremendously over the past decades, with the continuous scaling of CMOS technology to the nanometer regime.
 However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
-Although hardware designers traditionally employ safety margins to ensure a uniform functionality across a variety of possible working environments, there are two major problems if we keep using this approach nowadays.
-One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior.
-The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation.
-
-In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for performance improvement in embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
-In this case, designers tend to employ multi-core processors, heterogeneous systems and massive parallel accelerators to sustain the performance scaling.
-
-Specifically, large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications.
-However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs.
-Furthermore, timing analysis tools typically report a very conservative clock frequency to guarantee ``safe'' operations.
-This substantially limits the potential performance of the device to a further extent.
-
-In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath.
-For the former method, it should be noted that pipelining will not tend to reduce the circuit latency.
-Actually the latency in terms of clock cycles will increase.
-As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in datapath containing feedback where C-slow retiming is inappropriate.
-For the second approach, reducing the datapath precision would subtract out the latency, but at the cost of introducing quantization errors into the design.
-For hardware platforms such as FPGAs or ASICs, research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification has been an extensive topic~\cite{GeorgeDT11}, as it is possible to use a number system with customized precisions on these platforms.
+Currently, hardware designers tend to employ conservative safety margins to ensure a uniform functionality across a variety of possible working environments.
+However, continuing with this approach could become very costly in the short term future.
+This is because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior [xxx], meaning that we can no longer expect a uniform circuit performance.
+Furthermore, covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation [xxx].
+
+Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications [xxx].
+However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or graphics processing units (GPUs).
+
+In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design or to reduce the precision throughout the datapath.
+For the former method, it should be noted that pipelining will not tend to reduce the circuit latency because the latency in terms of clock cycles will increase.
+As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
+For the second approach, reducing the datapath precision would reduce the latency at the cost of introducing quantization errors into the design.
+This has inspired research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification~\cite{GeorgeDT11}.
 A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.
 
-Unfortunately, neither of the conventional approaches tends to remove the conservative safety margin.
+Unfortunately, neither of these conventional approaches tends to remove the conservative safety margin.
 In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}.
@@
 Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
-This paper elaborates on the prior work [xxx], with a further enrichment by incorporating silicon area as another evaluation metric for the trade-offs.
-In this work, we explicitly demonstrate the optimum design choice of the basic arithmetic operators (i.e.
+This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric.
+This enables us to find the optimum design choice of the basic arithmetic operators (i.e.
 binary adders) under various design constraints.
@@
 The rest of this paper is organized as follows.
-It first reviews in detail the current literature regarding the existing approaches that are used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
+It first reviews in detail the current literature regarding the approaches used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
 The analytical error models for two different adder structures: RCA and CSA, are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively.
@@
 Section~\ref{Section_ExpSetup} discusses a practical experimental setup to verify our models and test the proposed design methodology.
-The demonstration of the benefits of our proposed approach is then demonstrated in Section~\ref{Section_Experiments}.
+We then demonstration the benefits of our proposed approach in Section~\ref{Section_Experiments}.
 Finally, Section~\ref{Section_Conclusion} discusses the conclusions of this work and the possible research directions in the future.
@@
 \subsection{Word-length Optimization}\label{Section_Background_WL}
-There exists a significant amount of work demonstrating that optimizing the precision used throughout the datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
-As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification.
-Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
+There exists a significant amount of work demonstrating that optimizing the precision used throughout a datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
+There are two main research directions in this area.
+The first discusses methods to analyze the errors caused by the usage of finite precision and compute bounds on the worst-case errors seen at the output of the design.
+Related techniques include the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
 A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.
+The second stream uses these tools to choose the minimum precision within a datapath to satisfy an required accuracy specification [xxx].
+In this work, we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
+The truncation errors derived in this process are then compared to the overclocking errors generated in our proposed new scenario.
 
 \subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
-Note that, however, the choice of precision is not the only source of errors when designing a datapath.
+However, the choice of precision is not the only source of error when designing a datapath.
 Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
-This strand of research is motivated by the drastic performance variations introduced by process scaling.
-
-%it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.
-
-To address this problem, the international technology roadmap for semiconductors (ITRS07) pointed out that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects~\cite{semiconductor2007international}.
+This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the international technology roadmap for semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
 This topic is expected to be of growing importance in the future, because we will face new challenges as the technology scales further.
@@
 According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases.
-Research in this area is based on the observations that in practice, the worst case happens rarely.
 A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}.
@@
 Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
-
-Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns.
-Meanwhile, many studies have shown that errors can be potentially tolerated in various applications, e.g.
+However, the major problem of the BTWC work is the extra cost of silicon area due to the implementation of the checker circuits.
+
+Another field of study has shown that errors can be potentially tolerated in various applications, e.g.
 DSP applications concerning human perceptions.
-In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
-Current research in this area is focusing on designing probabilistic or imprecise circuits that employ techniques from either software level or hardware level.
+In this case, even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
+Current research in this area focuses on designing probabilistic or imprecise circuits both at a software level and a hardware level.
 For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
@@
 That is, higher voltage would be applied for computations generating most significant bits, and vice versa.
+Nevertheless, utilizing several voltage regions within a ripple carry adder will rarely be practical in real situations.
+Furthermore, the overhead of applying this technique is not addressed.
 
@@
 developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.
-
-However, the limitations of the existing work should not be neglected.
-Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed.
-Secondly, many studies propose alternative architectures, which means the adaptability of this kind of technique is limited on current hardware platforms.
-More importantly, correct results would never be obtained as long as the approximate architectures were employed.
-Thirdly, the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
-
-In this work, we propose an alternative methodology to remove these limitations.
+However, we should note that using imprecise architectures means correct results would never be obtained for certain input patterns.
+Another limitation is that the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
+In addition, these techniques cannot be directly applied onto existing hardware platforms such as FPGAs.
+
+In this work, we propose an alternative methodology to remove the limitations of those existing approaches.
 It is argued in this paper that our method can be easily applied onto existing hardware arithmetic operators such as RCAs and CCMs with almost no hardware overhead.
@@
 
-%, by simply allowing timing violations to happen.
-We compare to the situation where a specific timing requirement is met by reducing datapath precisions.
-Instead of simply performing experiments, we also present analytical models of errors generated due to both timing violation and precision loss.
-
-%In addition, a variety of research aimed at designing imprecise architectures to get rid of the worst cases.
-
-%such as non-uniform voltage scaling or imprecise architectures for computations.
-
-%achieving a uniform circuit performance and 100\% accuracy becomes increasingly difficult and expensive, especially when technology shrinks to the nanometer regime.
-
 \section{Ripple Carry Adder}\label{section_RCA}
 \subsection{Adder Structures in FPGAs}
-%something about fast carry logic in FPGA and pictures
 Adders serve as a key building block for arithmetic operations.
@@
 If, however, $T_S<\mu_{RCA}$, intermediate results will be sampled, potentially generating errors.
-%
+
 \begin{figure}[t]
@@
 
- %We note that it may be possible to operate at a higher clock frequency than $1/T_{S}$ by using alternative adder structures, such as carry-select adder and carry lookahead adder.
-However, the effectiveness of these techniques is limited in FPGAs due to the build-in structures for the acceleration of carry propagation.
-In addition, such techniques will require substantial extra silicon area.
-
 \subsection{Probabilistic Model of Truncation Error}\label{section_RCA_TruncationError}
@@
 Under this premise, the mean value of the truncated bits at signal input ($E_{Tin}$) is given by (\ref{ET at single input}).
-%
-%\vspace{-1ex}
+
 \begin{eqnarray}\label{ET at single input}
 %\small
-%\footnotesize
 %\scriptsize
@@
 \end{eqnarray}
-%\normalsize
 
 Since we assume there are two mutually independent inputs to the RCA, the overall expectation of truncation error for the RCA is given by (\ref{TruncationError}).
-%
-%\vspace{-1ex}
+
 \begin{eqnarray}\label{TruncationError}
@@
 For a given $T_S$, the maximum length of error-free carry propagation is described by~(\ref{Max.length of carry chain}), where $f_S$ denotes the sampling frequency.
-%
-%\vspace{-1ex}
+
 \begin{eqnarray}\label{Max.length of carry chain}
-%\small
-%\footnotesize
-%\scriptsize
     b := \left\lceil \frac{T_S}{\mu} \right\rceil= \left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
 \end{eqnarray}
-%\normalsize
 
@@
 Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{t_RCA}) and (\ref{m_RCA}):
-%
-%\vspace{-1ex}
+
 \begin{align}
@@
 \end{align}
-%\normalsize
 
@@
 Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Output Error}), where $\hat{S_i}$ and $S_i$ denote the actual and error-free output of bit $i$ respectively.
-%
-%\vspace{-1ex}
+
 \begin{eqnarray}\label{Output Error}
@@
 \end{eqnarray}
-%\normalsize
 
@@
 Interestingly, the value of overclocking error has no dependence on the length of carry chain $m$.
-%
-%Instead, $\hat{S}_{t+b}=\hat{S}_{t+b+1}=\cdots=\hat{S}_{t+m-2}=1$ and $\hat{S}_{t+m-1}=0$.
-It is worth noting that these expressions are obtained based on the assumption that all the internal bits are initialized to zero.
-%
+
 \begin{eqnarray}\label{etm}
@@
 Consequently, its probability $P_{tm}$ is given by (\ref{Ptm_RCA}).
-%
-%\vspace{-1ex}
+
 \begin{eqnarray}\label{Ptm_RCA}
@@
 \end{eqnarray}
-%\normalsize
+
 Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$, so $P_{tm}$ can be obtained by~(\ref{Ptm2}).
@@
 Expectation of overclocking error can be expressed by (\ref{Eo_exp}).
-%
-%\vspace{-1ex}
 \begin{eqnarray}\label{Eo_exp}
@@
 \end{eqnarray}
-%\normalsize
-%
+
 Using $P_{tm}$ and $e_{tm}$ from (\ref{etm}) and (\ref{Ptm2}) respectively, $E_O$ can be obtained by (\ref{Eo}).
@@
 \end{eqnarray}
-%\normalsize
+
 Overclocking errors are allowed to happen in the second scenario, therefore the word-length of RCA is set to be equal to the input word-length, that is, $n=k$.
@@
 \end{eqnarray}
-%\normalsize
-
-%
+
 Comparing (\ref{Eo_new_RCA}) and (\ref{Eo_trad_RCA}), we have (\ref{Comparison RCA}).
@@
             \label{Fig_CSA_Structure}
-        }\vspace{-2ex}
+        }%\vspace{-2ex}
         \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
@@
 
-%, silicon area is incorporated as the third metric besides accuracy and performance.
-We explore the trade-offs between these three factors for both adder structures.
-The objective is to demonstrate the best design choice for a given set of design constraints.
-
-%\begin{figure*}[t]
-%  \centering
-%  \includegraphics[width=\textwidth]{./Figures/CSAstructure.pdf}
-%  \caption{Structure of an $s$-stage CSA.}
-%\end{figure*}
-
-%In addition to RCA, there are several
-
 \subsection{Timing Models for Carry Select Adder}
@@
 This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.
-
-%In a CSA, the stage delay refers to the combination of the carry propagation delay and the delay of multiplexing the carry output of the giv stage.
 
@@
 In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
-%This design metric also consumes the maximum word-length of CSA for a given frequency, potentially corresponds to the minimum precision loss at inputs.
-Substituting (\ref{CSA_SingleStageDelay}) into (\ref{CSA_DelayEqual}) yields (\ref{CSA_DelayRep}), where $n_i$ denotes the CSA word-length of stage $i$.
+
 \begin{eqnarray}\label{CSA_DelayRep}
@@
 Sum up $n_i$ to give the total word-length of the CSA in (\ref{CSA_WL}).
-%The total word-length of the CSA is the sum of every stage, as given by (\ref{CSA_WL}).
 \begin{eqnarray}\label{CSA_WL}
@@
 
-%, the word-lengths of RCAs and CSAs are selected to avoid timing violation, as presented in~(\ref{CSA_RCA}).
-
 Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of $b$, as presented in~(\ref{CSA_Timing}).
-% we form the relationship between the word-length of CSA and RCA under a given timing constraint, as presented in~(\ref{CSA_Timing}).
 \begin{eqnarray}\label{CSA_Timing}
@@
 \end{eqnarray}
-
-%It can be seen that $s=1$ leads to $n_{CSA}=n_{RCA}$.
-This is because RCA forms the least significant stage of CSA.
-In addition, combine (\ref{CSA_DelayRep}) and (\ref{CSA_WL}) to ensure $n_{s-1}>0$, we obtain the upper bond of the stage number by~(\ref{CSA_StageNumber}).
-%\begin{eqnarray}\label{CSA_StageNumber}
-%  s<n_{RCA}\cdot\frac{\mu_c}{\mu_{mux}}+1
-%\end{eqnarray}
-
-%\subsection{Model Verification}
-%Using this information, we verify our timing model with experimental results, which are obtained from post place and route simulations on Xilinx Virtex-6 FPGAs.
-Fig.~\ref{CSA Model Verification} illustrates both the modeled value and the experimental results of the maximum word-length of the 2-stage CSA for various operating frequencies.
-In the following experiments within this section, the input data are randomly sampled from a 16-bit data set, which follows uniform distribution.
-It can be seen that the the modeled value match well with the experimental results.
-
-%
-%\begin{figure}[thbp]
-%  \centering
-%  \includegraphics[width=3in]{./Figures/Model.eps}
-%  \caption{Comparison of the maximum word-length between the modeled value and the experimental results from FPGA simulations.}
-%  \label{CSA Model Verification}
-%\end{figure}
 
@@
             \label{Fig_CSA2stage_Timing}
-        }
+        }%
         \subfigure[Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
@@
 
-%As greater word-length corresponds to smaller truncation errors, we compare the maximum word-length of RCA and CSA with 2 stages and 3 stages over a range of operating frequencies, as presented in
-
 Fig.~\ref{Fig_CSA2stage_Timing} also highlights that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
@@
 However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
-%In addition, we can see that the word-length of 3-stage CSA is always greater than 2-stage CSA across the entire frequency domain.
 
@@
 
-%To answer this question, the silicon area is incorporated into the trade-offs together with accuracy and performance.
-If the available hardware resources are limited, the full word-length of both CSA and RCA might not be implemented.
-The precision loss might results in large errors even at low frequencies.
-This is demonstrated by experiments where area constraints are applied besides the timing requirement.
-In the conventional design scenario, both of the constraints are met by reducing the word-length of the input signal.
-The errors at the outputs are recorded with the reference to the original word-length, which is 16 bits in the following experiments.
-In addition, we propose another circuit designing method where RCA is implemented with the maximum possible word-length under the given area budget, while the timing constraints are met by overclocking.
-
-%Our results could be of interest to a circuit designer in two aspects.
-On one hand, it is desirable to create a circuit that can run at a given frequency with the minimum achievable output errors and resource usage.
-On the other hand, the algorithm designer will wish the circuit to operate as fast as possible with the minimum area whilst a certain error budget can be tolerated.
-We select the optimum design methodology for both situations.
 \subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
@@
 Note that in this and all the following experiments within this section, in order to apply our models the input data is randomly generated following the uniform distribution.
-
-%, the input data are randomly generated following uniform distribution, in order to keep consistence with our models.
 
@@
 Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
-%Based on these criteria, the decision graph is depicted in
-%We also notice that for small frequencies, RCA with either overclocking or truncation of word-length of the input signal is the best design choice for any area constraint, since
+
 \begin{figure}[t]
@@
 Due to this reason, we will focus on the RCA in our following analysis and experiments.
-
-%this circumstance is unlikely to happen in the practice, especially with the continued technology scaling nowadays.
-Due to this reason, in the following sections we will focus on the situation where the hardware resources are limited, and therefore RCA is the design option in our following analysis and experiments.
 
@@
 Hence $e_{tm}$ in CCM can be modified from (\ref{etm}) to give (\ref{etm_CCM}).
-%
+
 \begin{eqnarray}\label{etm_CCM}
@@
 Hence the equivalent $s$ in (\ref{Eo_CCM}) can be obtained through~(\ref{ShiftNo}).
-%
-%\vspace{-3ex}
+
 \begin{eqnarray}\label{ShiftNo}
@@
 The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA.
-%XC6VLX240T-1FFG1156.
 
@@
 Finally, we perform an offline comparison of the output of the original circuit at the rated frequency with the output of the overclocked as well as the truncated designs using the same input vectors.
-%
+
 \begin{figure}[htbp]
@@
 
-%the potential timing errors generated from the test framework instead of CUT, when high test frequencies are applied.
-Comparisons are performed between the sampled results and the expected values.
-If mismatch is found, the results will be discarded.
-
-%.
-In this test framework, two cascaded MMCMs are employed in order to provide a wide range of frequency values.
-In addition, the output frequency of the MMCM can be dynamically reconfigured without re-implementing the whole design~\cite{Virtex6Clocking,MMCM}.
-This reconfiguration process is controlled by a finite state machine within the control logic.
-Before actual measurements on FPGA, the rated frequency of CUT is examined through Xilinx Timing Analyzer.
-This frequency is then utilized as the starting value when generating test frequencies.
-The new frequency will increase with a step of 10MHz and stop when the comparator shows that output errors are stabilized.
-The control logic also generates address and read enable signal for the on-chip memory.
-
-%In our experiments, the test clock frequency starts from the rated operating frequency of CUT, and increases with a step of 10MHz until the output error expectation stabilizes.
-
-%In order to avoid the potential timing errors generated from the test framework instead of CUT under high test frequencies, several methods are adopted.
-Firstly, the control signals for the test frequency generator is triggered by the system clock, which is much lower than the test frequency.
-This will guarantee a correct generation of the test clock.
-Secondly, since the address counter for the on-chip memory is driven by the test frequency, a deeply pipelined counter structure with initial delay of 258 cycles is used to ensure the correct sample of each address bit.
-Thirdly, the key internal control signals such as memory address and corresponding operands are recorded together with the outputs to the comparator.
-Comparisons are performed between these values and the corresponding original values.
-The results will be discarded if mismatch is found.
-
 \subsection{Benchmark Circuits}
@@
 Table~\ref{Rated_Frequency_table} summarizes the operating frequency of each implemented design in Xilinx ISE14.1 when the word-length of input signal is 8-bit.
-\vspace{-0.5ex}
-\begin{table}[htbp]
-%% increase table row spacing, adjust to taste
-\renewcommand{\arraystretch}{1.2}
-%\setlength{\tabcolsep}{2}
-\caption{Rated Frequencies of Example Designs.}
-\label{Rated_Frequency_table}
-\begin{center}
-\footnotesize
-%\vspace{-4ex}
-\begin{tabular}{ccc}
-\hline
+
+\begin{table}%
+\tbl{Rated Frequencies of example Designs.\label{Rated_Frequency_table}}{%
+\begin{tabular}{|c|c|c|}
 \hline
@@
 \hline
-\hline
-\end{tabular}
-\normalsize
-\end{center}
-%\vspace{-2.5ex}
-\end{table}
+\end{tabular}}
+\end{table}%
 
@@
 However, we shall see that our model remains close to the true empirical results in Section~\ref{Section_Experiments}.
-
-%\subsection{Evaluation Metric of Outputs}
-%The results are evaluated in terms of mean relative error (MRE), which represents the percentage of error at outputs.
-MRE is given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the correct output respectively.
-%%
-%\begin{eqnarray}\label{MRE}
-%%\small
-%\scriptsize
-%  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
-%\end{eqnarray}
-%\normalsize
 
@@
 
-%Lena image
 \begin{figure*}[htbp]
@@
 
-% for short carry chains (i.e. carry chain length of 2-bit or 3-bit),
-
-%In detail, the difference between the two types of data is explicitly
-
 \begin{figure}[tbp]
@@
 
-%\begin{figure}[tbp]
-%    \begin{minipage}[b]{0.48\textwidth}
-%        \centering
-%        \subfigure[The cumulative distribution function with respect to both type of input data.]{
-%            \centering
-%            \includegraphics[width=0.95\textwidth]{./Figures/CDF.eps}
-%            \label{Fig_CSA2stage_Timing}
-%        }
-%        \subfigure[Probability distribution of different length of carry chains in the $5^{th}$ order FIR filter, using both type of input data.]{
-%            \centering
-%            \includegraphics[width=0.95\textwidth]{./Figures/CC_length2.eps}
-%            \label{Fig_CSA3stage_Area}
-%        }
-%    \end{minipage}
-%    \centering
-%    \caption{Statistical analysis of two types of input data: the uniform data and the real image data: Lena.}
-%\end{figure}
-
 \subsection{Potential Benefits in Datapath Design}
-%The results can be interpreted in two folds.
 As we mentioned in Section~\ref{Section_OptimumAdder}, our results could be of interest to a circuit designer in two ways.
@@
 Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{FIR}.
-%Table goes here
 
@@
    \caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
-%   \vspace{-2ex}
    \centering
@@
 
-\section*{Acknowledgment}
-The authors would like to acknowledge the support of the EPSRC (Grants EP/I020557/1 and EP/I012036/1).
-
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex,
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results.}
-%\label{fig_sim}
+% Figure
+%\begin{figure}
+%\centerline{\includegraphics{acmsmall-mouse}}
+%\caption{Code before preprocessing.}
+%\label{fig:one}
 %\end{figure}
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results.}
-%\label{fig_sim}
-%\end{figure*}
-%
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% references section
-\bibliographystyle{./IEEEtran}
-\bibliography{./IEEEabrv,./Reference}
-
-% biography section
-%
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}{Author}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{Author}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Author}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=\textwidth]{./acmsmall-mouse.eps}
+%  \caption{Figure}
+
+% Table
+\begin{table}%
+\tbl{Simulation Configuration\label{tab:one}}{%
+\begin{tabular}{|l|l|}
+\hline
+TERRAIN{$^a$}   & (200m$\times$200m) Square\\\hline
+Node Number     & 289\\\hline
+Node Placement  & Uniform\\\hline
+Application     & Many-to-Many/Gossip CBR Streams\\\hline
+Payload Size    & 32 bytes\\\hline
+Routing Layer   & GF\\\hline
+MAC Layer       & CSMA/MMSN\\\hline
+Radio Layer     & RADIO-ACCNOISE\\\hline
+Radio Bandwidth & 250Kbps\\\hline
+Radio Range     & 20m--45m\\\hline
+\end{tabular}}
+\begin{tabnote}%
+\Note{Source:}{This is a table
+sourcenote. This is a table sourcenote. This is a table
+sourcenote.}
+\vskip2pt
+\Note{Note:}{This is a table footnote.}
+\tabnoteentry{$^a$}{This is a table footnote. This is a
+table footnote. This is a table footnote.}
+\end{tabnote}%
+\end{table}%
+
+% Acknowledgments
+\begin{acks}
+The authors would like to thank xxx.
+\end{acks}
+
+% Bibliography
+\bibliographystyle{ACM-Reference-Format-Journals}
+%\bibliography{acmsmall-sample-bibfile}
+\bibliography{Reference}
+                             % Sample .bib file with references that match those in
+                             % the 'Specifications Document (V1.5)' as well containing
+                             % 'legacy' bibs and bibs with 'alternate codings'.
+                             % Gerry Murray - March 2012
+
+% History dates
+\received{February 2007}{March 2009}{June 2009}
+
+% Electronic Appendix
+\elecappendix
+
+\medskip
 
 \end{document}
+% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2013-05-23 TRETS2013/TRETS_overclocking.tex
Conclusion, Modified Format of Figures

@@
 For instance, the Altera Cyclone series uses fast tables~\cite{AlteraCyclone} while the Xilinx Virtex series employs dedicated multiplexers and encoders for the fast carry logic~\cite{Virtex6}.
-Figure~\ref{FPGA adder} illustrates the structure of an $n$-bit RCA, which is composed of $n$ serial-connected full adders (FAs) and utilizes the internal fast carry logic of the Virtex-6 FPGA.
+Fig.~\ref{FPGA adder} illustrates the structure of an $n$-bit RCA, which is composed of $n$ serial-connected full adders (FAs) and utilizes the internal fast carry logic of the Virtex-6 FPGA.
 
 While the fast carry logic reduces the time of each individual carry-propagation delay, the overall delay of carry-propagation will eventually overwhelm the delay of sum generation of each LUT with increasing operand word-lengths.
-For our initial analysis, we assume that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay, and hence the critical path delay of the RCA is $\mu_{RCA}=n\mu$, as shown in~Figure~\ref{FPGA adder}.
+For our initial analysis, we assume that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay, and hence the critical path delay of the RCA is $\mu_{RCA}=n\mu$, as shown in~Fig.~\ref{FPGA adder}.
 For an $n$-bit RCA, it follows that if the sampling period $T_S$ is greater than $\mu_{RCA}$, correct results will be sampled.
@@
 Under this premise, the mean value of the truncated bits at signal input ($E_{Tin}$) is given by (\ref{ET at single input}).
-
+%
 \begin{eqnarray}\label{ET at single input}
@@
 %\scriptsize
-  \begin{split}
-    E_{Tin} &= \frac{1}{2}\sum_{i=n+1}^{k}2^{-i}\\
-    &= 2^{-n-1}-2^{-k-1}
-%  \vspace{-1ex}
-  \end{split}
+%  \begin{split}
+    E_{Tin} = \frac{1}{2}\sum_{i=n+1}^{k}2^{-i} = 2^{-n-1}-2^{-k-1}
+%  \vspace{-1ex}
+%  \end{split}
 \end{eqnarray}
@@
 Since we assume there are two mutually independent inputs to the RCA, the overall expectation of truncation error for the RCA is given by (\ref{TruncationError}).
-
+%
 \begin{eqnarray}\label{TruncationError}
@@
 For a given $T_S$, the maximum length of error-free carry propagation is described by~(\ref{Max.length of carry chain}), where $f_S$ denotes the sampling frequency.
-
+%
 \begin{eqnarray}\label{Max.length of carry chain}
@@
  \begin{itemize}
-   \item If $\!A_i\!=\!B_i\!=1$, a new carry chain is generated at bit $i$, and $S_i\!=\!C_{i-1}$;
-   \item If $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i\!=\!0$;
-   \item If $\!A_i\!=\!B_i$, the current carry chain annihilates at bit $i$, and $S_i\!\!=\!\!1$.
+   \item If $A_i=B_i=1$, a new carry chain is generated at bit $i$, and $S_i=C_{i-1}$;
+   \item If $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=0$;
+   \item If $A_i=B_i$, the current carry chain annihilates at bit $i$, and $S_i=1$.
  \end{itemize}
@@
 Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{t_RCA}) and (\ref{m_RCA}):
-
+%
 \begin{align}
@@
 Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Output Error}), where $\hat{S_i}$ and $S_i$ denote the actual and error-free output of bit $i$ respectively.
-
+%
 \begin{eqnarray}\label{Output Error}
@@
 Interestingly, the value of overclocking error has no dependence on the length of carry chain $m$.
-
+%
 \begin{eqnarray}\label{etm}
@@
 %\footnotesize
-  \begin{split}
-    e_{tm} &= \frac{\left|2^{t+m-1}-2^{t+m-2}-\dots-2^{t+b}\right|}{2^n}\\
-    &= 2^{t+b-n}
-  \end{split}
+%  \begin{split}
+    e_{tm} = \frac{\left|2^{t+m-1}-2^{t+m-2}-\dots-2^{t+b}\right|}{2^n} = 2^{t+b-n}
+%  \end{split}
 \end{eqnarray}
@@
 Consequently, its probability $P_{tm}$ is given by (\ref{Ptm_RCA}).
-
+%
 \begin{eqnarray}\label{Ptm_RCA}
@@
 Note that~(\ref{Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
-%\vspace{-1ex}
 %
@@
 Expectation of overclocking error can be expressed by (\ref{Eo_exp}).
+%
 \begin{eqnarray}\label{Eo_exp}
@@
 Using $P_{tm}$ and $e_{tm}$ from (\ref{etm}) and (\ref{Ptm2}) respectively, $E_O$ can be obtained by (\ref{Eo}).
-%\vspace{-1ex}
+%
 \begin{eqnarray}\label{Eo}
@@
 Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of RCA and CSA in this section.
-
 \begin{figure}[htbp]
-    \begin{minipage}[b]{.49\textwidth}
-        \centering
-        \subfigure[The structure diagram of a CSA with $s$ stages.]{
-            \includegraphics[width=0.95\textwidth]{./Figures/CSA_structure.pdf}
+        \centering
+        \subfigure[A CSA with $s$ stages.]{
+            \includegraphics[width=0.6\textwidth]{./Figures/CSA_structure.pdf}
             \label{Fig_CSA_Structure}
         }%\vspace{-2ex}
-        \subfigure[The structure of the $i^{th}$ stage in the CSA.]{
-        %\centering
-            \includegraphics[width=2.4in]{./Figures/CSA_SingleStage.pdf}
+        \subfigure[The $i^{th}$ stage in the CSA.]{
+        \centering
+            \includegraphics[width=2.2in]{./Figures/CSA_SingleStage.pdf}
             \label{Fig_CSA_SingleStage}
         }
-    \end{minipage}
-    \centering
     \caption{The structure diagram of CSA.}
@@
 Hence we can obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
+%
 \begin{eqnarray}\label{CSA_SingleStageDelay}
@@
 Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{CSA_DelayEqual}).
+%
 \begin{eqnarray}\label{CSA_DelayEqual}
@@
 In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
-
+%
 \begin{eqnarray}\label{CSA_DelayRep}
@@
 Sum up $n_i$ to give the total word-length of the CSA in (\ref{CSA_WL}).
+%
 \begin{eqnarray}\label{CSA_WL}
-  \begin{split}
-    n_{CSA} &=\sum_{i=0}^{s-1}n_{i} \\
-    &= s\cdot n_{s-1}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
-  \end{split}
+%  \begin{split}
+    n_{CSA} =\sum_{i=0}^{s-1}n_{i}= s\cdot n_{s-1}-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+1)(s-2)}{2}
+%  \end{split}
 \end{eqnarray}
@@
 Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{TimingConstraint_CSA}).
+%
 \begin{eqnarray}\label{TimingConstraint_CSA}
@@
 Hence for the same frequency requirement, we can form the relationship between the delay of the most significant stage of CSA and the delay of RCA, as given by~(\ref{WL_MSB_CSA}),
+%
 \begin{eqnarray}\label{WL_MSB_CSA}
@@
 Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of $b$, as presented in~(\ref{CSA_Timing}).
+%
 \begin{eqnarray}\label{CSA_Timing}
@@
 
-\begin{figure}[tbp]
-    \begin{minipage}[b]{0.48\textwidth}
-        \centering
-        \subfigure[The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
-            \centering
-            \includegraphics[width=0.95\textwidth]{./Figures/CSA2stage_Model_Timing.eps}
+\begin{figure}[htbp]
+        \centering
+        \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
+            \includegraphics[width=3.5in]{./Figures/CSA2stage_Model_Timing.eps}
             \label{Fig_CSA2stage_Timing}
-        }%
-        \subfigure[Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
-            \centering
-            \includegraphics[width=0.95\textwidth]{./Figures/CSA3stage_Area.eps}
+        }
+        \subfigure[\scriptsize Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
+            \includegraphics[width=3.5in]{./Figures/CSA3stage_Area.eps}
             \label{Fig_CSA3stage_Area}
         }
-    \end{minipage}
-    \centering
     \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
@@
 In this case, the optimum design method is selected according to the following criteria:
+
 \begin{itemize}
@@
 Note that in this and all the following experiments within this section, in order to apply our models the input data is randomly generated following the uniform distribution.
-
-\begin{figure}[th]
+%
+\begin{figure}[t]
   \centering
@@
 The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
+  \vspace{-.5ex}
   \label{Fig_CSA_LUT25}
@@
 In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+%
 \begin{eqnarray}\label{MRE}
@@
 For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Fig.~\ref{CCM_fig}.
-\begin{figure*}[htbp]
-  \centering
-  \includegraphics[width=0.99\textwidth]{./Figures/CCM_CarryChain.pdf}
+
+\begin{figure}[htbp]
+  \vspace{-2ex}
+  \centering
+  \includegraphics[width=\textwidth]{./Figures/CCM_CarryChain.pdf}
+  \vspace{-2ex}
   \caption{Four possible carry chain types in a constant coefficient multiplier with $n$-bit inputs. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
   \label{CCM_fig}
-\end{figure*}
+\end{figure}
 
@@
 Hence $e_{tm}$ in CCM can be modified from (\ref{etm}) to give (\ref{etm_CCM}).
-
+%
 \begin{eqnarray}\label{etm_CCM}
@@
 Due to the dependencies in a CCM, carry generation requires $a_t=a_{t-s}=1$, propagation and annihilation of a carry chain is best considered separately for four types of carry chain generated at bit~$t$.
-We label these by $C_{tm}1$ to $C_{tm}4$ in Figure~\ref{CCM_fig}, defined by the end region of the carry chain.
+We label these by $C_{tm}1$ to $C_{tm}4$ in Fig.~\ref{CCM_fig}, defined by the end region of the carry chain.
 For $C_{tm}1$, we have:
+
 \begin{itemize}
-  \item Carry propagation: $\!a_i\neq\!a_{i+s}\!$ where $\!i\!\in[t+1,n-s-2]\!$;
-  \item Carry annihilation: $\!a_j\!=\!a_{j+s}\!$ where $\!j\!\in[t+1,n-s-1]\!$.
+  \item Carry propagation: $a_i\neq a_{i+s}$ where $i\in[t+1,n-s-2]$;
+  \item Carry annihilation: $a_j=a_{j+s}$ where $j\in[t+1,n-s-1]$.
 \end{itemize}
+
 Similarly for $C_{tm}2$, we have:
+
 \begin{itemize}
   \item Carry propagation: $a_i\neq a_{n-1}$ where $i\in[n-s-1,n-3]$; or $a_i\neq a_{i+s}$ where $i\in[t+1,n-s-2]$;
-  \item Carry annihilation: $\!a_j\!=a_{n-1}\!$ where $j\!\in\![n-s-1,n-2]$.
+  \item Carry annihilation: $a_j=a_{n-1}$ where $j\in[n-s-1,n-2]$.
 \end{itemize}
@@
 Finally, we perform an offline comparison of the output of the original circuit at the rated frequency with the output of the overclocked as well as the truncated designs using the same input vectors.
-
+%
 \begin{figure}[htbp]
   \centering
-  %\vspace{-3.5ex}
+  \vspace{-3ex}
   \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
@@
   \centering
-%  \vspace{-2.5ex}
+%  \vspace{-3ex}
   \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
@@
 
-\begin{figure*}[htbp]
+\begin{figure}[ht]
   %\vspace{-2ex}
-  \centering
-  \subfigure[425MHz,~n=8~,~SNR=47.97dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
-  \end{minipage}%
+  % 425M, 450M, 480M, 520M
+  \centering
+  \subfigure[\scriptsize n=8,~SNR=47.97dB.]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T8.eps}
   }% This is important! use % to indicate same line, otherwise new line
-  \subfigure[450MHz,~n=8,~SNR=44.94dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=8,~SNR=44.94dB.]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T65.eps}
   }%
-  \subfigure[480MHz,~n=8,~SNR=21.58dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=8,~SNR=21.58dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
   }%
-  \subfigure[520MHz,~n=8,~SNR=10.03dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=8,~SNR=10.03dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
   }
-  \subfigure[425MHz,~n=7,~SNR=26.02dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
-  \end{minipage}%
+  \subfigure[\scriptsize n=7,~SNR=26.02dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
   }% This is important! use % to indicate same line, otherwise new line
-  \subfigure[450MHz,~n=5,~SNR=21.76dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=5,~SNR=21.76dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
   }%
-  \subfigure[480MHz,~n=2,~SNR=6.57dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=2,~SNR=6.57dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
   }%
-  \subfigure[520MHz,~n=1,~SNR=3.95dB]{
-  \begin{minipage}[c]{0.24\textwidth}
-    \centering
-    \includegraphics[width=1.8in]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
-  \end{minipage}
+  \subfigure[\scriptsize n=1,~SNR=3.95dB]{
+    \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
   }
 %\vspace{-2ex}
-\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) under various operating frequencies.}
+\caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) when operating frequencies are $425MHz$, $450MHz$, $480MHz$ and $520MHz$ respectively (from left to right).}
 \label{FIR_Lena}
-\end{figure*}
+\end{figure}
 
@@
    \setlength{\tabcolsep}{3.5pt}
-   \caption{Relative Reduction of MRE in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}).}
+   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}) for two types of input data: the uniform data (Uni) and real image data from Lena (Lena).}{
    \centering
@@
    \begin{threeparttable}
-   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
-     \hline
+   \begin{tabular}{|c|cc|cc|cc|cc|cc||cc|}
      \hline
@@
      \multicolumn{2}{c||}{\textbf{DCT4}} &
-     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
-     &  {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena  }
-     &  {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena}\\
-     \hline
-     1.04 & 99.85\%	& 100.00\%  & 99.51\% &	99.74\% &	 72.28\% &	90.09\% &	 79.03\% &	 100.00\% &	 83.58\% &	 98.06\% & 86.14\% & 97.50\%\\
-     1.08 & 98.93\%	& 99.97\%	& 96.26\% &	93.75\% &	 71.64\% &	90.50\% &	 78.81\% &	 100.00\% &	 83.26\% &	 98.45\% & 85.15\% & 96.46\%\\
-     1.12 & 94.27\%	& 98.82\%   & 96.25\% &	93.62\% &	 73.63\% &   88.25\% &	 81.88\% &	 84.87\%  &	 89.44\% &	 99.56\% & 86.68\% & 92.84\%\\
-     1.16 & 99.66\%	& 99.91\%   & 73.73\% &	93.62\% &	 73.10\% &   89.92\% &	 79.30\% &	 84.23\%  &	 79.07\% &	 99.44\% & 80.44\% & 93.23\%\\
-     1.20 & 96.03\%	& 99.90\%   & 81.55\% &	81.52\% &	 70.76\% &	75.67\% &	 64.96\% &	 84.50\%  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.46\% & 84.95\% \\
-     1.24 & 98.46\%	& 99.32\%   & 81.43\% &	81.67\% &	 70.47\% &	76.12\% &	 63.66\% &	 84.23\%  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.44\% & 84.92\%\\
-     1.28 & 95.39\%	& 99.29\%   & 60.41\% &	78.24\% &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	54.38\% &	 75.15\%  &	N/A\tnote{*}	  & N/A\tnote{*} & 67.92\% & 83.58\%\\
-     1.32 & 95.37\%	& 98.75\%   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 95.37\%	& 98.75\% \\
-     \hline
+     \multicolumn{2}{c|}{\textbf{Geo.Mean}}\\
+     &  {Uni} & {Lena } &  {Uni} & {Lena } &  {Uni} & {Lena }
+     &  {Uni} & {Lena } &  {Uni} & {Lena } &  {Uni} & {Lena }\\
+     \hline
+     1.04 & 99.85	& 100.00  & 99.51 &	99.74 &	 72.28 &	90.09 &	 79.03 &	 100.00 &	 83.58 &	 98.06 & 86.14 & 97.50\\
+     1.08 & 98.93	& 99.97   & 96.26 &	93.75 &	 71.64 &	90.50 &	 78.81 &	 100.00 &	 83.26 &	 98.45 & 85.15 & 96.46\\
+     1.12 & 94.27	& 98.82   & 96.25 &	93.62 &	 73.63 &   88.25 &	 81.88 &	 84.87  &	 89.44 &	 99.56 & 86.68 & 92.84\\
+     1.16 & 99.66	& 99.91   & 73.73 &	93.62 &	 73.10 &   89.92 &	 79.30 &	 84.23  &	 79.07 &	 99.44 & 80.44 & 93.23\\
+     1.20 & 96.03	& 99.90   & 81.55 &	81.52 &	 70.76 &	75.67 &	 64.96 &	 84.50  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.46 & 84.95 \\
+     1.24 & 98.46	& 99.32   & 81.43 &	81.67 &	 70.47 &	76.12 &	 63.66 &	 84.23  &	 N/A\tnote{*}	  & N/A\tnote{*} & 77.44 & 84.92\\
+     1.28 & 95.39	& 99.29   & 60.41 &	78.24 &	 N/A\tnote{*}	    &   N/A\tnote{*}     &	54.38 &	 75.15  &	N/A\tnote{*}	  & N/A\tnote{*} & 67.92 & 83.58\\
+     1.32 & 95.37	& 98.75   & N/A\tnote{*}	  &	 N/A\tnote{*}	    &	 N/A\tnote{*}	    &	 N/A\tnote{*}   & N/A\tnote{*}   & N/A\tnote{*}    &    N/A\tnote{*}   & N/A\tnote{*} & 95.37	& 98.75 \\
      \hline
@@
    \end{tablenotes}
-   \end{threeparttable}
+   \end{threeparttable}}
    \label{Ratio_MRE}
@@
    \setlength{\tabcolsep}{3.5pt}
-   \caption{Frequency Speedups in Overclocking Scenario Under Various Error Budgets.}
+   \tbl{Frequency Speedups ($\%$) in Overclocking Scenario Under Various Error Budgets for two types of input data: uniform data (Uni) and real image data from Lena (Lena).}{
 %   \vspace{-2ex}
@@
    \footnotesize
-   \begin{tabular}{c|cc|cc|cc|cc|cc||cc}
-     \hline
-     \hline
-     \multirow{2}*{\begin{tabular}{c}\textbf{Error Budget}\\\textbf{\%}\end{tabular}} &
+   \begin{tabular}{|c|cc|cc|cc|cc|cc||cc|}
+     \hline
+     \multirow{2}*{\begin{tabular}{c}\textbf{Error}\\\textbf{Budget($\%$)}\end{tabular}} &
      \multicolumn{2}{c|}{\textbf{FIR}} &
@@
      \multicolumn{2}{c||}{\textbf{DCT4}} &
-     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
+     \multicolumn{2}{c|}{\textbf{Geo.Mean}} \\
      %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
-     & {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena  }
-     & {Uniform} & {Lena } &  {Uniform} & {Lena } &  {Uniform} & {Lena }\\
-     \hline
-     0.05 & 4.76\%&	21.43\%&	 6.82\%&	6.82\%&	0.95\%&	 1.26\%&	12.40\%&	 24.03\%&	 0.72\%&	 0.96\%  &3.07\%    &5.32\%\\
-     0.5  & 19.05\%&	21.43\%&	 13.64\%&	6.82\%&	0.63\%&	 10.06\%&	24.03\%&	 24.03\%&	0.48\%&	 12.44\%   &4.52\% &13.45\%\\
-     1    & 19.05\%&	28.57\%&	 13.64\%&	18.18\%&	 10.06\%&	16.35\%&	 24.03\%&	 24.03\%&	 0.48\%&	 12.44\%    &7.86\% &19.10\%\\
-     5    & 19.15\%&	25.53\%&	 18.18\%&	18.18\%&	 0.54\%&	0.82\%&	 0.63\%&	 0.94\%&	 7.66\%&	 12.44\%    &3.91\%    &5.36\%\\
-     10   & 19.15\%&	25.53\%&	 10.64\%&	10.64\%&	 0.54\%&	1.09\%&	 6.92\%&	 13.21\%&	 4.91\%&	 4.911\%    &5.19\%    &7.19\%\\
-     20   & 19.15\%&	25.53\%&	 5.77\%&	15.39\%&	 8.70\%&	8.70\%&	 3.26\%&	 3.26\%&	 6.70\%&	 10.88\%    &7.32\%    &10.39\%\\
-     50   & 15.69\%&	15.69\%&	 10.53\%&	19.30\%&	 42.50\%&	50.00\%&	 46.74\%&	 54.89\%&	 15.06\%&	 19.25\%    &21.8\% &27.59\%\\
-     \hline
-     \hline
-   \end{tabular}
+     & {Uni} & {Lena } &  {Uni} & {Lena } &  {Uni} & {Lena }
+     & {Uni} & {Lena } &  {Uni} & {Lena } &  {Uni} & {Lena }\\
+     \hline
+     0.05 & 4.76 &	21.43&	 6.82&	6.82&	0.95&	 1.26&	12.40&	 24.03&	 0.72&	 0.96  &3.07 & 5.32\\
+     0.5  & 19.05&	21.43&	 13.64&	6.82&	0.63&	 10.06&	24.03&	 24.03&	0.48&	 12.44   &4.52 &13.45\\
+     1    & 19.05&	28.57&	 13.64&	18.18&	 10.06&	16.35&	 24.03&	 24.03&	 0.48&	 12.44    &7.86 &19.10\\
+     5    & 19.15&	25.53&	 18.18&	18.18&	 0.54&	0.82&	 0.63&	 0.94&	 7.66&	 12.44    &3.91    &5.36\\
+     10   & 19.15&	25.53&	 10.64&	10.64&	 0.54&	1.09&	 6.92&	 13.21&	 4.91&	 4.911  &5.19  &7.19\\
+     20   & 19.15&	25.53&	 5.77&	15.39&	 8.70&	8.70&	 3.26&	 3.26&	 6.70&	 10.88    &7.32    &10.39\\
+     50   & 15.69&	15.69&	 10.53&	19.30&	 42.50&	50.00&	 46.74&	 54.89&	 15.06&	 19.25    &21.8 &27.59\\
+     \hline
+   \end{tabular}}
    \normalsize
@@
    \setlength{\tabcolsep}{3.5pt}
-   \caption{Area Overhead of Our Approach with respect to Given Frequency Requirements}
+   \tbl{Area Overhead of Our Approach with respect to Given Frequency Requirements}{
    \label{Table_AreaFrequency}
@@
      \multicolumn{2}{c||}{\textbf{DCT4}} &
-     \multicolumn{2}{c}{\textbf{Geo.Mean}}\\
-     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices  }
-     &  {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices}\\
+     \multicolumn{2}{c|}{\textbf{Geo.Mean}}\\
+     &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices }
+     &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices}\\
      \hline
@@
      \hline
-     \hline
    \end{tabular}
@@
    \setlength{\tabcolsep}{3.5pt}
-   \caption{Area Overhead of Our Approach with respect to Given Error Budgets.}
+   \tbl{Area Overhead of Our Approach with respect to Given Error Budgets.}{
    \label{Table_AreaError}
@@
      \multicolumn{2}{c||}{\textbf{DCT4}} &
-     \multicolumn{2}{c}{\textbf{Geo.Mean}} \\
+     \multicolumn{2}{c|}{\textbf{Geo.Mean}} \\
      %\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
-     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }
-     & {LUTs} & {Slices } &  {LUTs} & {Slices } &  {LUTs} & {Slices }\\
+     & {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices }
+     & {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices } &  {\scriptsize LUTs} & {\scriptsize Slices }\\
      \hline
@@
      \hline
-     \hline
-   \end{tabular}
+   \end{tabular}}
    \normalsize
@@
 \section{Conclusion}  \label{Section_Conclusion}
-The conclusion goes here.
+In this paper, we have explored the probabilistic behavior of key arithmetic primitives in an FPGA when operating beyond the deterministic region.
+Two design scenarios that might generate errors: violating timing constraints and reducing precisions, have been investigated.
+It has been found that simply allowing timing violations to happen would potentially lead to either reductions in average errors or speedups in clock frequencies, in comparison to the traditional approach where the target timing is met by limiting the precisions throughout the datapath.
+To verify this hypothesis, probabilistic models have been developed for errors generated from both design methodologies, whilst empirical results on a Virtex-6 FPGA have also been obtained over a set of DSP applications.
+Besides, the silicon area has also been taken into account for the trade-offs.
+We have shown that applying our approach on basic arithmetic primitives would potentially outperform utilizing the traditional approach on either the same architectures or structures specifically designed for high performance, of which the precision loss is even greater under a tight area budget.
+
+Whilst this research has shown a promising direction for sustaining performance scaling, there are several issues that would be of interest for future research.
+A critical finding from this work is the direction inconsistency between carry propagation (from LSB to MSB) and results sampling (from MSB to LSB).
+In this case, although the probability of generating overclocking errors might be small, the magnitude of error is large.
+Another limitation of performance improvement is that the inputs are applied in parallel, while the correct outputs are updated based on a bit-serial fashion due to the delay of carry propagation.
+To tackle this problem, we wish to investigate non-conventional arithmetic operations and data representations.
+One possible candidate is known as ``online arithmetic '' [xxx], in which the computation is performed bit by bit from MSB to LSB, and carry propagation can be nearly removed because a redundant number system [xxx] is used to represent numbers.
+In this case, we would expect an even more significant performance improvement when applying our approach into the aforementioned area.
 
@@
 % Table
-\begin{table}%
-\tbl{Simulation Configuration\label{tab:one}}{%
-\begin{tabular}{|l|l|}
-\hline
-TERRAIN{$^a$}   & (200m$\times$200m) Square\\\hline
-Node Number     & 289\\\hline
-Node Placement  & Uniform\\\hline
-Application     & Many-to-Many/Gossip CBR Streams\\\hline
-Payload Size    & 32 bytes\\\hline
-Routing Layer   & GF\\\hline
-MAC Layer       & CSMA/MMSN\\\hline
-Radio Layer     & RADIO-ACCNOISE\\\hline
-Radio Bandwidth & 250Kbps\\\hline
-Radio Range     & 20m--45m\\\hline
-\end{tabular}}
-\begin{tabnote}%
-\Note{Source:}{This is a table
-sourcenote. This is a table sourcenote. This is a table
-sourcenote.}
-\vskip2pt
-\Note{Note:}{This is a table footnote.}
-\tabnoteentry{$^a$}{This is a table footnote. This is a
-table footnote. This is a table footnote.}
-\end{tabnote}%
-\end{table}%
+%\begin{table}%
+%\tbl{Simulation Configuration\label{tab:one}}{%
+%\begin{tabular}{|l|l|}
+%\hline
+%TERRAIN{$^a$}   & (200m$\times$200m) Square\\\hline
+%Node Number     & 289\\\hline
+%Node Placement  & Uniform\\\hline
+%Application     & Many-to-Many/Gossip CBR Streams\\\hline
+%Payload Size    & 32 bytes\\\hline
+%Routing Layer   & GF\\\hline
+%MAC Layer       & CSMA/MMSN\\\hline
+%Radio Layer     & RADIO-ACCNOISE\\\hline
+%Radio Bandwidth & 250Kbps\\\hline
+%Radio Range     & 20m--45m\\\hline
+%\end{tabular}}
+%\begin{tabnote}%
+%\Note{Source:}{This is a table
+%sourcenote. This is a table sourcenote. This is a table
+%sourcenote.}
+%\vskip2pt
+%\Note{Note:}{This is a table footnote.}
+%\tabnoteentry{$^a$}{This is a table footnote. This is a
+%table footnote. This is a table footnote.}
+%\end{tabnote}%
+%\end{table}%
 

### 2013-05-25 TRETS2013/TRETS_overclocking.tex
Modified References

@@
 
-Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications [xxx].
+Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications~\cite{UnderwoodFPGAvsCPU,David_MINRES}.
 However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or graphics processing units (GPUs).
@@
 The first discusses methods to analyze the errors caused by the usage of finite precision and compute bounds on the worst-case errors seen at the output of the design.
-Related techniques include the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
-A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.
-The second stream uses these tools to choose the minimum precision within a datapath to satisfy an required accuracy specification [xxx].
+Related techniques include the simulation-based approach~\cite{SungWLop_Simulation} and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
+A detailed summary of these methods can be found in~\cite{GeorgeDT11,lee2006accuracy}.
+The second stream uses these tools to choose the minimum precision within a datapath to satisfy an required accuracy specification~\cite{RoldaoWLop_Simulation}.
 In this work, we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
@@
 
-In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.xxx.
+In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.~\ref{Fig_CarryDistribution}.
 As the input data is 8-bit, the longest possible carry chain length is 9-bit.
@@
 For the image data Lena, one input of RCA uses the original data and the other uses the delayed original data for several clock cycles.}
-  \label{CarryDistribution}
+  \label{Fig_CarryDistribution}
 \end{figure}
@@
 Whilst this research has shown a promising direction for sustaining performance scaling, there are several issues that would be of interest for future research.
-A critical finding from this work is the direction inconsistency between carry propagation (from LSB to MSB) and results sampling (from MSB to LSB).
-In this case, although the probability of generating overclocking errors might be small, the magnitude of error is large.
-Another limitation of performance improvement is that the inputs are applied in parallel, while the correct outputs are updated based on a bit-serial fashion due to the delay of carry propagation.
+A critical finding from this work is the direction inconsistency between carry propagation (from the LSB to the MSB) and results sampling (from the MSB to the LSB).
+In this case, although the probability of generating overclocking errors might be small, the magnitude of error is large, which restricts the performance improvement to a large extent.
+Another limitation is that the inputs of current designs are applied digits by digits, while the correct outputs are updated based on a bit-serial fashion due to the delay of carry propagation.
 To tackle this problem, we wish to investigate non-conventional arithmetic operations and data representations.
-One possible candidate is known as ``online arithmetic '' [xxx], in which the computation is performed bit by bit from MSB to LSB, and carry propagation can be nearly removed because a redundant number system [xxx] is used to represent numbers.
-In this case, we would expect an even more significant performance improvement when applying our approach into the aforementioned area.
+One possible candidate is known as ``online arithmetic ''~\cite{Ercegovac_Overview,Ercegovac_Book}, in which the computation is performed bit-serially from the MSB to the LSB.
+This potentially fill the gap of the aforementioned direction inconsistencies.
+In addition, an alternative number representation metric by using redundant numbers could be employed to largely reduce the lengths of carry chains.
+While research in this area mainly focus on the ASIC domain~\cite{RedundantMult_1985,RedundantMult_1987}, it is worthwhile exploring the potential benefits and overheads when employing this method in our approach.
+
+%, and this data representation metric has been utilized in ASIC designs
+
+%and carry propagation can be nearly removed because a redundant number system [xxx] is used to represent numbers.
+Therefore it is worthwhile exploring the potential benefits and overheads when employing this method in our approach.
 

### 2013-05-28 TRETS2013/TRETS_overclocking.tex
Add Contribution

@@
 
-\category{C.2.2}{Computer-Communication Networks}{Network Protocols}
-
-\terms{Design, Algorithms, Performance}
-
-\keywords{A,B}
+\category{C.2.2}{Category put here}{Detail category}
+
+\terms{Design, FPGA, Performance}
+
+\keywords{Overclocking, Imprecise Design}
 
@@
 This work is supported by the EPSRC, under
-grant EP/I020557/1 and grand EP/I012036/1.
+grant EP/I020557/1 and grant EP/I012036/1.
 
@@
 \section{Introduction}
-Circuit performance has increased tremendously over the past decades, with the continuous scaling of CMOS technology to the nanometer regime.
+With the continuous scaling of CMOS technology to the nanometer regime, circuit performance has increased tremendously over the past decades.
 However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
 Currently, hardware designers tend to employ conservative safety margins to ensure a uniform functionality across a variety of possible working environments.
-However, continuing with this approach could become very costly in the short term future.
-This is because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior [xxx], meaning that we can no longer expect a uniform circuit performance.
-Furthermore, covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation [xxx].
+Nevertheless, continuing with this approach could become very costly in the short term future.
+This is because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior, meaning that we can no longer expect a uniform circuit performance.
+Furthermore, covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation.
 
@@
 In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design or to reduce the precision throughout the datapath.
-For the former method, it should be noted that pipelining will not tend to reduce the circuit latency because the latency in terms of clock cycles will increase.
+For the former method, it should be noted that pipelining will not tend to reduce the latency of the datapath, whilst the latency in terms of clock cycles will actually increase.
 As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
@@
 
-In this paper, we describe an alternative circuit design methodology when considering tradeoffs between accuracy, performance and area.
+In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area.
 We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
@@
 
+\begin{itemize}
+	\item Detailed modeling methods of probabilistic errors generated in basic arithmetic primitives from two design scenarios to trade accuracy for performance: overclocking the datapath or truncating precisions that used throughout the datpath,
+	\item Exploring the accuracy-performance-area trade-offs for key arithmetic operators to illustrate the optimum architecture for a certain arithmetic function under a given requirement of silicon area,
+	\item Demonstration of the proposed findings analytically and experimentially from FPGA implementations that allowing rare timing violations to happen leads to an reduction of average errors or an improvement of performance over trancating the datapath precisions to meet timing.
+\end{itemize}
+
 The rest of this paper is organized as follows.
 It first reviews in detail the current literature regarding the approaches used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
-The analytical error models for two different adder structures: RCA and CSA, are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively.
+The analytical error models for two different adder structures: the ripple carry adder (RCA) and the carry-select adder (CSA), are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively.
 The decision of the optimum adder structure under the accuracy-performance-area trade-offs, is then put forward in Section~\ref{Section_OptimumAdder}.
-It is followed by a description of the probabilistic error models for CCM in Section~\ref{section_CCM}.
+It is followed by a description of the probabilistic error models for another arithmetic operator, the constant coefficient multiplier (CCM), in Section~\ref{section_CCM}.
 Section~\ref{Section_ExpSetup} discusses a practical experimental setup to verify our models and test the proposed design methodology.
-We then demonstration the benefits of our proposed approach in Section~\ref{Section_Experiments}.
-Finally, Section~\ref{Section_Conclusion} discusses the conclusions of this work and the possible research directions in the future.
+We then demonstrate the benefits of our proposed approach in Section~\ref{Section_Experiments}.
+Finally, conclusion of this work and possible future work are discussed in Section~\ref{Section_Conclusion}.
+%discusses the conclusions of this work and the possible research directions in the future.
 
@@
 A detailed summary of these methods can be found in~\cite{GeorgeDT11,lee2006accuracy}.
-The second stream uses these tools to choose the minimum precision within a datapath to satisfy an required accuracy specification~\cite{RoldaoWLop_Simulation}.
+In the second research field, these tools are utilized to choose the minimum precision within a datapath to satisfy a required accuracy specification~\cite{RoldaoWLop_Simulation}.
 In this work, we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
@@
 \subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
-However, the choice of precision is not the only source of error when designing a datapath.
+It is worth noting that the choice of precision is not the only source of error when designing a datapath.
 Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
-This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the international technology roadmap for semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
-This topic is expected to be of growing importance in the future, because we will face new challenges as the technology scales further.
+This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the International Technology Roadmap for Semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
+This topic is expected to be of growing importance in the future, because we will face new design challenges as the technology scales further.
 
@@
 For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively.
-Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
-However, the major problem of the BTWC work is the extra cost of silicon area due to the implementation of the checker circuits.
+Related work also includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
+However, the major problem of the BTWC work is the extra cost introduced by implementing the checker circuits.
+%of silicon area due to the implementation of the checker circuits.
 
@@
 DSP applications concerning human perceptions.
-In this case, even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
+In this case, even greater performance or power benefits can be achieved, as the design overhead of the checkers can be eliminated.
 Current research in this area focuses on designing probabilistic or imprecise circuits both at a software level and a hardware level.
-For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
+For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, which are mapped to different hardware with different speed-grades, supply voltages etc., respectively.
 This technique enables a relatively high service quality, in the meantime energy reduction can be obtained due to approximation.
@@
 
-While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance/energy efficiency.
+While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance and/or energy efficiency.
 For example, Lu et~al.
@@
 It is argued in this paper that our method can be easily applied onto existing hardware arithmetic operators such as RCAs and CCMs with almost no hardware overhead.
-We support this hypothesis experimentally and analytically by presenting theoretical probabilistic error models.
+We support this hypothesis analytically by presenting theoretical probabilistic error models and experimentally using FPGAs.
 
@@
 Adders serve as a key building block for arithmetic operations.
-Generally speaking, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
+In general, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
 As such, the philosophy of our approach is first exemplified with the analysis of a RCA.
-We later describe how this methodology can be extended to other arithmetic operators in Section~\ref{section_CCM} by discussing  the CCM that is commonly used in DSP applications and numerical algorithms.
-
-Typically the maximum frequency of a RCA is determined by the longest carry propagation.
+We later describe how this methodology can be extended to other arithmetic operators such as CSAs and CCMs, which are commonly used in DSP applicationsn and numerical algorithms, in Section~\ref{Section_CSA} and Section~\ref{section_CCM} respectively.
+
+%and  that are commonly used in DSP applications and numerical algorithms.
+
+Typically the maximum frequency of a RCA is determined by the longest carry propagation delay.
 Consequently, modern FPGAs offer built-in architectures for very fast ripple carry addition.
@@
 While the fast carry logic reduces the time of each individual carry-propagation delay, the overall delay of carry-propagation will eventually overwhelm the delay of sum generation of each LUT with increasing operand word-lengths.
-For our initial analysis, we assume that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay, and hence the critical path delay of the RCA is $\mu_{RCA}=n\mu$, as shown in~Fig.~\ref{FPGA adder}.
+We perform our initial analysis based on the assumption that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay within an FPGA.
+Hence the critical path delay of the RCA is given by~(\ref{Eq:RCA_delay}), as shown in Fig.~\ref{FPGA adder}.
+%
+\begin{eqnarray}\label{Eq:RCA_delay}
+	\mu_{RCA}=n\cdot\mu
+\end{eqnarray}
+
+% $\mu_{RCA}=n\mu$, as shown in~. 
 For an $n$-bit RCA, it follows that if the sampling period $T_S$ is greater than $\mu_{RCA}$, correct results will be sampled.
@@
    \setlength{\tabcolsep}{3.5pt}
-   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}) for two types of input data: the uniform data (Uni) and real image data from Lena (Lena).}{
+   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}) for Two Types of Input Data: the Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
    \centering
@@
    \setlength{\tabcolsep}{3.5pt}
-   \tbl{Frequency Speedups ($\%$) in Overclocking Scenario Under Various Error Budgets for two types of input data: uniform data (Uni) and real image data from Lena (Lena).}{
+   \tbl{Frequency Speedups ($\%$) in Overclocking Scenario Under Various Error Budgets for Two Types of Input Data: Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
 %   \vspace{-2ex}

### 2013-05-29 TCAD2013/overclocking_tcad.tex

@@
 
-\title{Imprecise Computing in Datapath Design: An Overclocking Approach}
+\title{Imprecise Datapath Design: An Overclocking Approach}
 %Imprecise Computing in Datapath Design: Precision Loss or Timing Violations}
-%Imprecise Datapath Design: An Overclocking Approach
+%Imprecise Datapath Design: An Overclocking Approach --this
 %Imprecise Computation Through Overclocking
@@
 \begin{abstract}
-As process scaling introduces significant performance variations, releasing the tight accuracy requirement rather than covering all possible worst cases would potentially offer the greater freedom to create a design with better performance or energy efficiency.
+As process scaling introduces significant performance variations, much more conservative timing margins will have to be applied to avoid timing violations.
+Potentially, releasing the tight accuracy requirement would offer greater freedom to create a design with better performance or energy efficiency.
 In this paper, we compare two different approaches that could trade accuracy for performance.
 One is the traditional approach where the precision used in the datapath is limited to meet a target latency.
-The other is a proposed new approach to boost the clock frequency by simply allowing the datapath to operate without timing closure.
-We demonstrate analytically and experimentally that on average, our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach, since the worst case caused by timing violations only happens rarely, while the precision loss results in errors to all data.
-We also show that for embedded applications where silicon area is also a limited factor, using the proposed approach on simple arithmetic primitives could achieve better accuracy or performance than using the traditional method on advanced operators.
+The other is a proposed new approach which simply allows the datapath to operate without timing closure.
+We demonstrate analytically and experimentally that on average our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach.
+This is because the worst case caused by timing violations only happens rarely, while the precision loss results in errors to most data.
+We also show that for basic arithmetic operations such as addition, applying our approach to simple operators (i.e.
+ripple carry adders) can achieve better accuracy or performance than using the traditional method to both original operators and intrinsically faster operators (i.e.
+carry select adders) which consumes the same silicon area.
+
+%for embedded applications where silicon area is also a limited factor, using the proposed approach on simple arithmetic primitives could achieve better accuracy or performance than using the traditional method on advanced operators.
 \end{abstract}
@@
 However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
-Although hardware designers traditionally employ safety margins to ensure a uniform functionality across a variety of possible working environments, there are two major problems if we keep using this approach nowadays.
-One is that the uniform performance should no longer be expected in the future, because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior.
-The other problem is that covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation.
-
-In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for performance improvement in embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
-In this case, designers tend to employ multi-core processors, heterogeneous systems and massive parallel accelerators to sustain the performance scaling.
-
-Specifically, large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications.
-However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or GPUs.
-Furthermore, timing analysis tools typically report a very conservative clock frequency to guarantee ``safe'' operations.
+Currently, hardware designers tend to employ conservative safety margins to ensure a uniform functionality across a variety of possible working environments.
+However, continuing with this approach could become very costly in the short term future.
+This is because the highly scaled CMOS devices would inevitably exhibit probabilistic or statistical behavior [xxx], meaning that we can no longer expect a uniform circuit performance.
+Furthermore, covering all possible worst cases would become increasingly difficult, expensive and result in large yield loss because of the variation [xxx].
+
+%In addition, we also notice that the clock frequency is no longer scaling significantly with time, and the dark silicon becomes an important issue in circuit design since energy efficiency is considered to be the main limitation for performance improvement in embedded or mobile applications~\cite{FutureMicroprocessor2005,DarkSilicon2011}.
+In this case, designers tend to employ multi-core processors, heterogeneous systems and massive parallel hardware accelerators to sustain the performance scaling.
+
+Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications [xxx].
+However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or graphics processing units (GPUs).
+
+%Furthermore, timing analysis tools typically report a very conservative clock frequency to guarantee ``safe'' operations.
 This substantially limits the potential performance of the device to a further extent.
 
-In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design, or reduce the precision throughout the datapath.
-For the former method, it should be noted that pipelining will not tend to reduce the circuit latency.
-Actually the latency in terms of clock cycles will increase.
-As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in datapath containing feedback where C-slow retiming is inappropriate.
-For the second approach, reducing the datapath precision would subtract out the latency, but at the cost of introducing quantization errors into the design.
-For hardware platforms such as FPGAs or ASICs, research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification has been an extensive topic~\cite{GeorgeDT11}, as it is possible to use a number system with customized precisions on these platforms.
+In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design or to reduce the precision throughout the datapath.
+For the former method, it should be noted that pipelining will not tend to reduce the circuit latency because the latency in terms of clock cycles will increase.
+As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
+For the second approach, reducing the datapath precision would reduce the latency at the cost of introducing quantization errors into the design.
+This has inspired research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification~\cite{GeorgeDT11}.
 A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.
 
-Unfortunately, neither of the conventional approaches tends to remove the conservative safety margin.
+Unfortunately, neither of these conventional approaches tends to remove the conservative safety margin.
 In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}.
@@
 \subsection{Word-length Optimization}\label{Section_Background_WL}
-There exists a significant amount of work demonstrating that optimizing the precision used throughout the datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
-As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification.
+There exists a significant amount of work demonstrating that optimizing the precision used throughout a datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
+There are two main research directions in this area.
+The first discusses methods to analyze the errors caused by the usage of finite precision and compute bounds on the worst-case errors seen at the output of the design.
+Related techniques include the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
+A detailed summary of these methods can be found in~\cite{GeorgeDT11, lee2006accuracy}.
+The second stream uses these tools to choose the minimum precision within a datapath to satisfy an required accuracy specification [xxx].
+In this work, we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
+The truncation errors derived in this process are then compared to the overclocking errors generated in our proposed new scenario.
+
+%As loosing precisions causes truncation or overflow errors, a main stream of research focus on analyzing errors generated from using the minimum precision and providing bounds of inputs to ensure the overall error are within the given accuracy specification.
 Current literatures report two major approaches in this area: the simulation-based approach [xxx] and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
@@
 \subsection{Imprecise Circuit Design Methodology}\label{Section_Background_Imprecise}
-Note that, however, the choice of precision is not the only source of errors when designing a datapath.
+However, the choice of precision is not the only source of error when designing a datapath.
 Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
-This strand of research is motivated by the drastic performance variations introduced by process scaling.
-
-%it becomes increasingly difficult and expensive to cover all possible worst cases when designing circuits, because the rapid scaling of technology introduces drastic variations on circuit performance.
-
-To address this problem, the international technology roadmap for semiconductors (ITRS07) pointed out that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects~\cite{semiconductor2007international}.
+This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the international technology roadmap for semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
 This topic is expected to be of growing importance in the future, because we will face new challenges as the technology scales further.
 
+%the drastic performance variations introduced by process scaling.
+
+%To address this problem, the international technology roadmap for semiconductors (ITRS07) pointed out that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects~\cite{semiconductor2007international}.
+This topic is expected to be of growing importance in the future, because we will face new challenges as the technology scales further.
+
 According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases.
-Research in this area is based on the observations that in practice, the worst case happens rarely.
 A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}.
@@
 Related work includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
-
-Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns.
-Meanwhile, many studies have shown that errors can be potentially tolerated in various applications, e.g.
+However, the major problem of the BTWC work is the extra cost of silicon area due to the implementation of the checker circuits.
+
+%Another key observation that has been made from existing work is that the worst-case normally happens with specific input patterns. Meanwhile, many studies have
+
+Another field of study has shown that errors can be potentially tolerated in various applications, e.g.
 DSP applications concerning human perceptions.
-In this case, an even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
-Current research in this area is focusing on designing probabilistic or imprecise circuits that employ techniques from either software level or hardware level.
+In this case, even greater performance/power benefits can be achieved, as the design overhead of the checkers can be eliminated.
+Current research in this area focuses on designing probabilistic or imprecise circuits both at a software level and a hardware level.
 For instance at the programming language level, a tool was proposed~\cite{EnerJ2011Uwash,Truffle2012Uwash} to divide the program into the precise parts and the approximate parts, both of which are mapped to different hardware with different speed-grades, supply voltages etc.
@@
 developed approximate adders at the transistor level and compared the energy efficiency of their proposed architectures over truncation of input word-length of conventional structures~\cite{Gupta2013TransCADICS}.
-
-However, the limitations of the existing work should not be neglected.
+However, we should note that using imprecise architectures means correct results would never be obtained for certain input patterns.
+Another limitation is that the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
+In addition, these techniques cannot be directly applied onto existing hardware platforms such as FPGAs.
+
+%However, the limitations of the existing work should not be neglected.
 Firstly, some techniques, such as employing several voltages regions within a ripple carry adder, are not practical to achieve in real situations, and the overhead of applying this technique is not discussed.
@@
 
-In this work, we propose an alternative methodology to remove these limitations.
+In this work, we propose an alternative methodology to remove the limitations of those existing approaches.
 It is argued in this paper that our method can be easily applied onto existing hardware arithmetic operators such as RCAs and CCMs with almost no hardware overhead.

### 2013-05-29 TRETS2013/TRETS_overclocking.tex

@@
 While the fast carry logic reduces the time of each individual carry-propagation delay, the overall delay of carry-propagation will eventually overwhelm the delay of sum generation of each LUT with increasing operand word-lengths.
-We perform our initial analysis based on the assumption that the carry propagation delay of each FA is a constant value $\mu$, which is a combination of logic delay and routing delay within an FPGA.
+We perform our initial analysis based on the assumption that the carry propagation delay of each FA is a constant value $\mu_c$, which is a combination of logic delay and routing delay within an FPGA.
 Hence the critical path delay of the RCA is given by~(\ref{Eq:RCA_delay}), as shown in Fig.~\ref{FPGA adder}.
@@
 \begin{eqnarray}\label{Eq:RCA_delay}
-	\mu_{RCA}=n\cdot\mu
+	\mu_{RCA}=n\cdot\mu_c
 \end{eqnarray}
@@
 For an $n$-bit RCA, it follows that if the sampling period $T_S$ is greater than $\mu_{RCA}$, correct results will be sampled.
-If, however, $T_S<\mu_{RCA}$, intermediate results will be sampled, potentially generating errors.
+If, however, faster-than-rated sampling frequencies are applied such that $T_S<\mu_{RCA}$, intermediate results will be sampled, potentially generating errors.
 
@@
 To this end, the operand word-length is truncated in order to meet the timing requirement.
-This process results in truncation or roundoff error.
-In our proposed new scenario, circuits are implemented with greater word-length, but are clocked beyond the safe region so that timing violations sometimes occur.
-This process generates ``overclocking error''.
+This process would result in truncation or roundoff error.
+In our proposed new design scenario, circuits are implemented with greater word-length, but are clocked beyond the safe region so that timing violations sometimes occur.
+This process would generate ``overclocking error''.
 
 \subsection{Probabilistic Model of Truncation Error}\label{section_RCA_TruncationError}
-For ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
-For our initial analysis, we assume every bit of each input is uniformly and independently generated.
+For the ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
+In our initial analysis, we assume every bit of each input is uniformly and independently generated.
 However, this assumption will be relaxed in Section~\ref{Section_Experiments} where the predictions are verified using real image data.
@@
 
-If the input signal of a circuit is $k$ bits, truncation error occurs when the input signal is truncated from $k$ bits to $n$ bits.
+If the input signal of a circuit contains $k$ bits, truncation error occurs when the input signal is truncated from $k$ bits to $n$ bits.
 Under this premise, the mean value of the truncated bits at signal input ($E_{Tin}$) is given by (\ref{ET at single input}).
@@
 
-Since we assume there are two mutually independent inputs to the RCA, the overall expectation of truncation error for the RCA is given by (\ref{TruncationError}).
-%
-\begin{eqnarray}\label{TruncationError}
+Since we assume there are two mutually independent inputs to the RCA, the overall expectation of truncation error for the RCA is given by (\ref{Eq:TruncationError}).
+%
+\begin{eqnarray}\label{Eq:TruncationError}
 %\small
@@
 \subsubsection{Generation of Overclocking Error}\label{subsub:Generation of Overclocking Error}
-For a given $T_S$, the maximum length of error-free carry propagation is described by~(\ref{Max.length of carry chain}), where $f_S$ denotes the sampling frequency.
-%
-\begin{eqnarray}\label{Max.length of carry chain}
-    b := \left\lceil \frac{T_S}{\mu} \right\rceil= \left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
+For a given $T_S$, the maximum length of error-free carry propagation is described by~(\ref{Eq:Max_CClength}), where $f_S$ denotes the sampling frequency.
+%
+\begin{eqnarray}\label{Eq:Max_CClength}
+    b := \left\lceil \frac{T_S}{\mu_c} \right\rceil= \left\lceil \frac{1}{\mu_c\cdot f_S}\right\rceil
 \end{eqnarray}
@@
 However, since the length of an actual carry chain during execution is dependent upon input patterns, in general, the worst case may occur rarely.
-To determine when this timing constraint is not met and the size of the error in this case, we expand standard results~\cite{DigitalICDesign} to the following statements, which examine carry generation, propagation and annihilation, as well as the corresponding summation results of a single bit $i$, according to the relationship between its input patterns $A_i$ and $B_i$:
+To determine when this timing constraint is not met and the size of the error in this case, we expand standard results~\cite{DigitalICDesign} to the following statements, which examine carry generation, propagation and annihilation, as well as the corresponding summation results of a single bit $i$ within an $n$-bit RCA ($0\leq i<n$), according to the relationship between its input patterns $A_i$ and $B_i$:
 %
  \begin{itemize}
-   \item If $A_i=B_i=1$, a new carry chain is generated at bit $i$, and $S_i=C_{i-1}$;
-   \item If $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=0$;
-   \item If $A_i=B_i$, the current carry chain annihilates at bit $i$, and $S_i=1$.
+   \item Carry generation: $A_i=B_i=1$, a new carry chain is generated at bit $i$, and $S_i=C_{i-1}$;
+   \item Carry propagation: $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=0$;
+   \item Carry annihilation: $A_i=B_i$ (either $0$ or $1$), the current carry chain annihilates at bit $i$, and $S_i=1$.
  \end{itemize}
@@
 For an $n$-bit RCA, let $C_{tm}$ denote the carry chain generated at bit $S_t$ with the length of $m$ bits.
-For a certain $f_S$, the maximum length of error-free carry propagation, $b$, is determined through (\ref{Max.length of carry chain}).
+For a certain $f_S$, the maximum length of error-free carry propagation, $b$, is determined through (\ref{Eq:Max_CClength}).
 The presence of overclocking error requires $m>b$.
-Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{t_RCA}) and (\ref{m_RCA}):
+Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{Eq:t_RCA}) and (\ref{Eq:m_RCA}):
 %
@@
 %\scriptsize
-  \label{t_RCA}  0&\leq t \leq n-b\\
-    b&<m\leq n+1-t      \label{m_RCA}
+  \label{Eq:t_RCA}  0&\leq t \leq n-b\\
+    b&<m\leq n+1-t      \label{Eq:m_RCA}
 %    \vspace{-1ex}
@@
 For $C_{tm}$, correct results will be generated from bit $S_t$ to bit $S_{t+b-1}$.
-Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Output Error}), where $\hat{S_i}$ and $S_i$ denote the actual and error-free output of bit $i$ respectively.
-%
-\begin{eqnarray}\label{Output Error}
+Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Eq:Output_Error}), where $\hat{S_i}$ and $S_i$ denote the actual value and error-free value of outputs at bit $i$, respectively.
+%
+\begin{eqnarray}\label{Eq:Output_Error}
 %\small
@@
 However, when a timing violation occurs, the carry will not propagate through all these bits.
-Substituting these values into (\ref{Output Error}) yields (\ref{etm}).
-Interestingly, the value of overclocking error has no dependence on the length of carry chain $m$.
-%
-\begin{eqnarray}\label{etm}
+Hence we have $\hat{S}_{t+b}=\hat{S}_{t+b-1}=\cdots=\hat{S}_{t+m-2}=1$ for carry propagation, and $\hat{S}_{t+m-1}=0$ for carry annihilation.
+Substituting these values into (\ref{Eq:Output_Error}) yields (\ref{Eq:etm}).
+Interestingly as seen in~(\ref{Eq:etm}), the magnitude of overclocking error has no dependence on the length of carry chain $m$.
+%
+\begin{eqnarray}\label{Eq:etm}
 %\small
@@
 The carry chain $C_{tm}$ occurs when there is a carry generated at bit $t$, a carry annihilated at bit $t+m-1$ and the carry propagates in between.
-Consequently, its probability $P_{tm}$ is given by (\ref{Ptm_RCA}).
-%
-\begin{eqnarray}\label{Ptm_RCA}
+Consequently, its probability $P_{tm}$ is given by (\ref{Eq:Ptm_RCA}).
+%
+\begin{eqnarray}\label{Eq:Ptm_RCA}
 %\small
@@
 
-Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$, so $P_{tm}$ can be obtained by~(\ref{Ptm2}).
-Note that~(\ref{Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
-%
-\begin{eqnarray}\label{Ptm2}
+Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$, so $P_{tm}$ can be obtained by~(\ref{Eq:Ptm2}).
+Note that~(\ref{Eq:Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
+%Furthermore, (\ref{Eq:Ptm_RCA}) can be employed for any probability distribution of inputs, as long as the value of own.
+%
+\begin{eqnarray}\label{Eq:Ptm2}
 %\small
@@
 
+Furthermore, it can be seen that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
+
 \subsubsection{Expectation of Overclocking Error}
-Expectation of overclocking error can be expressed by (\ref{Eo_exp}).
-%
-\begin{eqnarray}\label{Eo_exp}
+Expectation of overclocking error can be expressed by (\ref{Eq:Eo_exp}).
+%
+\begin{eqnarray}\label{Eq:Eo_exp}
 %\small
@@
 
-Using $P_{tm}$ and $e_{tm}$ from (\ref{etm}) and (\ref{Ptm2}) respectively, $E_O$ can be obtained by (\ref{Eo}).
-%
-\begin{eqnarray}\label{Eo}
+Using $P_{tm}$ and $e_{tm}$ from (\ref{Eq:etm}) and (\ref{Eq:Ptm2}) respectively, $E_O$ can be obtained in (\ref{Eq:Eo}).
+%
+\begin{eqnarray}\label{Eq:Eo}
 %\small
@@
 \subsection{Comparison between Two Scenarios}\label{section_RCA_Comparison}
-In the traditional scenario, the word-length of RCA must be truncated, using $n=b-1$ bits, in order to meet a given $f_S$. The error expectation is then given by (\ref{Eo_trad_RCA}).
-%
-\begin{eqnarray}\label{Eo_trad_RCA}
+In the traditional scenario, the word-length of RCA must be truncated, using $n=b-1$ bits, in order to meet a given $f_S$. The error expectation is then given by (\ref{Eq:Eo_trad_RCA}).
+%
+\begin{eqnarray}\label{Eq:Eo_trad_RCA}
 %\small
@@
 
-Overclocking errors are allowed to happen in the second scenario, therefore the word-length of RCA is set to be equal to the input word-length, that is, $n=k$.
-Hence we obtain (\ref{Eo_new_RCA}) according to (\ref{Eo}).
-%
-\begin{eqnarray}\label{Eo_new_RCA}
+Overclocking errors are allowed to happen in our proposed new scenario.
+Therefore the word-length of RCA is set to be equal to the input word-length, that is, $n=k$.
+Hence we obtain (\ref{Eq:Eo_new_RCA}) according to (\ref{Eq:Eo}).
+%
+\begin{eqnarray}\label{Eq:Eo_new_RCA}
 %\vspace{-1ex}
@@
 
-Comparing (\ref{Eo_new_RCA}) and (\ref{Eo_trad_RCA}), we have (\ref{Comparison RCA}).
+Comparing (\ref{Eq:Eo_new_RCA}) and (\ref{Eq:Eo_trad_RCA}), we have (\ref{Eq:Comparison RCA}).
 This equation indicates that by allowing timing violations, the overall error expectation of RCA outputs drops by a factor of 2 in comparison to traditional scenario.
@@
 %
-\begin{eqnarray}\label{Comparison RCA}
+\begin{eqnarray}\label{Eq:Comparison RCA}
 %\vspace{-1ex}
@@
 \subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, alternative adder architectures, such as carry select adder (CSA) have been proposed to boost performance.
-For CSA, the carry chain is divided into multiple overlapped sections to increase the operating speed, as shown in Fig.~\ref{Fig_CSA_Structure}.
-There are multiple stages within a CSA.
-Each stage contains two RCAs and two multiplexers, as seen in Fig.~\ref{Fig_CSA_SingleStage}.
-For a given input, two additions are performed simultaneously where the carry input is zero and one respectively.
+Since the delay of RCA is determined by the length of carry chain, alternative adder architectures, such as carry select adder (CSA), have been proposed to boost performance.
+In a CSA, the carry chain is divided into multiple overlapped stages, while each stage contains two RCAs and two multiplexers, as shown in Fig.~\ref{Fig_CSA_Structure} and Fig.~\ref{Fig_CSA_SingleStage}, respectively.
+For a given input, two additions are performed simultaneously within a single stage where the carry input is zero and one seperately.
 One of these two results is then selected according to the actual carry input.
 Although this structure brings performance benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
-Furthermore, in FPGA technology, multiplexers are expensive.
+Furthermore, in FPGA technology, multiplexers are expensive to implement.
 Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of RCA and CSA in this section.
@@
 \subsection{Timing Models for Carry Select Adder}
-We initially model the CSA in order to understand the relationship between the operating frequency and maximum word-length of the CSA.
+We initially model the CSA in order to understand the relationship between the operating frequency and the maximum word-length of the CSA.
 This information can then be employed to determine the truncation error based on the models presented in Section~\ref{section_RCA_TruncationError}.
@@
 We still follow the aforementioned assumption that the critical path delay of the CSA is due to carry propagation and multiplexing the carry output, instead of generating the sum outputs.
-It should be noted that unlike other stages, the least significant stage of the CSA is only built by one RCA without multiplexers, since it is directly driven by the carry input.
-Hence we can obtain the delay of the $i^{th}$ stage as presented in~(\ref{CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
-%
-\begin{eqnarray}\label{CSA_SingleStageDelay}
+It should be noted that unlike other stages, the least significant stage of the CSA can be built only by one RCA without multiplexers, since it is directly driven by the carry input.
+Hence we can obtain the delay of the $i^{th}$ stage as presented in~(\ref{Eq:CSA_SingleStageDelay}), where $\mu_{c}$, $\mu_{mux}$ and $n_i$ denote the delay of $1$-bit carry propagation, the delay of multiplexing and the word-length of the $i^{th}$ stage of the CSA, respectively.
+%
+\begin{eqnarray}\label{Eq:CSA_SingleStageDelay}
   d_i=\left\{
@@
 
-Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{CSA_DelayEqual}).
-%
-\begin{eqnarray}\label{CSA_DelayEqual}
+Under the timing-driven design environment, the delay of each stage of CSA is equalized in order to achieve the fastest operation, as presented in~(\ref{Eq:CSA_DelayEqual}).
+%
+\begin{eqnarray}\label{Eq:CSA_DelayEqual}
   d_{s-1}=d_{s-2}=\cdots=d_{0}
@@
 
-In this case, combining~(\ref{CSA_SingleStageDelay}) and (\ref{CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{CSA_DelayRep}).
-%
-\begin{eqnarray}\label{CSA_DelayRep}
+In this case, combining~(\ref{Eq:CSA_SingleStageDelay}) and (\ref{Eq:CSA_DelayEqual}) yields $n_i$, which is represented by the word-length of the most significant stage $n_{s-1}$, in (\ref{Eq:CSA_DelayRep}).
+%
+\begin{eqnarray}\label{Eq:CSA_DelayRep}
  n_i=\left\{
@@
 
-Sum up $n_i$ to give the total word-length of the CSA in (\ref{CSA_WL}).
-%
-\begin{eqnarray}\label{CSA_WL}
+Sum up $n_i$ to give the total word-length of the CSA in (\ref{Eq:CSA_WL}).
+%
+\begin{eqnarray}\label{Eq:CSA_WL}
 %  \begin{split}
@@
 
-Conventionally under a given frequency constraint, the word-length of RCA is truncated by using $n_{RCA}=b-1$ bits, where $b$ is determined by~(\ref{Max.length of carry chain}).
-Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{TimingConstraint_CSA}).
-%
-\begin{eqnarray}\label{TimingConstraint_CSA}
+Conventionally under a given frequency constraint, the word-length of RCA is truncated by using $n_{RCA}=b-1$ bits, where $b$ is determined by~(\ref{Eq:Max_CClength}).
+Similarly for CSA, the word-length of each stage should be selected in order to satisfy~(\ref{Eq:TimingConstraint_CSA}).
+%
+\begin{eqnarray}\label{Eq:TimingConstraint_CSA}
   \begin{matrix}
@@
 
-Hence for the same frequency requirement, we can form the relationship between the delay of the most significant stage of CSA and the delay of RCA, as given by~(\ref{WL_MSB_CSA}),
-%
-\begin{eqnarray}\label{WL_MSB_CSA}
+Hence for the same frequency requirement, we can form the relationship between the delay of the most significant stage of CSA and the delay of RCA, as given by~(\ref{Eq:WL_MSB_CSA}),
+%
+\begin{eqnarray}\label{Eq:WL_MSB_CSA}
     \mu_c\cdot (b-1) = n_{s-1}\cdot\mu_c+\mu_{mux}
@@
 
-Substitute~(\ref{WL_MSB_CSA}) into (\ref{CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of $b$, as presented in~(\ref{CSA_Timing}).
-%
-\begin{eqnarray}\label{CSA_Timing}
+Substitute~(\ref{Eq:WL_MSB_CSA}) into (\ref{Eq:CSA_WL}) to replace $n_{s-1}$, we derive the representation of the word-length of CSA in terms of $b$, as presented in~(\ref{Eq:CSA_Timing}).
+%
+\begin{eqnarray}\label{Eq:CSA_Timing}
   n_{CSA}=s\cdot (b-1)-\frac{\mu_{mux}}{\mu_{c}}\cdot\frac{(s+2)(s-1)}{2}
@@
 We perform post place-and-route simulations on the CSA with 2 stages using Xilinx Virtex-6 FPGA.
-The delay of the $i^{th}$ stage $d_i$ in~(\ref{CSA_SingleStageDelay}) is recorded with respect to different word-lengths.
-The total word-length of CSA can be predicted through~(\ref{CSA_Timing}).
+The delay of the $i^{th}$ stage $d_i$ in~(\ref{Eq:CSA_SingleStageDelay}) is recorded with respect to different word-lengths.
+The total word-length of CSA can be predicted through~(\ref{Eq:CSA_Timing}).
 In addition, the maximum word-lengths of the 2-stage CSA and RCA are obtained experimentally by increasing $n_{CSA}$ and $n_{RCA}$ respectively until errors are observed at the output.
@@
 Fig.~\ref{Fig_CSA2stage_Timing} also highlights that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
-The RCA only outperforms than the CSA when very high frequency is applied.
+The RCA only outperforms when very high frequency is applied.
 This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
@@
 However, the accuracy benefits brought by CSA comes at the cost of a large area overhead.
-Fig.~\ref{Fig_CSA3stage_Area} depicts the number of Look-Up Tables (LUTs) in the FPGA used for an RCA, a 2-stage CSA and a 3-stage CSA.
+Fig.~\ref{Fig_CSA3stage_Area} depicts the number of LUTs in the FPGA used for an RCA, a 2-stage CSA and a 3-stage CSA.
 It can be seen that in order to meet a given frequency, the 3-stage CSA consumes $2.4\times\sim3.7\times$ area than RCA, while the 2-stage CSA requires $1.7\times\sim3.1\times$ extra area.
@@
 If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
-In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
-%
-\begin{eqnarray}\label{MRE}
+In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+%
+\begin{eqnarray}\label{Eq:MRE}
   MRE=\left|\frac{E_{error}}{E_{out}}\right|\times 100\%
@@
 Let $E_{Tin}$ and $E_{Tout}$ denote the expectation of truncation error at the input and output of CCM respectively.
-We then have (\ref{Et_CCM}), where $coe$ denotes the coefficient value of the CCM, and $E_{Tin}$ can be obtained according to~(\ref{TruncationError}).
-%
-\begin{eqnarray}\label{Et_CCM}
+We then have (\ref{Eq:Et_CCM}), where $coe$ denotes the coefficient value of the CCM, and $E_{Tin}$ can be obtained according to~(\ref{Eq:TruncationError}).
+%
+\begin{eqnarray}\label{Eq:Et_CCM}
 %\vspace{-1ex}
@@
 \subsubsection{Absolute Value of Overclocking Error}
-The absolute value of overclocking error of carry chain $C_{tm}$ is increased by a factor of $2^s$ due to shifting, compared to RCA.
-Hence $e_{tm}$ in CCM can be modified from (\ref{etm}) to give (\ref{etm_CCM}).
-%
-\begin{eqnarray}\label{etm_CCM}
+The absolute value of overclocking error of carry chain $C_{tm}$ is increased by a factor of $2^s$ due to shifting, when compared to RCA.
+Hence $e_{tm}$ in CCM can be modified from (\ref{Eq:etm}) to give (\ref{Eq:etm_CCM}).
+%
+\begin{eqnarray}\label{Eq:etm_CCM}
 %\vspace{-1ex}
@@
 For the first two types of carry chain $C_{tm}1$ and $C_{tm}2$, the probability of carry propagation and annihilation is $1/2$ and the probability of carry generation is $1/4$, under the premise that all bits of input signal are mutually independent.
-Therefore (\ref{Ptm_CCM1}) can be obtained by substituting this into~(\ref{Ptm_RCA}).
-%
-\begin{eqnarray}\label{Ptm_CCM1}
+Therefore (\ref{Eq:Ptm_CCM1}) can be obtained by substituting this into~(\ref{Eq:Ptm_RCA}).
+%
+\begin{eqnarray}\label{Eq:Ptm_CCM1}
 %\vspace{-1ex}
@@
 
-For carry annihilation of $C_{tm}3$, $a_{n-1}=a_{n-1}$, which is always true. Thus the probability of $C_{tm}3$ is given by (\ref{Ptm_CCM2}).
-%
-\begin{eqnarray}\label{Ptm_CCM2}
+For carry annihilation of $C_{tm}3$, it requires $a_{n-1}=a_{n-1}$, which is always true. Thus the probability of $C_{tm}3$ is given by (\ref{Eq:Ptm_CCM2}).
+%
+\begin{eqnarray}\label{Eq:Ptm_CCM2}
 %\vspace{-1ex}
@@
 
-Altogether, $P_{tm}$ for a CCM is given by (\ref{Ptm_CCM}).
-\begin{eqnarray}\label{Ptm_CCM}
+Altogether, $P_{tm}$ for a CCM is given by (\ref{Eq:Ptm_CCM}).
+%
+\begin{eqnarray}\label{Eq:Ptm_CCM}
 %\small
@@
 \subsubsection{Expectation of Overclocking Error}
-Since the carry chain of a CCM will not propagate over $a_{n-1}$, the upper bound of parameter $t$ and $m$ should be modified from (\ref{t_RCA}) and (\ref{m_RCA}) to give (\ref{t_CCM}) and (\ref{m_CCM}).
+Since the carry chain of a CCM will not propagate over $a_{n-1}$, the upper bound of parameter $t$ and $m$ should be modified from (\ref{Eq:t_RCA}) and (\ref{Eq:m_RCA}) to give (\ref{Eq:t_CCM}) and (\ref{Eq:m_CCM}).
 %
@@
 %\scriptsize
-  \label{t_CCM} 0\leqslant t\leqslant n-b-1\\
-  \label{m_CCM} b<m\leqslant n-t
+  \label{Eq:t_CCM} 0\leqslant t\leqslant n-b-1\\
+  \label{Eq:m_CCM} b<m\leqslant n-t
 %  \vspace{-1ex}
@@
 
-Finally, by substituting (\ref{Ptm_CCM}) and (\ref{etm_CCM}) with modified bounds of $t$ and $m$ into (\ref{Eo_exp}), we obtain the expectation of overclocking error for a CCM to be given by (\ref{Eo_CCM}).
-%
-\begin{eqnarray}\label{Eo_CCM}
+Finally, by substituting (\ref{Eq:Ptm_CCM}) and (\ref{Eq:etm_CCM}) with modified bounds of $t$ and $m$ into (\ref{Eq:Eo_exp}), we obtain the expectation of overclocking error for a CCM to be given by (\ref{Eq:Eo_CCM}).
+%
+\begin{eqnarray}\label{Eq:Eo_CCM}
 %\vspace{-1ex}
@@
 \subsection{CCM with Multiple RCAs and Shifters}\label{CCM_Multi}
-In the case where a CCM is composed of two shifters and one RCA, such as operation $\!B\!=\!20A\!=\!(\!A<<2)+(\!A<<4)$, let the shifted bits be denoted as $s_1$ and $s_2$ respectively.
-Hence the equivalent $s$ in (\ref{Eo_CCM}) can be obtained through~(\ref{ShiftNo}).
-
-\begin{eqnarray}\label{ShiftNo}
+In the case where a CCM is composed of two shifters and one RCA, such as operation $B=20A=(A<<2)+(A<<4)$, let the shifted bits be denoted as $s_1$ and $s_2$ respectively.
+Hence the equivalent $s$ in (\ref{Eq:Eo_CCM}) can be obtained through~(\ref{Eq:ShiftNo}).
+%
+\begin{eqnarray}\label{Eq:ShiftNo}
 %\footnotesize
@@
   \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software.
-Note that the error-free data are obtained by either pre-computation or initial run with low frequencies.}
+The error-free data are obtained by either pre-computation or initial run with low frequencies.}
   \label{Test Framework}
@@
 
-For example, the predicted frequencies and the actual frequencies of a $5^{th}$~order FIR filter using different word-lengths are depicted in Fig.~\ref{TimingMargin}.
+For example, the predicted frequencies and the actual frequencies of a $5^{th}$~order FIR filter using different word-lengths are depicted in Fig.~\ref{Fig:TimingMargin}.
 The ``actual'' maximum frequencies are computed by increasing the operating frequency from the rated value until errors are observed at the output; the maximum operating frequency with correct output is recorded for the current word-length.
-As can be seen in Fig.~\ref{TimingMargin}, the circuit can operate without errors at a much higher frequency in practice than predicted according to our experiments.
+As can be seen in Fig.~\ref{Fig:TimingMargin}, the circuit can operate without errors at a much higher frequency in practice than predicted according to our experiments.
 A maximum speed differential of $3.2\times$ is obtained when the input signal is 5-bit.
 
-\begin{figure}[t]
+\begin{figure}[ht]
   \centering
@@
 The solid line is obtained through real FPGA tests using our platform.}
-  \label{TimingMargin}
+  \label{Fig:TimingMargin}
   %\vspace{-3.5ex}
@@
 To do this, for each truncated word-length, we select the maximum frequency at which we see no overclocking error on the FPGA board in our lab.
-For example, in Fig.~\ref{TimingMargin}, the operating frequency of the design when the word-lengths are truncated to 8,~5 and 2 bits are 400MHz,~450MHz and 500MHz respectively.
-
-Fig.~\ref{TimingMargin} also demonstrates that when the circuit is truncated, it allows the circuit to operate at a higher frequency than the frequency of full precision implementation.
+For example, in Fig.~\ref{Fig:TimingMargin}, the operating frequency of the design when the word-lengths are truncated to 8,~5 and 2 bits are 400MHz,~450MHz and 500MHz respectively.
+
+Fig.~\ref{Fig:TimingMargin} also demonstrates that when the circuit is truncated, it allows the circuit to operate at a higher frequency than the frequency of full precision implementation.
 However, a non-uniform period change can be observed for both results.
 For instance, the maximum operating frequency keeps almost constant when the operand word-length reduces from 8 to 6 or from 5 to 3 in both the experimental results and those of timing analyzer.
-This will cause a slight deviation between our analytical model which assumes that the single bit carry propagation delay to be a constant value, as discussed in (\ref{Eo_trad_RCA}) with expression $n=b-1$.
-This deviation will be influenced by many factors including how the architecture has been packed onto LUTs and CLBs and process variation causing non-uniform interconnection delays~\cite{FPGAPV}.
+This will cause a slight deviation between our analytical model which assumes that the single bit carry propagation delay to be a constant value, as discussed in (\ref{Eq:Eo_trad_RCA}) with expression $n=b-1$.
+This deviation will be influenced by many factors such as how the architecture has been packed onto LUTs and CLBs.
+In addition, process variation might cause non-uniform interconnection delays~\cite{FPGAPV}.
 However, we shall see that our model remains close to the true empirical results in Section~\ref{Section_Experiments}.
@@
 This is determined through static analysis.
-The second depends on timing information, such as the single bit carry propagation delay $\mu$.
-In order to keep consistency with the assumption made in models that $\mu$ is a fixed value, it is obtained according to the actual FPGA measurement results.
+The second depends on timing information, such as the single bit carry propagation delay $\mu_c$.
+In order to keep consistency with the assumption made in models that $\mu_c$ is a fixed value, it is obtained according to the actual FPGA measurement results.
 
@@
 This process repeats until the maximum frequency $f_{n-1}$ is applied in~(\ref{Eq_decideMu_2}).
-Based on these frequency values, $\mu$ can be determined.
-
+Based on these frequency values, $\mu_c$ can be determined.
+%
 \begin{eqnarray}\label{Eq_decideMu_0}
@@
 \subsection{Case study: FIR filter}
-We first assess the accuracy of our proposed models of error.
-The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data.
+We first assess the accuracy of our proposed models of errors.
+We record the value of MRE based on (\ref{Eq:MRE}) in a $5^{th}$~order FIR with respect to different operating frequencies.
+The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{Fig:FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data.
 The results demonstrate that our models match well with the practical results obtained using the uniform independent inputs.
@@
 Two types of inputs are employed in the overclocking scenario: the uniformly distributed data and the real image data from Lena.}
-  \label{FIR}
+  \label{Fig:FIR}
 \end{figure}
@@
 \caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) when operating frequencies are $425MHz$, $450MHz$, $480MHz$ and $520MHz$ respectively (from left to right).}
-\label{FIR_Lena}
+\label{Fig:FIR_Lena}
 \end{figure}
 
-According to Fig.~\ref{FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as the analytical model validates.
+According to Fig.~\ref{Fig:FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as the analytical model validates.
 In addition, we see that using real data, more significant reduction of MRE are achieved, and that no errors are observed when frequency is initially increased.
@@
 
-The output images of the FIR filter for both of the two scenarios with increasing frequencies are presented in Fig.~\ref{FIR_Lena}, from which we can clearly see the differences between the errors generated in these two scenarios.
+The output images of the FIR filter for both of the two scenarios with increasing frequencies are presented in Fig.~\ref{Fig:FIR_Lena}, from which we can clearly see the differences between the errors generated in these two scenarios.
 In the overclocking scenario, we observe errors in the MSBs for certain input patterns.
-This leads to ``salt and pepper noise'', as shown on the images in the top row of Fig.~\ref{FIR_Lena}.
-In the traditional scenario, truncation causes an overall degradation of the whole image, as can be seen in the bottom row of Fig.~\ref{FIR_Lena}.
-Furthermore, it is difficult to recover from the latter type of error, since it is generated due to precision loss.
-
-In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.~\ref{Fig_CarryDistribution}.
-As the input data is 8-bit, the longest possible carry chain length is 9-bit.
+This leads to ``salt and pepper noise'', as shown on the images in the top row of Fig.~\ref{Fig:FIR_Lena}.
+In the traditional scenario, truncation causes an overall degradation of the whole image, as can be seen in the bottom row of Fig.~\ref{Fig:FIR_Lena}.
+Furthermore, it is worth noting that recovering from the latter type of error is more difficult, since it is generated due to precision loss.
+
+%it is difficult to recover from the latter type of error, since it is generated due to precision loss.
+
+In addition, we record the probability distribution of different length of carry chains using an 8-bit RCA with both data types, as shown in Fig.~\ref{Fig:CarryDistribution}.
+As the input data is 8-bit, the longest possible carry chain is of length 9-bit.
 It can be observed that when using Lena data,  the probability is only higher for carry chain with a length of 3-bit.
@@
 For the image data Lena, one input of RCA uses the original data and the other uses the delayed original data for several clock cycles.}
-  \label{Fig_CarryDistribution}
+  \label{Fig:CarryDistribution}
 \end{figure}
@@
 Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
-For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Relative Reduction MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
-
-\begin{eqnarray}\label{Relative Reduction MRE}
+For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Table:Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Eq:Relative_Reduction_MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
+%
+\begin{eqnarray}\label{Eq:Relative_Reduction_MRE}
   \frac{MRE_{Trad}-MRE_{ovrc}}{MRE_{Trad}}\times 100\%
@@
 In this table, the frequency is normalized to the maximum error-free frequency for each design when the input signal is 8-bit.
-The N/A in Table~\ref{Ratio_MRE} refers to the situations where a certain frequency simply cannot be achieved using the traditional scenario.
+The N/A in Table~\ref{Table:Ratio_MRE} refers to the situations where a certain frequency simply cannot be achieved using the traditional scenario.
 It can be seen that a significant reduction of MRE can be achieved using the proposed overclocking scenario, and the geometric mean reduction varies from $67.9\%$ to $95.4\%$ using uniform input data.
-Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{FIR}.
-
-\begin{table*}[htbp]
+Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{Fig:FIR}.
+
+\begin{table*}[tbp]
  %\vspace{-2ex}
@@
    \setlength{\tabcolsep}{3.5pt}
-   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Relative Reduction MRE}) for Two Types of Input Data: the Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
+   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Eq:Relative_Reduction_MRE}) for Two Types of Input Data: the Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
    \centering
@@
    \end{threeparttable}}
-   \label{Ratio_MRE}
+   \label{Table:Ratio_MRE}
 % \vspace{-1ex}
@@
 
-\begin{table*}[htbp]
+Table~\ref{Table:Max_Frequency} illustrates the frequency speedups for each design when the specified error tolerance varies from 0.05\% to 50\%.
+For all designs, we see that the overclocking scenario still outperforms the traditional scenario for each MRE budget in terms of operating frequency.
+Likewise, the frequency speedup is higher for real image inputs than uniform inputs.
+The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
+
+\begin{table*}[tbp]
  %\vspace{-2ex}
@@
    \normalsize
-   \label{Max_Frequency}
+   \label{Table:Max_Frequency}
 %   \vspace{-3ex}
@@
 
-Table~\ref{Max_Frequency} illustrates the frequency speedups for each design when the specified error tolerance varies from 0.05\% to 50\%.
-For all designs, we see that the overclocking scenario still outperforms the traditional scenario for each MRE budget in terms of operating frequency.
-Likewise, the frequency speedup is higher for real image inputs than uniform inputs.
-The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
-
 \subsection{Area Overhead of Our Approach}
 For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario.
-Consequently, the area overheads of our approach are summarized in Table~\ref{Table_AreaFrequency} and Table~\ref{Table_AreaError} for both design goals.
+Consequently, the area overheads of our approach are summarized in Table~\ref{Table:AreaFrequency} and Table~\ref{Table:AreaError} for both design goals.
 In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms.
 It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
+This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the our proposed new approach, especially when the clock frequency is initially increased.
 
 An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies.
-As seen in Table~\ref{Table_AreaFrequency}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
-Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Table~\ref{Table_AreaError}, because a specific error budget can be tolerated.
-
-In general, we can observe a relatively small area overhead of our approach, especially when frequency is initially increased or with a small error budget (i.e. $\sim10\%$).
-
-\begin{table*}[htbp]
+As seen in Table~\ref{Table:AreaFrequency}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
+Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Table~\ref{Table:AreaError}, because a specific error budget can be tolerated.
+
+%In general, we can observe a relatively small area overhead of our approach, especially
+
+In general, a very small area overhead of our approach can be observed when the design is initially operated beyond the safe region with higher frequencies or with a small error budget (i.e.
+$\sim10\%$).
+In addition at even higher operating frequencies or larger error specifications, our approach achieves large performance or accuracy improvements at a cost of a relatively small extra area.
+%frequency is initially increased or with a small error budget (i.e. $\sim10\%$).
+
+\begin{table*}[tbp]
  %% increase table row spacing, adjust to taste
@@
    \end{threeparttable}}
-   \label{Ratio_MRE}
+   \label{Table:AreaFrequency}
  \end{table*}
 
- \begin{table*}[htbp]
+ \begin{table*}[tbp]
  %% increase table row spacing, adjust to taste
@@
    \normalsize
-   \label{Max_Frequency}
+   \label{Table:AreaError}
  \end{table*}
@@
 In addition, an alternative number representation metric by using redundant numbers could be employed to largely reduce the lengths of carry chains.
-While research in this area mainly focus on the ASIC domain~\cite{RedundantMult_1985,RedundantMult_1987}, it is worthwhile exploring the potential benefits and overheads when employing this method in our approach.
+While research in this area mainly focus on the ASIC domain~\cite{RedundantMult_1985,RedundantMult_1987}, it is worthwhile exploring the potential benefits and overheads when employing this method using our approach.
 

### 2013-06-21 TRETS2013/TRETS_overclocking.tex
TRETS revised by George, words and sentences

@@
 \author{KAN SHI, DAVID BOLAND\\
-and GEORGE A CONSTANTINIDES
+and GEORGE A. CONSTANTINIDES
 \affil{Imperial College London}
@@
 \begin{abstract}
-As process scaling introduces significant performance variations, much more conservative timing margins will have to be applied to avoid timing violations.
-Potentially, releasing the tight accuracy requirement would offer greater freedom to create a design with better performance or energy efficiency.
+%As process scaling introduces significant performance variations, much more conservative timing margins will have to be applied to avoid timing violations. Potentially, r
+Releasing the tight accuracy requirement would potentially offer greater freedom to create a design with better performance or energy efficiency.
 In this paper, we compare two different approaches that could trade accuracy for performance.
@@
 The other is a proposed new approach which simply allows the datapath to operate without timing closure.
-We demonstrate analytically and experimentally that on average our approach obtains either smaller errors or faster operating frequencies in comparison to the traditional approach.
-This is because the worst case caused by timing violations only happens rarely, while the precision loss results in errors to most data.
-We also show that for basic arithmetic operations such as addition, applying our approach to simple operators (i.e.
+We demonstrate analytically and experimentally that on average our approach obtains either smaller errors for equivalent faster operating frequencies in comparison to the traditional approach.
+This is because the worst case caused by timing violations only happens rarely, while precision loss results in errors to most data.
+We also show that for basic arithmetic operations such as addition, applying our approach to the simple building block of ripple carry adders can achieve better accuracy or performance than using faster adder designs to achieve similar latency.
+
+ %operators (i.e.
 ripple carry adders) can achieve better accuracy or performance than using the traditional method to both original operators and intrinsically faster operators (i.e.
@@
 \section{Introduction}
-With the continuous scaling of CMOS technology to the nanometer regime, circuit performance has increased tremendously over the past decades.
+%With the continuous scaling of CMOS technology to the nanometer regime, circuit performance has increased tremendously over the past decades.
 However, the drastic variations introduced by higher integration densities is anticipated to be the major obstacle when designing reliable, high performance circuits.
@@
 
+Performance is a critical issue when designing embedded computing systems.
 Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications~\cite{UnderwoodFPGAvsCPU,David_MINRES}.
@@
 For the former method, it should be noted that pipelining will not tend to reduce the latency of the datapath, whilst the latency in terms of clock cycles will actually increase.
-As a result, this method will not be applicable to many embedded applications, which typically have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
+As a result, this method will not be applicable to many embedded applications, which often have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
 For the second approach, reducing the datapath precision would reduce the latency at the cost of introducing quantization errors into the design.
-This has inspired research into exploiting the potential benefits of using the minimum precision necessary to satisfy a design specification~\cite{GeorgeDT11}.
+This has inspired research into exploiting the potential benefits of using the minimum precision necessary to satisfy a certain accuracy or performance specification~\cite{GeorgeDT11}.
 A brief review of existing approaches in this area will be discussed in Section~\ref{Section_Background_WL}.
 
-Unfortunately, neither of these conventional approaches tends to remove the conservative safety margin.
-In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the variation-induced guard-bands~\cite{NewBox2004}.
+Unfortunately, neither of these conventional approaches tends to remove the conservative safety margin, which is introduced to ensure a uniform functionality across a variety of possible working environments.
+Nevertheless, continuing with employing the guard-bands to cover all worst cases would become increasingly difficult and expensive in the short-term future, because of the continuous scaling of the process technology.
+In recent years, we have seen a growth of research that explores the potential power or performance benefits that can be obtained when relaxing the guard-bands~\cite{NewBox2004}.
 The detailed review of this research field will be presented in Section~\ref{Section_Background_Imprecise}.
@@
 In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area.
-We suggest that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
+Since it is unlikely to create a completly error-free design as any data representation would introduce quantization errors, we take a radical shift forward by suggesting that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
 Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
 This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric.
-This enables us to find the optimum design choice of the basic arithmetic operators (i.e.
-binary adders) under various design constraints.
+This enables us to find the optimum design choice of the basic arithmetic operators under various design constraints.
 A summary of the main contributions of this work are as follows:
@@
 	\item Exploring the accuracy-performance-area trade-offs for key arithmetic operators to illustrate the optimum architecture for a certain arithmetic function under a given requirement of silicon area,
-	\item Demonstration of the proposed findings analytically and experimentially from FPGA implementations that allowing rare timing violations to happen leads to an reduction of average errors or an improvement of performance over trancating the datapath precisions to meet timing.
+	\item Demonstration of the proposed findings analytically and experimentially from FPGA implementations that allowing rare timing violations to happen leads to a reduction of average errors or an improvement of performance over trancating the datapath precisions to meet timing.
 \end{itemize}
@@
 \subsection{Word-length Optimization}\label{Section_Background_WL}
-There exists a significant amount of work demonstrating that optimizing the precision used throughout a datapath would bring a substantial benefits on clock speed, silicon area and power consumption.
+There exists a significant amount of work demonstrating that optimizing the datapath precision would bring a substantial benefits on clock speed, silicon area and power consumption.
 There are two main research directions in this area.
@@
 Related techniques include the simulation-based approach~\cite{SungWLop_Simulation} and the analytical-based approach such as interval arithmetic~\cite{moore1966IA}, affine arithmetic~\cite{de2004affine}, Satisfiability-Modulo Theories~\cite{SAT2010} and polynomial representations~\cite{Boland2011TCAD}.
-A detailed summary of these methods can be found in~\cite{GeorgeDT11,lee2006accuracy}.
+A detailed summary of these methods can be found in~\cite{GeorgeDT11}.
 In the second research field, these tools are utilized to choose the minimum precision within a datapath to satisfy a required accuracy specification~\cite{RoldaoWLop_Simulation}.
-In this work, we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
+In this work, two different design scenarios are analyzed.
+In the conventional scenario, we speculate and reduce the original word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
+In the proposed new scenario, we operate the datapath with the original word-length while allowing timing violations sometimes to occur.
+The truncation errors derived in the former scenario are then compared to the overclocking errors generated in our proposed new scenario.
+
+%we speculate and employ the maximum word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
 The truncation errors derived in this process are then compared to the overclocking errors generated in our proposed new scenario.
@@
 Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
-This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the International Technology Roadmap for Semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
+This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnect, as pointed out by the International Technology Roadmap for Semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
 This topic is expected to be of growing importance in the future, because we will face new design challenges as the technology scales further.
 
-According to the existing literatures, one way to operating circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases.
+According to the existing literature, one way to operate circuits beyond the deterministic region is to relax the design constraints and the guard-bands that are conventionally used to avoid the worst cases.
 A series of work known as ``Better-Than-Worst-Case (BTWC) Design'' introduced a universal framework to push the circuit performance to its limits~\cite{BetterThanWS2005}.
@@
 Another field of study has shown that errors can be potentially tolerated in various applications, e.g.
-DSP applications concerning human perceptions.
+DSP applications involving human perception.
 In this case, even greater performance or power benefits can be achieved, as the design overhead of the checkers can be eliminated.
@@
 
-While the aforementioned literatures take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance and/or energy efficiency.
+While the aforementioned literature take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance and/or energy efficiency.
 For example, Lu et~al.
@@
 However, we should note that using imprecise architectures means correct results would never be obtained for certain input patterns.
-Another limitation is that the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed from current research.
+Another limitation is that the link between the probability of output correctness and energy savings or performance improvements are rarely analyzed in current research.
 In addition, these techniques cannot be directly applied onto existing hardware platforms such as FPGAs.
@@
 In this work, we propose an alternative methodology to remove the limitations of those existing approaches.
-It is argued in this paper that our method can be easily applied onto existing hardware arithmetic operators such as RCAs and CCMs with almost no hardware overhead.
-We support this hypothesis analytically by presenting theoretical probabilistic error models and experimentally using FPGAs.
+It is argued in this paper that our method can be easily applied to existing hardware arithmetic operators, and we support this hypothesis analytically by presenting theoretical probabilistic error models, and experimentally by using FPGAs.
 
@@
 As such, the philosophy of our approach is first exemplified with the analysis of a RCA.
-We later describe how this methodology can be extended to other arithmetic operators such as CSAs and CCMs, which are commonly used in DSP applicationsn and numerical algorithms, in Section~\ref{Section_CSA} and Section~\ref{section_CCM} respectively.
+We later describe how this methodology can be extended to other arithmetic operators such as CSAs and CCMs, which are commonly used in DSP applications and numerical algorithms, in Section~\ref{Section_CSA} and Section~\ref{section_CCM} respectively.
 
@@
 While the fast carry logic reduces the time of each individual carry-propagation delay, the overall delay of carry-propagation will eventually overwhelm the delay of sum generation of each LUT with increasing operand word-lengths.
-We perform our initial analysis based on the assumption that the carry propagation delay of each FA is a constant value $\mu_c$, which is a combination of logic delay and routing delay within an FPGA.
+We perform our initial analysis based on the assumption that the carry propagation delay of each FA is a constant value $\mu_c$, which is a combination of logic delay and routing delay.
 Hence the critical path delay of the RCA is given by~(\ref{Eq:RCA_delay}), as shown in Fig.~\ref{FPGA adder}.
@@
 \subsection{Probabilistic Model of Truncation Error}\label{section_RCA_TruncationError}
-For the ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
+For ease of discussion, we assume that the input to our circuit is a fixed point number scaled to lie in the range $[-1,1)$.
 In our initial analysis, we assume every bit of each input is uniformly and independently generated.
 However, this assumption will be relaxed in Section~\ref{Section_Experiments} where the predictions are verified using real image data.
-The errors at the output are evaluated in terms of the absolute value and the probability of their occurring.
+The errors at the output are evaluated in terms of the absolute value and the probability of their occurrence.
 These two metrics are combined as the error expectation.
@@
    \item Carry generation: $A_i=B_i=1$, a new carry chain is generated at bit $i$, and $S_i=C_{i-1}$;
-   \item Carry propagation: $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=0$;
-   \item Carry annihilation: $A_i=B_i$ (either $0$ or $1$), the current carry chain annihilates at bit $i$, and $S_i=1$.
+   \item Carry propagation: $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=\bar{C_{i-1}}=0$;
+   \item Carry annihilation: $A_i=B_i$ (either $0$ or $1$), the current carry chain annihilates at bit $i$, and $S_i=C_{i-1}=1$.
  \end{itemize}
@@
 
-Furthermore, it can be seen that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
+Furthermore, it can be seen that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions with mutually independent bits, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
 
@@
 
-In our analysis, the stage delay of stage $i$ in the CSA refers to the combination of the $i$-bit carry propagation delay and the delay of multiplexing the carry output.
+In our analysis, the stage delay of the $i^{th}$ stage in the CSA refers to the combination of the $i$-bit carry propagation delay and the delay of multiplexing the carry from the carry input of the $i^{th}$ stage to the carry output of the CSA.
 For a CSA with $s$ stages~($s\geqslant 2$), let the stage delay be denoted by $d_{s-1},~\dots,~d_{0}$, where $d_{s-1}$ and $d_{0}$ represent the delay of the most significant and the least significant stages, respectively.
@@
         \centering
-        \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA.]{
+        \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.]{
             \includegraphics[width=3.5in]{./Figures/CSA2stage_Model_Timing.eps}
@@
 
-Fig.~\ref{Fig_CSA2stage_Timing} also highlights that in comparison to the RCA, the CSA achieves greater word-length when frequency is initially increased.
-The RCA only outperforms when very high frequency is applied.
+Fig.~\ref{Fig_CSA2stage_Timing} also highlights that for a relatively relexed frequency cosntraint, the CSA achieves greater word-length than the RCA.
+This is because the stage parallelism in the CSA enables a greater overall word-length, even though the multiplexer delay limits the word-length of each stage in the CSA when compared to the RCA.
+When more stringent latency requirement is applied, however, the word-length of each stage is largely limited such that the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
+
+%in comparison to the RCA, the CSA achieves greater word-length for relatively relexed frequency constraints.
+The RCA only outperforms when very high frequency requirement is applied.
 This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
-However when frequency increases, the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
+However when more stringent latency requirement is applied, the word-length of each stage in CSA is limited.
+Hence the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
 
@@
 \subsection{Determination of the Optimum Adder Structure for Given Frequency Requirements}
-First, suppose the algorithm designer wished to create a circuit that can run at a given frequency with the minimum achievable output errors and minimum resource usage, i.e.
+First, suppose the algorithm designer wished to create a circuit that can run at a given frequency in a given resource constraint while achieving the minimum possible output error.
+A decision must then be taken over which adder structure achieves this minimum, and whether the structure should be overclocked
+
+% with the minimum achievable output errors and minimum resource usage, i.e.
 a pair of $\{Area, Frequency\}$ constraint is applied.
@@
 
-\begin{itemize}
-  \item Design with the minimum mean value of errors at the output is the optimum design;
-  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
-  \item If both the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
-\end{itemize}
-
-For instance, in Fig.~\ref{Fig_CSA_LUT25} we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios when the number of the available LUTs is set to 25.
+%\begin{itemize}
+%  \item Design with the minimum mean value of errors at the output is the optimum design;
+%  \item If multiple designs achieve the same accuracy, then the design with minimum area is the optimum design;
+%  \item If both the accuracy and area are identical for multiple designs, they are all treated as the optimum design.
+%\end{itemize}
+
+As an example slice through the design space, in Fig.~\ref{Fig_CSA_LUT25} we record the mean value of error at outputs with respect to different operating frequencies for both design scenarios when the number of the available LUTs is set to 25.
 In this graph, we have labeled the optimum adder structure.
@@
 
-We first notice that for all frequency values, the overclocked RCA achieves smaller error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}.
+We first notice that for all frequency values, the overclocked RCA achieves no larger error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}.
 It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
-Although the CSA with 3 stages outperforms temporarily when frequency is further increased, the overclocked RCA is still the optimum design when high operating frequencies are applied.
+Although the CSA with 3 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.
 
@@
 From this figure, several observations can be made.
-Firstly, if the available area is large enough to implement a CSA in full precision, it will be the optimum design.
+Firstly, if the frequency requirement is not large whilst the available area is large enough to implement a CSA in full precision, it will be the optimum design.
 This is expected from our earlier analysis in Fig.~\ref{Fig_CSA2stage_Timing}.
-Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is initially increased, as it consumes less area although both achieve the same error expectation.
+Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is low, as it consumes less area although both achieve the same error expectation.
 Thirdly, only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision.
-In this case, area becomes the dominate factor and precision is lost for the CSA, meaning the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
-Last but not the least, for a more stringent area constraint, the word-length of RCA is also limited.
+In this case, area becomes the dominant factor and precision is lost for the CSA, meaning the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
+Finally, for very stringent area constraints, the word-length of RCA is also limited.
 This results in truncation errors initially for all design scenarios.
@@
 For a tight accuracy requirement, i.e.
-$MRE<0.005\%$, CSA serves as the optimum design choice with respect to large accessible area, as it intrinsically operates faster than RCA.
+$MRE<0.005\%$, CSA serves as the optimum design choice for large area constraints, as it intrinsically operates faster than RCA.
 Once again, when the area budget shrinks, the RCA performs best because the precision of the CSA is limited.
@@
 \subsection{Design Guidance}
-To sum up, the experiments reveal that for both design goals, CSA is the best option only when there is enough hardware resources.
+To sum up, the experiments reveal that for both design goals, the CSA is not compatitive with the overclocking approach unless one has very relexed area budget.
+As a result, for the remainder of this paper, we will focus on the RCA in our following analysis and experiments.
+
+% is the best option only when there is enough hardware resources.
 However for the remainder of this paper, we are interested in cases where there is a limited area budget, as may be the case in the embedded applications.
@@
 
-\subsection{Exploring the Conservative Timing Margin} % (fold)
+\subsection{Correcting for Conservative Timing Margin} % (fold)
 \label{sub:exploring_the_conservative_timing_margin}
@@
 A maximum speed differential of $3.2\times$ is obtained when the input signal is 5-bit.
-
+%
 \begin{figure}[ht]
@@
 \subsection{Area Overhead of Our Approach}
-For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially leads to a smaller design, in comparison to our proposed overclocking scenario.
+For both aforementioned design goals, it should be noted that an extra benefit of using the traditional approach is that reducing datapath precision would potentially lead to a smaller design, in comparison to our proposed overclocking scenario.
 Consequently, the area overheads of our approach are summarized in Table~\ref{Table:AreaFrequency} and Table~\ref{Table:AreaError} for both design goals.
@@
 It has been found that simply allowing timing violations to happen would potentially lead to either reductions in average errors or speedups in clock frequencies, in comparison to the traditional approach where the target timing is met by limiting the precisions throughout the datapath.
-To verify this hypothesis, probabilistic models have been developed for errors generated from both design methodologies, whilst empirical results on a Virtex-6 FPGA have also been obtained over a set of DSP applications.
+To verify this hypothesis, probabilistic models have been developed for errors generated from both design methodologies, and empirical results on a Virtex-6 FPGA have also been obtained over a set of DSP applications.
 Besides, the silicon area has also been taken into account for the trade-offs.
@@
 
-Whilst this research has shown a promising direction for sustaining performance scaling, there are several issues that would be of interest for future research.
+While this research has shown a promising direction for sustaining performance scaling, in the future we wish to apply this approach onto arithmetic units based on alternative number representations, and explore the probabilistic behavior of these operators under a variety of process, voltage and temperature variations.
+
+%explore the probabilistic behaviour of alternative
+
+%While this research has shown a promising direction for sustaining performance scaling, there are several issues that would be of interest for future research.
 A critical finding from this work is the direction inconsistency between carry propagation (from the LSB to the MSB) and results sampling (from the MSB to the LSB).
@@
 % Acknowledgments
-\begin{acks}
-The authors would like to thank xxx.
-\end{acks}
+%\begin{acks}
+%The authors would like to thank xxx.
+%\end{acks}
 
@@
 % History dates
-\received{February 2007}{March 2009}{June 2009}
+%\received{February 2007}{March 2009}{June 2009}
 

### 2013-06-21 TRETS2013/TRETS_overclocking.tex
TRETS modified introduction of CSA section

@@
 }
+%\vspace{-5ex}
 
@@
 \subsection{Introduction}
-Since the delay of RCA is determined by the length of carry chain, alternative adder architectures, such as carry select adder (CSA), have been proposed to boost performance.
+As seen in~(\ref{Eq:Comparison RCA}), a factor of 2 reduction in error expection can be achieved by using the proposed approach in RCA.
+However, implementing our approach costs extra silicon area in comparison to the conventional approach, because we keep the original word-length $k$ in the new scenario instead of truncating to only $b-1$ bits in the traditional scenario.
+Besides our approach, there are existing approaches that could be employed to trade silicon area for low latency.
+For instance, alternative adder architectures, such as carry select adder (CSA), have been proposed to boost performance.
 In a CSA, the carry chain is divided into multiple overlapped stages, while each stage contains two RCAs and two multiplexers, as shown in Fig.~\ref{Fig_CSA_Structure} and Fig.~\ref{Fig_CSA_SingleStage}, respectively.
@@
 Due to this reason, we explore the trade-offs between silicon area, accuracy and performance of RCA and CSA in this section.
+\vspace{-7ex}
 \begin{figure}[htbp]
@@
 \end{figure}
+\vspace{-2ex}
 
@@
 It can be seen that our models for both RCA and CSA match well with the experimental results.
-
+%
 \begin{figure}[htbp]
         \centering
+        \vspace{-3ex}
         \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.]{
@@
         }
+        \vspace{-1.5ex}
     \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
@@
   \centering
+  \vspace{-2ex}
   \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
+  \vspace{-2ex}
   \caption{A comparison between two design scenarios when the number of available LUT is 25.
@@
 However, the RCA with overclocking can still be employed as the optimum design, because it loses less precision than the CSA under the same area constraint.
-
+%
 \begin{figure}[t]
   \centering
+  \vspace{-2ex}
   \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
+  \vspace{-2ex}
   \caption{A demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
@@
 Fig.~\ref{Fig_CSA_Tradeoff_Error} can thus be obtained based on these criteria.
-
+%
 \begin{figure}[t]
     \centering
+    \vspace{-2ex}
     \includegraphics[width=3.7in]{./Figures/Tradeoff_Error.eps}
+    \vspace{-2ex}
     \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
@@
 For an $n$-bit input signal, it should be noted that an $n$-bit RCA is sufficient for this operation, because no carry will be generated or propagated when adding with zeros, as shown in Fig.~\ref{CCM_fig}.
-
+%
 \begin{figure}[htbp]
@@
   \includegraphics[width=\textwidth]{./Figures/CCM_CarryChain.pdf}
-  \vspace{-2ex}
+  \vspace{-6ex}
   \caption{Four possible carry chain types in a constant coefficient multiplier with $n$-bit inputs. The notion $s$ denotes the shifted bits and $BP$ denotes the binary point.}
@@
   \centering
-  \vspace{-3ex}
+  \vspace{-4ex}
   \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
-  %\vspace{-4.5ex}
+  \vspace{-2ex}
   \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software.
@@
   \centering
+  \vspace{-2ex}
   \includegraphics[width=3.2in]{./Figures/Exp/FIR/RatedFrequency3.eps}
@@
   \centering
-%  \vspace{-3ex}
+  \vspace{-3ex}
   \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
-%  \vspace{-5ex}
+  \vspace{-2ex}
   \caption{A demonstration of two design perspectives with a $5^{th}$~order FIR filter, which is implemented on Virtex-6 FPGA.
@@
 This finding explicitly demonstrates that longer carry chains happens with an even smaller probability when utilizing real data.
-
+%
 \begin{figure}[tbp]
   \centering
+  \vspace{-2ex}
   \includegraphics[width=3.5in]{./Figures/CC_length2.eps}
+  \vspace{-2ex}
   \caption{Probability distribution of different length of carry chains in a 8-bit RCA.

### 2013-06-25 TRETS2013/TRETS_overclocking.tex
TRETS modified CSA map
TRETS delete some useless graphs from git repo

@@
 It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
-Although the CSA with 3 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.
+Although the CSA with 4 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.
 
@@
 This is expected from our earlier analysis in Fig.~\ref{Fig_CSA2stage_Timing}.
-Secondly, the 2-stage CSA is better than the 3-stage CSA when frequency is low, as it consumes less area although both achieve the same error expectation.
+Secondly, the 2-stage CSA is better than the 3-stage CSA and the 4-stage CSA when frequency is low, as it consumes less area although all achieve the same error expectation.
 Thirdly, only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision.
@@
   \vspace{-2ex}
-  \includegraphics[width=3.5in]{./Figures/Tradeoff.eps}
+  \includegraphics[width=4.5in]{./Figures/Tradeoff_Freq.eps}
   \vspace{-2ex}
@@
     \vspace{-2ex}
-    \includegraphics[width=3.7in]{./Figures/Tradeoff_Error.eps}
+    \includegraphics[width=4.5in]{./Figures/Tradeoff_Error2.eps}
     \vspace{-2ex}
@@
 \begin{figure}[htbp]
-  \vspace{-2ex}
+  \vspace{-4ex}
   \centering

### 2013-06-25 TRETS2013/TRETS_overclocking.tex
TRETS minor change format

@@
 \usepackage{graphicx}
-\usepackage{epstopdf}
+%\usepackage{epstopdf}
 \usepackage{multirow}
@@
 Note that~(\ref{Eq:Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
-%Furthermore, (\ref{Eq:Ptm_RCA}) can be employed for any probability distribution of inputs, as long as the value of own.
 %
@@
 
-Furthermore, it can be seen that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions with mutually independent bits, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
+In addition, note that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions with mutually independent bits, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
 
@@
 %
-\begin{figure}[htbp]
-        \centering
+%\begin{figure}[htbp]
+%        \centering
+%        \vspace{-3ex}
+%        \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.]{
+%            \includegraphics[width=3.5in]{./Figures/CSA2stage_Model_Timing2.eps}
+%            \label{Fig_CSA2stage_Timing}
+%        }
+%        \subfigure[\scriptsize Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
+%            \includegraphics[width=3.5in]{./Figures/CSA3stage_Area2.eps}
+%            \label{Fig_CSA3stage_Area}
+%        }
+%        \vspace{-1.5ex}
+%    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
+%\end{figure}
+
+\begin{figure}[ht]
+    %\centering
     \vspace{-3ex}
-        \subfigure[\scriptsize The modeled value and the experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.]{
-            \includegraphics[width=3.5in]{./Figures/CSA2stage_Model_Timing.eps}
+    \subfigure[]{
+        \includegraphics[width=.50\textwidth]{./Figures/CSA2stage_Model_Timing2.eps}
         \label{Fig_CSA2stage_Timing}
-        }
-        \subfigure[\scriptsize Hardware resource usage for an RCA and a CSA with 2 and 3 stages.]{
-            \includegraphics[width=3.5in]{./Figures/CSA3stage_Area.eps}
+    }%
+    \subfigure[]{
+        \includegraphics[width=.5\textwidth]{./Figures/CSA3stage_Area2.eps}
         \label{Fig_CSA3stage_Area}
@@
     \vspace{-1.5ex}
-    \caption{A comparison between RCA and CSA in terms of the maximum word-length of input signal and the area consumption.}
+    \caption{(a) The modeled value and experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.
+(b) Hardware resource usage for an RCA and a CSA with 2 and 3 stages.}
+    \vspace{-1ex}
 \end{figure}
@@
   \centering
-  \vspace{-2ex}
+  \vspace{-3ex}
   \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
@@
   \centering
-  \vspace{-2ex}
+  \vspace{-2.5ex}
   \includegraphics[width=4.5in]{./Figures/Tradeoff_Freq.eps}
-  \vspace{-2ex}
+  \vspace{-2.5ex}
   \caption{A demonstration of the optimum design methodology which achieves the minimum error at outputs with respect to a variety of frequency and area constraints.}
@@
     \includegraphics[width=4.5in]{./Figures/Tradeoff_Error2.eps}
-    \vspace{-2ex}
+    \vspace{-2.5ex}
     \caption{A demonstration of the optimum design methodology which runs at the fastest frequency with respect to a variety of accuracy and area constraints.}
     \label{Fig_CSA_Tradeoff_Error}
+    \vspace{-1ex}
 \end{figure}
@@
   \label{CCM_fig}
+  \vspace{-4ex}
 \end{figure}
@@
   \centering
-  \vspace{-4ex}
+  \vspace{-5ex}
   \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
-  \vspace{-2ex}
+  \vspace{-3ex}
   \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software.
@@
   \label{Test Framework}
-  %\vspace{-1ex}
+  \vspace{-1.5ex}
 \end{figure}
@@
 Table~\ref{Rated_Frequency_table} summarizes the operating frequency of each implemented design in Xilinx ISE14.1 when the word-length of input signal is 8-bit.
-
-\begin{table}%
+%
+\begin{table}[htbp]%
+\vspace{-1ex}
 \tbl{Rated Frequencies of example Designs.\label{Rated_Frequency_table}}{%
@@
   \includegraphics[width=3.2in]{./Figures/Exp/FIR/RatedFrequency3.eps}
-  %\vspace{-1.5ex}
+  \vspace{-1ex}
   \caption{The maximum operating frequencies for different input word-lengths of an FIR filter.
@@
   \label{Fig:TimingMargin}
-  %\vspace{-3.5ex}
+  \vspace{-.5ex}
 \end{figure}
@@
 \begin{figure}[ht]
-  %\vspace{-2ex}
+  \vspace{-2ex}
   % 425M, 450M, 480M, 520M
@@
   }
-%\vspace{-2ex}
+\vspace{-2ex}
 \caption{Output images of the FIR filter for both overclocking scenario (top row) and traditional scenario (bottom row) when operating frequencies are $425MHz$, $450MHz$, $480MHz$ and $520MHz$ respectively (from left to right).}
@@
   \vspace{-2ex}
-  \includegraphics[width=3.5in]{./Figures/CC_length2.eps}
-  \vspace{-2ex}
+  \includegraphics[width=3.5in]{./Figures/CC_length3.eps}
+  \vspace{-1.5ex}
   \caption{Probability distribution of different length of carry chains in a 8-bit RCA.
@@
   \label{Fig:CarryDistribution}
+  \vspace{-1ex}
 \end{figure}
@@
 Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{Fig:FIR}.
-
+%
 \begin{table*}[tbp]
- %\vspace{-2ex}
+\vspace{-1ex}
  %% increase table row spacing, adjust to taste
@@
    \label{Table:Ratio_MRE}
-% \vspace{-1ex}
+ %\vspace{-1ex}
  \end{table*}
@@
 The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
-
+%
 \begin{table*}[tbp]
- %\vspace{-2ex}
+\vspace{-1ex}
  %% increase table row spacing, adjust to taste
@@
    \label{Table:Max_Frequency}
-%   \vspace{-3ex}
+   \vspace{-1ex}
  \end{table*}
@@
 %frequency is initially increased or with a small error budget (i.e. $\sim10\%$).
-
+%
 \begin{table*}[tbp]
+\vspace{-2ex}
  %% increase table row spacing, adjust to taste
@@
  \begin{table*}[tbp]
+ \vspace{-1ex}
  %% increase table row spacing, adjust to taste

### 2013-06-30 TRETS2013/TRETS_overclocking.tex
TRETS add correlation probability

@@
 In addition, note that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions with mutually independent bits, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
+If there is dependency between input bits, the probability value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ would change.
+For instance, if $A_i$ and $B_i$ are not independent, we have $P_{(A_i=1)}=E_{(A_i)}=1/2$ and $P_{(B_i=1)}=E_{(B_i)}=1/2$ seperately for uniform distribution, where $E_{(A_i)}$ denotes the expectation of $A_i$.
+The probability of $A_i=B_i=1$ is then given by (\ref{Eq:P_dependency})~\cite{TransitionProb} where $\sigma_{(A_i)}$ denotes the standard variation of $A_i$ and $\rho_i$ denotes the temporal correlation between the two inputs at the $i^{th}$ bit.
+$\rho_i=0$ corresponds to the case where bits are uncorrelated.
+%
+\begin{eqnarray}\label{Eq:P_dependency}
+    P_{(A_i=B_i=1)}=E_{(A_i)}E_{(B_i)}+\rho_i\sigma_{(A_i)}\sigma_{(B_i)}
+\end{eqnarray}
+
+It can be seen that if $\rho_i=0$ then $P_{(A_i=B_i=1)}=1/4$ as being used to derive (\ref{Eq:Ptm2}). Otherwise $\rho_i$ should be determined before employing our models.
+
+%, that is, the expectation of $A_i$ and $B_i$
 
@@
         }
+    \vspace{-2ex}
     \caption{The structure diagram of CSA.}
@@
 %\end{figure}
-
-\begin{figure}[ht]
+%
+\begin{figure}[t]
     %\centering
@@
     }
-    \vspace{-1.5ex}
-    \caption{(a) The modeled value and experimental results of the maximum word-length of RCA and CSA, with respect to various frequency requirements.
+    \vspace{-2ex}
+    \caption{(a) The modeled value and experimental results of the maximum word-length of RCA and CSA, for various frequency requirements.
 (b) Hardware resource usage for an RCA and a CSA with 2 and 3 stages.}
@@
 \begin{figure}[htbp]
-  \vspace{-4ex}
+  \vspace{-5ex}
   \centering
@@
 \label{Fig:FIR_Lena}
+\vspace{-1.5ex}
 \end{figure}
@@
    \centering
-   \footnotesize
+   %\footnotesize
+   \scriptsize
    %\vspace{-4mm}
@@
    \begin{tablenotes}
-   \footnotesize
+   \scriptsize
     \item[*] Current frequency cannot be achieved in the traditional scenario. These points are excluded from the calculation of geometric means.
@@
    \centering
-   \footnotesize
+   %\footnotesize
+   \scriptsize
    \begin{tabular}{|c|cc|cc|cc|cc|cc||cc|}
@@
    \centering
-   \footnotesize
+   %\footnotesize
+   \scriptsize
    \begin{threeparttable}
@@
  \end{table*}
-
+%
  \begin{table*}[tbp]

### 2013-07-30 TRETS2013/TRETS_overclocking.tex
TRETS add self-cite and non-independent cases

@@
 
-\keywords{Overclocking, Imprecise Design}
+\keywords{Overclocking, Imprecise Design, Approximate Computing}
 
@@
 Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
-This paper elaborates on the prior work [xxx], by incorporating silicon area as another evaluation metric.
+This paper elaborates on the prior work~\cite{SKfccm13}, by incorporating silicon area as another evaluation metric.
 This enables us to find the optimum design choice of the basic arithmetic operators under various design constraints.
@@
 The carry chain $C_{tm}$ occurs when there is a carry generated at bit $t$, a carry annihilated at bit $t+m-1$ and the carry propagates in between.
-Consequently, its probability $P_{tm}$ is given by (\ref{Eq:Ptm_RCA}).
+Consequently, its probability $P_{tm}$ is given by (\ref{Eq:Ptm_RCA_General}).
+%
+\begin{eqnarray}\label{Eq:Ptm_RCA_General}
+    P_{tm}=P_{(A_t=B_t=1,~A_i\neq B_i,~A_{t+m-1}=B_{t+m-1})},~i\in [t+1,t+m-2]
+\end{eqnarray}
+
+Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, (\ref{Eq:Ptm_RCA_General}) can be modified as given in~(\ref{Eq:Ptm_RCA}).
+Also we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$.
+Thus $P_{tm}$ can be obtained by~(\ref{Eq:Ptm2}).
+Note that~(\ref{Eq:Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
 %
@@
 \end{eqnarray}
-
-Under the assumption that $A$ and $B$ are mutually independent and uniformly distributed, we have $P_{(A_i=B_i=1)}=1/4$, $P_{(A_i\neq B_i)}=1/2$ and $P_{(A_i=B_i)}=1/2$, so $P_{tm}$ can be obtained by~(\ref{Eq:Ptm2}).
-Note that~(\ref{Eq:Ptm2}) takes into account the carry annihilation always occurs when $t+m-1=n$.
 %
@@
 In addition, note that the probabilistic models for the magnitude and probability of overclocking errors can be easily generalized for any input distributions with mutually independent bits, since (\ref{Eq:Output_Error}) and (\ref{Eq:etm}) are not related to the input distribution, while (\ref{Eq:Ptm_RCA}) can be employed as long as the value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ is known.
-If there is dependency between input bits, the probability value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ would change.
+If there is dependency between input bits, (\ref{Eq:Ptm_RCA_General}) should be used and the probability value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ would change.
 For instance, if $A_i$ and $B_i$ are not independent, we have $P_{(A_i=1)}=E_{(A_i)}=1/2$ and $P_{(B_i=1)}=E_{(B_i)}=1/2$ seperately for uniform distribution, where $E_{(A_i)}$ denotes the expectation of $A_i$.
@@
 
-It can be seen that if $\rho_i=0$ then $P_{(A_i=B_i=1)}=1/4$ as being used to derive (\ref{Eq:Ptm2}). Otherwise $\rho_i$ should be determined before employing our models.
-
-%, that is, the expectation of $A_i$ and $B_i$
+It can be seen that if $\rho_i=0$ then $P_{(A_i=B_i=1)}=1/4$ as used to derive (\ref{Eq:Ptm2}). Otherwise $\rho_i$ should be determined before employing our models.
 

### 2013-08-05 TRETS2013/TRETS_overclocking.tex
Minor changes

@@
 
-\keywords{Overclocking, Imprecise Design, Approximate Computing}
+\keywords{Overclocking, Imprecise Design, Approximate Computing, Truncation}
 
@@
 In the conventional scenario, we speculate and reduce the original word-length in the datapath under a given timing constraint while ensuring no timing errors will occur.
-In the proposed new scenario, we operate the datapath with the original word-length while allowing timing violations sometimes to occur.
+In the proposed new scenario, we operate the datapath with the original word-length while allowing timing violations sometimes to happen.
 The truncation errors derived in the former scenario are then compared to the overclocking errors generated in our proposed new scenario.
@@
 Recently we have seen a growth of parallel streams of research which aim at exploring alternative methods to trade accuracy for design efficiency.
-This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnect, as pointed out by the International Technology Roadmap for Semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
+This strand of research is motivated by the fact that extra benefits of manufacturing, test, power and timing can be obtained if the tight requirement of absolute correctness is released for devices and interconnects, as pointed out by the International Technology Roadmap for Semiconductors (ITRS) in 2007~\cite{semiconductor2007international}.
 This topic is expected to be of growing importance in the future, because we will face new design challenges as the technology scales further.
@@
 First, suppose the algorithm designer wished to create a circuit that can run at a given frequency in a given resource constraint while achieving the minimum possible output error.
-A decision must then be taken over which adder structure achieves this minimum, and whether the structure should be overclocked
+A decision must then be taken over which adder structure achieves this minimum, and whether the structure should be overclocked.
 
@@
 
-We first notice that for all frequency values, the overclocked RCA achieves no larger error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}.
+We first notice from Fig.~\ref{Fig_CSA_LUT25} that for all frequency values, the overclocked RCA achieves no larger error expectation than the RCA with truncated operand word-lengths, as predicted by the models for the RCA in Section~\ref{section_RCA_Comparison}.
 It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
@@
 Secondly, the 2-stage CSA is better than the 3-stage CSA and the 4-stage CSA when frequency is low, as it consumes less area although all achieve the same error expectation.
-Thirdly, only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision.
+Thirdly, it is possible that only part of the CSA can be implemented under a tighter area budget, whereas the RCA still keeps full precision.
 In this case, area becomes the dominant factor and precision is lost for the CSA, meaning the RCA with overclocking is the optimum design method across almost the whole frequency domain in this situation.
@@
 If the design goal is to operate the circuit as fast as possible with the minimum area whilst a certain error budget can be tolerated, the optimum design methodology can be decided as illustrated in Fig.~\ref{Fig_CSA_Tradeoff_Error}.
-In this situation, the error specifications are evaluated in terms of the mean relative error (MRE), as given by~(\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
+In this situation, the error specifications are evaluated in terms of the mean relative error ($MRE$), as given by~(\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of outputs, respectively.
 %
@@
 
-In our experiments, MRE is set ranging from $0.001\%$ to $50\%$.
-For a certain value of MRE, the design with the maximum operating frequency is selected as the optimum design.
+In our experiments, $MRE$ is set ranging from $0.001\%$ to $50\%$.
+For a certain value of $MRE$, the design with the maximum operating frequency is selected as the optimum design.
 Moreover, the smallest design is the optimum one if multiple structures operate at the same frequency, with a certain area requirement.
@@
 
-For a tight accuracy requirement, i.e.
+For a tight accuracy requirement, e.g.
 $MRE<0.005\%$, CSA serves as the optimum design choice for large area constraints, as it intrinsically operates faster than RCA.
@@
 The general architecture is depicted in Fig.~\ref{Test Framework}.
-The main body of the test framework consists of the circuit under test (CUT), the test frequency generator and the control logic, as shown in the dotted box in Fig.~\ref{Test Framework}.
+The main body of the test framework consists of the circuit under test (CUT), the test frequency generator and the control logic, as shown in the top dotted box in Fig.~\ref{Test Framework}.
 The I/Os of the CUT are registered by the launch registers (LRs) and the sample registers (SRs), which are all triggered by the test clock.
@@
   \centering
-  \vspace{-5ex}
-  \includegraphics[width=3.5in]{./Figures/TestFramework.pdf}
-  \vspace{-3ex}
-  \caption{Test framework, which is composed of a measurement architecture (the dotted box) on an FPGA and an off-line comparator using software.
+  \vspace{-3.5ex}
+  \includegraphics[width=3.7in]{./Figures/TestFramework.pdf}
+  \vspace{-1.5ex}
+  \caption{Test framework, which is composed of a measurement architecture (the top dotted box) on an FPGA and an off-line comparator using software.
 The error-free data are obtained by either pre-computation or initial run with low frequencies.}
@@
 
-For example, the predicted frequencies and the actual frequencies of a $5^{th}$~order FIR filter using different word-lengths are depicted in Fig.~\ref{Fig:TimingMargin}.
+For example, the frequencies predicted by Xilinx ISE and the actual frequencies of a $5^{th}$~order FIR filter using different word-lengths are depicted in Fig.~\ref{Fig:TimingMargin}.
 The ``actual'' maximum frequencies are computed by increasing the operating frequency from the rated value until errors are observed at the output; the maximum operating frequency with correct output is recorded for the current word-length.
@@
 We first assess the accuracy of our proposed models of errors.
-We record the value of MRE based on (\ref{Eq:MRE}) in a $5^{th}$~order FIR with respect to different operating frequencies.
+We record the value of $MRE$ based on (\ref{Eq:MRE}) in a $5^{th}$~order FIR with respect to different operating frequencies.
 The modeled values of both overclocking error and truncation error of the FIR filter are presented in Fig.~\ref{Fig:FIR} (dotted lines), as well as the actual measurements on the FPGA (solid lines) with two types of input data.
@@
   }%
-  \subfigure[\scriptsize n=8,~SNR=21.58dB]{
+  \subfigure[\scriptsize n=8,~SNR=21.58dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T62.eps}
   }%
-  \subfigure[\scriptsize n=8,~SNR=10.03dB]{
+  \subfigure[\scriptsize n=8,~SNR=10.03dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_T6.eps}
   }
-  \subfigure[\scriptsize n=7,~SNR=26.02dB]{
+  \subfigure[\scriptsize n=7,~SNR=26.02dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q7T10.eps}
   }% This is important! use % to indicate same line, otherwise new line
-  \subfigure[\scriptsize n=5,~SNR=21.76dB]{
+  \subfigure[\scriptsize n=5,~SNR=21.76dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q4T10.eps}
   }%
-  \subfigure[\scriptsize n=2,~SNR=6.57dB]{
+  \subfigure[\scriptsize n=2,~SNR=6.57dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q2T10.eps}
   }%
-  \subfigure[\scriptsize n=1,~SNR=3.95dB]{
+  \subfigure[\scriptsize n=1,~SNR=3.95dB.]{
     \includegraphics[width=.24\textwidth]{./Figures/Exp/FIR/LenaImages/FIRLena_Q1T10.eps}
@@
 According to Fig.~\ref{Fig:FIR}, output errors are reduced in the overclocking scenario for both input types in comparison to the traditional scenario, as the analytical model validates.
-In addition, we see that using real data, more significant reduction of MRE are achieved, and that no errors are observed when frequency is initially increased.
+In addition, we see that using real data, more significant reduction of $MRE$ are achieved, and that no errors are observed when frequency is initially increased.
 This is because for real data, long carry chains are typically generated with even smaller probabilities, and the longest carry chain rarely occurs.
@@
 As we mentioned in Section~\ref{Section_OptimumAdder}, our results could be of interest to a circuit designer in two ways.
-Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible MRE, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
-For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Table:Ratio_MRE} in terms of the relative reduction of MRE as given in~(\ref{Eq:Relative_Reduction_MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
+Typically, either the designer will want to create a circuit that can run at a given frequency with the minimum possible $MRE$, or the algorithm designer will wish to run as fast as possible whilst maintaining a specific error tolerance.
+For the first design target, the experimental results for all five example designs on FPGA are summarized in Table~\ref{Table:Ratio_MRE} in terms of the relative reduction of $MRE$ as given in~(\ref{Eq:Relative_Reduction_MRE}) where $MRE_{Trad}$ and $MRE_{ovrc}$ denote the value obtained in the traditional scenario and in the overclocking scenario, respectively.
 %
@@
 The N/A in Table~\ref{Table:Ratio_MRE} refers to the situations where a certain frequency simply cannot be achieved using the traditional scenario.
-It can be seen that a significant reduction of MRE can be achieved using the proposed overclocking scenario, and the geometric mean reduction varies from $67.9\%$ to $95.4\%$ using uniform input data.
-Even larger differences of MRE can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{Fig:FIR}.
+It can be seen that a significant reduction of $MRE$ can be achieved using the proposed overclocking scenario, and the geometric mean reduction varies from $67.9\%$ to $95.4\%$ using uniform input data.
+Even larger differences of $MRE$ can be observed when testing with real image data for each design, ranging from $83.6\%$ to $98.8\%$, as expected given the results shown in Fig.~\ref{Fig:FIR}.
 %
@@
    \setlength{\tabcolsep}{3.5pt}
-   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Eq:Relative_Reduction_MRE}) for Two Types of Input Data: the Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
+   \tbl{Relative Reduction of MRE ($\%$) in Overclocking Scenario for Various Normalized Frequencies Based on~(\ref{Eq:Relative_Reduction_MRE}) for Two Types of Input Data: Uniform Data (Uni) and Real Image Data from Lena (Lena).}{
    \centering
@@
 Table~\ref{Table:Max_Frequency} illustrates the frequency speedups for each design when the specified error tolerance varies from 0.05\% to 50\%.
-For all designs, we see that the overclocking scenario still outperforms the traditional scenario for each MRE budget in terms of operating frequency.
+For all designs, we see that the overclocking scenario still outperforms the traditional scenario for each $MRE$ budget in terms of operating frequency.
 Likewise, the frequency speedup is higher for real image inputs than uniform inputs.
@@
 It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
-This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the our proposed new approach, especially when the clock frequency is initially increased.
+This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the our proposed new approach, especially for not stringent frequency requirements.
+%when the clock frequency is initially increased.
 
@@
 
-In general, a very small area overhead of our approach can be observed when the design is initially operated beyond the safe region with higher frequencies or with a small error budget (i.e.
+In general, a very small area overhead of our approach can be observed when the design is initially operated beyond the safe region with higher frequencies or with a small error budget (e.g.
 $\sim10\%$).

### 2014-01-17 TRETS2013/ReviewResponse/Response.tex
Templete of revision

\documentclass[a4paper, 11pt]{article}

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{xcolor}

\topmargin -10mm
\oddsidemargin 0mm
\evensidemargin 0mm
\textwidth 158mm
\textheight 226mm
\parskip 0mm

\def\Response{\noindent \textbf{Response:~}}
\newcommand{\Question}[1]{\textcolor[rgb]{0.51,0.00,0.00}{#1}}
\newcommand{\PaperText}[1]{\emph{#1}}

\title{Revision of Paper TRETS-2013-0065 Imprecise Datapath Design: An Overclocking Approach}
\author{Kan Shi, David Boland and George A. Constantinides}
\date{}

\pagenumbering{arabic}

\begin{document}
\maketitle

\section*{Reviewer 3}
\begin{enumerate}
  \item \Question{The first sentence of the abstract is completely devoid of context, and may be the worst sentence in the entire article, given its importance. A much more appropriate sentence is the start of Section 1, Paragraph 4.}

      \Response We have modified the first two sentences of the abstract, which now read as follows:\\

      \PaperText{In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area. We compare two different approaches that could trade accuracy for performance.}\\

  \item \Question{What are the chances that an entire design with all its complexities could be accelerated in this fashion? (i.e. Could the overall clock frequency be increased?)}

      \Response to be added.\\

  \item \Question{In Figure 1, you use $\mu$, whereas in the text and in Equation 4, you use $\mu_c$.  The converse is true for Section 7.4 and equations (35), (36), and (37).}

      \Response Thanks. It should be $\mu$ in Fig.1 and Equations (35), (36) and (37). It has been fixed.\\

  \item \Question{In Section 3.2, it would be helpful if you could illustrate or define your [-1,1) fixed-point format. Do you number your bits from k-1 to 0 or from 0 to k-1?}

      \Response We meant that all numbers are normalized to fractional numbers within the range [-1,1). The truncation process is illustrated in the figure below, which is not included in this manuscript due to the space limit. As seen in this figure, the original number embodies k fractional bits, while the truncated number embodies n fractional bits. Given that all bits are mutually independent and uniformly distributed, Equation (2) gives the mean value of the truncated bits. We have modified the second paragraph of Section 3.2:\\

      \PaperText{to be added.}\\

  \item \Question{In Section 3.3, for $A_i\neq B_i$ (Carry Propagation), you seem to be saying that $S_i = C_{i-1} = 0$.  If $A_i \neq B_i$ then $A_i + B_i = 1$, but that tells us nothing unless we know $C_{i-1}$, and it is not necessarily 0 as you claim.}

      \Response Thanks for pointing this out. In this case it should be $C_{i-1} =1$, because carry is propagated from bit $i-1$ to bit $i$. Hence $S_i=A_i+B_i+C_{i-1}=0$.

      This statement is modified as follows:\\

      \PaperText{Carry propagation: (see paper)}

\end{enumerate}

\end{document}

### 2014-01-18 TRETS2013/ReviewResponse/Response.tex
Reviewer 3: Main body

@@
 
-      \Response Thanks. It should be $\mu$ in Fig.1 and Equations (35), (36) and (37). It has been fixed.\\
+      \Response Thanks. It should be $\mu_c$ in Fig.1 and Equations (35), (36) and (37). It has been fixed.\\
 
@@
 
-      \PaperText{Carry propagation: (see paper)}
+      \PaperText{Carry propagation: $A_i\neq B_i$, the carry propagates for this carry at bit $i$, and $C_{i-1}=1$, $S_i=0$.}\\
+
+  \item \Question{For $A_i = B_i$ (either 0 or 1), there is no carry annihilation if their value is 1, and $S_i = C_{i-1} = 1$ seems to be a condition, not a consequence.}
+
+      \Response This statement is only applied to determine the annihilation of an existing carry chain, i.e.
+$C_{i-1}=1$.
+In this case if $A_i=B_i=1$, the current carry chain is annihilated, meanwhile a new carry chain is generated.
+If $A_i=B_i=0$, the current carry chain is annihilated but without generating a new chain.
+In both situations we have $S_i=C_{i-1}=1$.
+
+  \item \Question{In 3.2, we have $k$ as the full RCA length, and $n$ as the truncated length.  Compare that to $n$ in 3.3.2 as the length of the non-truncated but overclocked RCA.}
+
+      \Response In both sections, $k$ is used to denote the word-length of the input signal, whereas $n$ is the word-length of RCA.
+
+  \item \Question{Also in 3.3.2, the MSB is given as $2^n$, instead of $2^0$ as would be expected for the [-1, 1) fixed-point format you mentioned.}
+
+      \Response : $2^n$ is used here because $2^i$ is used in Equation (7).
+Nevertheless we agree it might be confusing to put $2^n$ here, and we have changed the second paragraph of Section 3.3.2 to look as follows:\\
+
+      \PaperText{For $C_{tm}$, correct results will be generated from bit $S_t$ to bit $S_{t+b-1}$.
+Hence the absolute value of error seen at the output, normalized to the MSB, is given by (7), where $\hat{S}_i$ and $S_i$ denote the actual value and error-free value of outputs at bit $i$, respectively.}\\
+
+  \item \Question{Still in 3.3.2, you seem to be saying that when a timing error occurs, none of the bits propagate.
+I think you are assuming the worst case, where no carry propagation occurs, so it is no surprise that you comment that the magnitude of overclocking error has no dependence on the length of carry chain $m$.}
+
+      \Response To be added.
+
+  \item \Question{In 3.3.4, I see the $E_O = 2^{-b}-2^{-n-1}$ result, but am puzzled by it.
+At the very least, I am not sure where the $-b$ exponent is coming from, since (8) defines $e_{tm} = 2^{t+b-n}$.}
+
+      \Response We would like to derive Equation (14) as follows:
+      xxx
+
+  \item \Question{The third and fourth paragraphs of Section 5.1 mention the 4-stage CSA, but Figure 4 does not show any data for a 4-stage CSA.}
+
+      \Response Thanks. In the third paragraph of Section 3.1, it should be the 3-stage CSA. Therefore the last sentence of this paragraph is revised as:\\
+
+      \PaperText{Although the CSA with 3 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.}\\
+
+      The 4-stage CSA is introduced in the fourth paragraph and Fig.
+5 and Fig.
+6, where we consider a variety of area constraints.
+Ideally with larger available area, CSA with more stages will be included in both Fig.
+5 and Fig.
+6.
+However the general trend will be similar.
+In previous paragraphs of this section, we only use 2-stage CSA and 3-stage CSA as examples to illustrate the design method.
+We have clarified this point by adding the following sentence to the fourth paragraph of Section 3.1:\\
+
+      \PaperText{We implement CSA with all possible stage numbers within the given area specification.}\\
+
+  \item \Question{In the experimental setup, I would be curious to know whether you used any particular constraints on the circuits-under-test to enhance their chances of success.}
+
+      \Response Actually no specific constraints are applied, except the global clock constraint.
+
+  \item \Question{May I assume that your figures will be colorized?}
+
+      \Response Yes, Fig.~3, Fig.~4 and Fig.~10 will be colorized.
+
+  \item \Question{An incomplete list of spelling or grammar or punctuation comments.}
+
+      \Response Thanks, they have been revised.
 

### 2014-01-18 TRETS2013/ReviewResponse/Response.tex
Reviewer 3: add equations

@@
 \usepackage{amssymb}
+\usepackage{amsmath}
 \usepackage{graphicx}
@@
 Given that all bits are mutually independent and uniformly distributed, Equation (2) gives the mean value of the truncated bits.
-We have modified the second paragraph of Section 3.2:\\
+We have modified the first sentence of the second paragraph of Section 3.2:\\
 
-      \PaperText{to be added.}\\
+      \PaperText{If the input signal of a circuit contains $k$ fractional bits, truncation error occurs when the input signal is truncated from $k$ bits to $n$ bits.}\\
 
@@
       \Response We would like to derive Equation (14) as follows:
-      xxx
+
+      \begin{align*}
+        E_O&=\sum_t\sum_m P_{tm}\cdot e_{tm}\\ &=\sum_{t=0}^{n-b}2^{t+b-n}\cdot\left(\sum_{m=b+1}^{n-t}(1/2)^{m+1}+(1/2)^{n-t+1}\right)\\
+        &=\sum_{t=0}^{n-b}2^{t+b-n}\cdot\left((1/2)^{b+1}-(1/2)^{n-t+1}+(1/2)^{n-t+1}\right)\\
+        &=\sum_{t=0}^{n-b}2^{t+b-n}\cdot2^{-b-1}=\sum_{t=0}^{n-b}2^{t-n-1}\\
+        &=2^{-n-1}\cdot\left(2^{n-b+1}-1\right)\\
+        &=2^{-b}-2^{-n-1}
+      \end{align*}
+
+      The detailed process is not included in the manuscript due to the space limit.
 

### 2014-01-18 TRETS2013/ReviewResponse/Response.tex
Reviewer 3: Add figure and done

@@
 \usepackage{xcolor}
+\usepackage{epstopdf}
 
@@
 
-  \item \Question{What are the chances that an entire design with all its complexities could be accelerated in this fashion? (i.e. Could the overall clock frequency be increased?)}
+  \item \Question{What are the chances that an entire design with all its complexities could be accelerated in this fashion?
+(i.e.
+Could the overall clock frequency be increased?) Imprecision may be tolerable in data, but is probably not tolerable in control.}
 
-      \Response to be added.\\
+      \Response True. However the method described in this manuscript focuses on designing datapath instead of the control logic.\\
 
@@
 Given that all bits are mutually independent and uniformly distributed, Equation (2) gives the mean value of the truncated bits.
+
+      \begin{figure}[htbp]
+        \centering
+        \includegraphics[width=3.2in]{./Figure/Truncation.pdf}
+        %\caption{title.}
+      \end{figure}
+
       We have modified the first sentence of the second paragraph of Section 3.2:\\
@@
   \item \Question{Still in 3.3.2, you seem to be saying that when a timing error occurs, none of the bits propagate.
+You assume $S_{t+b}=S_{t+b+1}=\cdots=S_{t+m-2}=0$ when there is no error, and $S_{t+b}=S_{t+b+1}=\cdots=S_{t+m-2}=1$ when there is an error.
 I think you are assuming the worst case, where no carry propagation occurs, so it is no surprise that you comment that the magnitude of overclocking error has no dependence on the length of carry chain $m$.}
 
-      \Response To be added.
+      \Response The value of output $S_i$ is determined based on the statements in Section 3.3.1.
+The assumption made here is that the internal signals are reset to zero before each computation.
+In this case, for carry propagation and timing error occurs, we have $S_i=A_i+B_i+C_{i-1}=A_i+B_i=1$.
 

### 2014-01-20 TRETS2013/ReviewResponse/Response.tex
Reviewer 2: Main body

@@
 \maketitle
+
+We thank the reviewers for their constructive comments and suggestions. We would like to offer the following response detailing the changes we have made as a result of their recommendations.
+
+\section*{Reviewer 2}
+\begin{enumerate}
+  \item \Question{I believe the practical behavior is that the circuit will operate perfectly away from timing-spec corners, but that the over-clocking will simply exacerbate these.
+Do you believe correcting for PVT guardband by subtracting it is fair?
+What if arithmetic logic is more susceptible to temperature issues due to hot-spots and high toggle rate?
+The net effect in imprecision could be dramatically higher at process corners.
+I believe this should be noted/discussed (or refuted), but I think it is safe to call this future work.}
+
+      \Response In this manuscript, for ease of discussion the PVT variation is not considered.
+However we agree your point that the variation is a critical issue, as it will challenge several assumptions that made in this manuscript such as the uniform carry propagation delay within a ripple-carry-adder.
+We plan to address this problem in the future work as presented in the Conclusion Section.
+
+  \item \Question{A second point I would make is that you seem to have an assumption that errors do not compound.
+What if your arithmetic is in an IIR or used in later computations?
+Do the principles of the paper hold when you get an imprecise data point, then multiply or divide it in some future computation?
+I think that looking at a single adder in isolation is a bit optimistic.}
+
+      \Response
+
+  \item \Question{A third source of inaccuracy is that most FPGA timing models include crosstalk in their guardband - i.e.
+don't specifically do crosstalk-aware timing analysis or glitching.
+Is your modeling being optimistic by looking at a circuit in isolation?
+The measured/visual empirical results would incorporate this, but the model doesn't incorporate anything like it.}
+
+      \Response The analytical model described in this manuscript is not specifically for FPGAs.
+Instead, it can be applied to general ripple-carry-based arithmetic operators, which is used in modern FPGAs.
+Hence there will be inaccuracies between the proposed model and the FPGA timing models.
+However as you mentioned, we use empirical results from FPGA to verify the model and to demonstrate the hypothesis.
+In this case, the assumptions in the models are relaxed.
+It can be seen from the manuscript that the model prediction matches well with the empirical results.
+
+  \item \Question{In the introduction you claim that ``pipelining will not tend to reduce the latency of the datapath''.
+I don't think this is practically the case - not all paths are critical and pipelining does not imply C-slowing.
+For example, since a typical FPGA memory and DSP block operate grater than 500 MHz, in my preceding example you may need to pipeline some portions of the FPGA routing and logic, but you do not need to further pipeline these.}
+
+      \Response True. However in this paper we focus on datapath which only contains arithmetic operators.
+
+  \item \Question{Wording has some comma-itis. E.g. first sentence of the intro should not have a comma in ``demonstrated that, significant performance ...''}
+
+      \Response Thanks. It has been revised.
+
+  \item \Question{You don't specify the speed-grade of the Xilinx device. It might be relevant if you have a down-binned device.}
+
+      \Response The FPGA used in the ML605 board is Xilinx Virtex-6 XC6VLX240T-1FFG1156. The speed grade is -1. This has been included in the manuscript.
+\end{enumerate}
 
@@
 In previous paragraphs of this section, we only use 2-stage CSA and 3-stage CSA as examples to illustrate the design method.
-We have clarified this point by adding the following sentence to the fourth paragraph of Section 3.1:\\
+We have clarified this point by adding the following sentence to the fourth paragraph of Section 5.1:\\
 
@@
 
-      \Response Yes, Fig.~3, Fig.~4 and Fig.~10 will be colorized.
+      \Response Yes, Fig.~3, Fig.~4 and Fig.~10 will be colorized in the final manuscript.
 

### 2014-01-20 TRETS2013/TRETS_overclocking.tex
Reviewer 2: Main body

@@
 \usepackage{graphicx}
-%\usepackage{epstopdf}
+\usepackage{epstopdf}
 \usepackage{multirow}
@@
 \begin{abstract}
-%As process scaling introduces significant performance variations, much more conservative timing margins will have to be applied to avoid timing violations. Potentially, r
-Releasing the tight accuracy requirement would potentially offer greater freedom to create a design with better performance or energy efficiency.
-In this paper, we compare two different approaches that could trade accuracy for performance.
+%Releasing the tight accuracy requirement would potentially offer greater freedom to create a design with better performance or energy efficiency.
+In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area.
+We compare two different approaches that could trade accuracy for performance.
 One is the traditional approach where the precision used in the datapath is limited to meet a target latency.
@@
 We also show that for basic arithmetic operations such as addition, applying our approach to the simple building block of ripple carry adders can achieve better accuracy or performance than using faster adder designs to achieve similar latency.
-
- %operators (i.e.
-ripple carry adders) can achieve better accuracy or performance than using the traditional method to both original operators and intrinsically faster operators (i.e.
-carry select adders) which consumes the same silicon area.
 \end{abstract}
 
-\category{C.2.2}{Category put here}{Detail category}
-
-\terms{Design, FPGA, Performance}
-
-\keywords{Overclocking, Imprecise Design, Approximate Computing, Truncation}
+\category{B.3.3}{Performance Analysis and Design Aids}{Detail category}
+
+\terms{Design Methodologies, Overclocking, FPGA, Performance Modeling and Analysis}
+
+\keywords{Approximate Computing, Truncation, Imprecise Design}
 
@@
 Performance is a critical issue when designing embedded computing systems.
-Specifically, a large volume of current studies has demonstrated that, significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications~\cite{UnderwoodFPGAvsCPU,David_MINRES}.
+Specifically, a large volume of current studies has demonstrated that significant performance gains can be achieved by FPGA-based accelerators over software designs across a wide range of applications~\cite{UnderwoodFPGAvsCPU,David_MINRES}.
 However, one of the major factors that limits the performance of these accelerators is that they typically run at much lower clock frequencies than general purpose processors (GPPs) or graphics processing units (GPUs).
@@
 In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area.
-Since it is unlikely to create a completly error-free design as any data representation would introduce quantization errors, we take a radical shift forward by suggesting that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
+Since it is unlikely to create a completely error-free design as any data representation would introduce quantization errors, we take a radical shift forward by suggesting that for certain applications it is beneficial to move away from the traditional model of creating a conservative design that is guaranteed to avoid timing violations.
 Instead, it may be preferable to create a design in which timing violations may occur, under the knowledge that they only occur rarely because specific input patterns are required to generate the worst case errors.
@@
 \begin{itemize}
-	\item Detailed modeling methods of probabilistic errors generated in basic arithmetic primitives from two design scenarios to trade accuracy for performance: overclocking the datapath or truncating precisions that used throughout the datpath,
+	\item Detailed modeling methods of probabilistic errors generated in basic arithmetic primitives from two design scenarios to trade accuracy for performance: overclocking the datapath or truncating precisions used throughout the datapath,
 	\item Exploring the accuracy-performance-area trade-offs for key arithmetic operators to illustrate the optimum architecture for a certain arithmetic function under a given requirement of silicon area,
-	\item Demonstration of the proposed findings analytically and experimentially from FPGA implementations that allowing rare timing violations to happen leads to a reduction of average errors or an improvement of performance over trancating the datapath precisions to meet timing.
+	\item Demonstration of the proposed findings analytically and experimentally from FPGA implementations that allowing rare timing violations to happen leads to a reduction of average errors or an improvement of performance over truncating the datapath precisions to meet timing.
 \end{itemize}
 
-The rest of this paper is organized as follows.
-It first reviews in detail the current literature regarding the approaches used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
+The rest of this paper is organized as follows: It first reviews in detail the current literature regarding the approaches used in word-length optimization and approximate datapath design in Section~\ref{Section_Background}.
 The analytical error models for two different adder structures: the ripple carry adder (RCA) and the carry-select adder (CSA), are discussed in Section~\ref{section_RCA} and Section~\ref{Section_CSA}, respectively.
@@
 Optionally the system can be recovered at the observation of errors.
-As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overscaling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit.
+As an exemplary design, the Razor project~\cite{Razor2003,Razor2004} was proposed to shave the conservative timing margins by overcalling the supply voltage and clock frequency, while monitoring the output error rates by utilizing a self-checking circuit.
 This work demonstrated that the benefits brought by removing the safe margin outweigh the cost of monitoring and recovering from errors.
-For example, $22\%$ or over $30\%$ power consumption can be saved with $\sim0.01\%$ or $\sim1\%$ error rates at the output, respectively.
-Related work also includes a similar frequency overscaling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
+For example, over $30\%$ power consumption can be saved with $\sim1\%$ error rates at the output, respectively.
+Related work also includes a similar frequency overcalling technique by operating circuits slightly slower than the critical path delay with dedicated checker circuits to ensure that timing errors will not occur~\cite{TEAtime2004}, or developing timing analysis tools that decide the optimum operating frequencies in the non-deterministic region due to process variation~\cite{ProbabilisticSTA}.
 However, the major problem of the BTWC work is the extra cost introduced by implementing the checker circuits.
@@
 
-While the aforementioned literature take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for peformance and/or energy efficiency.
+While the aforementioned literature take advantage of the fact that only specific input patterns could cause timing errors, research on imprecise architectures take this one step further by designing simplified circuits for performance and/or energy efficiency.
 For example, Lu et~al.
 proposed a ``shrinking'' datapath that can be utilized to mimic and speculate the original logic functions~\cite{IntelSpeeding}.
-Kulkarni et.al.
-described an underdesigned $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
+Kulkarni et~al.
+described an under-designed $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
 In both cases, reduction of area and power consumption can be achieved with the cost of accuracy.
@@
 
-%and  that are commonly used in DSP applications and numerical algorithms.
-
 Typically the maximum frequency of a RCA is determined by the longest carry propagation delay.
@@
 
-% $\mu_{RCA}=n\mu$, as shown in~. 
 For an $n$-bit RCA, it follows that if the sampling period $T_S$ is greater than $\mu_{RCA}$, correct results will be sampled.
@@
   \centering
-  \includegraphics[width=3in]{./Figures/FastCarryLogic3.eps}
+  \includegraphics[width=3.2in]{./Figures/FastCarryLogic.pdf}
   %  \vspace{-2ex}
@@
    \item Carry generation: $A_i=B_i=1$, a new carry chain is generated at bit $i$, and $S_i=C_{i-1}$;
-   \item Carry propagation: $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $S_i=\bar{C_{i-1}}=0$;
+   \item Carry propagation: $A_i\neq B_i$, the carry propagates for this carry chain at bit $i$, and $\bar{C_{i-1}}=1$, $S_i=0$;
    \item Carry annihilation: $A_i=B_i$ (either $0$ or $1$), the current carry chain annihilates at bit $i$, and $S_i=C_{i-1}=1$.
@@
 For $C_{tm}$, correct results will be generated from bit $S_t$ to bit $S_{t+b-1}$.
-Hence the absolute value of error seen at the output, normalized to the MSB ($2^n$), is given by (\ref{Eq:Output_Error}), where $\hat{S_i}$ and $S_i$ denote the actual value and error-free value of outputs at bit $i$, respectively.
+Hence the absolute value of error seen at the output, normalized to the MSB, is given by (\ref{Eq:Output_Error}), where $\hat{S_i}$ and $S_i$ denote the actual value and error-free value of outputs at bit $i$, respectively.
 %
@@
 If there is dependency between input bits, (\ref{Eq:Ptm_RCA_General}) should be used and the probability value of $P_{(A_i=B_i=1)}$ and $P_{(A_i\neq B_i)}$ would change.
-For instance, if $A_i$ and $B_i$ are not independent, we have $P_{(A_i=1)}=E_{(A_i)}=1/2$ and $P_{(B_i=1)}=E_{(B_i)}=1/2$ seperately for uniform distribution, where $E_{(A_i)}$ denotes the expectation of $A_i$.
+For instance, if $A_i$ and $B_i$ are not independent, we have $P_{(A_i=1)}=E_{(A_i)}=1/2$ and $P_{(B_i=1)}=E_{(B_i)}=1/2$ separately for uniform distribution, where $E_{(A_i)}$ denotes the expectation of $A_i$.
 The probability of $A_i=B_i=1$ is then given by (\ref{Eq:P_dependency})~\cite{TransitionProb} where $\sigma_{(A_i)}$ denotes the standard variation of $A_i$ and $\rho_i$ denotes the temporal correlation between the two inputs at the $i^{th}$ bit.
@@
 \subsection{Introduction}
-As seen in~(\ref{Eq:Comparison RCA}), a factor of 2 reduction in error expection can be achieved by using the proposed approach in RCA.
+As seen in~(\ref{Eq:Comparison RCA}), a factor of 2 reduction in error expectation can be achieved by using the proposed approach in RCA.
 However, implementing our approach costs extra silicon area in comparison to the conventional approach, because we keep the original word-length $k$ in the new scenario instead of truncating to only $b-1$ bits in the traditional scenario.
@@
 In a CSA, the carry chain is divided into multiple overlapped stages, while each stage contains two RCAs and two multiplexers, as shown in Fig.~\ref{Fig_CSA_Structure} and Fig.~\ref{Fig_CSA_SingleStage}, respectively.
-For a given input, two additions are performed simultaneously within a single stage where the carry input is zero and one seperately.
+For a given input, two additions are performed simultaneously within a single stage where the carry input is zero and one separately.
 One of these two results is then selected according to the actual carry input.
@@
 
-Fig.~\ref{Fig_CSA2stage_Timing} also highlights that for a relatively relexed frequency cosntraint, the CSA achieves greater word-length than the RCA.
+Fig.~\ref{Fig_CSA2stage_Timing} also highlights that for a relatively relaxed frequency constraint, the CSA achieves greater word-length than the RCA.
 This is because the stage parallelism in the CSA enables a greater overall word-length, even though the multiplexer delay limits the word-length of each stage in the CSA when compared to the RCA.
 When more stringent latency requirement is applied, however, the word-length of each stage is largely limited such that the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
-
-%in comparison to the RCA, the CSA achieves greater word-length for relatively relexed frequency constraints.
-The RCA only outperforms when very high frequency requirement is applied.
-This is because at low frequencies, although the multiplexer delay limits the word-length of each stage in CSA when compared to RCA, the stage parallelism in CSA enables a greater word-length.
-However when more stringent latency requirement is applied, the word-length of each stage in CSA is limited.
-Hence the multiplexer delay becomes comparable to the delay of the carry chain, and this inhibits the benefits of parallelism.
 
@@
 The results are obtained from post place-and-route simulations on Xilinx Virtex-6 FPGAs.}
-  \vspace{-.5ex}
+  \vspace{-2ex}
   \label{Fig_CSA_LUT25}
@@
 It can also be observed that the CSA cannot be implemented with the original word-length due to the limited area budget and this leads to large truncation errors.
-Although the CSA with 4 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.
+Although the CSA with 3 stages is best for some frequencies, the overclocked RCA is still the optimum design when high operating frequencies are applied.
 
 We then perform similar experiments with a variety of area constraints.
-The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}.
-From this figure, several observations can be made.
+We implement CSA with all possible stage numbers within the given area specification.
+The optimum design methods with respect to different operating frequencies and area consumptions are demonstrated in Fig.~\ref{Fig_CSA_Tradeoff}, from which several observations can be made.
 Firstly, if the frequency requirement is not large whilst the available area is large enough to implement a CSA in full precision, it will be the optimum design.
@@
 
+\vspace{-0.5ex}
 \subsection{Determination of the Optimum Adder Structure for Given Accuracy Requirements}
@@
 \subsection{Design Guidance}
-To sum up, the experiments reveal that for both design goals, the CSA is not compatitive with the overclocking approach unless one has very relexed area budget.
+To sum up, the experiments reveal that for both design goals, the CSA is not competitive with the overclocking approach unless one has very relaxed area budget.
 As a result, for the remainder of this paper, we will focus on the RCA in our following analysis and experiments.
@@
 In our proposed overclocking scenario, the circuit is overclocked while keeping the original operand word-length.
-The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 FPGA.
+The benefits of the proposed methodology are demonstrated over a set of DSP example designs, which are implemented on the Xilinx ML605 board with a Virtex-6 LX240T-1 FPGA.
 
@@
   %\frac{1}{f_0} &= n\mu+d_c
-  d_0 &= n\mu+d_c
+  d_0 &= n\mu_c+d_c
   \vspace{-13ex}
@@
 \begin{align}\label{Eq_decideMu_1}
-  d_1 &= (n-1)\mu+d_c    \\
+  d_1 &= (n-1)\mu_c+d_c    \\
   &\cdots               \notag
@@
 \begin{eqnarray}\label{Eq_decideMu_2}
-  {d_{n-1}} &= \mu+d_c
+  {d_{n-1}} &= \mu_c+d_c
 \end{eqnarray}
@@
 It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
-This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the our proposed new approach, especially for not stringent frequency requirements.
-%when the clock frequency is initially increased.
+This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the proposed new approach, especially for not stringent frequency requirements.
 
@@
 
-%In general, we can observe a relatively small area overhead of our approach, especially
-
 In general, a very small area overhead of our approach can be observed when the design is initially operated beyond the safe region with higher frequencies or with a small error budget (e.g.
@@
 In addition at even higher operating frequencies or larger error specifications, our approach achieves large performance or accuracy improvements at a cost of a relatively small extra area.
-%frequency is initially increased or with a small error budget (i.e. $\sim10\%$).
 %
@@
 While this research has shown a promising direction for sustaining performance scaling, in the future we wish to apply this approach onto arithmetic units based on alternative number representations, and explore the probabilistic behavior of these operators under a variety of process, voltage and temperature variations.
-
-%explore the probabilistic behaviour of alternative
 

### 2014-01-21 TRETS2013/ReviewResponse/Response.tex

@@
 
-      \Response
+      \Response In the analysis, we consider the ripple carry adder and the constant coefficient multiplier individually to reason their probabilistic behavior under overclocking and truncation.
+However we combine both operators into several benchmark circuits (including IIR) in our experiments.
+In this case, errors do propagate from different operators.
+However as shown in Fig.10, for instance, the overall error reduction in an FIR filter using the overclocking approach is over 2, which is predicted in Equation (17) for a single RCA.
+This means more benefits can be achieved when combining different arithmetic operators.
+
+      As for utilizing the imprecise results for successive computations, we agree with the reviewers on the point that this is not included in this manuscript.
+We would like to investigate this in the future.
+
+      %This motivates us to explore utilizing alternative computer arithmetic which performs computations in a most-significant-digit-first fashion.
 
@@
 
-      \Response Thanks. In the third paragraph of Section 3.1, it should be the 3-stage CSA. Therefore the last sentence of this paragraph is revised as:\\
+      \Response Thanks. In the third paragraph of Section 3.1, it should be the 3-stage CSA. The last sentence of this paragraph has been revised as:\\
 

### 2014-02-12 TRETS2013/ReviewResponse/Response.tex
Edits to response

--- 2014-01-20 TRETS2013/ReviewResponse/Response.tex
@@
 
-      \Response In this manuscript, for ease of discussion the PVT variation is not considered.
-However we agree your point that the variation is a critical issue, as it will challenge several assumptions that made in this manuscript such as the uniform carry propagation delay within a ripple-carry-adder.
-We plan to address this problem in the future work as presented in the Conclusion Section.
+      \Response We would like to clarify that we run the actual (arithmetic) circuit under test on an FPGA board.
+So when we said in the original manuscript that we `subtract' the guard band, we meant that frequency of operation of the model is adjusted to match the observed operation.
+This is purely done for a fair comparison, to separate out performance boost from timing margins from error-inducing over clocking (the latter being the focus of this paper).
+We did not want to include the conservative timing margins within our quoted performance improvement.
+We have clarified this point in Section XXX in the revised manuscript.
 
@@
 
-      \Response
+      \Response This is a good point.
+We have not addressed this concern theoretically to date, although we do address it empirically in the paper (see Section XXX, where several chained arithmetic units are used, including an IIR filter as suggested by the reviewer; results are in line with other benchmarks).
+Nevertheless, we do intend to consider the theoretical limits of this behaviour, and have added this to the future work in Section XXX.
 
@@
 
-      \Response The analytical model described in this manuscript is not specifically for FPGAs.
-Instead, it can be applied to general ripple-carry-based arithmetic operators, which is used in modern FPGAs.
-Hence there will be inaccuracies between the proposed model and the FPGA timing models.
-However as you mentioned, we use empirical results from FPGA to verify the model and to demonstrate the hypothesis.
-In this case, the assumptions in the models are relaxed.
-It can be seen from the manuscript that the model prediction matches well with the empirical results.
+      \Response Again, this is a good point.
+We have opted for the simplest possible model to capture the notion of over clocking, and have then reverted to experimental results to verify whether the model sufficiently captures the complexity of a real implementation.
+For the circuits we have used, the model prediction matches well with the empirical results, as shown in Section XXX.
+These benchmarks are sufficiently large to have confidence that the presence of more than one basic arithmetic core does not have a significant impact on the overall behaviour (including due to crosstalk).
+However, it is certainly possible that the accuracy of the model degrades as the device fills up, an issue we intend to explore in future work and have added to the list of future work in Section XXX.
 
@@
 
-      \Response True. However in this paper we focus on datapath which only contains arithmetic operators.
+      \Response Your point is valid if the pipeline stages are unequally distributed in time across the critical path, a non-ideal situation but - as you point out - a practical one, especially in FPGA implementation.
+An alternative way to improve latency in the case of your example would be to equally distribute the registers corresponding to the existing 10 ticks of latency, although we accept that this retiming is not always possible in FPGA designs.
+We have modified the comment to "assuming perfect pipeline stage balancing, further pipelining will not tend to reduce the latency of the datapath"; this can be found in Section XXX of the revised manuscript.
 
@@
 
-      \Response Thanks. It has been revised.
+      \Response Thanks. This has been improved, we hope.
 
@@
 
-      \Response The FPGA used in the ML605 board is Xilinx Virtex-6 XC6VLX240T-1FFG1156. The speed grade is -1. This has been included in the manuscript.
+      \Response The precise FPGA used was a Xilinx Virtex-6 XC6VLX240T-1FFG1156 (speed grade is -1). This has now been included in Section XXX of the revised manuscript.
 \end{enumerate}
@@
 
-      \PaperText{In this paper, we describe an alternative circuit design methodology when considering trade-offs between accuracy, performance and silicon area.
+      \PaperText{In this paper, we describe an alternative circuit design methodology to provide a trade-off between accuracy, performance and silicon area.
 We compare two different approaches that could trade accuracy for performance.}\\
@@
 
-      \Response True. However the method described in this manuscript focuses on designing datapath instead of the control logic.\\
+      \Response We agree.
+The approach is targeted at datapath logic.
+In our experience, the critical path of complex signal processing systems often resides in the datapath, in which case this approach would directly improve the clock frequency.
+In the case where the critical path lies elsewhere, it may still be possible to improve the overall operating speed of the system-level design solely by this approach, by using multiple clock domains, which may be practical in the case of large sections of datapath with simple control structures (e.g.
+the filters we present) that are then interfaced to more complex control at IP boundaries.
+We now note this in Section XXX as an area for future work.
 
@@
   \item \Question{In Section 3.2, it would be helpful if you could illustrate or define your [-1,1) fixed-point format. Do you number your bits from k-1 to 0 or from 0 to k-1?}
+
+ XXX -> Kan, THE TEXT BELOW IS NOT ANSWERING THE QUESTION! The question is simple: is your MSB labelled $a_0$ or $a_1$ or $a_k$ or $a_{k-1}$ - which order are the bits in??
 
@@
 
+ XXX -> Kan, check this answer makes sense with reference to the one above about the format.
+
       \PaperText{For $C_{tm}$, correct results will be generated from bit $S_t$ to bit $S_{t+b-1}$.
@@
 
-      \Response The value of output $S_i$ is determined based on the statements in Section 3.3.1.
-The assumption made here is that the internal signals are reset to zero before each computation.
-In this case, for carry propagation and timing error occurs, we have $S_i=A_i+B_i+C_{i-1}=A_i+B_i=1$.
+      \Response The value of output $S_i$ is determined based on the statements in Section 3.3.1. In this case, for carry propagation and timing error occurs, we have $S_i=A_i+B_i+C_{i-1}=A_i+B_i=1$.
 
@@
 
-      \Response We would like to derive Equation (14) as follows:
+      \Response We would derive Equation (14) as follows:
 
@@
 
-      \Response Actually no specific constraints are applied, except the global clock constraint.
+      \Response  No specific constraints are applied, except the global clock constraint.
 

### 2014-02-12 TRETS2013/ReviewResponse/Response.tex
Reviewers response: George's comment

@@
 We did not want to include the conservative timing margins within our quoted performance improvement.
-We have clarified this point in Section XXX in the revised manuscript.
+We have clarified this point in Section 7.3 in the revised manuscript.\\
 
@@
       \Response This is a good point.
-We have not addressed this concern theoretically to date, although we do address it empirically in the paper (see Section XXX, where several chained arithmetic units are used, including an IIR filter as suggested by the reviewer; results are in line with other benchmarks).
-Nevertheless, we do intend to consider the theoretical limits of this behaviour, and have added this to the future work in Section XXX.
+We have not addressed this concern theoretically to date, although we do address it empirically in the paper (see Section 8, where several chained arithmetic units are used, including an IIR filter as suggested by the reviewer; results are in line with other benchmarks).
+Nevertheless, we do intend to consider the theoretical limits of this behaviour, and have added this to the future work in Section 9.\\
 
@@
 We have opted for the simplest possible model to capture the notion of over clocking, and have then reverted to experimental results to verify whether the model sufficiently captures the complexity of a real implementation.
-For the circuits we have used, the model prediction matches well with the empirical results, as shown in Section XXX.
+For the circuits we have used, the model prediction matches well with the empirical results, as shown in Section 8.
 These benchmarks are sufficiently large to have confidence that the presence of more than one basic arithmetic core does not have a significant impact on the overall behaviour (including due to crosstalk).
-However, it is certainly possible that the accuracy of the model degrades as the device fills up, an issue we intend to explore in future work and have added to the list of future work in Section XXX.
+However, it is certainly possible that the accuracy of the model degrades as the device fills up, an issue we intend to explore in future work and have added to the list of future work in Section 9.\\
 
@@
 An alternative way to improve latency in the case of your example would be to equally distribute the registers corresponding to the existing 10 ticks of latency, although we accept that this retiming is not always possible in FPGA designs.
-We have modified the comment to "assuming perfect pipeline stage balancing, further pipelining will not tend to reduce the latency of the datapath"; this can be found in Section XXX of the revised manuscript.
+We have modified the comment to:
+      \PaperText{assuming perfect pipeline stage balancing, further pipelining will not tend to reduce the latency of the datapath.}
+
+      This can be found in paragraph 2, Section 1 of the revised manuscript.\\
 
@@
 
-      \Response Thanks. This has been improved, we hope.
+      \Response Thanks. This has been improved, we hope.\\
 
@@
 
-      \Response The precise FPGA used was a Xilinx Virtex-6 XC6VLX240T-1FFG1156 (speed grade is -1). This has now been included in Section XXX of the revised manuscript.
+      \Response The precise FPGA used was a Xilinx Virtex-6 XC6VLX240T-1FFG1156 (speed grade is -1). This has now been included in Section 7 of the revised manuscript.
 \end{enumerate}
@@
 the filters we present) that are then interfaced to more complex control at IP boundaries.
-We now note this in Section XXX as an area for future work.
+We now note this in Section 9 as an area for future work.\\
 
@@
 
-  \item \Question{In Section 3.2, it would be helpful if you could illustrate or define your [-1,1) fixed-point format. Do you number your bits from k-1 to 0 or from 0 to k-1?}
+  \item \Question{In Section 3.2, it would be helpful if you could illustrate or define your [-1,1) fixed-point format.
+I'll ignore the typical ${-1}^s$ sign bit, since you make no mention of it.
+For the rest of the number, I would infer a value of $\sum2^{-i}$, for $i$ = 0 to $k-1$, to accommodate your range.
+If I use that, I obtain $E_{Tin} = 2^{-n} - 2^{-k-2}$ for your Equation (2).
+That in turn leads to $E_T = 2^{-n+1} - 2^{-k-1}$ for Equation (3).
+Do you number your bits from $k-1$ to 0 or from 0 to $k-1$?}
 
- XXX -> Kan, THE TEXT BELOW IS NOT ANSWERING THE QUESTION! The question is simple: is your MSB labelled $a_0$ or $a_1$ or $a_k$ or $a_{k-1}$ - which order are the bits in??
+ %XXX -> Kan, THE TEXT BELOW IS NOT ANSWERING THE QUESTION! The question is simple: is your MSB labelled $a_0$ or $a_1$ or $a_k$ or $a_{k-1}$ - which order are the bits in??
 
       \Response We meant that all numbers are normalized to fractional numbers within the range [-1,1).
-The truncation process is illustrated in the figure below, which is not included in this manuscript due to the space limit.
+The MSB is labelled as $a_1$, and the truncation process is illustrated in the figure below, which is not included in this manuscript due to the space limit.
 As seen in this figure, the original number embodies k fractional bits, while the truncated number embodies n fractional bits.
@@
 If $A_i=B_i=0$, the current carry chain is annihilated but without generating a new chain.
-In both situations we have $S_i=C_{i-1}=1$.
+In both situations we have $S_i=C_{i-1}=1$.\\
 
@@
 
-      \Response In both sections, $k$ is used to denote the word-length of the input signal, whereas $n$ is the word-length of RCA.
+      \Response In both sections, $k$ is used to denote the word-length of the input signal, whereas $n$ is the word-length of RCA.\\
 
@@
 
- XXX -> Kan, check this answer makes sense with reference to the one above about the format.
+ %XXX -> Kan, check this answer makes sense with reference to the one above about the format.
 
@@
 
-      \Response The value of output $S_i$ is determined based on the statements in Section 3.3.1. In this case, for carry propagation and timing error occurs, we have $S_i=A_i+B_i+C_{i-1}=A_i+B_i=1$.
+      \Response The value of output $S_i$ is determined based on the statements in Section 3.3.1.
+In this case, for carry propagation and timing error occurs, we have $S_i=A_i+B_i+C_{i-1}=A_i+B_i=1$.\\
 
@@
 
-      The detailed process is not included in the manuscript due to the space limit.
+      The detailed process is not included in the manuscript due to the space limit.\\
 
@@
 
-      \Response  No specific constraints are applied, except the global clock constraint.
+      \Response  No specific constraints are applied, except the global clock constraint.\\
 
@@
 
-      \Response Yes, Fig.~3, Fig.~4 and Fig.~10 will be colorized in the final manuscript.
+      \Response Yes, Fig.~3, Fig.~4 and Fig.~10 will be colorized in the final manuscript.\\
 

### 2014-04-25 TRETS2013/TRETS_overclocking.tex
Review 2nd round: grammer changes

@@
 }
-%\vspace{-5ex}
+\vspace{-5ex}
 
@@
 The other is a proposed new approach which simply allows the datapath to operate without timing closure.
-We demonstrate analytically and experimentally that on average our approach obtains either smaller errors for equivalent faster operating frequencies in comparison to the traditional approach.
+We demonstrate analytically and experimentally that on average our approach obtains either smaller errors or equivalent faster operating frequencies in comparison to the traditional approach.
 This is because the worst case caused by timing violations only happens rarely, while precision loss results in errors to most data.
@@
 
-\category{B.3.3}{Performance Analysis and Design Aids}{Detail category}
+\category{B.8.2}{Performance and Reliability}{Performance Analysis and Design Aids}
 
@@
 In order to boost the operating frequency of a datapath, the standard approaches are either to heavily pipeline the design or to reduce the precision throughout the datapath.
-For the former method, it should be noted that pipelining will not tend to reduce the latency of the datapath, whilst the latency in terms of clock cycles will actually increase.
+For the former method, it should be noted that assuming perfect pipeline stage balancing, further pipelining will not tend to reduce the latency of the datapath.
 As a result, this method will not be applicable to many embedded applications, which often have strict latency requirements, or in any datapath containing feedback where C-slow retiming is inappropriate.
@@
 
+\vspace{-.5ex}
 \begin{itemize}
@@
 \end{itemize}
+%\vspace{-2ex}
 
@@
 Kulkarni et~al.
-described an under-designed $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straight-forward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
-In both cases, reduction of area and power consumption can be achieved with the cost of accuracy.
+described an under-designed $2\times2$ multiplier unit, of which the worst case was replaced by a normal case based on the straightforward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
+In both cases, reduction of area and power consumption can be achieved at the cost of accuracy.
 In addition, Gupta et~al.
@@
 In general, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
-As such, the philosophy of our approach is first exemplified with the analysis of a RCA.
+As such, the philosophy of our approach is first exemplified with the analysis of an RCA.
 We later describe how this methodology can be extended to other arithmetic operators such as CSAs and CCMs, which are commonly used in DSP applications and numerical algorithms, in Section~\ref{Section_CSA} and Section~\ref{section_CCM} respectively.
@@
 The presence of overclocking error requires $m>b$.
-Since the length of carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{Eq:t_RCA}) and (\ref{Eq:m_RCA}):
+Since the length of the carry chain cannot be greater than $n$, parameters $t$ and $m$ are bounded by (\ref{Eq:t_RCA}) and (\ref{Eq:m_RCA}):
 %
@@
 In this graph, we have labeled the optimum adder structure.
-Note that in this and all the following experiments within this section, in order to apply our models the input data is randomly generated following the uniform distribution.
+Note that in this and all the following experiments within this section, in order to apply our models, the input data is randomly generated following the uniform distribution.
 %
@@
 The filter parameters are generated through MATLAB filter design toolbox, and they are normalized to integers for implementation.
-Table~\ref{Rated_Frequency_table} summarizes the operating frequency of each implemented design in Xilinx ISE14.1 when the word-length of input signal is 8-bit.
+Table~\ref{Rated_Frequency_table} summarizes the operating frequency of each implemented design in Xilinx ISE14.1 when the word-length of the input signal is 8-bit.
 %
@@
 However, a non-uniform period change can be observed for both results.
-For instance, the maximum operating frequency keeps almost constant when the operand word-length reduces from 8 to 6 or from 5 to 3 in both the experimental results and those of timing analyzer.
+For instance, the maximum operating frequency remains almost constant when the operand word-length reduces from 8 to 6 or from 5 to 3 in both the experimental results and those of timing analyzer.
 This will cause a slight deviation between our analytical model which assumes that the single bit carry propagation delay to be a constant value, as discussed in (\ref{Eq:Eo_trad_RCA}) with expression $n=b-1$.
@@
 Likewise, the frequency speedup is higher for real image inputs than uniform inputs.
-The geometric mean of frequency speedups of $3.1\%$ to $21.8\%$ can be achieved by using uniform data, while $5.3\%$ to $27.6\%$ when using real image data.
+The geometric mean of frequency speedups of $3.07\%$ to $21.8\%$ can be achieved by using uniform data, with $5.32\%$ to $27.6\%$ when using real image data.
 %
@@
 In our experiments, the area overhead is evaluated in terms of the number of LUTs and Slices in the FPGA technology, while similar metrics can also be employed if applying our approach into other hardware platforms.
-It can be seen that for a given frequency requirement with minimum possible errors, the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
-This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the proposed new approach, especially for not stringent frequency requirements.
+It can be seen that for a given frequency requirement with minimum possible errors (Table~\ref{Table:AreaFrequency}), the geometric mean of area overhead ranges from $1.16\times$ and $1.15\times$ to $5.57\times$ and $4.46\times$ for LUTs and Slices, respectively.
+This result illustrates that although using traditional approach would lead to smaller design, the area benefits are less attractive than the performance or accuracy benefits brought by utilizing the proposed new approach, especially for relaxed frequency requirements.
 
 An even smaller area overhead can be found for a specified error budget with the maximum clock frequencies.
-As seen in Table~\ref{Table:AreaFrequency}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
+As seen in Table~\ref{Table:AreaError}, the geometric mean of area overhead in terms of LUTs and Slices is $1.00\times\sim4.67\times$ and $1.00\times\sim3.70\times$ respectively.
 Notice that an area overhead of $1\times$ means both the overclocking scenario and the traditional scenario use the original precision, however the former achieves frequency speedups as seen in Table~\ref{Table:AreaError}, because a specific error budget can be tolerated.
@@
    \tbl{Area Overhead of Our Approach with respect to Given Frequency Requirements}{
-   \label{Table_AreaFrequency}
    \centering
@@
    \tbl{Area Overhead of Our Approach with respect to Given Error Budgets.}{
-   \label{Table_AreaError}
    \centering
@@
 
-While this research has shown a promising direction for sustaining performance scaling, in the future we wish to apply this approach onto arithmetic units based on alternative number representations, and explore the probabilistic behavior of these operators under a variety of process, voltage and temperature variations.
+While this research has shown a promising direction for sustaining performance scaling, in the future we wish to extend the current model by considering the propagation of error through arithmetic circuits at the component level, and to apply this approach beyond datapath designs with a variety of PVT variations.
+
+%apply this approach onto arithmetic units based on alternative number representations, and explore the probabilistic behavior of these operators under a variety of process, voltage and temperature variations.
 

### 2014-05-05 TRETS2013/TRETS_overclocking.tex

@@
     \subfigure[]{
-        \includegraphics[width=.50\textwidth]{./Figures/CSA2stage_Model_Timing2.eps}
+        \includegraphics[width=.50\textwidth]{./Figures/CSA2stage_Model_Timing_color.eps}
         \label{Fig_CSA2stage_Timing}
@@
     \subfigure[]{
-        \includegraphics[width=.5\textwidth]{./Figures/CSA3stage_Area2.eps}
+        \includegraphics[width=.5\textwidth]{./Figures/CSA3stage_Area_color.eps}
         \label{Fig_CSA3stage_Area}
@@
   \vspace{-3ex}
-  \includegraphics[width=3.3in]{./Figures/Error_LUT25.eps}
+  \includegraphics[width=3.3in]{./Figures/Error_LUT25_color.eps}
   \vspace{-2ex}
@@
   \vspace{-3ex}
-  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Error_New_TCAD.eps}
+  \includegraphics[width=3.5in]{./Figures/Exp/FIR/FIR_Compare_color.eps}
   \vspace{-2ex}

### 2014-05-05 FPT2014/bare_conf.tex
Initial structure

\documentclass[conference]{IEEEtran}

%\usepackage{cite}

\usepackage[cmex10]{amsmath}

\usepackage{algorithm}
\usepackage{algorithmic}

% Graph package
\ifx\pdfoutput\undefined
\usepackage{graphicx}
\else
\usepackage[pdftex]{graphicx}
\fi
\usepackage{epstopdf}

\usepackage{multirow}

% *** SUBFIGURE PACKAGES ***
\usepackage[tight,footnotesize]{subfigure}
% subfigure.sty was written by Steven Douglas Cochran. This package makes it
% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
% work, it is a good idea to load it with the tight package option to reduce
% the amount of white space around the subfigures.

%\usepackage[caption=false]{caption}
%\usepackage[font=footnotesize]{subfig}
% subfig.sty, also written by Steven Douglas Cochran, is the modern
% replacement for subfigure.sty. However, subfig.sty requires and
% automatically loads Axel Sommerfeldt's caption.sty which will override
% IEEEtran.cls handling of captions and this will result in nonIEEE style
% figure/table captions. To prevent this problem, be sure and preload
% caption.sty with its "caption=false" package option. This is will preserve
% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
% (recommended due to many improvements over 1.2) of subfig.sty supports
% the caption=false option directly:
\usepackage[caption=false,font=footnotesize]{subfig}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}

% can use linebreaks \\ within to get better formatting as desired
\title{Efficient FPGA Implementation of\\ Overclocking Friendly Online Arithmetic Operators}

% author names and affiliations
%\author{\IEEEauthorblockN{Kan Shi, David Boland, and George A. Constantinides}
%\IEEEauthorblockA{Department of Electrical and Electronic Engineering\\
%Imperial College London\\London, UK\\
%\{k.shi11, david.boland03,g.constantinides\}@imperial.ac.uk}
%}

\maketitle

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}

\section{Background and Relevant Work}
\subsection{Online Arithmetic}

\subsection{FPGA Architecture}

\section{Digit-parallel Online Adder on FPGAs}

\section{Digit-parallel Online Multiplier on FPGAs}

\section{Results}

%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

\bibliographystyle{./IEEEtran}
\bibliography{./IEEEabrv,./Reference.bib}

\end{document}

### 2014-05-06 FPT2014/bare_conf.tex
Online Adder

@@
 
-\subsection{FPGA Architecture}
+%\subsection{FPGA Architecture}
 
 \section{Digit-parallel Online Adder on FPGAs}
+\subsection{Related Works}
+There has been previous works focusing on efficient FPGA implementation of the digit-parallel online adder.
+Generally the existing approaches can be classified into three types:%, as discussed below.
+A more detailed review of current works can be found in xxx.
+\begin{enumerate}
+	\item efficient mapping of the digit-parallel online adder onto sophisticated FPGAs resources [xxx];
+	\item multiple operands addition by designing compressor trees based on bit counters [xxx];
+	\item modifying existing FPGA architecture for more efficient online addition [xxx] and for specific applications [xxx].
+\end{enumerate}
+
+Type 2 and type 3 are beyond the scope of this paper, as we focus on the general purpose online adder that takes 2 inputs and generate 1 outputs, as shown in Figure xxx.
+Specifically in type 1, both works took advantage of the built-in carry resources in FPGAs.
+Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as shown within the gray background in Figure xxx.
+However, directly applying this approach in the FPGAs could be less efficient.
+This is because there is no carry propagation between the 2 full adders within a 4:2 compressor, and the net delay between them can be large.
+Instead, Kamp et al and Ortiz et al described very similar mapping techniques for online adders with 2 different data representations, respectively.
+The main idea is to map the logic block within the dotted circle in Figure xxx.
+In this case, the fast-carry logic in the FPGA can be employed, and the delay between the 2 FAs is largely reduced.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan.pdf}
+	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
+The grey background highlights the 4:2 compressor.
+Dotted circle indicates the logic block (LB) which can be mapped to the FPGA carry resources.}
+\end{figure}
+
+However, we notice the major limitations of both approaches that they only target on FPGAs with 4-input LUTs and 2 LUTs within a logic slice, such as the Xilinx Spartan series and the Altera Cyclone series.
+This is naturally reasonable because one LB can be mapped to a single slice.
+Nevertheless, for FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in [xxx] will result in either resource waste or logic fault.
+For instance, if 2 LBs are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreviousWork}, the outputs of the second LB will be faulty because the its carry input cannot be initialized.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork.pdf}
+	\caption{Direct utilization of previous approaches on a Virtex-6 FPGA will results in faulty outputs.}
+	\label{Fig:PreviousWork}
+\end{figure}
+
+\subsection{Proposed Mapping Method}
 
@@
 \section{Results}
-
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
 

### 2014-05-07 FPT2014/bare_conf.tex
Adder section initial draft

@@
 Instead, Kamp et al and Ortiz et al described very similar mapping techniques for online adders with 2 different data representations, respectively.
-The main idea is to map the logic block within the dotted circle in Figure xxx.
+The main idea is to map the logic block within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
 In this case, the fast-carry logic in the FPGA can be employed, and the delay between the 2 FAs is largely reduced.
@@
 Dotted circle indicates the logic block (LB) which can be mapped to the FPGA carry resources.}
+	\label{Fig:PreviousWork}
 \end{figure}
@@
 This is naturally reasonable because one LB can be mapped to a single slice.
-Nevertheless, for FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in [xxx] will result in either resource waste or logic fault.
-For instance, if 2 LBs are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreviousWork}, the outputs of the second LB will be faulty because the its carry input cannot be initialized.
+Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in [xxx] will result in either resource waste or logic fault.
+For instance, if 2 LBs are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}s, the outputs of the second LB will be faulty because the its carry input cannot be explicitly initialized.
 
-\begin{figure}
+\begin{figure}[htbp]
 	\centering
@@
 	\caption{Direct utilization of previous approaches on a Virtex-6 FPGA will results in faulty outputs.}
-	\label{Fig:PreviousWork}
+	\label{Fig:PreWorkVirtex6}
 \end{figure}
@@
 \subsection{Proposed Mapping Method} 
+To tackle this problem, we first modify the structure of the online adder to enable an efficient FPGA mapping.
+The structure of a 3-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
+In this equivalent structure, the first FA in each 4:2 compressor is split into 2 parts, which only generate carry and sum respectively.
+In this case they can be mapped individually on 2 LUTs.
+The second FA, which generates the outputs, is unchanged and can be implemented using the fast-carry logic.
+
+%propose an alternative mapping method that targets on the slice containing 4 LUTs such as the Xilinx Virtex series and all Xilinx 7 series FPGAs.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FPGA_New.pdf}
+	\caption{Modified structure of online adder.
+Left: an example of 3-digit online adder.
+The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 slice.
+Right: one LB.
+the dotted box outlines the logic that can be mapped onto 1 LUT and the corresponding fast-carry logic.}
+	\label{Fig:ModifiedOA}
+\end{figure}
+
+The detailed slice mapping of the 2 LBs is shown in Fig.~\ref{Fig:SliceNew}.
+The I/O signals are identical to the previous example in Fig.~\ref{Fig:ModifiedOA}.
+It can be seen that a 6-LUT can be configured with two different output ports O6 and O5.
+For LB1, the carry input can be initialized by setting the O6 of LUT2 equal to 0 constantly.
+In this case, the output of MUXCY2 is O5 of LUT2, and the carry from LB2 will not affect the results of LB1.
+Using this mapping method the resources within 1 slice can be fully utilized, potentially leads to significant area reduction.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.48\textwidth]{./Figures/SDadder_FastCarry_New.pdf}
+	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for Not Care.}
+	\label{Fig:SliceNew}
+\end{figure}
 

### 2014-05-08 FPT2014/bare_conf.tex
Multiplier

@@
 \usepackage[cmex10]{amsmath}
+\usepackage{amssymb}
 
@@
 \usepackage{algorithmic}
+\usepackage{indentfirst}
+\renewcommand{\algorithmicrequire}{ \textbf{Initialization:}}
+\renewcommand{\algorithmicensure}{ \textbf{Recurrence:}}
 
@@
 
-\section{Background and Relevant Work}
-\subsection{Online Arithmetic}
+\section{Background: Online Arithmetic}
+\subsection{Key Features of Online Arithmetic}
+In conventional arithmetic, results are generated either from the least significant digit, e.g.
+addition and multiplication, or from the most significant digit, e.g.
+division and square root.
+This inconsistency in computing directions can result in large latency when propagating data among different operations.
+Online arithmetic was proposed to solve this problem [xxx].
+With online arithmetic, both the inputs and the outputs are processed in a MSD-first manner.
+This enables parallelism and duplication among various operations, and the overall computation latency can be significantly reduced.
+
+Online arithmetic was originally designed for digit-serial operation, of which the data flow is illustrated in Fig~\ref{Fig:OnlineDataFlow}.
+It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required and $\delta$ is called ``online delay''.
+Notice that $\delta$ is normally a constant, which is independent of the precision in a given operation.
+For ease of discussion, in the following of this paper the input data are normalized to fixed point numbers in the range $(-1,1)$.
+Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
+
+\begin{figure}[htbp]
+  \centering
+  %\vspace{-2.5ex}
+  \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.pdf}
+  %\vspace{-3ex}
+  \caption{Dataflow in digit-serial Online Arithmetic. $\delta$ denotes the online delay.}
+  %\vspace{-.5ex}
+  \label{Fig:OnlineDataFlow}
+\end{figure}
+
+\begin{eqnarray}\label{Eq:Online_Operands}
+\footnotesize
+  X_{[j]}=\sum_{i=1}^{j+\delta}x_ir^{-i},~Y_{[j]}=\sum_{i=1}^{j+\delta}y_ir^{-i},~Z_{[j]}=\sum_{i=1}^{j}z_ir^{-i}
+\normalsize
+\end{eqnarray}
+
+MSD-first operation is possible with the employment of the redundant number system \cite{RedundantNumber}, in which each digit is represented with a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
+Due to the redundancy, the MSDs of the result can be calculated only based on partial information of the inputs and then the value of the number can be revised by the following digits.
+
+\subsection{Binary Online Addition}
+Adders serve as a critical building block for arithmetic operations.
+To perform digit-parallel online addition, a redundant adder can be directly utilized.
+The adder structure diagram is shown in Fig~\ref{Fig:Radix2SD_adder}.
+A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
+As seen in Figure~\ref{Fig:Radix2SD_adder}, the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/SDAdder.pdf}
+%\vspace{-8.5ex}
+	\caption{An $N$-digit binary digit-parallel online adder with $(N+1)$-digit outputs.}
+	\label{Fig:Radix2SD_adder}
+\end{figure}
+
+In Section~\ref{Sec:OA_FPGA}, we will present a novel method of mapping the digit parallel online adder efficiently on FPGAs using the built-in carry resources.
+
+\subsection{Binary Online Multiplication}
+Multiplication is another key arithmetic operator.
+Typically the online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit number as given in~(\ref{Eq:Online_Operands}).
+For a given iteration $j$, the product digit $z_j$ is generated through a selection function $sel()$.
+For the radix $r$ and a chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
+As radix-2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
+In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}) \cite{Oregon_OnlineNetwork}.
+Notice that the election is made only based on 1 integer bit and 1 fractional bit of $W_{[j]}$.
+
+\begin{algorithm}[tbp]
+  \caption{Online Multiplication}
+  \begin{algorithmic}[1]
+    \REQUIRE~$X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$
+    \ENSURE~$for~~ j=-\delta,~-\delta+1,~\cdots,~N-1 ~~do$
+      \begin{eqnarray}\label{Eq:OnlineMult_General}
+        \begin{matrix}
+          H_{[j]}   & = & r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)\\
+          W_{[j]}   & = & P_{[j]} + H_{[j]}\\
+          z_j       & = & sel(W_{[j]})\\
+          P_{[j+1]} & = & r\left(W_{[j]}-z_j\right)
+        \end{matrix}
+      \end{eqnarray}
+  \label{Algorithm:OnlineMult}
+  \vspace{-2ex}
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{eqnarray}\label{Eq:SelFunc_OM}
+%\small
+  sel(W_{[j]})=\begin{cases}
+    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
+    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
+    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
+  \end{cases}
+%\normalsize
+\end{eqnarray}
+
+In Section~\ref{Sec:OM_FPGA}, we will describe a modified online multiplication algorithm and its FPGA implementation, which are designed specifically targeting on digit parallel operations.
 
@@
 
-\section{Digit-parallel Online Adder on FPGAs}
+\section{Digit Parallel Online Adder on FPGAs}\label{Sec:OA_FPGA}
 \subsection{Related Works}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 	\centering
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 	\centering
 	\includegraphics[width=.48\textwidth]{./Figures/SDadder_FastCarry_New.pdf}
-	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for Not Care.}
+	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
 	\label{Fig:SliceNew}
@@
 
-\section{Digit-parallel Online Multiplier on FPGAs}
+\subsection{Performance Analysis}
+
+\section{Digit Parallel Online Multiplier on FPGAs}\label{Sec:OM_FPGA}
+\subsection{Algorithm of Digit Parallel Online Multiplication}
+Algorithm xxx as described in Section.xxx can be synthesized into a unrolled digit parallel structure, which has been demonstrated to be ``overclocking friendly'' because timing errors initially affect the least significant digits [xxx].
+This synthesis method is straightforward and can be utilized to design other digit parallel online operators.
+
+However, in order to implement the digit parallel online multiplier (OM), large area budget is required because of the large area overhead of a single iteration stage and the overall stage numbers required.
+For instance in an $N$-digit OM, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, and $(N+\delta)$ iterations for the most significant $N$ digits result.
+Each iteration stage consists of all operations in Eq.xxx.
+In comparison, in an $N$-digit array multiplier there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
+
+Instead of simply implementing the unrolled format of Algorithm xxx, it can be optimized given that all inputs are digit parallel.
+Initially the online delay $\delta$ is employed to generate the MSD of the results only based on partial information of the inputs.
+Nevertheless if all digits of inputs are given simultaneously, $\delta$ is no longer necessary.
+Due to the same reason, $H[j]$, which takes 1 digit of input per stage as shown in Algorithm xxx, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
+The optimized digit parallel online multiplication algorithm is described in Algorithm xxx.
+
+\subsection{FPGA Implementation}
+The structure diagram of a 4-digit OM using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a).
+Generally in an $N$-digit OM, there are only $N$ stages to generate results with $2N$ digits.
+Each stage can be efficiently implemented using FPGAs, and the structure diagram of stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b).
+In each stage, an online adder is used to derive $W_{[j]}$.
+The selection logic, as described in Section xxx and Eq.xxx, takes 3 digits input (6 bits) and generate 1 digit output (2 bits).
+Hence it can be implemented using two 6-LUTs for each output bit.
+Similarly the generation of $P_{[j]}$ can also be implemented using one 6-LUT, since only the integer parts of $W_{[j]}$ might change due to the selection of $z_j$.
+In addition, the structure of Stage 1 can be further optimized by removing the online adder, because $P_{[0]}=0$.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.pdf}
+	\caption{(a) Structural diagram of a 4-digit online multiplier using the proposed algorithm.
+(b) Structure of one stage.
+The word-length of all signals are labelled in terms of the number of digits.
+$N$ denotes the word-length of the input signal.}
+	\label{Fig:PMStructure}
+\end{figure}
+
+\subsection{Structure Optimization for the MSD Half of the Results}
+
+Normally the OM is connected with other arithmetic operators in real applications.
+If the outputs of an OM is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs.
+In the conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
+However both the computation time and the structure remains unchanged, because the results are generated from LSDs.
+
+In comparison, the online multiplier offers the possibility to optimize the structure to a further extent if only the MSD half of the results are required, as the results are generated initially from the MSD.
+The modified structure diagram is illustrated in Fig.~\ref{Fig:PMStructure_MSDhalf}(a).
+The word-length of the online adder in a given Stage $j$ can be reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
+This is because there is no carry propagation in the online adder, and all digits of the online adder are obtained in parallel.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
+	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result. }
+	\label{Fig:PMStructure_MSDhalf}
+\end{figure}
+
+\subsection{Performance Analysis}
 

### 2014-05-11 FPT2014/bare_conf.tex
Add adder figures

@@
 % author names and affiliations
+\author{Authors removed for blind review}
 %\author{\IEEEauthorblockN{Kan Shi, David Boland, and George A. Constantinides}
@@
 	\centering
-	\includegraphics[width=.48\textwidth]{./Figures/SDadder_FastCarry_New.pdf}
+	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FastCarry_New.pdf}
 	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
@@
 
+In this mapping approach, the theoretical area figures of the online adder in terms of the number of LUTs and Slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+\begin{eqnarray}\label{Eq:OAareaLUT}
+	Area\_LUT = 2N
+\end{eqnarray}
+%
+\begin{eqnarray}\label{Eq:OAareaSlice}
+	Area\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
+\end{eqnarray}
+
 \subsection{Performance Analysis}
+In our experiments we compare 3 types of adders using Virtex-6 FPGAs: ripple carry adder (RCA), online adder which is implemented using behavioural description based on 4:2 compressors (OA\_behv) and online adder which is built using our proposed approach (OA\_real).
+Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "Carry4" is used to create OA\_real.
+
+The rated frequencies of all designs for a variety of operand word-lengths are shown in Fig.~\ref{Fig:AdderFreq}.
+The frequency values are obtained through Xilinx Timing Analyzer after placing and routing in ISE 14.1.
+It can be seen that our approach outperforms RCA when $N>8$, and that our approach is always faster than the online adder based on 4:2 compressors.
+Also we can see that the frequency of RCA decreases drastically with respect to the increment of the operand word-length, whereas the online adder maintains a relatively high frequency even for large designs.
+This is because the critical path of the online adder is irrelevant to the operand word-lengths.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.45\textwidth]{./Figures/Exp/Adder_Freq.eps}
+	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.1.}
+	\label{Fig:AdderFreq}
+\end{figure}
+
+The area comparisons are demonstrated in Fig.\ref{Fig:AdderArea}.
+The theoretical area of the online adder (OA\_theory) based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also included.
+It can be seen that OA\_behv is not area efficient for FPGAs, as the dedicated FPGA resources are not fully utilized.
+In comparison, our implementation achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
+The area overhead of our approach against RCA is $1.80\times\sim1.98\times$
+in LUTs and $1.00\times\sim1.88\times$ in Slices. However this is close to the theoretical minimum area overhead for online adders.
+
+\begin{figure}[tbp]
+  %\vspace{-2.5ex}
+  \centering
+  \subfigure[LUTs]{
+  \begin{minipage}{0.45\textwidth}
+    %\centering
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_LUTs2.eps}
+    \vspace{1ex}
+  \end{minipage}%
+  }
+  \subfigure[Slices]{
+  \begin{minipage}{0.45\textwidth}
+    %\centering
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_Slices2.eps}
+    \vspace{1ex}
+  \end{minipage}
+  }
+  %\vspace{-3ex}
+  \caption{Area comparisons of different binary adder implementations.}
+  \label{Fig:AdderArea}
+  %\vspace{-2ex}
+\end{figure}
 
@@
 \subsection{Performance Analysis}
+In the experiments we compare 3 types of binary multipliers with different word-lengths.
+One is created from the Xilinx Core Generator [xxx] with standard arithmetic, and it is configured with speed optimization.
+The other two multipliers are with online arithmetic, but the results are generated with full precision and half precision, respectively.
+
+We first compare the maximum frequencies of the multipliers for a variety of operand word-lengths.
+Similar to the experiments in Section xxx, we record both the frequencies from the Xilinx Timing Analyzer and the maximum error-free frequencies acquired through tests, in which the input patterns are sampled from the UI data.
+The results are presented in Fig.xxx.
+
+The comparison of area in terms of the number of LUTs and Slices with respect to different operand word-lengths are illustrated in Fig.xxx and Fig.xxx, respectively.
+
+Although our proposed new online multiplier demonstrates a better operating frequency in the practice, we can push this one step further by operating the circuits beyond their deterministic region and allowing timing violations to happen.
+In this case, we examine the overclocking behaviour of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (xxx).
+For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.
 

### 2014-05-18 FPT2014/bare_conf.tex
Add draft abstract

@@
 
-%\usepackage{cite}
+\usepackage{cite}
 
@@
 \usepackage{multirow}
+
+\usepackage{courier}	%use courier font, activate using \texttt{}
 
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Efficient FPGA Implementation of\\ Overclocking Friendly Online Arithmetic Operators}
+\title{Efficient FPGA Implementation of\\ Digit Parallel Online Arithmetic Operators}
 
@@
 %\boldmath
-The abstract goes here.
+Online arithmetic was designed for most significant digits first computing.
+It has been widely utilized for ASIC implementations with significant performance improvements.
+In addition, recent research has shown that digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to the operators with conventional arithmetic.
+Unfortunately, the utilization of online arithmetic operators requires large area overhead, and the efficient implementation of general purpose online operators on FPGAs remains under investigation.
+In this paper, we propose novel approaches to implement the online adder and the online multiplier efficiently on current FPGAs with 6-input LUTs.
+The FPGA carry resources are intensively used for both area reduction and performance improvements.
+The performance of the proposed architectures are experimentally demonstrated
+
+%, they are targeting on FPGAs with 4-input LUTs, which are now gradually replaced by 6-input LUTs.
+
 \end{abstract}
@@
 % creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
+%\IEEEpeerreviewmaketitle
 
@@
 To tackle this problem, we first modify the structure of the online adder to enable an efficient FPGA mapping.
-The structure of a 3-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
+The structure of a 4-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
 In this equivalent structure, the first FA in each 4:2 compressor is split into 2 parts, which only generate carry and sum respectively.
@@
 
-\begin{figure}[tbp]
+\begin{figure*}[tbp]
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FPGA_New.pdf}
+	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit.pdf}
 	\caption{Modified structure of online adder.
-Left: an example of 3-digit online adder.
+Left: an example of 4-digit online adder.
 The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 slice.
@@
 	\label{Fig:ModifiedOA}
-\end{figure}
+\end{figure*}
 
@@
 \begin{eqnarray}\label{Eq:OAareaLUT}
-	Area\_LUT = 2N
+	OAarea\_LUT = 2N
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Eq:OAareaSlice}
-	Area\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
+	OAarea\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
 \end{eqnarray}
@@
 \subsection{Performance Analysis}
-In our experiments we compare 3 types of adders using Virtex-6 FPGAs: ripple carry adder (RCA), online adder which is implemented using behavioural description based on 4:2 compressors (OA\_behv) and online adder which is built using our proposed approach (OA\_real).
-Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "Carry4" is used to create OA\_real.
+In our experiments we compare 3 types of adders using Virtex-6 FPGAs: ripple carry adder (\texttt{RCA}), online adder which is implemented using behavioural description based on 4:2 compressors (\texttt{OA\_behv}) and online adder which is built using our proposed approach (\texttt{OA\_new}).
+Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "\texttt{Carry4}" is used to create \texttt{OA\_new}.
 
@@
 The frequency values are obtained through Xilinx Timing Analyzer after placing and routing in ISE 14.1.
-It can be seen that our approach outperforms RCA when $N>8$, and that our approach is always faster than the online adder based on 4:2 compressors.
-Also we can see that the frequency of RCA decreases drastically with respect to the increment of the operand word-length, whereas the online adder maintains a relatively high frequency even for large designs.
+It can be seen that our approach outperforms \texttt{RCA} when $N>8$, and that our approach is always faster than the online adder based on 4:2 compressors.
+Also we can see that the frequency of \texttt{RCA} decreases drastically with respect to the increment of the operand word-length, whereas the online adder maintains a relatively high frequency even for large designs.
 This is because the critical path of the online adder is irrelevant to the operand word-lengths.
@@
 The area comparisons are demonstrated in Fig.\ref{Fig:AdderArea}.
-The theoretical area of the online adder (OA\_theory) based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also included.
-It can be seen that OA\_behv is not area efficient for FPGAs, as the dedicated FPGA resources are not fully utilized.
+The theoretical area of the online adder (\texttt{OA\_theory}) based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also included.
+It can be seen that \texttt{OA\_behv} is not area efficient for FPGAs, as the dedicated FPGA resources are not fully utilized.
 In comparison, our implementation achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
-The area overhead of our approach against RCA is $1.80\times\sim1.98\times$
+The area overhead of our approach against \texttt{RCA} is $1.80\times\sim1.98\times$
 in LUTs and $1.00\times\sim1.88\times$ in Slices. However this is close to the theoretical minimum area overhead for online adders.
@@
   \centering
-  \subfigure[LUTs]{
+  \subfigure[Usage of LUTs.]{
   \begin{minipage}{0.45\textwidth}
@@
   }
-  \subfigure[Slices]{
+  \subfigure[Usage of Slices]{
   \begin{minipage}{0.45\textwidth}
@@
 
-However, in order to implement the digit parallel online multiplier (OM), large area budget is required because of the large area overhead of a single iteration stage and the overall stage numbers required.
-For instance in an $N$-digit OM, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, and $(N+\delta)$ iterations for the most significant $N$ digits result.
+However, in order to implement the digit parallel online multiplier (\texttt{OM}), large area budget is required because of the large area overhead of a single iteration stage and the overall stage numbers required.
+For instance in an $N$-digit \texttt{OM}, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, and $(N+\delta)$ iterations for the most significant $N$ digits result.
 Each iteration stage consists of all operations in Eq.xxx.
@@
 \subsection{FPGA Implementation}
-The structure diagram of a 4-digit OM using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a).
-Generally in an $N$-digit OM, there are only $N$ stages to generate results with $2N$ digits.
+The structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a).
+Generally in an $N$-digit \texttt{OM}, there are only $N$ stages to generate results with $2N$ digits.
 Each stage can be efficiently implemented using FPGAs, and the structure diagram of stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b).
@@
 
+Notice that the blocks that generate partial products $Xy_j$ can be incorporated into the online adder for further area reduction.
+In the online adder as seen in Fig.~\ref{Fig:SliceNew}, maximally only 4 inputs per LUT are used.
+This leaves 2 available inputs per LUT.
+However in order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
+Therefore instead of using extra logic to generate $Xy_j$, it can be incorported into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.pdf}
+	\caption{An example of achieving area reduction by combining the logic blocks that generate partial products into the Online Adder by fully utilizing the 6-LUTs.}
+	\label{Fig:PartialProduct}
+\end{figure}
+
+The theoretical minimum resource usages of the proposed \texttt{OM} can be calculated as follows.
+In an $N$-digit \texttt{OM}, overall $N-1$ online adders are needed.
+According to Algorithm xxx, the word-length of each online adder is $N+2$-digit (2 integer digits and $N$ fractional digits).
+Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of Slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
+Note that $L_{S1}$ and $S_{S1}$ denote the LUT and Slice usages of Stage 1, which is purely built with combinational logic without online adders.
+
+\begin{eqnarray}\label{Eq:OMareaLUT}
+	OMarea\_{LUT} = 2(N+2)(N-1) + {L}_{S1}
+\end{eqnarray}
+
+\begin{eqnarray}\label{Eq:OMareaSlice}
+	OMarea\_{Slice} = (1+\left\lceil{\frac{N}{2}}\right\rceil)(N-1)+S_{S1}
+\end{eqnarray}
+
 \subsection{Structure Optimization for the MSD Half of the Results}
 
-Normally the OM is connected with other arithmetic operators in real applications.
-If the outputs of an OM is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs.
+Normally the \texttt{OM} is connected with other arithmetic operators in real applications.
+If the outputs of an \texttt{OM} is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs.
 In the conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
@@
 \subsection{Performance Analysis}
-In the experiments we compare 3 types of binary multipliers with different word-lengths.
-One is created from the Xilinx Core Generator [xxx] with standard arithmetic, and it is configured with speed optimization.
-The other two multipliers are with online arithmetic, but the results are generated with full precision and half precision, respectively.
+In the experiments we compare 3 types of binary multipliers.
+One is created from the Xilinx Core Generator [xxx] with standard arithmetic.
+The \texttt{CoreGen} multiplier is implemented based on LUTs, and it is configured with speed optimization.
+The other two multipliers are both built with online arithmetic, except that the products are generated with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
 
@@
 
-The comparison of area in terms of the number of LUTs and Slices with respect to different operand word-lengths are illustrated in Fig.xxx and Fig.xxx, respectively.
+The comparison of area in terms of the number of LUTs and Slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
+It can be seen that the area of \texttt{OM\_full} is close to the theoretical values predicted by (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}).
+In comparison to the \texttt{CoreGen} multiplier, the area overheads of \texttt{OM\_full} are $48\%\sim84\%$ for LUTs, and $0\%\sim83\%$ for Slices.
+On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared to the \texttt{CoreGen} multiplier.
+The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim55\%$ for Slices.
+
+\begin{figure}[tbp]
+  %\vspace{-2.5ex}
+  \centering
+  \subfigure[Usage of LUTs.]{
+  \begin{minipage}{0.45\textwidth}
+    %\centering
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTs.eps}
+    \vspace{1ex}
+  \end{minipage}%
+  }
+  \subfigure[Usage of Slices]{
+  \begin{minipage}{0.45\textwidth}
+    %\centering
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slice.eps}
+    \vspace{1ex}
+  \end{minipage}
+  }
+  %\vspace{-3ex}
+  \caption{Area comparisons of different binary multipliers.}
+  \label{Fig:OMArea}
+  %\vspace{-2ex}
+\end{figure}
 
 Although our proposed new online multiplier demonstrates a better operating frequency in the practice, we can push this one step further by operating the circuits beyond their deterministic region and allowing timing violations to happen.
-In this case, we examine the overclocking behaviour of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (xxx).
-For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.
+In this case, we examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (xxx).
+For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.\cite{Ercegovac_DSPOnline}
 
-\section{Results}
+%\section{Results}
 
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
 %
@@
 
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
-
 \section{Conclusion}
@@
 \bibliographystyle{./IEEEtran}
-\bibliography{./IEEEabrv,./Reference.bib}
+
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+
+\bibliography{./IEEEabrv,./Reference}
 

### 2014-05-19 FPT2014/bare_conf.tex
add introduction draft

@@
 % author names and affiliations
-\author{Authors removed for blind review}
+\author{Authors removed for blind review\\ \\ \\}
 %\author{\IEEEauthorblockN{Kan Shi, David Boland, and George A. Constantinides}
@@
 %\boldmath
-Online arithmetic was designed for most significant digits first computing.
-It has been widely utilized for ASIC implementations with significant performance improvements.
-In addition, recent research has shown that digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to the operators with conventional arithmetic.
+Online arithmetic has been widely utilized for ASIC implementations with significant performance improvements, as it is designed to perform computations from the most significant digits.
+Recent research also shows that the digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to the operators with conventional arithmetic.
 Unfortunately, the utilization of online arithmetic operators requires large area overhead, and the efficient implementation of general purpose online operators on FPGAs remains under investigation.
@@
 
-\section{Introduction}
+\section{Introduction}\label{Sec:Intro}
+In the conventional form of computer arithmetic, the computation results are generated either from the least significant digit (LSD), e.g.
+addition and multiplication, or from the most significant digit (MSD), e.g.
+division and square root.
+This inconsistency in computing directions will potentially result in large latency when propagating data among different operations.
+Online arithmetic was designed to solve this problem \cite{Ercegovac_OnlineOverview,Ercegovac_Book}.
+With online arithmetic, both inputs and outputs are processed in a MSD-first manner.
+This enables parallelism and duplication among various operations, and the overall computation latency can be significantly reduced [xxx].
+A brief overview of online arithmetic is given in Section~\ref{Sec:Background}.
 
-\section{Background: Online Arithmetic}
+Recent research has demonstrated another key advantage of online arithmetic that it allows gracefully degradation when operating beyond the deterministic region, e.g.
+under overclocking.
+This stream of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
+However, traditional form of computer arithmetic does not fail gracefully when timing violation happens, because timing errors initially affect MSDs of the results.
+In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occurs at LSDs of the results.
+Despite its attractiveness, the usage of online arithmetic on existing FPGAs is still limited due to the huge area overhead.
+
+Generally, it is difficult to efficiently map the arithmetic circuits solely onto the look-up-tables (LUTs), which are fundamental building blocks of FPGAs.
+Lots of efforts has been done to alleviate this concern.
+For instance, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce the carry propagation delay by over one order of magnitude~\cite{Virtex6}.
+There is a large amount of studies exploring methods that can effectively map circuits using the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or propose alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2} .
+Besides, hard DSP blocks are also included to boost multiplications and multiply-accumulations [xxx].
+However, most of these approaches are designed to accelerate computations with the conventional arithmetic.
+
+For online arithmetic, we notice from existing literatures that there are 2 directions that are worth investigating.
+First, although there has been previous research about FPGA implementations of online arithmetic, they typically only focus on online adders.
+A brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
+However, the implementation of other key arithmetic primitives, such as online multipliers, are lack of exploration.
+Second, we found that existing approaches of building general purpose online adders are specifically for FPGAs with 4-input LUTs, and 2 LUTs within a Slice.
+However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many current FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+
+In this paper, both issues are addressed.
+In Section~\ref{Sec:OA_FPGA}, we propose a novel approach of mapping the digit parallel online adder onto FPGA with 6-LUTs.
+The mapping is based on the fast carry logic, and the available resources within a slice can be fully utilized.
+In addition, in Section~\ref{Sec:OM_FPGA} we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
+The theoretical resource usage of both operators is given, and it is verified experimentally on Xilinx Virtex-6 FPGAs.
+We demonstrate that the proposed designs achieves significant area reduction and performance gain over their original implementations.
+
+The main contributions of this paper are as follows:
+\begin{enumerate}
+    \item An efficient approach of mapping online adders onto modern FPGAs;
+    \item Area efficient implementation of digit parallel online multiplication algorithm on FPGAs;
+\end{enumerate}
+
+%The theoretical area overhead of an online adder is given in terms of the usage of LUTs and Slices.
+
+\section{Background: Online Arithmetic}\label{Sec:Background}
 \subsection{Key Features of Online Arithmetic}
-In conventional arithmetic, results are generated either from the least significant digit, e.g.
-addition and multiplication, or from the most significant digit, e.g.
-division and square root.
-This inconsistency in computing directions can result in large latency when propagating data among different operations.
-Online arithmetic was proposed to solve this problem [xxx].
-With online arithmetic, both the inputs and the outputs are processed in a MSD-first manner.
-This enables parallelism and duplication among various operations, and the overall computation latency can be significantly reduced.
 
+Online arithmetic has been widely used in numerous applications such as xxx [xxx].
 Online arithmetic was originally designed for digit-serial operation, of which the data flow is illustrated in Fig~\ref{Fig:OnlineDataFlow}.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
   \centering
@@
   %\vspace{-3ex}
-  \caption{Dataflow in digit-serial Online Arithmetic. $\delta$ denotes the online delay.}
+  \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
   %\vspace{-.5ex}
@@
 
-MSD-first operation is possible with the employment of the redundant number system \cite{RedundantNumber}, in which each digit is represented with a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
-Due to the redundancy, the MSDs of the result can be calculated only based on partial information of the inputs and then the value of the number can be revised by the following digits.
+MSD-first operation is possible with the employment of the redundant number system .
+Normally there are 2 most commonly used redundant number representation: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}.
+For instance with SD representation, each digit is represented with a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
+In comparison, the standard non-redundant representation only uses a digit set $\{0,r-1\}$.
+Thus a standard number corresponds to several possible redundant representations.
+For example, the two's complement number $0.111$ can be represented in the online form as $0.10\overline{1}$, $0.0\overline{1}1$ and $0.111$ among many other possible representations.
+
+Due to the redundancy, the MSDs of the result can be calculated only based on partial information of the inputs, which is required by digit-serial online arithmetic.
+Then the value of the number can be revised by the following digits, because each number embodies multiple representations.
 
@@
 To perform digit-parallel online addition, a redundant adder can be directly utilized.
-The adder structure diagram is shown in Fig~\ref{Fig:Radix2SD_adder}.
-A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As seen in Figure~\ref{Fig:Radix2SD_adder}, the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+The adder structure diagram is shown in Fig.~\ref{Fig:Radix2SD_adder}.
+An major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
+As seen in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
 This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
@@
 	\includegraphics[width=.5\textwidth]{./Figures/SDAdder.pdf}
-%\vspace{-8.5ex}
-	\caption{An $N$-digit binary digit-parallel online adder with $(N+1)$-digit outputs.}
+    \vspace{-5ex}
+	\caption{An $N$-digit binary digit-parallel online adder with $(N+1)$-digit outputs. Both inputs and outputs are represented using SD representation.}
+    \vspace{2ex}
 	\label{Fig:Radix2SD_adder}
@@
 
-In Section~\ref{Sec:OA_FPGA}, we will present a novel method of mapping the digit parallel online adder efficiently on FPGAs using the built-in carry resources.
+(truncate precision)
+
+%In Section~\ref{Sec:OA_FPGA}, we will present a novel method of mapping the digit parallel online adder efficiently on FPGAs using the built-in carry resources.
 
@@
   \label{Algorithm:OnlineMult}
-  \vspace{-2ex}
+  %\vspace{-2ex}
   \end{algorithmic}
@@
 \subsection{Related Works}
-There has been previous works focusing on efficient FPGA implementation of the digit-parallel online adder.
-Generally the existing approaches can be classified into three types:%, as discussed below.
-A more detailed review of current works can be found in xxx.
+There has been previous works about FPGA implementation of digit parallel online adders. From the literature, the existing approaches can be classified into three types:
+
 \begin{enumerate}
-	\item efficient mapping of the digit-parallel online adder onto sophisticated FPGAs resources [xxx];
-	\item multiple operands addition by designing compressor trees based on bit counters [xxx];
-	\item modifying existing FPGA architecture for more efficient online addition [xxx] and for specific applications [xxx].
+    \item efficient mapping of the digit-parallel online adder onto sophisticated FPGAs resources \cite{FPT09RA,ASAP09RA};
+    \item multiple operands addition by designing compressor trees based on bit counters \cite{TC13RA,ASPDAC10RA_FPGA};
+    \item modifying existing FPGA architecture for more efficient digit-parallel online addition \cite{DAC07_CounterTree} and for specific applications \cite{FPL09_onlineCCM}.
 \end{enumerate}
 
-Type 2 and type 3 are beyond the scope of this paper, as we focus on the general purpose online adder that takes 2 inputs and generate 1 outputs, as shown in Figure xxx.
+Type 2 and type 3 are beyond the scope of this paper, as our interests are in the field of two-operand online addition that performs $Z=X+Y$, as shown in Fig.~\ref{Fig:Radix2SD_adder}, and we are using the main-stream FPGAs for implementation.
+
 Specifically in type 1, both works took advantage of the built-in carry resources in FPGAs.
-Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as shown within the gray background in Figure xxx.
+Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as shown within the gray background in Fig.~\ref{Fig:PreviousWork}.
 However, directly applying this approach in the FPGAs could be less efficient.
@@
 This is naturally reasonable because one LB can be mapped to a single slice.
-Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in [xxx] will result in either resource waste or logic fault.
-For instance, if 2 LBs are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}s, the outputs of the second LB will be faulty because the its carry input cannot be explicitly initialized.
+Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in \cite{FPT09RA} or \cite{ASAP09RA} will result in either resource waste or logic fault.
+For instance, if two logic blocks are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 	\centering
 	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork.pdf}
-	\caption{Direct utilization of previous approaches on a Virtex-6 FPGA will results in faulty outputs.}
+	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
 	\label{Fig:PreWorkVirtex6}
@@
 In the experiments we compare 3 types of binary multipliers.
-One is created from the Xilinx Core Generator [xxx] with standard arithmetic.
-The \texttt{CoreGen} multiplier is implemented based on LUTs, and it is configured with speed optimization.
+One is created from the Xilinx Core Generator with standard arithmetic.
+The \texttt{CoreGen} multiplier is implemented based on LUTs, and it is configured with speed optimization \cite{XilinxMult} .
 The other two multipliers are both built with online arithmetic, except that the products are generated with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.

### 2014-05-19 FPT2014/bare_conf.tex
add more stuff

@@
 \usepackage{algorithm}
-\usepackage{algorithmic}
+%\usepackage{algorithmic}
+\usepackage{algpseudocode}
 \usepackage{indentfirst}
-\renewcommand{\algorithmicrequire}{ \textbf{Initialization:}}
-\renewcommand{\algorithmicensure}{ \textbf{Recurrence:}}
+%\renewcommand{\algorithmicrequire}{ \textbf{Initialization:}}
+%\renewcommand{\algorithmicensure}{ \textbf{Recurrence:}}
 
@@
 Unfortunately, the utilization of online arithmetic operators requires large area overhead, and the efficient implementation of general purpose online operators on FPGAs remains under investigation.
-In this paper, we propose novel approaches to implement the online adder and the online multiplier efficiently on current FPGAs with 6-input LUTs.
-The FPGA carry resources are intensively used for both area reduction and performance improvements.
-The performance of the proposed architectures are experimentally demonstrated
+In this paper, we propose novel approaches to implement the online operators such as adder and multiplier efficiently on current FPGAs with 6-input LUTs.
+The FPGA carry resources are used for both area reduction and performance improvements.
+We demonstrate experimentally that the proposed architectures achieve significant area savings and frequency speed-ups comparing to the original implementations.
+
+%The performance of the proposed architectures are experimentally demonstrated
 
@@
 To perform digit-parallel online addition, a redundant adder can be directly utilized.
-The adder structure diagram is shown in Fig.~\ref{Fig:Radix2SD_adder}.
+The structure diagram of an online adder with all signals represented with SD numbers is shown in Fig.~\ref{Fig:Radix2SD_adder}.
 An major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As seen in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
 This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
@@
 
-(truncate precision)
-
 %In Section~\ref{Sec:OA_FPGA}, we will present a novel method of mapping the digit parallel online adder efficiently on FPGAs using the built-in carry resources.
@@
 Typically the online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit number as given in~(\ref{Eq:Online_Operands}).
-For a given iteration $j$, the product digit $z_j$ is generated through a selection function $sel()$.
+For a given iteration $j$, the product digit $z_j$ is generated with MSD-first through a selection function $sel()$.
 For the radix $r$ and a chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
@@
 \begin{algorithm}[tbp]
-  \caption{Online Multiplication}
+  \caption{Online Multiplication}  \label{Algorithm:OnlineMult}
   \begin{algorithmic}[1]
-    \REQUIRE~$X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$
-    \ENSURE~$for~~ j=-\delta,~-\delta+1,~\cdots,~N-1 ~~do$
-      \begin{eqnarray}\label{Eq:OnlineMult_General}
-        \begin{matrix}
-          H_{[j]}   & = & r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)\\
-          W_{[j]}   & = & P_{[j]} + H_{[j]}\\
-          z_j       & = & sel(W_{[j]})\\
-          P_{[j+1]} & = & r\left(W_{[j]}-z_j\right)
-        \end{matrix}
-      \end{eqnarray}
-  \label{Algorithm:OnlineMult}
-  %\vspace{-2ex}
+   \State \textbf{Initialization:}~$X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$\vspace{.5ex}
+    \For{$j=-\delta,~-\delta+1,~\cdots,~2N-1$}\vspace{.5ex}
+        \State $H_{[j]} \leftarrow r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)$\vspace{.5ex}
+        \State $W_{[j]} \leftarrow P_{[j]} + H_{[j]}$\vspace{.5ex}
+        \State $Z_{[j]}~ \leftarrow sel(W_{[j]})$\vspace{.5ex}
+        \State $P_{[j+1]} \leftarrow r\left(W_{[j]}-Z_{[j]}\right)$\vspace{.5ex}
+    \EndFor
   \end{algorithmic}
@@
 
-In Section~\ref{Sec:OM_FPGA}, we will describe a modified online multiplication algorithm and its FPGA implementation, which are designed specifically targeting on digit parallel operations.
+It is worth noting that the precision of the product $Z$ can be determined by directly truncating from the LSDs, as there is no carry propagations from the LSD to the MSD.
+This is useful especially when the multiplication product is used by successive computations, where only the first $N$ digits of the results are normally used.
+In comparison, the product is generated starting from the LSD with conventional arithmetic.
+Hence the successive operations cannot commence until the full-precision result is generated.
+This feature of online arithmetic has inspired research about dynamically control of computation precision in numerous applications.
+
+%Since there is no carry chain propagating from the LSD to the MSD, the precision of the results can be selected by directly truncating from the LSDs.
+
+In Section~\ref{Sec:OM_FPGA}, we will first describe an optimized online multiplication algorithm and its FPGA implementation, which are designed specifically targeting on digit parallel operations.
+Then we provide a modified structure which only generates the most significant half the products, in order to achieve extra area savings.
 
@@
 \subsection{Performance Analysis}
-In our experiments we compare 3 types of adders using Virtex-6 FPGAs: ripple carry adder (\texttt{RCA}), online adder which is implemented using behavioural description based on 4:2 compressors (\texttt{OA\_behv}) and online adder which is built using our proposed approach (\texttt{OA\_new}).
+In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using behavioural descriptions based on 4:2 compressors (\texttt{OA\_behv}).
 Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "\texttt{Carry4}" is used to create \texttt{OA\_new}.
+In addition, we also include ripple carry adder (\texttt{RCA}) which uses conventional arithmetic, into the comparisons.
+All designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1.
 
-The rated frequencies of all designs for a variety of operand word-lengths are shown in Fig.~\ref{Fig:AdderFreq}.
-The frequency values are obtained through Xilinx Timing Analyzer after placing and routing in ISE 14.1.
-It can be seen that our approach outperforms \texttt{RCA} when $N>8$, and that our approach is always faster than the online adder based on 4:2 compressors.
-Also we can see that the frequency of \texttt{RCA} decreases drastically with respect to the increment of the operand word-length, whereas the online adder maintains a relatively high frequency even for large designs.
-This is because the critical path of the online adder is irrelevant to the operand word-lengths.
+We record the rated frequencies of all designs when varying the operand word-lengths.
+The results are shown in Fig.~\ref{Fig:AdderFreq}.
+The frequency values are obtained through Xilinx Timing Analyzer after placing and routing the designs in ISE 14.1.
+It can be seen that both designs with online arithmetic achieves relatively stable operating frequencies across a variety of operand word-lengths.
+This is as expected, because the critical path delay in the online adder is ideally a fixed value and it is irrelevant to the operand precisions.
+In comparison, the rated frequency of \texttt{RCA} drops drastically for larger designs.
+In this case, both online adders will eventually outperform \texttt{RCA}.
+However our approach operates constantly faster than \texttt{OA\_behv} for any operand word-length.
+The speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $20\%$ to $26\%$.
 
@@
 
-The area comparisons are demonstrated in Fig.\ref{Fig:AdderArea}.
-The theoretical area of the online adder (\texttt{OA\_theory}) based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also included.
-It can be seen that \texttt{OA\_behv} is not area efficient for FPGAs, as the dedicated FPGA resources are not fully utilized.
-In comparison, our implementation achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
-The area overhead of our approach against \texttt{RCA} is $1.80\times\sim1.98\times$
-in LUTs and $1.00\times\sim1.88\times$ in Slices. However this is close to the theoretical minimum area overhead for online adders.
+We compare the resource usages of all three adder designs with respect to a variety of operand word-lengths.
+The results are shown in Fig.\ref{Fig:AdderArea}.
+The theoretical area budgets of the online adder predicted by (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also plotted with dotted lines in Fig.\ref{Fig:AdderArea}.
+Several observations can be made from the results.
+Firstly the predicted resource usages of both LUTs and Slices match well the results obtained from real implementations.
+Secondly it can be seen that the behavioural implementation \texttt{OA\_behv} is not area efficient for FPGAs, because the dedicated FPGA resources are not fully utilized.
+In comparison, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
+Thirdly, our design still costs more area than \texttt{RCA}, with the area overhead of $80\%\sim98\%$ in terms of LUTs, and $0\%\sim88\%$ in terms of Slices.
+This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
+However research has shown that this overhead can be reduced for multiple-operand adders or adder trees [xxx].
 
@@
   \centering
-  \subfigure[Usage of LUTs.]{
+  \subfigure[]{
   \begin{minipage}{0.45\textwidth}
@@
   }
-  \subfigure[Usage of Slices]{
+  \subfigure[]{
   \begin{minipage}{0.45\textwidth}
@@
   %\vspace{-3ex}
-  \caption{Area comparisons of different binary adder implementations.}
+  \caption{Area comparisons of different binary adder implementations with respect to a variety of operand word-lengths. (a) Usage of LUTs. (b) Usage of Slices.}
   \label{Fig:AdderArea}
@@
 \subsection{Algorithm of Digit Parallel Online Multiplication}
-Algorithm xxx as described in Section.xxx can be synthesized into a unrolled digit parallel structure, which has been demonstrated to be ``overclocking friendly'' because timing errors initially affect the least significant digits [xxx].
-This synthesis method is straightforward and can be utilized to design other digit parallel online operators.
+Algorithm \ref{Algorithm:OnlineMult} as described in Section~\ref{Sec:Background} can be synthesized into a unrolled digit parallel structure.
+Recent study has shown that the digit-parallel online multiplier is more tolerant to timing violations in comparison to conventional arithmetic, because timing errors initially affect the least significant digits and this will lead to small error magnitude[xxx].
+This implementation method is straightforward and can be utilized to design other digit parallel online operators.
 
-However, in order to implement the digit parallel online multiplier (\texttt{OM}), large area budget is required because of the large area overhead of a single iteration stage and the overall stage numbers required.
+On the other hand, significant area budget is required in order to implement this type of digit parallel online multiplier (\texttt{OM}).
+Typically this is due to three main reasons.
+First, in comparison to the conventional multiplier, more iteration stages are needed.
 For instance in an $N$-digit \texttt{OM}, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, and $(N+\delta)$ iterations for the most significant $N$ digits result.
-Each iteration stage consists of all operations in Eq.xxx.
-In comparison, in an $N$-digit array multiplier there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
+Second, in each stage the logic is complex as it involves operations such as online addition, digit-vector multiplication, shifting and other combination logic such as the selection function.
+Besides, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $N+2+\delta$, because the selection function needs 2 integer digits as well as 1 fraction digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
+Whereas in an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
+Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
 
-Instead of simply implementing the unrolled format of Algorithm xxx, it can be optimized given that all inputs are digit parallel.
-Initially the online delay $\delta$ is employed to generate the MSD of the results only based on partial information of the inputs.
+We address the first 2 design issues by providing an alternative online multiplication algorithm.
+Instead of simply implementing the unrolled format of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
+We notice that the online delay $\delta$ is employed in this algorithm because the input data are available in a digit serial fashion.
+Hence $\delta$ is used to accumulate enough input digits to generate the MSD of the result.
 Nevertheless if all digits of inputs are given simultaneously, $\delta$ is no longer necessary.
-Due to the same reason, $H[j]$, which takes 1 digit of input per stage as shown in Algorithm xxx, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
-The optimized digit parallel online multiplication algorithm is described in Algorithm xxx.
+Due to the same reason, $H[j]$, which takes one digit of each input per stage as shown in the original algorithm, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
+To summarize, the modified algorithm for digit parallel online multiplication is described in Algorithm~\ref{Algorithm:OM_DigitParallel}, where $N$ denotes the operand word-length, function $frac(W_{[N]})$ refers to select the fractional digits of $W_{[N]}$, and the selection function $sel()$ is given previously in (\ref{Eq:SelFunc_OM}).
+
+\begin{algorithm}[tbp]
+  \caption{Digit Parallel Online Multiplication}\label{Algorithm:OM_DigitParallel}
+  \begin{algorithmic}[1]
+    \State \textbf{Initialization:} $P_{[0]}=0$						\vspace{.5ex}
+    \For{$j=1,~2,~\cdots,~N$}										\vspace{.5ex}
+    	\State $Xy_j \leftarrow X \cdot y_j$						\vspace{.5ex}
+    	\State $W_{[j]}    \leftarrow  P_{[j-1]} + Xy_j$			\vspace{.5ex}
+     	\State $Z_{[j]}  ~      \leftarrow  sel(W_{[j]})$			\vspace{.5ex}
+	 	\State $P_{[j+1]}  \leftarrow  r\left(W_{[j]}-Z_{[j]}\right)$	\vspace{.5ex}
+    \EndFor															\vspace{.5ex}
+    \State $Z_{[N+1:2N]} \leftarrow frac(W_{[N]})$
+  \end{algorithmic}
+\end{algorithm}
+
+In comparison to the original online multiplication algorithm, the maximum stages required to generate results with full precision drops by a factor of 2 using the proposed new algorithm.
+In each stage, the word-length of all signals also reduces from $N+2+\delta$ to $N+2$, as $\delta$ is not necessary for digit parallel operations.
+In addition, the $frac()$ function can be implemented only based on wire connection without using other logic resources.
 
 \subsection{FPGA Implementation}
-The structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a).
-Generally in an $N$-digit \texttt{OM}, there are only $N$ stages to generate results with $2N$ digits.
-Each stage can be efficiently implemented using FPGAs, and the structure diagram of stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b).
-In each stage, an online adder is used to derive $W_{[j]}$.
-The selection logic, as described in Section xxx and Eq.xxx, takes 3 digits input (6 bits) and generate 1 digit output (2 bits).
+We also explore an area efficient implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} on FPGAs.
+The general structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a), and the structure diagram of stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b) with the word-lengths of all signals labelled.
+Area optimizations can be performed on all modules.
+It can be seen that in each stage, an $N+2$-digit online adder is used to derive $W_{[j]}$.
+Our proposed online adder architecture can be employed.
+The selection logic takes 3 digits input (6 bits) and generate 1 digit output (2 bits).
 Hence it can be implemented using two 6-LUTs for each output bit.
-Similarly the generation of $P_{[j]}$ can also be implemented using one 6-LUT, since only the integer parts of $W_{[j]}$ might change due to the selection of $z_j$.
+Similarly the generation of $P_{[j]}$ can also be implemented using one 6-LUT, since only the integer digits of $W_{[j]}$ need to be modified due to the selection of $Z_{[j]}$.
 In addition, the structure of Stage 1 can be further optimized by removing the online adder, because $P_{[0]}=0$.
@@
 The word-length of all signals are labelled in terms of the number of digits.
-$N$ denotes the word-length of the input signal.}
+$N$ denotes the word-length of the input signals.}
 	\label{Fig:PMStructure}
@@
 
-Notice that the blocks that generate partial products $Xy_j$ can be incorporated into the online adder for further area reduction.
-In the online adder as seen in Fig.~\ref{Fig:SliceNew}, maximally only 4 inputs per LUT are used.
+The blocks that generate partial products $Xy_j$ can be incorporated into the online adder with 6-LUT for further area reduction.
+In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, only 4 inputs per LUT are used to the maximum.
 This leaves 2 available inputs per LUT.
-However in order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
-Therefore instead of using extra logic to generate $Xy_j$, it can be incorported into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
+In order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
+Therefore instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
+Notice that this approach is only available for FPGAs with 6-LUTs.
 
@@
 	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.pdf}
-	\caption{An example of achieving area reduction by combining the logic blocks that generate partial products into the Online Adder by fully utilizing the 6-LUTs.}
+	\caption{Left: Direct implementation with extra logic to generate partial products.
+Right: Combining the logic blocks that generate partial products into the Online Adder by fully utilizing all the inputs of the 6-LUTs.
+In this case, further area reduction can be achieved.}
 	\label{Fig:PartialProduct}
@@
 In an $N$-digit \texttt{OM}, overall $N-1$ online adders are needed.
-According to Algorithm xxx, the word-length of each online adder is $N+2$-digit (2 integer digits and $N$ fractional digits).
+According to Algorithm~\ref{Algorithm:OM_DigitParallel}, the word-length of each online adder is $(N+2)$-digit (2 integer digits and $N$ fractional digits).
 Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of Slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
-Note that $L_{S1}$ and $S_{S1}$ denote the LUT and Slice usages of Stage 1, which is purely built with combinational logic without online adders.
+Note that $L_{S1}$ and $S_{S1}$ denote the LUT and Slice usages of the first stage, which is purely built with combinational logic without online adders.
 
@@
 \subsection{Structure Optimization for the MSD Half of the Results}
-
-Normally the \texttt{OM} is connected with other arithmetic operators in real applications.
-If the outputs of an \texttt{OM} is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs.
+As discussed before in Section~\ref{Sec:Background}, normally the multiplier is connected with other arithmetic operators in real applications.
+If the outputs of a multiplier is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs of the system.
 In the conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
@@
 
-In comparison, the online multiplier offers the possibility to optimize the structure to a further extent if only the MSD half of the results are required, as the results are generated initially from the MSD.
-The modified structure diagram is illustrated in Fig.~\ref{Fig:PMStructure_MSDhalf}(a).
-The word-length of the online adder in a given Stage $j$ can be reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
-This is because there is no carry propagation in the online adder, and all digits of the online adder are obtained in parallel.
+In comparison, the online multiplier offers the flexibility to simplify the structure correspondingly without affecting accuracy, if only the MSD half of the results are required.
+This is possible because in the \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD as described previously.
+This will potentially lead to a more area efficient design.
+For example, the modified structure diagram of a 4-digit \texttt{OM} is illustrated in Fig.~\ref{Fig:PMStructure_MSDhalf}(a).
+The word-length of all signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
+It can be seen that instead of keeping identical word-length throughout all stages, as shown in Fig.~\ref{Fig:PMStructure}, in the modified structure the signal word-lengths depend on the stage number $j$ and fewer bits of signals are needed for LSD stages.
 
@@
 	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
-	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result. }
+	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
+(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
 	\label{Fig:PMStructure_MSDhalf}
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTs.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTslog.eps}
     \vspace{1ex}
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slice.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slicelog.eps}
     \vspace{1ex}
@@
 In this case, we examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (xxx).
-For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.\cite{Ercegovac_DSPOnline}
+For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.
 
 %\section{Results}
-
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
 

### 2014-05-20 FPT2014/bare_conf.tex
Add experiments on Online Multipiers

@@
 
-\subsection{Performance Analysis}
+\subsection{Performance Analysis}\label{subsec:OA_Performance}
 In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using behavioural descriptions based on 4:2 compressors (\texttt{OA\_behv}).
@@
 \subsection{Performance Analysis}
-In the experiments we compare 3 types of binary multipliers.
-One is created from the Xilinx Core Generator with standard arithmetic.
-The \texttt{CoreGen} multiplier is implemented based on LUTs, and it is configured with speed optimization \cite{XilinxMult} .
-The other two multipliers are both built with online arithmetic, except that the products are generated with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
+Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier which is implemented to derive full precision results using behavioral descriptions (\texttt{OM\_initial}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
+In addition, we also incorporate multipliers with conventional binary arithmetic, and it is created using the Xilinx Core Generator.
+The \texttt{CoreGen} multiplier is implemented based on LUTs without DSPs, and it is configured with speed optimization \cite{XilinxMult}.
 
-We first compare the maximum frequencies of the multipliers for a variety of operand word-lengths.
-Similar to the experiments in Section xxx, we record both the frequencies from the Xilinx Timing Analyzer and the maximum error-free frequencies acquired through tests, in which the input patterns are sampled from the UI data.
-The results are presented in Fig.xxx.
+The comparison of area in terms of the cost of LUTs and the cost of Slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
+The results are obtained from ISE 14.1 after mapping the design to the Virtex-6 FPGA.
+The area predictions for \texttt{OM\_full} from (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}) are also included in both figures.
+Again we can see that the predicted resource usages match well with practical implementations.
+In comparison to \texttt{OM\_initial}, clearly significant area savings can be obtained by the optimized design \texttt{OM\_full}.
+Specifically, the LUTs usage and Slices usage drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
 
-The comparison of area in terms of the number of LUTs and Slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
-It can be seen that the area of \texttt{OM\_full} is close to the theoretical values predicted by (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}).
 In comparison to the \texttt{CoreGen} multiplier, the area overheads of \texttt{OM\_full} are $48\%\sim84\%$ for LUTs, and $0\%\sim83\%$ for Slices.
-On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared to the \texttt{CoreGen} multiplier.
+On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
 The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim55\%$ for Slices.
@@
   %\vspace{-3ex}
-  \caption{Area comparisons of different binary multipliers.}
+  \caption{Area comparisons of different types of binary multipliers. (a) Usage of LUTs. (b) Usage of Slices}
   \label{Fig:OMArea}
@@
 
-Although our proposed new online multiplier demonstrates a better operating frequency in the practice, we can push this one step further by operating the circuits beyond their deterministic region and allowing timing violations to happen.
-In this case, we examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (xxx).
-For instance, Fig.xxx demonstrates the MRE of the 8-digit multipliers.
+We also check the rated frequencies of \texttt{OM\_full}, \texttt{OM\_half} and \texttt{CoreGen} for a variety of operand word-lengths.
+The frequency values are still obtained from the Xilinx Timing Analyzer.
+The results are plotted in Fig.xxx, from which we can see that there is an increasing gap between the online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
+This might because in the online multiplier, although the carry resources in the FPGA are efficiently used, each 4-digit carry logic within a Slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
+Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is huge for large operand word-lengths.
+This also explains the fact that \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, as the critical path of both designs are similar.
+
+However, we can take advantage of the ``overclocking friendly'' feature of the online arithmetic, and push the previous tests one step further by operating the circuits beyond their deterministic region while allowing timing violations to happen.
+In this case, we can examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (\ref{Eq:MRE})), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of correct output, respectively.
+
+\begin{eqnarray}\label{Eq:MRE}
+  MRE=\frac{E_{error}}{E_{out}}\times100\%
+\end{eqnarray}
+
+For instance, Fig.~\ref{Fig:PM_MRE} demonstrates the MRE of the 8-digit multipliers.
+Notice that the input data to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
+We see that although the Timing Analyzer predicts slower frequencies for \texttt{OM}, it actually operates faster than \texttt{CoreGen} without the occurrence of timing errors.
+Besides,
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./Figures/Exp/MRE_PM.eps}
+  \caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
+(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
+  \label{Fig:PM_MRE}
+\end{figure}
 

### 2014-05-21 FPT2014/bare_conf.tex
Self check 2

@@
 Unfortunately, the utilization of online arithmetic operators requires large area overhead, and the efficient implementation of general purpose online operators on FPGAs remains under investigation.
-In this paper, we propose novel approaches to implement the online operators such as adder and multiplier efficiently on current FPGAs with 6-input LUTs.
+In this paper, we propose novel approaches to implement key primitives of online arithmetic, such as adders and multipliers, efficiently on modern FPGAs with 6-input LUTs.
 The FPGA carry resources are used for both area reduction and performance improvements.
@@
 With online arithmetic, both inputs and outputs are processed in a MSD-first manner.
-This enables parallelism and duplication among various operations, and the overall computation latency can be significantly reduced [xxx].
+This enables parallelism and duplication among multiple operations, and the overall computation latency can be significantly reduced.
 A brief overview of online arithmetic is given in Section~\ref{Sec:Background}.
@@
 Recent research has demonstrated another key advantage of online arithmetic that it allows gracefully degradation when operating beyond the deterministic region, e.g.
-under overclocking.
+under overclocking \cite{SKDAC14}.
 This stream of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
@@
 In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occurs at LSDs of the results.
+
 Despite its attractiveness, the usage of online arithmetic on existing FPGAs is still limited due to the huge area overhead.
-
 Generally, it is difficult to efficiently map the arithmetic circuits solely onto the look-up-tables (LUTs), which are fundamental building blocks of FPGAs.
@@
 There is a large amount of studies exploring methods that can effectively map circuits using the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or propose alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2} .
-Besides, hard DSP blocks are also included to boost multiplications and multiply-accumulations [xxx].
-However, most of these approaches are designed to accelerate computations with the conventional arithmetic.
+Besides, hard DSP blocks are also included to boost multiplications and multiply-accumulations~\cite{XilinxDSP}.
+However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.
 
@@
 However, the implementation of other key arithmetic primitives, such as online multipliers, are lack of exploration.
-Second, we found that existing approaches of building general purpose online adders are specifically for FPGAs with 4-input LUTs, and 2 LUTs within a Slice.
-However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many current FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+Second, we found that existing approaches of building general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan 3 series \cite{XilinxSpartan}.
+However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
 
-In this paper, both issues are addressed.
+In this paper, both issues will be addressed.
 In Section~\ref{Sec:OA_FPGA}, we propose a novel approach of mapping the digit parallel online adder onto FPGA with 6-LUTs.
 The mapping is based on the fast carry logic, and the available resources within a slice can be fully utilized.
-In addition, in Section~\ref{Sec:OM_FPGA} we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
-The theoretical resource usage of both operators is given, and it is verified experimentally on Xilinx Virtex-6 FPGAs.
-We demonstrate that the proposed designs achieves significant area reduction and performance gain over their original implementations.
-
-The main contributions of this paper are as follows:
+In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
+In addition, the theoretical resource usage of both operators is given, and they are verified experimentally on Xilinx Virtex-6 FPGAs.
+We demonstrate that the proposed designs achieve significant area reduction and performance gain over their original implementations.
+In summary, the main contributions of this paper are as follows:
 \begin{enumerate}
@@
     \item Area efficient implementation of digit parallel online multiplication algorithm on FPGAs;
+    \item Theoretical area models of the proposed architectures.
 \end{enumerate}
@@
 
-Online arithmetic has been widely used in numerous applications such as xxx [xxx].
+Online arithmetic has been widely used in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
 Online arithmetic was originally designed for digit-serial operation, of which the data flow is illustrated in Fig~\ref{Fig:OnlineDataFlow}.
 It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required and $\delta$ is called ``online delay''.
-Notice that $\delta$ is normally a constant, which is independent of the precision in a given operation.
+Notice that $\delta$ is normally a small constant, which is independent of the precision in a given operation.
 For ease of discussion, in the following of this paper the input data are normalized to fixed point numbers in the range $(-1,1)$.
 Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
-
+%
 \begin{figure}[tbp]
@@
 \end{figure}
-
+%
 \begin{eqnarray}\label{Eq:Online_Operands}
@@
 
-MSD-first operation is possible with the employment of the redundant number system .
+MSD-first operation is possible with the employment of the redundant number system.
 Normally there are 2 most commonly used redundant number representation: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}.
-For instance with SD representation, each digit is represented with a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
+For instance with SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
 In comparison, the standard non-redundant representation only uses a digit set $\{0,r-1\}$.
@@
 In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}) \cite{Oregon_OnlineNetwork}.
-Notice that the election is made only based on 1 integer bit and 1 fractional bit of $W_{[j]}$.
+Notice that the election is made only based on 2 integer digits and 1 fractional digit of $W_{[j]}$.
 
@@
 
-It is worth noting that the precision of the product $Z$ can be determined by directly truncating from the LSDs, as there is no carry propagations from the LSD to the MSD.
+It is worth noting that the precision of the product $Z$ can be determined by directly truncating from the LSDs, since there is no carry propagations from the LSD to the MSD.
 This is useful especially when the multiplication product is used by successive computations, where only the first $N$ digits of the results are normally used.
 In comparison, the product is generated starting from the LSD with conventional arithmetic.
-Hence the successive operations cannot commence until the full-precision result is generated.
-This feature of online arithmetic has inspired research about dynamically control of computation precision in numerous applications.
+Hence the successive operations cannot commence until the result with full-precision is generated.
+This feature of online arithmetic has inspired research about dynamically control of computation precision in numerous applications~\cite{Online_Truncation}.
 
@@
 Specifically in type 1, both works took advantage of the built-in carry resources in FPGAs.
-Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as shown within the gray background in Fig.~\ref{Fig:PreviousWork}.
+Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as outlined in Fig.~\ref{Fig:PreviousWork} within the gray background.
 However, directly applying this approach in the FPGAs could be less efficient.
-This is because there is no carry propagation between the 2 full adders within a 4:2 compressor, and the net delay between them can be large.
-Instead, Kamp et al and Ortiz et al described very similar mapping techniques for online adders with 2 different data representations, respectively.
-The main idea is to map the logic block within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
-In this case, the fast-carry logic in the FPGA can be employed, and the delay between the 2 FAs is largely reduced.
+This is because there is no carry propagation between the 2 FAs within a 4:2 compressor, and the net delay between them can be large.
+Instead, Kamp et al \cite{FPT09RA} and Hormigo et al \cite{ASAP09RA} described very similar mapping techniques for online adders with SD representations and CS representations, respectively.
+They share the common idea that maps the logic block (\texttt{LB}) within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
+In this case, the fast-carry logic in the FPGA can be employed, and the delay between the 2 FAs can be largely reduced.
 
@@
 The grey background highlights the 4:2 compressor.
-Dotted circle indicates the logic block (LB) which can be mapped to the FPGA carry resources.}
+Dotted circle indicates the logic block (LB) which can be mapped to the FPGA using the carry resources.}
 	\label{Fig:PreviousWork}
@@
 
-However, we notice the major limitations of both approaches that they only target on FPGAs with 4-input LUTs and 2 LUTs within a logic slice, such as the Xilinx Spartan series and the Altera Cyclone series.
-This is naturally reasonable because one LB can be mapped to a single slice.
-Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying the approaches in \cite{FPT09RA} or \cite{ASAP09RA} will result in either resource waste or logic fault.
-For instance, if two logic blocks are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
+However, we notice the major limitations of both approaches that they only target on FPGAs with 4-input LUTs (4-LUT) and 2 LUTs within a logic Slice, such as the Xilinx Spartan series and the Altera Cyclone series.
+This is naturally reasonable because one \texttt{LB} can be mapped to a single Slice.
+Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a Slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or logic fault.
+For instance, if two \texttt{LB}s are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
+Additionally, the output of \texttt{XORCY2} should not be used.
 
@@
 	\label{Fig:PreWorkVirtex6}
+    \vspace{-2ex}
 \end{figure}
@@
 \subsection{Proposed Mapping Method}
-To tackle this problem, we first modify the structure of the online adder to enable an efficient FPGA mapping.
+To tackle this problem, we firstly modify the structure of the online adder to enable an efficient FPGA mapping.
 The structure of a 4-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
@@
 Right: one LB.
-the dotted box outlines the logic that can be mapped onto 1 LUT and the corresponding fast-carry logic.}
+The dotted box outlines the logic that can be mapped onto 1 LUT and the corresponding fast-carry logic.}
 	\label{Fig:ModifiedOA}
@@
 
-The detailed slice mapping of the 2 LBs is shown in Fig.~\ref{Fig:SliceNew}.
+The detailed slice mapping of the 2 \texttt{LB}s and the logic in each LUT are shown in Fig.~\ref{Fig:SliceNew}.
 The I/O signals are identical to the previous example in Fig.~\ref{Fig:ModifiedOA}.
-It can be seen that a 6-LUT can be configured with two different output ports O6 and O5.
-For LB1, the carry input can be initialized by setting the O6 of LUT2 equal to 0 constantly.
-In this case, the output of MUXCY2 is O5 of LUT2, and the carry from LB2 will not affect the results of LB1.
-Using this mapping method the resources within 1 slice can be fully utilized, potentially leads to significant area reduction.
+Normally 6-LUT can be configured with two different output ports \texttt{O6} and \texttt{O5}.
+For \texttt{LB1}, the carry input can be initialized by setting the \texttt{O6} of LUT2 to 0 constantly.
+In this case, the output of \texttt{MUXCY2} is always \texttt{O5} of LUT2, and the carry from \texttt{LB2} will not affect the results of \texttt{LB1}.
+For those logics to generate the MSD and the LSD, they can be combined into 1 Slice as observed from Fig.~\ref{Fig:ModifiedOA}.
+Therefore using this mapping method the resources within 1 slice can be fully utilized, potentially leads to significant area reduction.
 
@@
 In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using behavioural descriptions based on 4:2 compressors (\texttt{OA\_behv}).
-Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "\texttt{Carry4}" is used to create \texttt{OA\_new}.
 In addition, we also include ripple carry adder (\texttt{RCA}) which uses conventional arithmetic, into the comparisons.
 All designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1.
+Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "\texttt{Carry4}" is used to create \texttt{OA\_new}.
 
@@
 It can be seen that both designs with online arithmetic achieves relatively stable operating frequencies across a variety of operand word-lengths.
-This is as expected, because the critical path delay in the online adder is ideally a fixed value and it is irrelevant to the operand precisions.
+This is as expected, because the critical path delay in the online adder is theoretically a fixed value and it is irrelevant to the operand precisions.
 In comparison, the rated frequency of \texttt{RCA} drops drastically for larger designs.
-In this case, both online adders will eventually outperform \texttt{RCA}.
-However our approach operates constantly faster than \texttt{OA\_behv} for any operand word-length.
+In this case, both online adders outperform \texttt{RCA} for large word-lengths.
+Besides, our approach operates constantly faster than \texttt{OA\_behv}.
 The speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $20\%$ to $26\%$.
@@
 	\label{Fig:AdderFreq}
+	\vspace{-1ex}
 \end{figure}
 
-We compare the resource usages of all three adder designs with respect to a variety of operand word-lengths.
-The results are shown in Fig.\ref{Fig:AdderArea}.
-The theoretical area budgets of the online adder predicted by (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also plotted with dotted lines in Fig.\ref{Fig:AdderArea}.
+We also compare the resource usages of all three adder designs with respect to a variety of operand word-lengths.
+The results are presented in Fig.\ref{Fig:AdderArea}, in which the theoretical area budgets of the online adder predicted by (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also plotted with dotted lines.
 Several observations can be made from the results.
@@
 This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
-However research has shown that this overhead can be reduced for multiple-operand adders or adder trees [xxx].
+%However research has shown that this overhead can be reduced for multiple-operand adders or adder trees [xxx].
 
@@
   \label{Fig:AdderArea}
-  %\vspace{-2ex}
+  \vspace{-1ex}
 \end{figure}
@@
 Algorithm \ref{Algorithm:OnlineMult} as described in Section~\ref{Sec:Background} can be synthesized into a unrolled digit parallel structure.
-Recent study has shown that the digit-parallel online multiplier is more tolerant to timing violations in comparison to conventional arithmetic, because timing errors initially affect the least significant digits and this will lead to small error magnitude[xxx].
-This implementation method is straightforward and can be utilized to design other digit parallel online operators.
+Recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the least significant digits and this will lead to small error magnitude~\cite{SKDAC14}.
+This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
 
-On the other hand, significant area budget is required in order to implement this type of digit parallel online multiplier (\texttt{OM}).
+On the other hand, significant area budget is required in order to implement this type of \texttt{OM}.
 Typically this is due to three main reasons.
 First, in comparison to the conventional multiplier, more iteration stages are needed.
-For instance in an $N$-digit \texttt{OM}, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, and $(N+\delta)$ iterations for the most significant $N$ digits result.
-Second, in each stage the logic is complex as it involves operations such as online addition, digit-vector multiplication, shifting and other combination logic such as the selection function.
-Besides, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $N+2+\delta$, because the selection function needs 2 integer digits as well as 1 fraction digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
+For instance in an $N$-digit \texttt{OM}, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, while $(N+\delta)$ iterations to generate the most significant $N$ digits result.
+Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication, shifting and other combination logic blocks such as the selection function.
+Besides, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits as well as 1 fraction digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
 Whereas in an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
@@
 Instead of simply implementing the unrolled format of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
-We notice that the online delay $\delta$ is employed in this algorithm because the input data are available in a digit serial fashion.
+We notice that the online delay $\delta$ is employed in Algorithm~\ref{Algorithm:OnlineMult} because the input data are available in a digit serial fashion.
 Hence $\delta$ is used to accumulate enough input digits to generate the MSD of the result.
@@
 
-In comparison to the original online multiplication algorithm, the maximum stages required to generate results with full precision drops by a factor of 2 using the proposed new algorithm.
-In each stage, the word-length of all signals also reduces from $N+2+\delta$ to $N+2$, as $\delta$ is not necessary for digit parallel operations.
-In addition, the $frac()$ function can be implemented only based on wire connection without using other logic resources.
+In comparison to Algorithm~\ref{Algorithm:OnlineMult}, the maximum stages required to generate results with full precision drops by a factor of 2 using the proposed new algorithm.
+In each stage, the word-length of all signals also reduces from $(N+2+\delta)$ to $(N+2)$, as $\delta$ is not necessary for digit parallel operations.
+In addition, the $frac()$ function can be implemented only based on wire connections without using other logic resources.
 
 \subsection{FPGA Implementation}
-We also explore an area efficient implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} on FPGAs.
-The general structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a), and the structure diagram of stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b) with the word-lengths of all signals labelled.
+We now present an area efficient implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} on FPGAs.
+For example, the general structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a), and the structure diagram of a single stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b) with the word-lengths of all signals labelled.
 Area optimizations can be performed on all modules.
@@
 Similarly the generation of $P_{[j]}$ can also be implemented using one 6-LUT, since only the integer digits of $W_{[j]}$ need to be modified due to the selection of $Z_{[j]}$.
-In addition, the structure of Stage 1 can be further optimized by removing the online adder, because $P_{[0]}=0$.
-
+In addition, the structure of Stage 1 in Fig~\ref{Fig:PMStructure}(a) can be further optimized by removing the online adder, because $P_{[0]}=0$.
+%
 \begin{figure}[tbp]
@@
 	\label{Fig:PMStructure}
+	\vspace{-1ex}
 \end{figure}
@@
 The blocks that generate partial products $Xy_j$ can be incorporated into the online adder with 6-LUT for further area reduction.
-In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, only 4 inputs per LUT are used to the maximum.
-This leaves 2 available inputs per LUT.
-In order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
-Therefore instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
+In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, we notice that only 4 inputs per LUT are used.
+This leaves at least 2 available inputs per LUT.
+Originally in order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
+Instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
 Notice that this approach is only available for FPGAs with 6-LUTs.
-
+%
 \begin{figure}[tbp]
@@
 	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.pdf}
+	\vspace{-1ex}
 	\caption{Left: Direct implementation with extra logic to generate partial products.
@@
 	\label{Fig:PartialProduct}
+	\vspace{-1ex}
 \end{figure}
@@
 The theoretical minimum resource usages of the proposed \texttt{OM} can be calculated as follows.
-In an $N$-digit \texttt{OM}, overall $N-1$ online adders are needed.
+In an $N$-digit \texttt{OM}, overall $(N-1)$ online adders are needed.
 According to Algorithm~\ref{Algorithm:OM_DigitParallel}, the word-length of each online adder is $(N+2)$-digit (2 integer digits and $N$ fractional digits).
 Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of Slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
-Note that $L_{S1}$ and $S_{S1}$ denote the LUT and Slice usages of the first stage, which is purely built with combinational logic without online adders.
-
+Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and Slices used by the first stage, which is built without online adders.
+%
 \begin{eqnarray}\label{Eq:OMareaLUT}
@@
 \end{eqnarray}
-
+%
 \begin{eqnarray}\label{Eq:OMareaSlice}
@@
 
-In comparison, the online multiplier offers the flexibility to simplify the structure correspondingly without affecting accuracy, if only the MSD half of the results are required.
-This is possible because in the \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD as described previously.
+In comparison, the online multiplier offers the flexibility to simplify the structure corresponding to the required precision.
+This is possible because in the \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system.
 This will potentially lead to a more area efficient design.
@@
 	\label{Fig:PMStructure_MSDhalf}
+	\vspace{-2ex}
 \end{figure}
@@
 Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier which is implemented to derive full precision results using behavioral descriptions (\texttt{OM\_initial}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
-In addition, we also incorporate multipliers with conventional binary arithmetic, and it is created using the Xilinx Core Generator.
-The \texttt{CoreGen} multiplier is implemented based on LUTs without DSPs, and it is configured with speed optimization \cite{XilinxMult}.
+In addition, we also compare the \texttt{OM} with the multiplier with conventional binary arithmetic.
+The conventional multiplier is created using the Xilinx Core Generator with speed optimization~\cite{XilinxMult}, and it is implemented based on LUTs without DSPs.
 
@@
   \subfigure[]{
-  \begin{minipage}{0.45\textwidth}
+  \begin{minipage}{0.47\textwidth}
     %\centering
@@
   \label{Fig:OMArea}
-  %\vspace{-2ex}
+  \vspace{-2ex}
 \end{figure}
@@
 We also check the rated frequencies of \texttt{OM\_full}, \texttt{OM\_half} and \texttt{CoreGen} for a variety of operand word-lengths.
-The frequency values are still obtained from the Xilinx Timing Analyzer.
-The results are plotted in Fig.xxx, from which we can see that there is an increasing gap between the online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
-This might because in the online multiplier, although the carry resources in the FPGA are efficiently used, each 4-digit carry logic within a Slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
+The frequency values are still obtained from the post place and route timing reports.
+The results are plotted in Fig.\ref{Fig:OM_Freq}, from which we can see that there is an increasing gap between the online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
+This might because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a Slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
 Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is huge for large operand word-lengths.
-This also explains the fact that \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, as the critical path of both designs are similar.
-
-However, we can take advantage of the ``overclocking friendly'' feature of the online arithmetic, and push the previous tests one step further by operating the circuits beyond their deterministic region while allowing timing violations to happen.
-In this case, we can examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (MRE), which is given in (\ref{Eq:MRE})), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of correct output, respectively.
-
-\begin{eqnarray}\label{Eq:MRE}
-  MRE=\frac{E_{error}}{E_{out}}\times100\%
-\end{eqnarray}
-
-For instance, Fig.~\ref{Fig:PM_MRE} demonstrates the MRE of the 8-digit multipliers.
-Notice that the input data to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
-We see that although the Timing Analyzer predicts slower frequencies for \texttt{OM}, it actually operates faster than \texttt{CoreGen} without the occurrence of timing errors.
-Besides,
+This also explains the fact that \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, as the critical path of both designs are identical in theory.
 
@@
 	\centering
-  \includegraphics[width=.5\textwidth]{./Figures/Exp/MRE_PM.eps}
-  \caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
-(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
+	\includegraphics[width=.48\textwidth]{./Figures/Exp/OM_Freq.eps}
+	\caption{Rated frequencies of different types of binary multipliers for a variety of operand word-lengths.
+The results are obtained from the Xilinx Timing Analyzer in ISE 14.1 after placing and routing.}
+	\label{Fig:OM_Freq}
+
+\end{figure}
+
+However, we can take advantage of the ``overclocking friendly'' feature of the online arithmetic, and push the previous tests one step further by operating the circuits beyond their deterministic region while allowing timing violations to happen.
+We examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (\texttt{MRE}), which is given in (\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of correct output, respectively.
+%
+\begin{eqnarray}\label{Eq:MRE}
+  MRE=\frac{E_{error}}{E_{out}}\times100\%
+  \vspace{-1ex}
+\end{eqnarray}
+
+For instance, Fig.~\ref{Fig:PM_MRE} demonstrates the \texttt{MRE} values of the 8-digit multipliers.
+Notice that the input data to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
+We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operates faster than \texttt{CoreGen} without the occurrence of timing errors.
+This is in accordance with the results seen in the previous work \cite{SKDAC14}.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.48\textwidth]{./Figures/Exp/MRE_PM.eps}
+ % \vspace{-1ex}
+  \caption{Mean relative errors seen at the outputs of different types of binary multipliers, when clocked with faster-than-rated frequencies.}
   \label{Fig:PM_MRE}
+  \vspace{-1ex}
 \end{figure}
@@
 \section{Conclusion}
-The conclusion goes here.
+In this paper, we initially describe a novel methodology that can efficiently map digit parallel online adders onto FPGAs.
+We have shown the limitations of the previous works, and the approaches we use to tackle these limitations.
+The proposed mapping method is targeting on modern FPGAs, which are with 6-LUTs and 4 LUTs in a Slice, by fully utilizing the built-in carry resources.
+We have demonstrated analytically and experimentally that the proposed architecture is both area and performance efficient in comparison to the original design.
+
+We then propose an area efficient FPGA implementation of the online multiplier, which is specifically optimized for digit parallel operations.
+We also shown that significant area reduction and frequency speed-ups can be obtained in the proposed new design.
+
+In the future we wish to explore alternative mapping methods for the online multiplier that can effectively use carry resources with long word-lengths to improve  its performance to a further extent.
 
@@
 % use section* for acknowledgement
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 

### 2014-05-23 FPT2014/bare_conf.tex
Add extra future works
Davids review

@@
 %\boldmath
-Online arithmetic has been widely utilized for ASIC implementations with significant performance improvements, as it is designed to perform computations from the most significant digits.
-Recent research also shows that the digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to the operators with conventional arithmetic.
-Unfortunately, the utilization of online arithmetic operators requires large area overhead, and the efficient implementation of general purpose online operators on FPGAs remains under investigation.
+Online arithmetic has been widely utilized for ASIC implementations, as it is designed to perform computations from the most significant digits.
+Recent research also shows that digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to operators with conventional arithmetic.
+Unfortunately, online arithmetic operators require a large area overhead, while efficient implementation of general purpose online operators on FPGAs remains under investigation.
 In this paper, we propose novel approaches to implement key primitives of online arithmetic, such as adders and multipliers, efficiently on modern FPGAs with 6-input LUTs.
 The FPGA carry resources are used for both area reduction and performance improvements.
-We demonstrate experimentally that the proposed architectures achieve significant area savings and frequency speed-ups comparing to the original implementations.
+We demonstrate experimentally that the proposed architectures achieve significant area savings and frequency speed-ups compared to the original implementations.
 
@@
 With online arithmetic, both inputs and outputs are processed in a MSD-first manner.
-This enables parallelism and duplication among multiple operations, and the overall computation latency can be significantly reduced.
+This enables parallelism among multiple operations, and the overall computation latency can be significantly reduced.
 A brief overview of online arithmetic is given in Section~\ref{Sec:Background}.
 
-Recent research has demonstrated another key advantage of online arithmetic that it allows gracefully degradation when operating beyond the deterministic region, e.g.
+Recent research has demonstrated another key advantage of online arithmetic is that it allows gracefully degradation when operating beyond the deterministic region, e.g.
 under overclocking \cite{SKDAC14}.
 This stream of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
-However, traditional form of computer arithmetic does not fail gracefully when timing violation happens, because timing errors initially affect MSDs of the results.
-In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occurs at LSDs of the results.
+However, traditional forms of computer arithmetic do not fail gracefully when timing violation happens, because timing errors initially affect MSDs of the results.
+In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occur at LSDs of the results.
 
@@
 For instance, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce the carry propagation delay by over one order of magnitude~\cite{Virtex6}.
-There is a large amount of studies exploring methods that can effectively map circuits using the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or propose alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2} .
-Besides, hard DSP blocks are also included to boost multiplications and multiply-accumulations~\cite{XilinxDSP}.
+There is a large amount of studies exploring methods that can effectively map circuits using the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or propose alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
+Furthermore, hard DSP blocks are also included to boost multiplications and multiply-accumulations~\cite{XilinxDSP}.
 However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.
 
-For online arithmetic, we notice from existing literatures that there are 2 directions that are worth investigating.
+For online arithmetic, we notice from existing literature that there are two directions worth investigating.
 First, although there has been previous research about FPGA implementations of online arithmetic, they typically only focus on online adders.
 A brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
-However, the implementation of other key arithmetic primitives, such as online multipliers, are lack of exploration.
-Second, we found that existing approaches of building general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan 3 series \cite{XilinxSpartan}.
-However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGAs with 6-input LUTs and 4 LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+However, the implementations of other key arithmetic primitives, such as online multipliers, lack exploration.
+Second, we found that existing approaches of building general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
+However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and 4 LUTs in a Slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
 
@@
 In Section~\ref{Sec:OA_FPGA}, we propose a novel approach of mapping the digit parallel online adder onto FPGA with 6-LUTs.
-The mapping is based on the fast carry logic, and the available resources within a slice can be fully utilized.
+The mapping is based on the fast carry logic, and the available resources within a Slice can be fully utilized.
 In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
-In addition, the theoretical resource usage of both operators is given, and they are verified experimentally on Xilinx Virtex-6 FPGAs.
-We demonstrate that the proposed designs achieve significant area reduction and performance gain over their original implementations.
+In addition, the theoretical resource usage of both operators is given.
+We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
 In summary, the main contributions of this paper are as follows:
@@
 Notice that $\delta$ is normally a small constant, which is independent of the precision in a given operation.
-For ease of discussion, in the following of this paper the input data are normalized to fixed point numbers in the range $(-1,1)$.
+For ease of discussion, for the rest of this paper, the input data is normalized to fixed point numbers in the range $(-1,1)$.
 Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
@@
   \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.pdf}
-  %\vspace{-3ex}
+  \vspace{-4ex}
   \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
-  %\vspace{-.5ex}
+  \vspace{-1ex}
   \label{Fig:OnlineDataFlow}
@@
 For instance with SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
-In comparison, the standard non-redundant representation only uses a digit set $\{0,r-1\}$.
+In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots,r-1\}$.
 Thus a standard number corresponds to several possible redundant representations.
-For example, the two's complement number $0.111$ can be represented in the online form as $0.10\overline{1}$, $0.0\overline{1}1$ and $0.111$ among many other possible representations.
+For example, the two's complement number $0.011$ can be represented in the binary online form as $0.1\overline{1}1$, $0.10\overline{1}$ and $0.011$ among many other possible representations.
 
-Due to the redundancy, the MSDs of the result can be calculated only based on partial information of the inputs, which is required by digit-serial online arithmetic.
-Then the value of the number can be revised by the following digits, because each number embodies multiple representations.
+Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
+Then the value of the number can be revised using the subsequent digits, because each number embodies multiple representations.
 
@@
 Adders serve as a critical building block for arithmetic operations.
-To perform digit-parallel online addition, a redundant adder can be directly utilized.
+To perform digit-parallel online addition, a redundant adder can be used directly.
 The structure diagram of an online adder with all signals represented with SD numbers is shown in Fig.~\ref{Fig:Radix2SD_adder}.
-An major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 full adder (FA) delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+The module 3:2 denotes a 3:2 compressor, which takes 3 inputs and generates 2 outputs.
+Normally it can be implemented on the basis of a full adder (FA).
+A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
+As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
 This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDAdder.pdf}
-    \vspace{-5ex}
-	\caption{An $N$-digit binary digit-parallel online adder with $(N+1)$-digit outputs. Both inputs and outputs are represented using SD representation.}
-    \vspace{2ex}
+	\includegraphics[width=.5\textwidth]{./Figures/SDAdder2.pdf}
+    \vspace{-6ex}
+	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. Module 3:2 denotes the 3:2 compressor.}
+    %\vspace{2ex}
 	\label{Fig:Radix2SD_adder}
@@
 Multiplication is another key arithmetic operator.
-Typically the online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit number as given in~(\ref{Eq:Online_Operands}).
-For a given iteration $j$, the product digit $z_j$ is generated with MSD-first through a selection function $sel()$.
-For the radix $r$ and a chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
+Typically, online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit numbers as given in~(\ref{Eq:Online_Operands}).
+For a given iteration $j$, the product digit $z_j$ is generated MSD-first through a selection function $sel()$.
+For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
 As radix-2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
 In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}) \cite{Oregon_OnlineNetwork}.
-Notice that the election is made only based on 2 integer digits and 1 fractional digit of $W_{[j]}$.
+Notice that the selection is based on 2 integer digits and 1 fractional digit of $W_{[j]}$.
 
@@
         \State $W_{[j]} \leftarrow P_{[j]} + H_{[j]}$\vspace{.5ex}
-        \State $Z_{[j]}~ \leftarrow sel(W_{[j]})$\vspace{.5ex}
+        \State $z_{j}~ \leftarrow sel(W_{[j]})$\vspace{.5ex}
         \State $P_{[j+1]} \leftarrow r\left(W_{[j]}-Z_{[j]}\right)$\vspace{.5ex}
@@
 In Section~\ref{Sec:OM_FPGA}, we will first describe an optimized online multiplication algorithm and its FPGA implementation, which are designed specifically targeting on digit parallel operations.
-Then we provide a modified structure which only generates the most significant half the products, in order to achieve extra area savings.
+Then we provide a modified structure which only generates the most significant half of the product in order to achieve extra area savings.
 
@@
     \item efficient mapping of the digit-parallel online adder onto sophisticated FPGAs resources \cite{FPT09RA,ASAP09RA};
-    \item multiple operands addition by designing compressor trees based on bit counters \cite{TC13RA,ASPDAC10RA_FPGA};
+    \item multiple operands addition by designing compressor trees based on bit counters \cite{TC13RA,CSMult_CounterArray};
     \item modifying existing FPGA architecture for more efficient digit-parallel online addition \cite{DAC07_CounterTree} and for specific applications \cite{FPL09_onlineCCM}.
@@
 
-Type 2 and type 3 are beyond the scope of this paper, as our interests are in the field of two-operand online addition that performs $Z=X+Y$, as shown in Fig.~\ref{Fig:Radix2SD_adder}, and we are using the main-stream FPGAs for implementation.
+Type 2 examines the use of counters to sum $k$ $N$-digit numbers where $k>2$.
+Instead, we focus on two-operand online addition that performs $Z=X+Y$, as shown in Fig.~\ref{Fig:Radix2SD_adder}.
+In comparison to type 3, this paper attempts to obtain the best performance from mainstream FPGAs instead of suggesting ways to modifying the FPGA fabric.
 
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan.pdf}
+	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan2.pdf}
 	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
@@
 Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a Slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or logic fault.
-For instance, if two \texttt{LB}s are mapped to a slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
-Additionally, the output of \texttt{XORCY2} should not be used.
+For instance, if two \texttt{LB}s are mapped to a Slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
+Due to the same reason, the output of \texttt{XORCY2} should not be used.
 
@@
 \subsection{Proposed Mapping Method}
-To tackle this problem, we firstly modify the structure of the online adder to enable an efficient FPGA mapping.
+To tackle this problem, we first modify the structure of the online adder to enable an efficient FPGA mapping.
 The structure of a 4-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
@@
 
-%propose an alternative mapping method that targets on the slice containing 4 LUTs such as the Xilinx Virtex series and all Xilinx 7 series FPGAs.
+%propose an alternative mapping method that targets on the Slice containing 4 LUTs such as the Xilinx Virtex series and all Xilinx 7 series FPGAs.
 
@@
 	\centering
-	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit.pdf}
+	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit2.pdf}
 	\caption{Modified structure of online adder.
 Left: an example of 4-digit online adder.
-The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 slice.
+The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 Slice.
 Right: one LB.
 The dotted box outlines the logic that can be mapped onto 1 LUT and the corresponding fast-carry logic.}
+	\vspace{-1ex}	
 	\label{Fig:ModifiedOA}
@@
 
-The detailed slice mapping of the 2 \texttt{LB}s and the logic in each LUT are shown in Fig.~\ref{Fig:SliceNew}.
+The detailed Slice mapping of the 2 \texttt{LB}s and the logic in each LUT are shown in Fig.~\ref{Fig:SliceNew}.
 The I/O signals are identical to the previous example in Fig.~\ref{Fig:ModifiedOA}.
 Normally 6-LUT can be configured with two different output ports \texttt{O6} and \texttt{O5}.
-For \texttt{LB1}, the carry input can be initialized by setting the \texttt{O6} of LUT2 to 0 constantly.
-In this case, the output of \texttt{MUXCY2} is always \texttt{O5} of LUT2, and the carry from \texttt{LB2} will not affect the results of \texttt{LB1}.
+For \texttt{LB1}, the carry input can be initialized by setting the \texttt{O6} of LUT2 to 0.
+In this case, the output of \texttt{MUXCY2} is always \texttt{O5} of LUT2, and the carry from \texttt{LB2} will not affect the result of \texttt{LB1}.
 For those logics to generate the MSD and the LSD, they can be combined into 1 Slice as observed from Fig.~\ref{Fig:ModifiedOA}.
-Therefore using this mapping method the resources within 1 slice can be fully utilized, potentially leads to significant area reduction.
+Therefore using this mapping method the resources within 1 Slice can be fully utilized, leading to a significant area reduction.
 
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FastCarry_New.pdf}
-	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
+	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FastCarry_New2.pdf}
+	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA Slice which contains four 6-LUTs. NC stands for ``Not Care''.}
+	\vspace{-1ex}	
 	\label{Fig:SliceNew}
@@
 
-In this mapping approach, the theoretical area figures of the online adder in terms of the number of LUTs and Slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+In this mapping approach, the area figures of the online adder in terms of the number of LUTs and Slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
 \begin{eqnarray}\label{Eq:OAareaLUT}
-	OAarea\_LUT = 2N
+	OA\_LUT = 2N
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Eq:OAareaSlice}
-	OAarea\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
+	OA\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
 \end{eqnarray}
@@
 All designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1.
-Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component "\texttt{Carry4}" is used to create \texttt{OA\_new}.
+Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
 
@@
 This is as expected, because the critical path delay in the online adder is theoretically a fixed value and it is irrelevant to the operand precisions.
-In comparison, the rated frequency of \texttt{RCA} drops drastically for larger designs.
-In this case, both online adders outperform \texttt{RCA} for large word-lengths.
-Besides, our approach operates constantly faster than \texttt{OA\_behv}.
-The speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $20\%$ to $26\%$.
+In comparison, the rated frequency of the \texttt{RCA} drops drastically for larger word-lengths.
+It follows that both online adders outperform \texttt{RCA} for large word-lengths.
+Furthermore, our approach operates faster than \texttt{OA\_behv}; the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $20\%$ to $26\%$.
 
@@
 We also compare the resource usages of all three adder designs with respect to a variety of operand word-lengths.
-The results are presented in Fig.\ref{Fig:AdderArea}, in which the theoretical area budgets of the online adder predicted by (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}) are also plotted with dotted lines.
-Several observations can be made from the results.
-Firstly the predicted resource usages of both LUTs and Slices match well the results obtained from real implementations.
-Secondly it can be seen that the behavioural implementation \texttt{OA\_behv} is not area efficient for FPGAs, because the dedicated FPGA resources are not fully utilized.
-In comparison, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
-Thirdly, our design still costs more area than \texttt{RCA}, with the area overhead of $80\%\sim98\%$ in terms of LUTs, and $0\%\sim88\%$ in terms of Slices.
+The results are presented in Fig~\ref{Fig:AdderArea}.
+We can see that in comparison to the original \texttt{OA\_behv}, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
+This is because the dedicated FPGA resources are fully utilized.
+However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of Slices.
 This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_LUTs2.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_LUTs3.eps}
     \vspace{1ex}
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_Slices2.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/Adder_Slices3.eps}
     \vspace{1ex}
@@
 Algorithm \ref{Algorithm:OnlineMult} as described in Section~\ref{Sec:Background} can be synthesized into a unrolled digit parallel structure.
-Recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the least significant digits and this will lead to small error magnitude~\cite{SKDAC14}.
+Recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14}.
 This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
 
-On the other hand, significant area budget is required in order to implement this type of \texttt{OM}.
-Typically this is due to three main reasons.
+On the other hand, significant area overhead is required in order to implement this type of \texttt{OM}.
+This is due to three main reasons.
 First, in comparison to the conventional multiplier, more iteration stages are needed.
-For instance in an $N$-digit \texttt{OM}, totally $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, while $(N+\delta)$ iterations to generate the most significant $N$ digits result.
+For instance in an $N$-digit \texttt{OM}, $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, or $(N+\delta)$ iterations are required to generate the most significant $N$ digits.
 Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication, shifting and other combination logic blocks such as the selection function.
-Besides, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits as well as 1 fraction digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
-Whereas in an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
+Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits and 1 fractional digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
+In comparison, an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
 Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
@@
 Instead of simply implementing the unrolled format of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
-We notice that the online delay $\delta$ is employed in Algorithm~\ref{Algorithm:OnlineMult} because the input data are available in a digit serial fashion.
+We notice that the online delay $\delta$ is employed in Algorithm~\ref{Algorithm:OnlineMult} because the input data is available in a digit serial fashion.
 Hence $\delta$ is used to accumulate enough input digits to generate the MSD of the result.
-Nevertheless if all digits of inputs are given simultaneously, $\delta$ is no longer necessary.
+Nevertheless if all digits of inputs are available simultaneously, $\delta$ is no longer necessary.
 Due to the same reason, $H[j]$, which takes one digit of each input per stage as shown in the original algorithm, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
@@
 Our proposed online adder architecture can be employed.
-The selection logic takes 3 digits input (6 bits) and generate 1 digit output (2 bits).
+The selection logic takes 3 input digits (6 bits) and generate 1 output digit (2 bits).
 Hence it can be implemented using two 6-LUTs for each output bit.
@@
 
-The blocks that generate partial products $Xy_j$ can be incorporated into the online adder with 6-LUT for further area reduction.
+The blocks that generate partial products $Xy_j$ can be incorporated into the online adder for further area reduction.
 In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, we notice that only 4 inputs per LUT are used.
@@
 
-The theoretical minimum resource usages of the proposed \texttt{OM} can be calculated as follows.
+The theoretical minimum resource uses of the proposed \texttt{OM} can be calculated as follows.
 In an $N$-digit \texttt{OM}, overall $(N-1)$ online adders are needed.
@@
 \begin{eqnarray}\label{Eq:OMareaLUT}
-	OMarea\_{LUT} = 2(N+2)(N-1) + {L}_{S1}
+	OM\_{LUT} = 2(N+2)(N-1) + {L}_{S1}
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Eq:OMareaSlice}
-	OMarea\_{Slice} = (1+\left\lceil{\frac{N}{2}}\right\rceil)(N-1)+S_{S1}
+	OM\_{Slice} = (1+\left\lceil{\frac{N}{2}}\right\rceil)(N-1)+S_{S1}
 \end{eqnarray}
@@
 \subsection{Structure Optimization for the MSD Half of the Results}
-As discussed before in Section~\ref{Sec:Background}, normally the multiplier is connected with other arithmetic operators in real applications.
-If the outputs of a multiplier is utilized for subsequent operations, only the most significant half of the products are required to maintain the consistency of word-length between inputs and outputs of the system.
-In the conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
-However both the computation time and the structure remains unchanged, because the results are generated from LSDs.
+As discussed before, normally the multiplier is connected with other arithmetic operators in real applications.
+If the outputs of a multiplier is utilized for subsequent operations, and it is chosen to main the consistency of word-length between the I/Os of the system, then only the most significant half of the products are required.
+In a conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
+However, both the computation time and the structure remains unchanged, because the results are generated from LSDs.
 
 In comparison, the online multiplier offers the flexibility to simplify the structure corresponding to the required precision.
-This is possible because in the \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system.
+This is possible because in an \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system.
 This will potentially lead to a more area efficient design.
@@
 \subsection{Performance Analysis}
-Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier which is implemented to derive full precision results using behavioral descriptions (\texttt{OM\_initial}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
-In addition, we also compare the \texttt{OM} with the multiplier with conventional binary arithmetic.
+Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier based on behavioral descriptions (\texttt{OM\_initial}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
+In addition, we also compare the \texttt{OM} with the conventional binary arithmetic multiplier.
 The conventional multiplier is created using the Xilinx Core Generator with speed optimization~\cite{XilinxMult}, and it is implemented based on LUTs without DSPs.
@@
 The results are obtained from ISE 14.1 after mapping the design to the Virtex-6 FPGA.
-The area predictions for \texttt{OM\_full} from (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}) are also included in both figures.
-Again we can see that the predicted resource usages match well with practical implementations.
-In comparison to \texttt{OM\_initial}, clearly significant area savings can be obtained by the optimized design \texttt{OM\_full}.
-Specifically, the LUTs usage and Slices usage drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
+In comparison to \texttt{OM\_initial}, significant area savings have been obtained by the optimized design \texttt{OM\_full}.
+Specifically, the LUTs and Slice utilization drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
 
-In comparison to the \texttt{CoreGen} multiplier, the area overheads of \texttt{OM\_full} are $48\%\sim84\%$ for LUTs, and $0\%\sim83\%$ for Slices.
+In comparison to the \texttt{CoreGen} multiplier, the area overheads of \texttt{OM\_full} are between $48\%$ and $84\%$ for LUTs and up to $83\%$ for Slices.
 On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
-The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim55\%$ for Slices.
+The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%$ to $55\%$ for Slices.
 
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTslog.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTslog2.eps}
     \vspace{1ex}
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slicelog.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slicelog2.eps}
     \vspace{1ex}
@@
 The frequency values are still obtained from the post place and route timing reports.
+Notice that input stimulus to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
 The results are plotted in Fig.\ref{Fig:OM_Freq}, from which we can see that there is an increasing gap between the online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
@@
 For instance, Fig.~\ref{Fig:PM_MRE} demonstrates the \texttt{MRE} values of the 8-digit multipliers.
-Notice that the input data to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
-We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operates faster than \texttt{CoreGen} without the occurrence of timing errors.
+We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operate faster than \texttt{CoreGen} without the occurrence of timing errors.
 This is in accordance with the results seen in the previous work \cite{SKDAC14}.
@@
 In this paper, we initially describe a novel methodology that can efficiently map digit parallel online adders onto FPGAs.
-We have shown the limitations of the previous works, and the approaches we use to tackle these limitations.
-The proposed mapping method is targeting on modern FPGAs, which are with 6-LUTs and 4 LUTs in a Slice, by fully utilizing the built-in carry resources.
+The proposed mapping method targets modern FPGAs, which have 6-input LUTs and 4 LUTs in a Slice, and fully utilizes the built-in carry resources.
 We have demonstrated analytically and experimentally that the proposed architecture is both area and performance efficient in comparison to the original design.
+We then propose an area efficient FPGA implementation of the online multiplier, which is specifically optimized for digit parallel operations.
+We have shown that this also obtains significant area reduction and frequency speed-ups.
 
-We then propose an area efficient FPGA implementation of the online multiplier, which is specifically optimized for digit parallel operations.
-We also shown that significant area reduction and frequency speed-ups can be obtained in the proposed new design.
-
-In the future we wish to explore alternative mapping methods for the online multiplier that can effectively use carry resources with long word-lengths to improve  its performance to a further extent.
+In the future we wish to explore alternative mapping methods for the online multiplier that can effectively use carry resources with long word-lengths to improve  its performance further.
+We would also like to combine the proposed online primitives into real-world applications.
 

### 2014-05-26 FPT2014/bare_conf.tex
Feedbacks from George

@@
 %\boldmath
-Online arithmetic has been widely utilized for ASIC implementations, as it is designed to perform computations from the most significant digits.
-Recent research also shows that digit parallel online operators can fail more gracefully when operating beyond the deterministic region, in comparison to operators with conventional arithmetic.
-Unfortunately, online arithmetic operators require a large area overhead, while efficient implementation of general purpose online operators on FPGAs remains under investigation.
+Online arithmetic has been widely studied for ASIC implementations.
+It is designed to perform computations from the most significant digits, resulting in the ability to chain arithmetic operators together for low latency.
+Recent research also shows that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region, in comparison to operators with conventional arithmetic.
+Unfortunately, the utilization of online arithmetic operators in the past has required a large area overhead for FPGA implementation.
 In this paper, we propose novel approaches to implement key primitives of online arithmetic, such as adders and multipliers, efficiently on modern FPGAs with 6-input LUTs.
 The FPGA carry resources are used for both area reduction and performance improvements.
-We demonstrate experimentally that the proposed architectures achieve significant area savings and frequency speed-ups compared to the original implementations.
+We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ Slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
+
+% significant area savings and frequency speed-ups compared to a direction.
 
@@
 
-Recent research has demonstrated another key advantage of online arithmetic is that it allows gracefully degradation when operating beyond the deterministic region, e.g.
-under overclocking \cite{SKDAC14}.
+Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region, i.e.
+under overclocking \cite{SKDAC14_REVIEW}.
 This stream of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
-However, traditional forms of computer arithmetic do not fail gracefully when timing violation happens, because timing errors initially affect MSDs of the results.
+However, traditional forms of computer arithmetic do not fail gracefully when timing violation happens, because timing errors tend to affect MSDs of the results.
 In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occur at LSDs of the results.
 
-Despite its attractiveness, the usage of online arithmetic on existing FPGAs is still limited due to the huge area overhead.
-Generally, it is difficult to efficiently map the arithmetic circuits solely onto the look-up-tables (LUTs), which are fundamental building blocks of FPGAs.
-Lots of efforts has been done to alleviate this concern.
-For instance, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce the carry propagation delay by over one order of magnitude~\cite{Virtex6}.
-There is a large amount of studies exploring methods that can effectively map circuits using the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or propose alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
-Furthermore, hard DSP blocks are also included to boost multiplications and multiply-accumulations~\cite{XilinxDSP}.
+Despite its attractiveness, the usage of online arithmetic on existing FPGAs is still limited due to a large area overhead.
+For standard arithmetic, it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), the fundamental building blocks of FPGAs.
+As a result, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce the carry propagation delay by over one order of magnitude~\cite{Virtex6}.
+Significant work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or which proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
+Furthermore, hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply-accumulates~\cite{XilinxDSP}.
 However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.
 
-For online arithmetic, we notice from existing literature that there are two directions worth investigating.
-First, although there has been previous research about FPGA implementations of online arithmetic, they typically only focus on online adders.
-A brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
-However, the implementations of other key arithmetic primitives, such as online multipliers, lack exploration.
-Second, we found that existing approaches of building general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
+For online arithmetic, two research directions have been investigated.
+First, although there has been previous research about FPGA implementations of online arithmetic, the work only focused on online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
+Second, there are existing approaches to build general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
 However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and 4 LUTs in a Slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for efficient implementation.
+%However, the implementations of other key arithmetic primitives, such as online multipliers, lack exploration.
 
@@
 In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
-In addition, the theoretical resource usage of both operators is given.
+In addition, the resource usage of both operators is given.
 We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
-In summary, the main contributions of this paper are as follows:
-\begin{enumerate}
-    \item An efficient approach of mapping online adders onto modern FPGAs;
-    \item Area efficient implementation of digit parallel online multiplication algorithm on FPGAs;
-    \item Theoretical area models of the proposed architectures.
-\end{enumerate}
+For online adders, our method achieves over $67\%$ Slice savings and $1.2\times$ frequency speed-ups in comparison to a direct implementation.
+For online multipliers, the LUTs and Slice utilization of the proposed new architecture drops over $2.4\times$ and $3.2\times$, with a frequency speed-up more than $1.5\times$ in comparison to a direct implementation.
+In summary, the main contributions of this paper are an efficient mapping of online adders and multipliers to modern FPGAs.
+(to be completed)
+% by fully utilizing the fast carry logic for .
 
-%The theoretical area overhead of an online adder is given in terms of the usage of LUTs and Slices.
+%\begin{enumerate}
+%    \item An efficient approach of mapping online adders onto modern FPGAs;
+%    \item Area efficient implementation of digit parallel online multiplication algorithm on FPGAs;
+%    \item Theoretical area models of the proposed architectures.
+%\end{enumerate}
 
@@
 	\label{Fig:PreWorkVirtex6}
-    \vspace{-2ex}
+    %\vspace{-2ex}
 \end{figure}
@@
 	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA Slice which contains four 6-LUTs. NC stands for ``Not Care''.}
-	\vspace{-1ex}	
+	%\vspace{-1ex}	
 	\label{Fig:SliceNew}
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.45\textwidth]{./Figures/Exp/Adder_Freq.eps}
+	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.1.}
+	\label{Fig:AdderFreq}
+	\vspace{-1ex}
+\end{figure}
+
 We record the rated frequencies of all designs when varying the operand word-lengths.
@@
 It follows that both online adders outperform \texttt{RCA} for large word-lengths.
-Furthermore, our approach operates faster than \texttt{OA\_behv}; the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $20\%$ to $26\%$.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/Exp/Adder_Freq.eps}
-	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.1.}
-	\label{Fig:AdderFreq}
-	\vspace{-1ex}
-\end{figure}
+Furthermore, our approach operates faster than \texttt{OA\_behv}; the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $1.20\times$ to $1.26\times$.
 
@@
 Algorithm \ref{Algorithm:OnlineMult} as described in Section~\ref{Sec:Background} can be synthesized into a unrolled digit parallel structure.
-Recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14}.
-This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
+A recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14_REVIEW}.
+%This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
 
-On the other hand, significant area overhead is required in order to implement this type of \texttt{OM}.
-This is due to three main reasons.
+However, significant area overhead is required in order to implement this type of \texttt{OM}, due to three main reasons.
 First, in comparison to the conventional multiplier, more iteration stages are needed.
 For instance in an $N$-digit \texttt{OM}, $(2N+\delta)$ iterations are required to generate $2N$ digits outputs, or $(N+\delta)$ iterations are required to generate the most significant $N$ digits.
-Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication, shifting and other combination logic blocks such as the selection function.
-Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits and 1 fractional digits to generate $z_j$, as described in Section~\ref{Sec:Background}.
-In comparison, an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
+Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication (to generate $x_{j+\delta+1}\cdot Y_{[j+1]}$ and $y_{j+\delta+1}\cdot X_{[j]}$ in Algorithm~\ref{Algorithm:OnlineMult}), shifting and other combinational logic blocks such as the selection function.
+Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits and 1 fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
 Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
+%In comparison, an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
 
-We address the first 2 design issues by providing an alternative online multiplication algorithm.
+We address the first two design issues by providing an alternative online multiplication algorithm.
 Instead of simply implementing the unrolled format of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
@@
 Hence $\delta$ is used to accumulate enough input digits to generate the MSD of the result.
-Nevertheless if all digits of inputs are available simultaneously, $\delta$ is no longer necessary.
-Due to the same reason, $H[j]$, which takes one digit of each input per stage as shown in the original algorithm, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
+However if all digits of the inputs are available simultaneously, then the delay $\delta$ is no longer necessary.
+For the same reason, $H[j]$, which takes one digit of each input per stage as shown in the original algorithm, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
 To summarize, the modified algorithm for digit parallel online multiplication is described in Algorithm~\ref{Algorithm:OM_DigitParallel}, where $N$ denotes the operand word-length, function $frac(W_{[N]})$ refers to select the fractional digits of $W_{[N]}$, and the selection function $sel()$ is given previously in (\ref{Eq:SelFunc_OM}).
@@
     	\State $W_{[j]}    \leftarrow  P_{[j-1]} + Xy_j$			\vspace{.5ex}
-     	\State $Z_{[j]}  ~      \leftarrow  sel(W_{[j]})$			\vspace{.5ex}
+     	\State $z_{j}  ~~      \leftarrow  sel(W_{[j]})$			\vspace{.5ex}
 	 	\State $P_{[j+1]}  \leftarrow  r\left(W_{[j]}-Z_{[j]}\right)$	\vspace{.5ex}
@@
 
-In comparison to Algorithm~\ref{Algorithm:OnlineMult}, the maximum stages required to generate results with full precision drops by a factor of 2 using the proposed new algorithm.
+In comparison to Algorithm~\ref{Algorithm:OnlineMult}, the maximum number of stages required to generate results with full precision drops by a factor of 2 using the proposed new algorithm.
 In each stage, the word-length of all signals also reduces from $(N+2+\delta)$ to $(N+2)$, as $\delta$ is not necessary for digit parallel operations.
@@
 Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and Slices used by the first stage, which is built without online adders.
-%
+
 \begin{eqnarray}\label{Eq:OMareaLUT}
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
+	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
+(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
+	\label{Fig:PMStructure_MSDhalf}
+	%\vspace{-2ex}
+\end{figure}
+
 In comparison, the online multiplier offers the flexibility to simplify the structure corresponding to the required precision.
@@
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
-	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
-(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
-	\label{Fig:PMStructure_MSDhalf}
-	\vspace{-2ex}
-\end{figure}
-
 \subsection{Performance Analysis}
-Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier based on behavioral descriptions (\texttt{OM\_initial}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
+Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier based on behavioral descriptions (\texttt{OM\_behv}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
 In addition, we also compare the \texttt{OM} with the conventional binary arithmetic multiplier.
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTslog2.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_LUTslog.eps}
     \vspace{1ex}
@@
     %\centering
-    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slicelog2.eps}
+    \includegraphics[width=.95\textwidth]{./Figures/Exp/OM_Slicelog.eps}
     \vspace{1ex}
@@
   \label{Fig:OMArea}
-  \vspace{-2ex}
+  %\vspace{-2ex}
 \end{figure}
 
-We also check the rated frequencies of \texttt{OM\_full}, \texttt{OM\_half} and \texttt{CoreGen} for a variety of operand word-lengths.
+We also check the rated frequencies of all four types of multipliers for a variety of operand word-lengths.
 The frequency values are still obtained from the post place and route timing reports.
 Notice that input stimulus to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
-The results are plotted in Fig.\ref{Fig:OM_Freq}, from which we can see that there is an increasing gap between the online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
+The results are plotted in Fig.\ref{Fig:OM_Freq}, from which we can see that in comparison to \texttt{OM\_behv}, our proposed architectures achieve frequency speed-ups varying from $1.49\times$ to $1.98\times$.
+
+We also notice that there is an increasing gap between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
 This might because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a Slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
@@
 	\centering
-	\includegraphics[width=.48\textwidth]{./Figures/Exp/OM_Freq.eps}
+	\includegraphics[width=.48\textwidth]{./Figures/Exp/OM_Freq2.eps}
 	\caption{Rated frequencies of different types of binary multipliers for a variety of operand word-lengths.
@@
 We examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (\texttt{MRE}), which is given in (\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of correct output, respectively.
-%
+
 \begin{eqnarray}\label{Eq:MRE}
   MRE=\frac{E_{error}}{E_{out}}\times100\%
-  \vspace{-1ex}
+  %\vspace{-1ex}
 \end{eqnarray}
@@
 We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operate faster than \texttt{CoreGen} without the occurrence of timing errors.
-This is in accordance with the results seen in the previous work \cite{SKDAC14}.
+This is in accordance with the results seen in the previous work \cite{SKDAC14_REVIEW}.
 
@@
   \label{Fig:PM_MRE}
-  \vspace{-1ex}
+  %\vspace{-1ex}
 \end{figure}

### 2014-05-28 FPT2014/bare_conf.tex
George feedback 2

@@
 %\boldmath
-Online arithmetic has been widely studied for ASIC implementations.
-It is designed to perform computations from the most significant digits, resulting in the ability to chain arithmetic operators together for low latency.
+Online arithmetic has been widely studied for ASIC implementation.
+Online components are designed to perform computations most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
 Recent research also shows that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region, in comparison to operators with conventional arithmetic.
 Unfortunately, the utilization of online arithmetic operators in the past has required a large area overhead for FPGA implementation.
-In this paper, we propose novel approaches to implement key primitives of online arithmetic, such as adders and multipliers, efficiently on modern FPGAs with 6-input LUTs.
-The FPGA carry resources are used for both area reduction and performance improvements.
+In this paper, we propose novel approaches to implement the key primitives of online arithmetic, adders and multipliers, efficiently on modern Xilinx FPGAs with 6-input LUTs and carry resources.
 We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ Slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
@@
 division and square root.
-This inconsistency in computing directions will potentially result in large latency when propagating data among different operations.
+This inconsistency in computing directions potentially results in large latency when propagating data between different operations.
 Online arithmetic was designed to solve this problem \cite{Ercegovac_OnlineOverview,Ercegovac_Book}.
@@
 Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region, i.e.
-under overclocking \cite{SKDAC14_REVIEW}.
-This stream of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
+when overclocking \cite{SKDAC14_REVIEW}.
+This theme of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
 However, traditional forms of computer arithmetic do not fail gracefully when timing violation happens, because timing errors tend to affect MSDs of the results.
@@
 
-Despite its attractiveness, the usage of online arithmetic on existing FPGAs is still limited due to a large area overhead.
-For standard arithmetic, it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), the fundamental building blocks of FPGAs.
-As a result, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce the carry propagation delay by over one order of magnitude~\cite{Virtex6}.
-Significant work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or which proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
-Furthermore, hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply-accumulates~\cite{XilinxDSP}.
+Despite its attractiveness, the use of online arithmetic on existing FPGAs is still limited due to a large area overhead.
+Given for standard arithmetic, it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), the fundamental building blocks of FPGAs.
+As a result, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce carry propagation delay~\cite{Virtex6}.
+Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
+Hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply accumulates~\cite{XilinxDSP}.
 However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.
 
-For online arithmetic, two research directions have been investigated.
-First, although there has been previous research about FPGA implementations of online arithmetic, the work only focused on online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
-Second, there are existing approaches to build general purpose online adders are specifically for low cost FPGAs with 4-input LUTs and 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
+For online arithmetic, two major research directions have been investigated.
+First, although there has been previous research into FPGA implementations of online arithmetic, this work only focused on online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
+Second, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
 However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and 4 LUTs in a Slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
@@
 In this paper, both issues will be addressed.
-In Section~\ref{Sec:OA_FPGA}, we propose a novel approach of mapping the digit parallel online adder onto FPGA with 6-LUTs.
-The mapping is based on the fast carry logic, and the available resources within a Slice can be fully utilized.
-In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of digit parallel online multiplier.
-In addition, the resource usage of both operators is given.
+In Section~\ref{Sec:OA_FPGA}, we propose a novel approach to map the digit parallel online adders onto FPGAs with 6-LUTs.
+The mapping is based on the fast carry logic, and the available resources within a slice can be fully utilized.
+In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of a digit parallel online multiplier.
+The resource usage of both operators can be determined analytically.
 We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
@@
 Online arithmetic has been widely used in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
-Online arithmetic was originally designed for digit-serial operation, of which the data flow is illustrated in Fig~\ref{Fig:OnlineDataFlow}.
-It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required and $\delta$ is called ``online delay''.
-Notice that $\delta$ is normally a small constant, which is independent of the precision in a given operation.
-For ease of discussion, for the rest of this paper, the input data is normalized to fixed point numbers in the range $(-1,1)$.
+Online arithmetic was originally designed for digit-serial operation, as illustrated in Fig~\ref{Fig:OnlineDataFlow}.
+It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required, where $\delta$ is called the ``online delay''.
+$\delta$ is normally a small constant, which is independent of the precision.
+For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$.
 Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
@@
 
-MSD-first operation is possible with the employment of the redundant number system.
-Normally there are 2 most commonly used redundant number representation: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}.
-For instance with SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
+MSD-first operation is possible only if a redundant number system is used.
+Normally there are two most commonly used redundant number representations: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}.
+With SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
 In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots,r-1\}$.
 Thus a standard number corresponds to several possible redundant representations.
-For example, the two's complement number $0.011$ can be represented in the binary online form as $0.1\overline{1}1$, $0.10\overline{1}$ and $0.011$ among many other possible representations.
+For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.
 
 Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
-Then the value of the number can be revised using the subsequent digits, because each number embodies multiple representations.
+Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.
 
@@
 To perform digit-parallel online addition, a redundant adder can be used directly.
-The structure diagram of an online adder with all signals represented with SD numbers is shown in Fig.~\ref{Fig:Radix2SD_adder}.
-The module 3:2 denotes a 3:2 compressor, which takes 3 inputs and generates 2 outputs.
-Normally it can be implemented on the basis of a full adder (FA).
+The structure of an online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
+The module ``3:2'' denotes a 3:2 compressor, which takes 3 inputs and generates 2 outputs, and is logically equivalent to a full adder (FA).
 A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
@@
     \vspace{-6ex}
-	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. Module 3:2 denotes the 3:2 compressor.}
+	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
     %\vspace{2ex}
@@
 Multiplication is another key arithmetic operator.
-Typically, online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit numbers as given in~(\ref{Eq:Online_Operands}).
+Typically, online multiplication is performed in a recursive digit serial manner, as illustrated in Algorithm~\ref{Algorithm:OnlineMult} \cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit numbers as given in~(\ref{Eq:Online_Operands}).
 For a given iteration $j$, the product digit $z_j$ is generated MSD-first through a selection function $sel()$.
 For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
-As radix-2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
+As radix 2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
 In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}) \cite{Oregon_OnlineNetwork}.
-Notice that the selection is based on 2 integer digits and 1 fractional digit of $W_{[j]}$.
+Notice that the selection is based on two integer digits and one fractional digit of $W_{[j]}$.
 
@@
 
-It is worth noting that the precision of the product $Z$ can be determined by directly truncating from the LSDs, since there is no carry propagations from the LSD to the MSD.
-This is useful especially when the multiplication product is used by successive computations, where only the first $N$ digits of the results are normally used.
+It is worth noting that the precision of the product $Z$ can be determined by directly truncating from the LSDs, since there is no carry propagation from the LSD to the MSD.
+This is useful especially when the multiplication product is used by successive computations, where often only the first $N$ digits of the results are used.
 In comparison, the product is generated starting from the LSD with conventional arithmetic.
@@
 
-In Section~\ref{Sec:OM_FPGA}, we will first describe an optimized online multiplication algorithm and its FPGA implementation, which are designed specifically targeting on digit parallel operations.
+In Section~\ref{Sec:OM_FPGA}, we will first describe an optimized online multiplication algorithm and its FPGA implementation, which are designed specifically targeting digit parallel operations.
 Then we provide a modified structure which only generates the most significant half of the product in order to achieve extra area savings.
@@
 
-\section{Digit Parallel Online Adder on FPGAs}\label{Sec:OA_FPGA}
+\section{Digit Parallel Online Adder for FPGAs}\label{Sec:OA_FPGA}
 \subsection{Related Works}
-There has been previous works about FPGA implementation of digit parallel online adders. From the literature, the existing approaches can be classified into three types:
+There have been previous works about FPGA implementation of digit parallel online adders. From the literature, the existing approaches can be classified into three types:
 
@@
     \item efficient mapping of the digit-parallel online adder onto sophisticated FPGAs resources \cite{FPT09RA,ASAP09RA};
-    \item multiple operands addition by designing compressor trees based on bit counters \cite{TC13RA,CSMult_CounterArray};
+    \item multiple operand addition by designing compressor trees based on bit counters \cite{TC13RA,CSMult_CounterArray};
     \item modifying existing FPGA architecture for more efficient digit-parallel online addition \cite{DAC07_CounterTree} and for specific applications \cite{FPL09_onlineCCM}.
@@
 Instead, we focus on two-operand online addition that performs $Z=X+Y$, as shown in Fig.~\ref{Fig:Radix2SD_adder}.
-In comparison to type 3, this paper attempts to obtain the best performance from mainstream FPGAs instead of suggesting ways to modifying the FPGA fabric.
+In comparison to type 3, this paper attempts to obtain the best performance from mainstream FPGAs instead of suggesting ways to modify the FPGA fabric.
 
 Specifically in type 1, both works took advantage of the built-in carry resources in FPGAs.
-Conventionally the ASIC implementation of online adders is based on the 4:2 compressors, as outlined in Fig.~\ref{Fig:PreviousWork} within the gray background.
+Conventionally the ASIC implementation of online adders is based on 4:2 compressors, as outlined in Fig.~\ref{Fig:PreviousWork} within the gray background.
 However, directly applying this approach in the FPGAs could be less efficient.
@@
 Instead, Kamp et al \cite{FPT09RA} and Hormigo et al \cite{ASAP09RA} described very similar mapping techniques for online adders with SD representations and CS representations, respectively.
-They share the common idea that maps the logic block (\texttt{LB}) within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
-In this case, the fast-carry logic in the FPGA can be employed, and the delay between the 2 FAs can be largely reduced.
+They share the common idea of using a maps the logic block (\texttt{LB}) within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
+In this case, the fast-carry logic in the FPGA can be employed, and the delay between the two FAs can be greatly reduced.
 
@@
 	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
-The grey background highlights the 4:2 compressor.
+The gray background highlights the 4:2 compressor.
 Dotted circle indicates the logic block (LB) which can be mapped to the FPGA using the carry resources.}
@@
 
-However, we notice the major limitations of both approaches that they only target on FPGAs with 4-input LUTs (4-LUT) and 2 LUTs within a logic Slice, such as the Xilinx Spartan series and the Altera Cyclone series.
+However, we notice the major limitations of both approaches that they only target FPGAs with 4-input LUTs (4-LUT) and two LUTs within a logic slice, such as the Xilinx Spartan series and the Altera Cyclone series.
 This is naturally reasonable because one \texttt{LB} can be mapped to a single Slice.
-Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and 4 LUTs in a Slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or logic fault.
-For instance, if two \texttt{LB}s are mapped to a Slice with 4 LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} will be faulty because the its carry input cannot be explicitly initialized.
+Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and four LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or wrong results.
+For instance, if two \texttt{LB}s are mapped to a slice with four LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} should not be used because the its carry input cannot be explicitly initialized.
 Due to the same reason, the output of \texttt{XORCY2} should not be used.
@@
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork.pdf}
+	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork2.pdf}
 	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
@@
 \subsection{Proposed Mapping Method}
-To tackle this problem, we first modify the structure of the online adder to enable an efficient FPGA mapping.
+To tackle this problem, we first present an alternative structure of the online adder to enable an efficient FPGA mapping.
 The structure of a 4-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
@@
 In this case they can be mapped individually on 2 LUTs.
-The second FA, which generates the outputs, is unchanged and can be implemented using the fast-carry logic.
+The second FA, which generates the outputs, is unchanged and can be implemented using the fast carry logic.
 
@@
 	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit2.pdf}
-	\caption{Modified structure of online adder.
+	\caption{Alternative structure of online adder.
 Left: an example of 4-digit online adder.
@@
 Right: one LB.
-The dotted box outlines the logic that can be mapped onto 1 LUT and the corresponding fast-carry logic.}
+The dotted boxes outline the logic that can be mapped onto each LUT and the corresponding fast carry logic.}
 	\vspace{-1ex}	
@@
 
-The detailed Slice mapping of the 2 \texttt{LB}s and the logic in each LUT are shown in Fig.~\ref{Fig:SliceNew}.
+The detailed slice mapping of the two \texttt{LB}s and the logic in each LUT are shown in Fig.~\ref{Fig:SliceNew}.
 The I/O signals are identical to the previous example in Fig.~\ref{Fig:ModifiedOA}.
-Normally 6-LUT can be configured with two different output ports \texttt{O6} and \texttt{O5}.
+The 6-LUT can be configured with two different output ports \texttt{O6} and \texttt{O5}.
 For \texttt{LB1}, the carry input can be initialized by setting the \texttt{O6} of LUT2 to 0.
 In this case, the output of \texttt{MUXCY2} is always \texttt{O5} of LUT2, and the carry from \texttt{LB2} will not affect the result of \texttt{LB1}.
-For those logics to generate the MSD and the LSD, they can be combined into 1 Slice as observed from Fig.~\ref{Fig:ModifiedOA}.
-Therefore using this mapping method the resources within 1 Slice can be fully utilized, leading to a significant area reduction.
+The logic to generate the MSD and the LSD can be combined into one slice as observed from Fig.~\ref{Fig:ModifiedOA}.
+Therefore using this mapping method the resources within one slice can be fully utilized, leading to a significant area reduction.
 
@@
 \subsection{Performance Analysis}\label{subsec:OA_Performance}
-In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using behavioural descriptions based on 4:2 compressors (\texttt{OA\_behv}).
+In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using functional descriptions in Verilog based on 4:2 compressors (\texttt{OA\_behv}).
 In addition, we also include ripple carry adder (\texttt{RCA}) which uses conventional arithmetic, into the comparisons.
@@
 It can be seen that both designs with online arithmetic achieves relatively stable operating frequencies across a variety of operand word-lengths.
-This is as expected, because the critical path delay in the online adder is theoretically a fixed value and it is irrelevant to the operand precisions.
-In comparison, the rated frequency of the \texttt{RCA} drops drastically for larger word-lengths.
+This is as expected, because the critical path delay in the online adder is theoretically a fixed value independent of the operand precision.
+In comparison, the rated frequency of the \texttt{RCA} drops dramatically for larger word-lengths.
 It follows that both online adders outperform \texttt{RCA} for large word-lengths.
@@
 
-We also compare the resource usages of all three adder designs with respect to a variety of operand word-lengths.
+We also compare the resource usage of all three adder designs with respect to a variety of operand word-lengths.
 The results are presented in Fig~\ref{Fig:AdderArea}.
-We can see that in comparison to the original \texttt{OA\_behv}, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in Slices.
+We can see that in comparison to the original \texttt{OA\_behv}, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in slices.
 This is because the dedicated FPGA resources are fully utilized.
-However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of Slices.
+However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of slices.
 This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
@@
 Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication (to generate $x_{j+\delta+1}\cdot Y_{[j+1]}$ and $y_{j+\delta+1}\cdot X_{[j]}$ in Algorithm~\ref{Algorithm:OnlineMult}), shifting and other combinational logic blocks such as the selection function.
-Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 2 integer digits and 1 fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
+Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 1 integer digit and 1 fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
 Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
@@
 We address the first two design issues by providing an alternative online multiplication algorithm.
-Instead of simply implementing the unrolled format of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
-We notice that the online delay $\delta$ is employed in Algorithm~\ref{Algorithm:OnlineMult} because the input data is available in a digit serial fashion.
+Instead of simply implementing the unrolled version of Algorithm \ref{Algorithm:OnlineMult}, it can be optimized specifically for digit parallel operations.
+The online delay $\delta$ is employed in Algorithm~\ref{Algorithm:OnlineMult} because the input data is available in a digit serial fashion.
 Hence $\delta$ is used to accumulate enough input digits to generate the MSD of the result.
@@
 In each stage, the word-length of all signals also reduces from $(N+2+\delta)$ to $(N+2)$, as $\delta$ is not necessary for digit parallel operations.
-In addition, the $frac()$ function can be implemented only based on wire connections without using other logic resources.
+In addition, the $frac()$ function can be implemented only based on wire connections without using logic resources.
 
@@
 We now present an area efficient implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} on FPGAs.
-For example, the general structure diagram of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a), and the structure diagram of a single stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b) with the word-lengths of all signals labelled.
+The general structure of a 4-digit \texttt{OM} using the proposed algorithm is shown in Fig.~\ref{Fig:PMStructure}(a), and the structure of a single stage $j$ is shown in Fig.~\ref{Fig:PMStructure}(b) with the word-lengths of all signals labelled.
 Area optimizations can be performed on all modules.
-It can be seen that in each stage, an $N+2$-digit online adder is used to derive $W_{[j]}$.
+It can be seen that in each stage, an $(N+2)$ digit online adder is used to derive $W_{[j]}$.
 Our proposed online adder architecture can be employed.
-The selection logic takes 3 input digits (6 bits) and generate 1 output digit (2 bits).
+The selection logic takes 3 input digits (6 bits) and generates 1 output digit (2 bits).
 Hence it can be implemented using two 6-LUTs for each output bit.
@@
 	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.pdf}
-	\caption{(a) Structural diagram of a 4-digit online multiplier using the proposed algorithm.
+	\caption{(a) Structure of a 4-digit online multiplier using the proposed algorithm.
 (b) Structure of one stage.
@@
 The blocks that generate partial products $Xy_j$ can be incorporated into the online adder for further area reduction.
-In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, we notice that only 4 inputs per LUT are used.
-This leaves at least 2 available inputs per LUT.
-Originally in order to generate 1 digit partial product, 1 digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
-Instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all 6 LUT inputs.
+In the online adder structure as presented in Fig.~\ref{Fig:SliceNew}, we notice that only four inputs per LUT are used.
+This leaves at least two available inputs per LUT.
+Originally in order to generate one digit partial product, one digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
+Instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all six LUT inputs.
 Notice that this approach is only available for FPGAs with 6-LUTs.
@@
 
-The theoretical minimum resource uses of the proposed \texttt{OM} can be calculated as follows.
-In an $N$-digit \texttt{OM}, overall $(N-1)$ online adders are needed.
-According to Algorithm~\ref{Algorithm:OM_DigitParallel}, the word-length of each online adder is $(N+2)$-digit (2 integer digits and $N$ fractional digits).
-Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of Slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
+The resource usage of the proposed \texttt{OM} can be calculated as follows.
+In an $N$-digit \texttt{OM}, in total $(N-1)$ online adders are needed.
+According to Algorithm~\ref{Algorithm:OM_DigitParallel}, the word-length of each online adder is $(N+2)$-digit (two integer digits and $N$ fractional digits).
+Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
 Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and Slices used by the first stage, which is built without online adders.
@@
 \begin{eqnarray}\label{Eq:OMareaSlice}
-	OM\_{Slice} = (1+\left\lceil{\frac{N}{2}}\right\rceil)(N-1)+S_{S1}
+	OM\_{Slice} = \left(1+\left\lceil{\frac{N}{2}}\right\rceil\right)(N-1)+S_{S1}
 \end{eqnarray}
 
-\subsection{Structure Optimization for the MSD Half of the Results}
+\subsection{Structure Optimization for Half Precision Results}
 As discussed before, normally the multiplier is connected with other arithmetic operators in real applications.
-If the outputs of a multiplier is utilized for subsequent operations, and it is chosen to main the consistency of word-length between the I/Os of the system, then only the most significant half of the products are required.
+If the outputs of a multiplier is utilized for subsequent operations, and a consistent word-length is used throughout the system, then only the most significant half of the product is required.
 In a conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
@@
 For example, the modified structure diagram of a 4-digit \texttt{OM} is illustrated in Fig.~\ref{Fig:PMStructure_MSDhalf}(a).
-The word-length of all signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
-It can be seen that instead of keeping identical word-length throughout all stages, as shown in Fig.~\ref{Fig:PMStructure}, in the modified structure the signal word-lengths depend on the stage number $j$ and fewer bits of signals are needed for LSD stages.
+The word-length of signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
+It can be seen that instead of keeping identical word-length throughout the stages (in Fig.~\ref{Fig:PMStructure}), in the modified structure the signal word-lengths depend on the stage number $j$ and fewer bits of signals are needed for LSD stages.
 
 \subsection{Performance Analysis}
-Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the online multiplier based on behavioral descriptions (\texttt{OM\_behv}) against the proposed 2 types of multipliers, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
+Similar to the experiments as described in Section~\ref{subsec:OA_Performance}, we compare the direct RTL online multiplier (\texttt{OM\_behv}) against the proposed two types of multiplier, which are implemented to generate products with full precision (\texttt{OM\_full}) and half precision (\texttt{OM\_half}), respectively.
 In addition, we also compare the \texttt{OM} with the conventional binary arithmetic multiplier.
@@
 
-The comparison of area in terms of the cost of LUTs and the cost of Slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
+The comparison of area in terms of the cost of LUTs and the cost of slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
 The results are obtained from ISE 14.1 after mapping the design to the Virtex-6 FPGA.
 In comparison to \texttt{OM\_initial}, significant area savings have been obtained by the optimized design \texttt{OM\_full}.
-Specifically, the LUTs and Slice utilization drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
+Specifically, the LUTs and slice utilization drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
 
@@
 On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
-The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%$ to $55\%$ for Slices.
+The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%$ to $55\%$ for slices.
 
@@
 We also notice that there is an increasing gap between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
-This might because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a Slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
-Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is huge for large operand word-lengths.
+This is because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
+Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is hyperbole for large operand word-lengths.
 This also explains the fact that \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, as the critical path of both designs are identical in theory.

### 2014-05-29 FPT2014/bare_conf.tex
Change description of data

@@
 In this paper, we propose novel approaches to implement the key primitives of online arithmetic, adders and multipliers, efficiently on modern Xilinx FPGAs with 6-input LUTs and carry resources.
-We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ Slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
-
-% significant area savings and frequency speed-ups compared to a direction.
-
-%The performance of the proposed architectures are experimentally demonstrated
-
-%, they are targeting on FPGAs with 4-input LUTs, which are now gradually replaced by 6-input LUTs.
+We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
+Furthermore in comparison to standard arithmetic primitives, the area overheads of online operators drop from $8.41\times$ to $1.88\times$ for adders, and $8.11\times$ to $0.54\times$ for multipliers using our approach.
 
@@
 First, although there has been previous research into FPGA implementations of online arithmetic, this work only focused on online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
-Second, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with 2 LUTs within a Slice, such as the Altera Cyclone III \cite{AlteraCyclone} and Xilinx Spartan~3 series \cite{XilinxSpartan}.
-However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and 4 LUTs in a Slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+Second, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with two LUTs within a slice or a logic element (LE), such as the Xilinx Spartan~3 series \cite{XilinxSpartan} and the Altera Cyclone III \cite{AlteraCyclone}.
+However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and four LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
 Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for efficient implementation.
@@
 We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
-For online adders, our method achieves over $67\%$ Slice savings and $1.2\times$ frequency speed-ups in comparison to a direct implementation.
-For online multipliers, the LUTs and Slice utilization of the proposed new architecture drops over $2.4\times$ and $3.2\times$, with a frequency speed-up more than $1.5\times$ in comparison to a direct implementation.
-In summary, the main contributions of this paper are an efficient mapping of online adders and multipliers to modern FPGAs.
-(to be completed)
+For online adders, our method achieves over $67\%$ slice savings and $1.2\times$ frequency speed-ups in comparison to a direct implementation.
+The area overhead drops from up to $8.41\times$ to $1.88\times$ using the proposed online adder in comparison to the standard ripple-carry adder.
+For online multipliers, the LUTs and slice utilization of the proposed new architecture drops over $2.4\times$ and $3.2\times$, with a frequency speed-up more than $1.5\times$ in comparison to a direct implementation.
+When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$.
+This value drops to $1.84\times$ when using the proposed online multiplier.
+Furthermore, using the proposed structure can even achieve area savings of up to $55\%$ for half precision results in comparison to the standard multiplier.
+
+In summary, the main contributions of this paper are efficient methods to map online adders and multipliers to modern FPGAs. 
 % by fully utilizing the fast carry logic for .
@@
 For a given iteration $j$, the product digit $z_j$ is generated MSD-first through a selection function $sel()$.
-For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence \cite{Ercegovac_OnlineMult}.
-As radix 2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
-In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}) \cite{Oregon_OnlineNetwork}.
-Notice that the selection is based on two integer digits and one fractional digit of $W_{[j]}$.
-
+For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence.
+As the binary radix is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
+In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$ \cite{Ercegovac_OnlineMult}.
+%
 \begin{algorithm}[tbp]
@@
 However, directly applying this approach in the FPGAs could be less efficient.
-This is because there is no carry propagation between the 2 FAs within a 4:2 compressor, and the net delay between them can be large.
+This is because there is no carry propagation between the two FAs within a 4:2 compressor, and the net delay between them can be large.
 Instead, Kamp et al \cite{FPT09RA} and Hormigo et al \cite{ASAP09RA} described very similar mapping techniques for online adders with SD representations and CS representations, respectively.
-They share the common idea of using a maps the logic block (\texttt{LB}) within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
-In this case, the fast-carry logic in the FPGA can be employed, and the delay between the two FAs can be greatly reduced.
+They share the common idea of building the online adder based on the logic block (\texttt{LB}) as highlighted within the dotted circle in Fig.~\ref{Fig:PreviousWork}.
+In this case, the fast-carry logic in the FPGA can be employed, and the delay between the two 3:2 compressors can be greatly reduced.
 
@@
 However, we notice the major limitations of both approaches that they only target FPGAs with 4-input LUTs (4-LUT) and two LUTs within a logic slice, such as the Xilinx Spartan series and the Altera Cyclone series.
-This is naturally reasonable because one \texttt{LB} can be mapped to a single Slice.
+This is naturally reasonable because one \texttt{LB} can be mapped to a single slice.
 Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and four LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or wrong results.
@@
 The structure of a 4-digit online adder is given as an example in Fig.~\ref{Fig:ModifiedOA}.
-In this equivalent structure, the first FA in each 4:2 compressor is split into 2 parts, which only generate carry and sum respectively.
-In this case they can be mapped individually on 2 LUTs.
+In this equivalent structure, the first FA in each 4:2 compressor is split into two parts, which only generate carry and sum respectively.
+In this case they can be mapped individually on two LUTs.
 The second FA, which generates the outputs, is unchanged and can be implemented using the fast carry logic.
 
-%propose an alternative mapping method that targets on the Slice containing 4 LUTs such as the Xilinx Virtex series and all Xilinx 7 series FPGAs.
+%propose an alternative mapping method that targets on the slice containing 4 LUTs such as the Xilinx Virtex series and all Xilinx 7 series FPGAs.
 
@@
 Left: an example of 4-digit online adder.
-The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 Slice.
+The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 slice.
 Right: one LB.
@@
 	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FastCarry_New2.pdf}
-	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA Slice which contains four 6-LUTs. NC stands for ``Not Care''.}
+	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
 	%\vspace{-1ex}	
@@
 
-In this mapping approach, the area figures of the online adder in terms of the number of LUTs and Slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
 \begin{eqnarray}\label{Eq:OAareaLUT}
@@
 \begin{eqnarray}\label{Eq:OAareaSlice}
-	OA\_Slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
+	OA\_slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
 \end{eqnarray}
@@
 In addition, we also include ripple carry adder (\texttt{RCA}) which uses conventional arithmetic, into the comparisons.
-All designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1.
+While in our experiments all designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1, our methods can also be applied on other FPGAs with same slice architecture such as the Xilinx 7 series FPGAs.
 Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
@@
 It follows that both online adders outperform \texttt{RCA} for large word-lengths.
-Furthermore, our approach operates faster than \texttt{OA\_behv}; the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $1.20\times$ to $1.26\times$.
+Specifically, the frequency of \texttt{OA\_behv} is faster than \texttt{RCA} when $N\geqslant30$.
+In comparison, the proposed online adder is more efficient in performance, as it outperforms \texttt{RCA} for $N>16$.
+Furthermore, the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $1.20\times$ to $1.26\times$.
 
@@
   \centering
-  \subfigure[]{
+  \subfigure[Usage of LUTs]{
   \begin{minipage}{0.45\textwidth}
@@
   }
-  \subfigure[]{
+  \subfigure[Usage of slices]{
   \begin{minipage}{0.45\textwidth}
@@
   %\vspace{-3ex}
-  \caption{Area comparisons of different binary adder implementations with respect to a variety of operand word-lengths. (a) Usage of LUTs. (b) Usage of Slices.}
+  \caption{Area comparisons of different binary adder implementations with respect to a variety of operand word-lengths.}
   \label{Fig:AdderArea}
-  \vspace{-1ex}
+  \vspace{-2ex}
 \end{figure}
@@
 Second, the logic of each stage is complex as it involves operations such as online addition, digit-vector multiplication (to generate $x_{j+\delta+1}\cdot Y_{[j+1]}$ and $y_{j+\delta+1}\cdot X_{[j]}$ in Algorithm~\ref{Algorithm:OnlineMult}), shifting and other combinational logic blocks such as the selection function.
-Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs 1 integer digit and 1 fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
+Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs two integer digits and one fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
 Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
@@
 Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
-Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and Slices used by the first stage, which is built without online adders.
+Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and slices used by the first stage, which is built without online adders.
 
@@
 \begin{eqnarray}\label{Eq:OMareaSlice}
-	OM\_{Slice} = \left(1+\left\lceil{\frac{N}{2}}\right\rceil\right)(N-1)+S_{S1}
+	OM\_{slice} = \left(1+\left\lceil{\frac{N}{2}}\right\rceil\right)(N-1)+S_{S1}
 \end{eqnarray}
@@
 
-In comparison, the online multiplier offers the flexibility to simplify the structure corresponding to the required precision.
+In comparison, the \texttt{OM} offers the flexibility to simplify the structure corresponding to the required precision.
 This is possible because in an \texttt{OM}, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system.
@@
 In addition, we also compare the \texttt{OM} with the conventional binary arithmetic multiplier.
-The conventional multiplier is created using the Xilinx Core Generator with speed optimization~\cite{XilinxMult}, and it is implemented based on LUTs without DSPs.
+The conventional multiplier is created using the Xilinx Core Generator with speed optimization~\cite{XilinxMult}, and it is implemented based on LUTs without DSPs for a fairer comparison.
 
@@
 The results are obtained from ISE 14.1 after mapping the design to the Virtex-6 FPGA.
-In comparison to \texttt{OM\_initial}, significant area savings have been obtained by the optimized design \texttt{OM\_full}.
+In comparison to \texttt{OM\_behv}, significant area savings have been obtained by the optimized design \texttt{OM\_full}.
 Specifically, the LUTs and slice utilization drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
 
-In comparison to the \texttt{CoreGen} multiplier, the area overheads of \texttt{OM\_full} are between $48\%$ and $84\%$ for LUTs and up to $83\%$ for Slices.
-On the other hand, the \texttt{OM\_half} achieves area reductions for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
+In comparison to the \texttt{CoreGen} multiplier, the area overhead of online multipliers drops significantly when transferring to the proposed new structure.
+In order to generate full precision product, the area overheads of \texttt{OM\_behv} against \texttt{CoreGen} are $3.94\times\sim5.82\times$ for LUTs, and $3.58\times\sim8.11\times$ for slices, respectively.
+Using the proposed structure \texttt{OM\_full} the area overheads drop to $1.48\times\sim1.83\times$ for LUTs and up to $1.84\times$ for slices.
+Furthermore, if only half precision result is required, \texttt{OM\_half} is more area efficient for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
 The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%$ to $55\%$ for slices.
@@
   \centering
-  \subfigure[]{
+  \subfigure[Usage of LUTs]{
   \begin{minipage}{0.47\textwidth}
@@
   }
-  \subfigure[]{
+  \subfigure[Usage of slices]{
   \begin{minipage}{0.47\textwidth}
@@
   %\vspace{-3ex}
-  \caption{Area comparisons of different types of binary multipliers. (a) Usage of LUTs. (b) Usage of Slices}
+  \caption{Area comparisons of different types of binary multipliers.}
   \label{Fig:OMArea}
@@
 
-We also check the rated frequencies of all four types of multipliers for a variety of operand word-lengths.
-The frequency values are still obtained from the post place and route timing reports.
-Notice that input stimulus to the circuits are randomly sampled from a uniform distribution of $N$-digit numbers.
-The results are plotted in Fig.\ref{Fig:OM_Freq}, from which we can see that in comparison to \texttt{OM\_behv}, our proposed architectures achieve frequency speed-ups varying from $1.49\times$ to $1.98\times$.
+We also check the rated frequencies of all multipliers for a variety of operand word-lengths.
+The frequency values are plotted in Fig.~\ref{Fig:OM_Freq}, which are still obtained from the post place and route timing reports.
+In Fig.~\ref{Fig:OM_Freq} we see that in comparison to \texttt{OM\_behv}, our proposed architectures achieve frequency speed-ups varying from $1.49\times$ to $1.98\times$.
 
-We also notice that there is an increasing gap between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
+Notice that there is an increasing gap between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
 This is because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
@@
 For instance, Fig.~\ref{Fig:PM_MRE} demonstrates the \texttt{MRE} values of the 8-digit multipliers.
+The results are from post place and route simulations, and the input stimulus are randomly sampled from a uniform distribution of 8-digit numbers.
 We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operate faster than \texttt{CoreGen} without the occurrence of timing errors.
@@
  % \vspace{-1ex}
-  \caption{Mean relative errors seen at the outputs of different types of binary multipliers, when clocked with faster-than-rated frequencies.}
+  \caption{Mean relative errors seen at the outputs of different types of 8-digit binary multipliers, when clocked with faster-than-rated frequencies.}
   \label{Fig:PM_MRE}
@@
 In this paper, we initially describe a novel methodology that can efficiently map digit parallel online adders onto FPGAs.
-The proposed mapping method targets modern FPGAs, which have 6-input LUTs and 4 LUTs in a Slice, and fully utilizes the built-in carry resources.
-We have demonstrated analytically and experimentally that the proposed architecture is both area and performance efficient in comparison to the original design.
+The proposed mapping method targets modern FPGAs, which have 6-input LUTs and four LUTs in a slice, and fully utilizes the built-in carry resources.
+We have demonstrated  that the proposed architecture is both area and performance efficient in comparison to the original design.
 We then propose an area efficient FPGA implementation of the online multiplier, which is specifically optimized for digit parallel operations.

### 2014-06-03 FPT2014/bare_conf.tex
Draft 2nd version

@@
 In this paper, we propose novel approaches to implement the key primitives of online arithmetic, adders and multipliers, efficiently on modern Xilinx FPGAs with 6-input LUTs and carry resources.
-We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
+We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ slice savings and $1.5\times$ speed-ups for multipliers.
 Furthermore in comparison to standard arithmetic primitives, the area overheads of online operators drop from $8.41\times$ to $1.88\times$ for adders, and $8.11\times$ to $0.54\times$ for multipliers using our approach.
@@
 This value drops to $1.84\times$ when using the proposed online multiplier.
-Furthermore, using the proposed structure can even achieve area savings of up to $55\%$ for half precision results in comparison to the standard multiplier.
+In addition, using the proposed structure can even achieve area savings of up to $55\%$ for half precision results in comparison to the standard multiplier.
 

### 2014-06-03 TCAD2014/TCAD14.tex
TCAD14 initial commit

%
\documentclass[journal]{IEEEtran}

\usepackage{amsfonts,latexsym}

\ifx\pdfoutput\undefined
\usepackage{graphicx}
\else
\usepackage[pdftex]{graphicx}
\fi

\usepackage{epstopdf}
\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{multirow}

\usepackage{algorithm}
\usepackage{algpseudocode}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\newtheorem{proposition}{Proposition}[section]
\newtheorem{observation}{Observation}[section]
\newtheorem{definition}{Definition}[section]

\begin{document}

\title{Title}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{ }

%\author{Michael~Shell,~\IEEEmembership{Member,~IEEE,}
%        and~Jane~Doe,~\IEEEmembership{Life~Fellow,~IEEE}% <-this % stops a space
%\thanks{M. Shell is with the Department of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta, GA, 30332 USA.}% <-this % stops a space
%\thanks{J. Doe and J. Doe are with Anonymous University.}% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised December 27, 2012.}}

% note the % following the last \IEEEmembership and also \thanks - 
% these prevent an unwanted space from occurring between the last author name
% and the end of the author line. i.e., if you had this:
% 
% \author{....lastname \thanks{...} \thanks{...} }
%                     ^------------^------------^----Do not want these spaces!
%
% a space would be appended to the last name and could cause every name on that
% line to be shifted left slightly. This is one of those "LaTeX things". For
% instance, "\textbf{A} \textbf{B}" will typeset as "A B" not "AB". To get
% "AB" then you have to do: "\textbf{A}\textbf{B}"
% \thanks is no different in this regard, so shield the last } of each \thanks
% that ends a line with a % and do not let a space in before the next \thanks.
% Spaces after \IEEEmembership other than the last one are OK (and needed) as
% you are supposed to have spaces between the names. For what it is worth,
% this is a minor point as most people would not even notice if the said evil
% space somehow managed to creep in.

% The paper headers
\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
% The only time the second header will appear is for the odd numbered pages
% after the title page when using the twoside option.
%

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}

\end{abstract}

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}

\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
This paper is collocated into the reconfigurable computing context. An important problem into the reconfigurable computing is to analyse the error propagation when the circuit ``under test'' is setted with values of the frequency too high or in disagree with the values of the delay. The paper investigates the propagation of the error caused by a timing violation into a digital online multiplier. \\

...................\\

This work starts from the results obtained in a previus work on the Radix-2 Digit-parallel Online Multiplier (see \cite{onlinearith}).\\
 In \cite{onlinearith} the autors have provided methodologies to implement a parallel version of the online multiplier and they have proposed a probabilistic model describing the propagations of the error caused by timing violation conditions. They also backed up the models with experimental results from an image processing application demostrating that this novel design methodology can lead to substantial performance benefits compared to the design method using conventional arithmetic. The purpose of this paper is to provide a numerical model estimating the error on the online multiplier and a model to estimate the probability of timing violation in order to provide an ``a priori'' estimation for the error expectation for different values of the circuit parameters (frequency, number of digits, online delay, etc).  \\
In this paper we provide a formal model of the Overclocking Error for the radix-2 digit-parallel Online Multiplier. We also proved a mathematical '``support'' to the experimental results obtained in  \cite{onlinearith} and, in particular, we estimate the expectation of the overclocking error for these results. We provide a model describing the probablity of timing violation as ``chain start probability'' and ``chain rule probability'' representing the probability that a chain starts during the operation and the probability that a chain starts $\&$ perpetuals for a fixed number of digits, respectively.  \\

\section{Background}\label{Sec:Background}

Error models............(probably only \cite{onlinearith})..................

\subsection{Radix-2 Digit-parallel Online Multiplier}

Originally online arithmetic was designed for digit-serial operation. In order to generate the first output digit, $\delta$ digits of inputs are required. $\delta$ is known as the online delay, which is a constant, independent of the precision in a given operation. For ease of discussion, the input to our circuit is normalized to a fixed point number in the range $(-1,1)$. Based on this premise, the online representations of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}) for $j\in[-\delta,N-1]$ and $r$ denotes the radix.

\begin{eqnarray}\label{Eq:Online_Operands}
\footnotesize
  X_{[j]}=\sum_{i=1}^{j+\delta}x_ir^{-i},~Y_{[j]}=\sum_{i=1}^{j+\delta}y_ir^{-i},~Z_{[j]}=\sum_{i=1}^{j}z_ir^{-i}
\normalsize
\end{eqnarray}

MSD-first operation in online arithmetic is possible because they adopt a redundant number system, in which each digit is represented with a redundant digit set $\{-a, \cdots,-1, 0, 1, \cdots, a\}$ where $a\in[r/2,r-1]$. Due to the redundancy, the MSDs of the result can be estimated only based on partial information of the inputs and then the value of the number can be revised by the following digits.

Typically the online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm \ref{Algorithm:OnlineMult} where both inputs and outputs are $N$-digit number as represented in~(\ref{Eq:Online_Operands}). For a given iteration $j$, the product digit $z_j$ is generated through a selection function $sel()$. For the radix $r$ and a chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence. As radix-2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$. In this case we have $\delta=3$, and $sel()$ is given by (\ref{Eq:SelFunc_OM}), from which it can be seen that the decision is made only based on 1 integer bit and 1 fractional bit of $W_{[j]}$.
\begin{equation}\label{Eq:SelFunc_OM}
\begin{array}{ll}
  sel(W_{[j]})=
    1 & if \ W_{[j]} \geq \frac{1}{2} \\
    0 &  if  \ -\frac{1}{2}\leq W_{[j]}<\frac{1}{2} \\
    \overline{1} & if \ W_{[j]}<-\frac{1}{2}
\end{array}
\end{equation}

\vspace{0.5cm}

\begin{algorithm}{\bf Online Multiplication} \label{Algorithm:OnlineMult}
  \begin{algorithmic}[1]
 \State  {\bf Initialization:}   $X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$
  \State  {\bf Recurrence:}   $for~~ j=-\delta,~-\delta+1,~\cdots,~N-1 ~~do$
 \State  {\bf Compute:}    \label{Eq:OnlineMult_General}
\State  $    H_{[j]}  = r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)$\label{Eq:OnlineMult_H}
      \State   $  W_{[j]}    = P_{[j]} + H_{[j]}$
     \State    $  z_j        =  sel(W_{[j]})$
    \State     $  P_{[j+1]}  =  r\left(W_{[j]}-z_j\right)$\label{Eq:OnlineMult_P}
  \end{algorithmic}
\end{algorithm}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=7cm,height=4.5cm]{./Figures/circuit}
\caption{  . . . . . . . . . . . . }\label{circuit}
\end{center}
\end{figure}

..........................................\\

Let $\mu_{OM}$ denote the worst-case delay of an OM. It follows that if the clock period $T_S$ is greater than $\mu_{OM}$, correct results will be sampled. If, however, faster-than-rated sampling frequencies are applied such that $T_S<\mu_{OM}$, timing violations might happen and intermediate results will be sampled, potentially generating errors. For a given $T_S$, the maximum length of error-free propagation is described by (\ref{Eq:MaxChainLength}) where $f_S$ denotes the sampling frequency. We always ensure that the first digit of the product will be generated correctly, i.e. $b>\delta$.
%
\begin{eqnarray}\label{Eq:MaxChainLength}
\footnotesize
  b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
  %b:=\left\lceil T_S/{\mu} \right\rceil=\left\lceil {1}/{(\mu\cdot f_S)}\right\rceil
\normalsize
\end{eqnarray}
%
We now determine when this timing constraint is not met and the size of error in this case.\\

\section{Probability of Timing Violations}\label{section:Prob}

For an $N$-digit OM, let a propagation chain be generated at stage $S_{\tau}$ with the length of $d(\tau)$ digits, then the stage number $\tau$ is bounded by (\ref{Eq:Bound_GenChain}). The presence of timing violation requires $d(\tau)>b$. Besides, the chain cannot propagate over $S_{N-1}$. Thus the bound of parameter $d(\tau)$ is given by (\ref{Eq:Bound_ChainLength}).

\begin{equation}\label{Eq:Bound_GenChain}
 -\delta\leq \tau\leq N-1-b=\tau_{max}
\end{equation}

\begin{equation}\label{Eq:Bound_ChainLength}
  b<d(\tau)\leq N-1-\tau
\end{equation}
%

\noindent However, the actual length of a ``carry'' chain is dependent upon input patterns. We then examine the relationship between $d(\tau)$ and the inputs that corresponds to the generation, propagation and annihilation of this carry chain.  Let the specific input pattern of stage $S_{\tau}$ be represented by $C(\tau)$, which can be classified into four types, as listed in (\ref{Eq:class}).

\begin{equation}\label{Eq:class}
\footnotesize
    C(\tau)= \left\{ \begin{array}{llll}
        Case 1 & (C_1(\tau)): & x_{\tau +\delta+1}=0, & y_{\tau +\delta+1}=0\\
        Case 2 & (C_2(\tau)): & x_{\tau +\delta+1}\neq 0, & y_{\tau +\delta+1}\neq 0\\
        Case 3 & (C_3(\tau)): & x_{\tau +\delta+1}\neq 0, & y_{\tau +\delta+1}=0\\
        Case 4 & (C_4(\tau)): & x_{\tau +\delta+1}=0, & y_{\tau +\delta+1}\neq 0
\end{array} \right.
\normalsize
\end{equation}

\noindent The classification is based on whether a digit is zero, as all internal signals are reset to zero initially. Under the assumption that all digits are mutually independent and uniformly sampled from the digit set  $\{\overline{1},0,1\}$ as given in Section~\ref{Sec:Background}, the probabilities of $C_1,...,C_4$ are given in (\ref{Eq:probcaser}).

\begin{equation}\label{Eq:probcaser}
\begin{array}{ll}
C_1(\tau): \frac{1}{(2a+1)^2}, &  C_2(\tau): \frac{(2a+1)^2-2(a+1)-1}{(2a+1)^2}\\
C_3(\tau):\frac{a+1}{(2a+1)^2}, & C_4(\tau):  \frac{a+1}{(2a+1)^2}
\end{array}
\end{equation}

Notice that no carry chain will be generated under Case~1, because $P_{[\tau+1]}=0$. In other words, a chain could be generated if one of  the cases $C_2(\tau)$,...,$C_4(\tau)$ occur. In this case we provide the following propositions which describe the probabilities of timing violations.

\begin{proposition} (Chain rule probability)\\
Let $Pr_{\tau,d(\tau )}$ denote the probability that a carry chain start at stage $S_{\tau}$, and it have lenght $d(\tau )$, $\forall \tau \in [-\delta , N-1-b]$, $\forall d(\tau) \in [b , N-1-\tau]$, then it is given by (\ref{Eq:PChainRule})

\begin{equation}\label{Eq:PChainRule}
\footnotesize
Pr_{\tau,d(\tau )} =\left(\frac{1}{(2a+1)^2}\right)^\tau \left(\frac{(2a+1)^2-1}{(2a+1)^2}\right)^{d(\tau )}
\normalsize
\end{equation}

\noindent Proof:\\

Let $E_2$ be the event ``the carry chain is generated at stage $S_{\tau}$ and it have length $d(\tau )$'', we have

\begin{equation}
Pr_{\tau,d(\tau )} = Pr(E_2)=  \underbrace{Pr(C_1)\cdots  Pr(C_1)}_{\tau -1 \ times}\cdot
\end{equation}
$$
\cdot  \underbrace{ Pr(C_2 \ or \ C_3   \ or \ C_4)\cdots Pr(C_2  \ or \   C_3   \ or \   C_4)}_{d(\tau) \  times}   Pr(C_1)$$

that is

\begin{equation}\label{Eq:PChainRule_Exp}
\scriptsize
Pr_{\tau,d(\tau )} = Pr(C_1)^{\tau -1} Pr(C_2 \cup C_3 \cup C_4)^{d(\tau )} Pr(C_1)
\normalsize
\end{equation}

Substituting (\ref{Eq:probcaser}) into \ref{Eq:PChainRule_Exp} yields (\ref{Eq:PChainRule_raw}).

\begin{equation}\label{Eq:PChainRule_raw}
\scriptsize
Pr_{\tau,d(\tau )}= \left(\frac{1}{(2a+1)^2}\right)^{\tau -1} \left(\frac{(2a+1)^2-1}{(2a+1)^2}\right)^{d(\tau )} \frac{1}{(2a+1)^2}
\normalsize
\end{equation}

Simplifying (\ref{Eq:PChainRule_raw}) will give (\ref{Eq:PChainRule}).

\hspace{7cm} $\clubsuit$
\vspace{1ex}

\end{proposition}

For all possible values of $\tau$ and $d(\tau)$, the possibility that timing violaions happen is given by $Pr$ in (\ref{Eq:Prob_timingViol}). According to (\ref{Eq:Bound_GenChain}) and (\ref{Eq:Bound_ChainLength}), the ranges in which the parameters $\tau$ and $d(\tau)$ are defined depend upon the value of the swamping period $T_S$. Hence $Pr$ is a function of $T_S$.

\begin{equation}\label{Eq:Prob_timingViol}
Pr= \sum_\tau \sum_{d(\tau)} Pr_{\tau,d(\tau )}
\end{equation}

\section{Error Estimation}

In the presence of timing violation, multiple chains might not be correctly propagated in the online multiplication, resulting in overclocking errors generated from LSDs. Let $z_i$ and ${z_i}'$ denote the correct value and the actual value of the output digit at the stage $S_i$, respectively. Then we have ${z_i}'=z_i+\varepsilon_i$ where $\varepsilon_i$ is referred to as the overclocking error. We now locate the first output digit $z_{\lambda}$ that contains error. For a given $T_S$ and a minimum value of $\tau$ such that $d(\tau)_{max}>b$, we have $\lambda=\tau+d(\tau)_{max}+1$ for chain annihilation.
%
%. Let us consider the first chain that timing violation may occur, i.e. $d(\tau)_{max}>b$, denote that it annihilates at $S_{\lambda}$ where $\lambda=\tau+d_{max}(\tau)-1$. Therefore overclocking errors may happen from digit $\lambda$ to digit $N-1$ of the result.
%
As such, the overclocking error can be expressed by (\ref{Eq:ErrorMagnitude})

%, where $z_i$ and ${z_i}'$ denote the correct value and the actual value of the output digit of $S_i$, separately, and $\varepsilon_i\in\{\pm2^{-i},\pm2^{-i+1}\}$ since $z$ is represented using digit set $\{\overline{1},0,1\}$.
%
\begin{eqnarray}\label{Eq:ErrorMagnitude}
\scriptsize
 \left| \varepsilon\right|= \left|\sum_{j=\lambda}^{N} r^{-j}\varepsilon_j\right|
\normalsize
\end{eqnarray}

We would like to investigate the statistical characteristics of the $\varepsilon$. In general, the distribution of $\varepsilon$ can be obtained from the convolution of variable $\varepsilon_j$ where $j\in[\lambda,N]$. Each variable $\varepsilon_j$ is sum of uniform iid variables with mean zero, therefore its mean is zero and the mean of $\varepsilon$ is zero as well.

Let $v\varepsilon$ and $v\varepsilon_j$ denote the variances of variable $\varepsilon$ and $\varepsilon_j$, respectively. We can form the relationship between them as given in (\ref{Eq:VarianceErrorMagnitude}) based on (\ref{Eq:ErrorMagnitude}).

\begin{eqnarray}\label{Eq:VarianceErrorMagnitude}
\scriptsize
	v\varepsilon=\sum_{j=\lambda}^{N} r^{-2j}v\varepsilon_j
\normalsize
\end{eqnarray}

Normally for a given algorithm, in this case the Algorithm~\ref{Algorithm:OnlineMult}, the value of $\varepsilon_j$ can be determined based on the inputs, which are uniformly distributed with the digit set $\{\overline{a},\cdots,0,\cdots,a\}$. Hence for a single digit of inputs $X_{[j]}$ and $Y_{[j]}$, its variance can be denoted by $v\varepsilon^{in}$, which is a fixed value with respect to a given value of $a$. Let the variances of the input signals $X_{[j]}$ and $Y_{[j]}$ be denoted by $v\varepsilon^y_j $ and $ v\varepsilon^x_j$, respectively. Then we have (\ref{Eq:var_XY}) according to (\ref{Eq:Online_Operands}).

\begin{equation}\label{Eq:var_XY}
{v\varepsilon}^y_j = {v\varepsilon}^x_j =\sum_{i=1}^{j+\delta} r^{-2i} v\varepsilon^{in}
\end{equation}

In Algorithm~\ref{Algorithm:OnlineMult}, the variances of the input data propagate through for all iterations. For a single iteration $j$, we can calculate $v\lambda_j$ based on $v\varepsilon^y_j $ and $ v\varepsilon^x_j$. For example initially the variance of $H_{[j]}$ is given by (\ref{Eq:step4var}). 
%which is then used to generate $W_{[j]}$ with the variance given in ().

\begin{equation}\label{Eq:step4var}
{v\varepsilon}^H_j =r^{-2\delta}(v\varepsilon^{in}  v\varepsilon^y_{j+1} +v\varepsilon^{in}  v\varepsilon^x_j) 
\end{equation}

This value propagates throughout the entire iteration and finally we have the value of $v\varepsilon_j$ in (\ref{Eq:varerror}).

\begin{equation}\label{Eq:varerror}
v\varepsilon_j=r^2 \left( r^{-2\delta}\cdot {v\varepsilon}^H_j \right)
\end{equation}

Combining (\ref{Eq:step4var}) and (\ref{Eq:varerror}) yields

\begin{equation}\label{Eq:varerror_final}
v\varepsilon_j=r^2 \left( r^{-2\delta} \left( v\varepsilon^{in}  v\varepsilon^y_{j+1} +v\varepsilon^{in}  v\varepsilon^x_j \right) \right).
\end{equation}

Finally, (\ref{Eq:varerror_final}) can be used to derive the expression of $v\varepsilon$ in (\ref{Eq:varfinal}) according to (\ref{Eq:VarianceErrorMagnitude}). Notice that this expression forms the relationship between the variance of overclocking error and the given input distribution.

\begin{equation}\label{Eq:varfinal}
\begin{array}{l}
v\varepsilon =  \mathcal{F}(T_S, \mu, v\varepsilon^{in}, \delta)\\
=\sum_{k=\lambda}^{N}r^{-2k} \left( r^{2(1-\delta)} \left(v\varepsilon^{in}    v\varepsilon^y_{k+1} +v\varepsilon^{in}   v\varepsilon^x_k\right)\right)
\end{array}
\end{equation}

\section{Model Verification with FPGA results}

In this Section, we compare the proposed models for both the probability and the magnitude of overclocking errors with the experimental results from FPGAs. In the verification, we choose the redundant digit set $\{\overline{1},0,1\}$, which is most commonly used for binary redundant representations.

\subsection{Verification of Models for Error Probability}
We initially verify the models for the probability of timing violations. With the usage of the redundant digit set $\{\overline{1},0,1\}$, we have $a=1$. Substituting this in (\ref{Eq:PChainRule}) yields (\ref{Eq:OMerrorProb}).

\begin{equation}\label{Eq:OMerrorProb}
 \quad Pr_{\tau,d(\tau )} =\left(\frac{1}{9}\right)^\tau \left(\frac{8}{9}\right)^{d(\tau )} 
\end{equation}

Combining (\ref{Eq:OMerrorProb}) and (\ref{Eq:Prob_timingViol}) we obtain the values of the probability of timing violations with respect to a variety of sampling period $T_S$. The results of an 8-digit OM are shown in Fig.~\ref{Fig:ProbTimingViol}. For comparison, we also plot the results obtained from a Virtex-6 FPGA, and the data are obtained from post place-and-route simulations. It can be seen that the modelled probability values match well with the experimental results.

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=9cm,height=4.5cm]{./Figures/probTimingViolationFPGA.eps}
\caption{ Probability of timing violation for $N=8$ and $\delta=3$ }
\label{Fig:ProbTimingViol}
\end{center}
\end{figure}

\subsection{Verification of Models for Error Magnitude}
We then verify the proposed models for the estimation of timing errors. Fig.~\ref{FigerrorC} shows the distribution of the error $\varepsilon$ on the FPGA results of the Algorithm 1 with input data uniformly distributed into the digit set $\{\overline{1},0,1\}$. \\

\begin{figure}[tbp]
	\centering
	\includegraphics[width=8cm,height=5cm]{./Figures/FigerrorC}
\caption{Distribution of overclocking errors with respect to a variety of sampling period. The Xlable should be ``Sampling period'', which varies from 2ns to 3.5ns, and the Ylabel is ``Error Values''. }
	\label{FigerrorC}

\end{figure}

Several slice through Fig.~\ref{FigerrorC} are presented in Fig.~\ref{Fig:gaussianOnlinedistr} for different sampling period values and the corresponding variances of overclocking errors. We observe that the profile of the error distribution changes as the value of the sampling period changes, and the width of the bell changes as well also (see Fig.~\ref{Fig:gaussianOnlinedistr}). The value of the mean is zero for all the values of the sampling period, while the variance of the distribution changes as the sampling period changes. In particular, the values of the variance decrease as the sampling period increases in agreement with the information provided by the values of the probability of timing violation.\\

\begin{figure}[tbp]
\centering
	\includegraphics[width=9cm,height=6cm]{./Figures/gaussianOnlinedistr}
	\caption{Several slice through Fig.~\ref{FigerrorC} that shows error distribution with respect to a variety of sampling periods and the corresponding variances of overclocking error. The results are obtained from experiments.}
	\label{Fig:gaussianOnlinedistr}
\end{figure}

We have compared these experimental results with the results provided by the model defined in (\ref{Eq:varfinal}). The Figure \ref{Error_Function_Spline_experiment} shows the curve provided by the model (blue line) and the experimental results (red stars). It can be seen that the modelled results are close to the experimental results.

%the average of the values of the error obtained by comparing the two different values for each value of the sampling period is the $O(10^{-3})$. \\

\begin{figure}[tbp]
\begin{center}
\includegraphics[width=8cm,height=5cm]{./Figures/Error_Function_Spline_experiment}
\caption{Variances of overclocking errors. The results are obtained from the proposed models (blue line) and the experiments (red stars). (Legend and xylabels to be added.) }\label{Error_Function_Spline_experiment}
\end{center}
\end{figure}

%\noindent The {\bf Expectation of Overclocking Error} is also function of the sampling period and it is obtained by combining the values of $Pr$ and $\varepsilon$ as in (\ref{eovc}).

%\begin{equation}\label{eovc}
%E_{ovc}(T_S)= Pr(T_S) \cdot  v(T_S)
%\end{equation}

%\section*{Acknowledgment}

% Can use something like this to put references on a page
% by themselves when using endfloat and the captionsoff option.
\ifCLASSOPTIONcaptionsoff
  \newpage
\fi

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{1}

\bibitem{onlinearith} Datapath synthesis for overclocking: Online Arithmetic for Latency-Accuracy Trade-offs.
\bibitem{convol} J. B. Uspensky, Introduction to Mathematical Probability (New York: McGraw-Hill, 1937)
\bibitem{ross} Ross, Introduction to Probability Models, University of Southern California - Los Angeles (CA), 2010 ELSEVIER
\bibitem{spline} C. de Boor, A Practical Guide to Splines, Springer-Verlag, 1978.
\bibitem{kendall} Kendall E. Atkinson, On the order of convergence of natural cubic spline interpolation, SIAM Journal on Numerical Analysis, Vol 5 No 1, 1968

\bibitem{IEEEhowto:kopka}
H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

\end{thebibliography}

% biography section
% 
% If you have an EPS/PDF photo (graphicx package needed) extra braces are
% needed around the contents of the optional argument to biography to prevent
% the LaTeX parser from getting confused when it sees the complicated
% \includegraphics command within an optional argument. (You could create
% your own custom macro containing the \includegraphics command to make things
% simpler here.)
%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
% or if you just want to reserve a space for a photo:

%\begin{IEEEbiography}{Michael Shell}
%Biography text here.
%\end{IEEEbiography}

% if you will not have a photo at all:
%\begin{IEEEbiographynophoto}{John Doe}
%Biography text here.
%\end{IEEEbiographynophoto}

% You can push biographies down or up by placing
% a \vfill before or after them. The appropriate
% use of \vfill depends on what kind of text is
% on the last page and whether or not the columns
% are being equalized.

%\vfill

% Can be used to pull up biographies so that the bottom of the last one
% is flush with the other column.
%\enlargethispage{-5in}

\end{document}

### 2014-06-03 TCAD2014/TCAD14.tex
add original stuff from DAC paper

@@
 % The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~11, No.~4, December~2012}%
+\markboth{Journal name,~Vol.~xx, No.~x, December~2014}%
 {Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Journals}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-%
 
@@
 
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
 \begin{abstract}
@@
 
-% Note that keywords are not normally used for peerreview papers.
 \begin{IEEEkeywords}
-
+Keywords
 \end{IEEEkeywords}
@@
 
-\section{Background}\label{Sec:Background}
+\section{Background: Online Arithmetic}\label{Sec:Background}
+\subsection{Key Features of Online Arithmetic}
 
-Error models............(probably only \cite{onlinearith})..................
-
-\subsection{Radix-2 Digit-parallel Online Multiplier}
-
-Originally online arithmetic was designed for digit-serial operation.
-In order to generate the first output digit, $\delta$ digits of inputs are required.
-$\delta$ is known as the online delay, which is a constant, independent of the precision in a given operation.
-For ease of discussion, the input to our circuit is normalized to a fixed point number in the range $(-1,1)$.
-Based on this premise, the online representations of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}) for $j\in[-\delta,N-1]$ and $r$ denotes the radix.
-
+Online arithmetic has been widely used in numerous applications such as signal processing and control algorithms [xxx].
+Online arithmetic was originally designed for digit serial operation, as illustrated in Fig xx.
+It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required, where $\delta$ is called the ``online delay''.
+Normally $\delta$ a small constant, which is independent of the precision.
+For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$.
+Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (xx), where $j\in[-\delta,N-1]$ and $r$ denotes the radix [xxx].
 \begin{eqnarray}\label{Eq:Online_Operands}
@@
 
-MSD-first operation in online arithmetic is possible because they adopt a redundant number system, in which each digit is represented with a redundant digit set $\{-a, \cdots,-1, 0, 1, \cdots, a\}$ where $a\in[r/2,r-1]$.
-Due to the redundancy, the MSDs of the result can be estimated only based on partial information of the inputs and then the value of the number can be revised by the following digits.
+MSD first operation is possible only if a redundant number system is used.
+Normally there are two most commonly used redundant number representations: carry-save (CS) [xxx] and signed-digit (SD) [xx].
+With SD representation, each digit is represented using a redundant digit set $\{-a,\cdots,-1,0,1,\cdots,a\}$ where $a\in[r/2,r-1]$.
+In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots, r−1\}$.
+Thus a standard number corresponds to several possible redundant representations.
+For example, the binary number $0.011$ can be represented in SD form as 0.111, 0.101 or 0.011 among many other possible representations.
+Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
+Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.
 
-Typically the online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm \ref{Algorithm:OnlineMult} where both inputs and outputs are $N$-digit number as represented in~(\ref{Eq:Online_Operands}).
+\subsection{Binary Online Addition}
+
+Adders serve as a critical building block for arithmetic operations.
+To perform digit-parallel online addition, a redundant adder can be used directly.
+The structure of an online adder where all signals represented with SD numbers of digit set $\{−1,0,1\}$ is shown in Fig.
+xxx.
+The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA).
+A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
+As labelled in Fig.
+xxx, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products [xx].
+
+\subsection{Binary Online Multiplication}
+
+Multiplication is another key arithmetic operator.
+Typically, online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm \ref{Algorithm:OnlineMult} where both inputs and outputs are $N$-digit number as represented in~(\ref{Eq:Online_Operands}).
 For a given iteration $j$, the product digit $z_j$ is generated through a selection function $sel()$.
@@
 In this case we have $\delta=3$, and $sel()$ is given by (\ref{Eq:SelFunc_OM}), from which it can be seen that the decision is made only based on 1 integer bit and 1 fractional bit of $W_{[j]}$.
-\begin{equation}\label{Eq:SelFunc_OM}
-\begin{array}{ll}
-  sel(W_{[j]})=
-    1 & if \ W_{[j]} \geq \frac{1}{2} \\
-    0 &  if  \ -\frac{1}{2}\leq W_{[j]}<\frac{1}{2} \\
-    \overline{1} & if \ W_{[j]}<-\frac{1}{2}
-\end{array}
-\end{equation}
-
-\vspace{0.5cm}
 
@@
 \end{algorithm}
+
+\begin{equation}\label{Eq:SelFunc_OM}
+\begin{array}{ll}
+  sel(W_{[j]})=
+    1 & if \ W_{[j]} \geq \frac{1}{2} \\
+    0 &  if  \ -\frac{1}{2}\leq W_{[j]}<\frac{1}{2} \\
+    \overline{1} & if \ W_{[j]}<-\frac{1}{2}
+\end{array}
+\end{equation}
 

### 2014-06-05 TCAD2014/TCAD14.tex
add case study

@@
 \usepackage{multirow}
+\usepackage{subfigure}
 
@@
 
-Online arithmetic has been widely used in numerous applications such as signal processing and control algorithms [xxx].
-Online arithmetic was originally designed for digit serial operation, as illustrated in Fig xx.
+Online arithmetic has been widely used in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
+Online arithmetic was originally designed for digit serial operation, as illustrated in Fig.~\ref{Fig:OnlineDataFlow}.
 It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required, where $\delta$ is called the ``online delay''.
@@
 For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$.
-Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (xx), where $j\in[-\delta,N-1]$ and $r$ denotes the radix [xxx].
+Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix~\cite{Ercegovac_Book}.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.pdf}
+  %\vspace{-4ex}
+  \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
+  %\vspace{-1ex}
+  \label{Fig:OnlineDataFlow}
+\end{figure}
+%
 \begin{eqnarray}\label{Eq:Online_Operands}
@@
 MSD first operation is possible only if a redundant number system is used.
-Normally there are two most commonly used redundant number representations: carry-save (CS) [xxx] and signed-digit (SD) [xx].
+Normally there are two most commonly used redundant number representations: carry-save (CS)~\cite{CSadder}  and signed-digit (SD)~\cite{RedundantNumber}.
 With SD representation, each digit is represented using a redundant digit set $\{-a,\cdots,-1,0,1,\cdots,a\}$ where $a\in[r/2,r-1]$.
-In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots, r−1\}$.
+In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots,r-1\}$.
 Thus a standard number corresponds to several possible redundant representations.
-For example, the binary number $0.011$ can be represented in SD form as 0.111, 0.101 or 0.011 among many other possible representations.
+For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.
+
 Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
@@
 
-\subsection{Binary Online Addition}
+\subsection{Binary Online Addition}\label{subsec:OnlineAdder}
 
@@
 To perform digit-parallel online addition, a redundant adder can be used directly.
-The structure of an online adder where all signals represented with SD numbers of digit set $\{−1,0,1\}$ is shown in Fig.
-xxx.
+The structure of an online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
 The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA).
 A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.
-xxx, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
-This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products [xx].
+As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products~\cite{RedundantMult_1987}.
 
-\subsection{Binary Online Multiplication}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./Figures/SDAdder2.pdf}
+  \vspace{-6ex}
+  \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
+    %\vspace{2ex}
+  \label{Fig:Radix2SD_adder}
+\end{figure}
+
+\subsection{Binary Online Multiplication}\label{subsec:OnlineMultiplier}
 
 Multiplication is another key arithmetic operator.
-Typically, online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm \ref{Algorithm:OnlineMult} where both inputs and outputs are $N$-digit number as represented in~(\ref{Eq:Online_Operands}).
+Typically, online multiplication is performed in a recursive digit-serial manner, as illustrated in Algorithm \ref{Algorithm:OnlineMult}~\cite{Ercegovac_OnlineMult} where both inputs and outputs are $N$-digit number as represented in~(\ref{Eq:Online_Operands}).
 For a given iteration $j$, the product digit $z_j$ is generated through a selection function $sel()$.
 For the radix $r$ and a chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence.
-As radix-2 is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
-In this case we have $\delta=3$, and $sel()$ is given by (\ref{Eq:SelFunc_OM}), from which it can be seen that the decision is made only based on 1 integer bit and 1 fractional bit of $W_{[j]}$.
+As the binary radix is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
+In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$~\cite{Ercegovac_OnlineMult}.
 
-\begin{algorithm}{\bf Online Multiplication} \label{Algorithm:OnlineMult}
+\begin{algorithm}[tbp]
+  \caption{Online Multiplication}  \label{Algorithm:OnlineMult}
   \begin{algorithmic}[1]
- \State  {\bf Initialization:}   $X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$
-  \State  {\bf Recurrence:}   $for~~ j=-\delta,~-\delta+1,~\cdots,~N-1 ~~do$
- \State  {\bf Compute:}    \label{Eq:OnlineMult_General}
-\State  $    H_{[j]}  = r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)$\label{Eq:OnlineMult_H}
-      \State   $  W_{[j]}    = P_{[j]} + H_{[j]}$
-     \State    $  z_j        =  sel(W_{[j]})$
-    \State     $  P_{[j+1]}  =  r\left(W_{[j]}-z_j\right)$\label{Eq:OnlineMult_P}
+   \State \textbf{Initialization:}~$X_{[-\delta]}=Y_{[-\delta]}=P_{[-\delta]}=0$\vspace{.5ex}
+    \For{$j=-\delta,~-\delta+1,~\cdots,~2N-1$}\vspace{.5ex}
+        \State $H_{[j]} \leftarrow r^{-\delta}\left(x_{j+\delta+1}\cdot Y_{[j+1]}+y_{j+\delta+1}\cdot X_{[j]}\right)$\vspace{.5ex}
+        \State $W_{[j]} \leftarrow P_{[j]} + H_{[j]}$\vspace{.5ex}
+        \State $z_{j}~ \leftarrow sel(W_{[j]})$\vspace{.5ex}
+        \State $P_{[j+1]} \leftarrow r\left(W_{[j]}-Z_{[j]}\right)$\vspace{.5ex}
+    \EndFor
   \end{algorithmic}
@@
 
-\begin{equation}\label{Eq:SelFunc_OM}
-\begin{array}{ll}
-  sel(W_{[j]})=
-    1 & if \ W_{[j]} \geq \frac{1}{2} \\
-    0 &  if  \ -\frac{1}{2}\leq W_{[j]}<\frac{1}{2} \\
-    \overline{1} & if \ W_{[j]}<-\frac{1}{2}
-\end{array}
-\end{equation}
+\begin{eqnarray}\label{Eq:SelFunc_OM}
+%\small
+  sel(W_{[j]})=\begin{cases}
+    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
+    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
+    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
+  \end{cases}
+%\normalsize
+\end{eqnarray}
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=7cm,height=4.5cm]{./Figures/circuit}
-\caption{  . . . . . . . . . . . . }\label{circuit}
-\end{center}
+Algorithm \ref{Algorithm:OnlineMult} can be synthesized into a unrolled digit parallel structure as shown in  Figure~\ref{Fig:Radix2OnlineMultiplier}(a).
+In an $N$-digit online multiplier (OM), there are totally $N+\delta$ stages, of which the online inputs are generated from the appending logic according to (\ref{Eq:Online_Operands}).
+In each stage, an online adder is used as shown in Figure~\ref{Fig:Radix2OnlineMultiplier}(b).
+The SDVM module performs the signed-digit vector multiplication.
+When $r=2$ and the digit set $\{\overline{1},0,1\}$ is used, the implementation of SDVM is straight forward, because for instance the output of $(y_{j+\delta+1}\cdot X_{[j]})$ is 0, $X_{[j]}$ or $-X_{[j]}$ when $y$ is equal to 0, 1 and $-1$ respectively.
+
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.49\textwidth]{./Figures/OM_Unrolled.pdf}
+  %$\vspace{-4ex}
+  \caption{(a) Synthesis of Algorithm 1 into a digit-parallel online multiplier (b) Structure of one stage, in which the maximum digit widths of signals are labeled.}
+  %\vspace{-2ex}
+  \label{Fig:Radix2OnlineMultiplier}
 \end{figure}
 
-..........................................\\
+Instead of duplicating the digit serial implementation $(N+\delta)$ times, each stage in the digit parallel architecture can be optimized for area reduction.
+For instance, the SDVM modules and the appending logic are not required in the last $\delta$ stages because the inputs are 0.
+This leads to a smaller online adder in these stages.
+Similarly for the first $\delta$ stages the selection logic can be removed, as the first digit of the result is generated at stage 0 ($S_0$).
+
+\section{Probability Model of Overclocking Error}
+
+As it is unlikely that timing violation happens in the online adder, in this Section we model the overclocking error in the radix-2 OM.
+From Figure~\ref{Fig:Radix2OnlineMultiplier} we observe two types of delay chains.
+One is caused by generation and propagation of $P_{[j]}$ among different stages.
+The other is the generation of online inputs $X_{[j]}$ and $Y_{[j]}$ from the appending logic.
+Since the appending logic is basically wires and simple combinational logic \cite{Online_Conversion}, the overall latency will eventually be determined by the delay of the $P_{[j]}$ path, especially with increasing operand word-lengths.
+As such, we initially model the delay of each stage within an OM to be a constant value $\mu$, as shown in Figure~\ref{Fig:Radix2OnlineMultiplier}(b).
+We also assume that the generation of online inputs costs no delay.
+%\vspace{-1ex}
 
@@
 %
-We now determine when this timing constraint is not met and the size of error in this case.\\
+We now determine when this timing constraint is not met and the size of error in this case.
 
-\section{Probability of Timing Violations}\label{section:Prob}
+\subsection{Probability of Timing Violations}\label{subsection:Prob}
 
@@
 \end{equation}
-
+\vspace{-3ex}
+%
 \begin{equation}\label{Eq:Bound_ChainLength}
@@
 
-\noindent However, the actual length of a ``carry'' chain is dependent upon input patterns.
+However, the actual length of a ``carry'' chain is dependent upon input patterns.
 We then examine the relationship between $d(\tau)$ and the inputs that corresponds to the generation, propagation and annihilation of this carry chain.
@@
 
-\noindent The classification is based on whether a digit is zero, as all internal signals are reset to zero initially.
+The classification is based on whether a digit is zero, as all internal signals are reset to zero initially.
 Under the assumption that all digits are mutually independent and uniformly sampled from the digit set  $\{\overline{1},0,1\}$ as given in Section~\ref{Sec:Background}, the probabilities of $C_1,...,C_4$ are given in (\ref{Eq:probcaser}).
@@
 
-Substituting (\ref{Eq:probcaser}) into \ref{Eq:PChainRule_Exp} yields (\ref{Eq:PChainRule_raw}).
+Substituting (\ref{Eq:probcaser}) into (\ref{Eq:PChainRule_Exp}) yields (\ref{Eq:PChainRule_raw}).
 
 \begin{equation}\label{Eq:PChainRule_raw}
-\scriptsize
+\footnotesize
   Pr_{\tau,d(\tau )}= \left(\frac{1}{(2a+1)^2}\right)^{\tau -1} \left(\frac{(2a+1)^2-1}{(2a+1)^2}\right)^{d(\tau )} \frac{1}{(2a+1)^2}
@@
 
-For all possible values of $\tau$ and $d(\tau)$, the possibility that timing violaions happen is given by $Pr$ in (\ref{Eq:Prob_timingViol}).
+For all possible values of $\tau$ and $d(\tau)$, the possibility that timing violations happen is given by $Pr$ in (\ref{Eq:Prob_timingViol}).
 According to (\ref{Eq:Bound_GenChain}) and (\ref{Eq:Bound_ChainLength}), the ranges in which the parameters $\tau$ and $d(\tau)$ are defined depend upon the value of the swamping period $T_S$.
@@
 
-\section{Error Estimation}
+\subsection{Estimation of Timing Errors}
 
@@
 \begin{figure}[tbp]
-\begin{center}
+\centering
   \includegraphics[width=8cm,height=5cm]{./Figures/Error_Function_Spline_experiment}
@@
 (Legend and xylabels to be added.) }\label{Error_Function_Spline_experiment}
-\end{center}
 \end{figure}
 
-%\noindent The {\bf Expectation of Overclocking Error} is also function of the sampling period and it is obtained by combining the values of $Pr$ and $\varepsilon$ as in (\ref{eovc}).
+\section{Case Study: Image Filter}\label{Sec:CaseStudy}
+\subsection{Experimental Setup}
+The benefits of the proposed methodology are demonstrated by using a $3\times3$ Gaussian image filter, which is implemented with two types of computer arithmetic.
+One is the binary online arithmetic while the other is the binary traditional arithmetic.
+For design with online arithmetic, all inputs and outputs are represented in the online format as given in (\ref{Eq:Online_Operands}).
+The basic building blocks: adders and multipliers as described in Section~\ref{subsec:OnlineAdder} and Section~\ref{subsec:OnlineMultiplier} are employed.
+For design with traditional arithmetic, all signals are represented using the 2's complement format.
+We build this type of image filter by using speed-optimized adders and multipliers which are created using Xilinx Core Generator \cite{XilinxMult}.
 
-%\begin{equation}\label{eovc}
-%E_{ovc}(T_S)= Pr(T_S) \cdot  v(T_S)
-%\end{equation}
+In order to achieve the desired latency between input and output, both designs are overclocked and the errors seen at the output are recorded.
+The results are obtained from a Xilinx Virtex-6 FPGA xxx through post place and route simulations.
+The results are evaluated in terms of mean relative error (MRE), which represents the percentage of error at outputs, as given by (\ref{Eq:MRE}) where $E_{error}$ and $E_{out}$ refer to the mean value of error and correct output, respectively.
+%
+\begin{eqnarray}\label{Eq:MRE}
+\scriptsize
+  MRE=\left|\frac{E_{error}}{E_{out}}\right|\times100\%
+  %MRE=\left|{E_{error}}/{E_{out}}\right|\times100\%
+\end{eqnarray}
+\normalsize
+
+In our experiments, two types of input data are utilized.
+One is randomly sampled from a uniform distribution of $N$-digit numbers.
+This type is referred to as ``Uniform Independent (UI) inputs''.
+The other is called ``real inputs'', which are the pixel values of several $512\times512$ benchmark images.
+
+\subsection{Quantify the Impact of Overclocking}
+The MRE values of the image filter with traditional arithmetic (dotted lines) and online arithmetic (solid lines) when $N=8$ are illustrated in Fig.~\ref{Fig:MRE_ImageFilter}.
+According to the timing analysis tool, the rated operating frequencies of the two designs are $169$MHz and $148$MHz, respectively.
+However as seen in Fig.~\ref{Fig:MRE_ImageFilter}, for the UI inputs, design with online arithmetic actually operates at a higher frequency without timing violations in comparison to the design using traditional arithmetic.
+This error-free frequency is even larger when using the real image data as inputs, since the real data do not exactly follow the uniform distribution or the independent assumption.
+In Fig.~\ref{Fig:MRE_ImageFilter} the ``Lena'' benchmark image is used as the real inputs.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.48\textwidth]{./Figures/Exps/MRE.eps}
+    %\vspace{-4ex}
+    \caption{Overclocking error in an image filter with two types of computer arithmetic: online arithmetic and standard binary arithmetic, of which the rated frequencies are 148.3MHz and 168.7MHz, respectively, according to the timing analysis tool.}
+    \label{Fig:MRE_ImageFilter}
+    %\vspace{-3ex}
+\end{figure}
+
+If errors can be tolerated, we may allow timing violations to happen for better performance.
+The sensitivity of overclocking for a given arithmetic can be evaluated by the data slope in Figure~\ref{Fig:MRE_ImageFilter}.
+For instance under an error budget of $1\%$~MRE, using UI inputs the frequency speedup of the traditional design is $3.89\%$ with respect to the maximum frequency without errors, whereas the design with online arithmetic can be overclocked by $6.85\%$.
+This indicates that online arithmetic is less sensitive to overclocking, as discussed in Section~\ref{Sec:MeanError}.
+The difference is greater using real image data: $13.74\%$ frequency speedup with online arithmetic against $4.04\%$ with traditional arithmetic, because longer chains happen with a smaller probability with real inputs.
+%\vspace{-1ex}
+
+The output images for both design scenarios are presented in Fig.~\ref{Fig:LenaImage}.
+Since the overclocking errors are in the least significant ends of the results with online arithmetic, the degradation on the image can be hardly observed.
+In contrast, timing violations cause error in the MSDs with traditional arithmetic.
+This leads to ``salt and pepper noise'' and severe quality loss as shown on the images in the right column of Fig.~\ref{Fig:LenaImage}.
+Furthermore, errors in the MSDs result in large noise power.
+Hence the signal-to-noise ratio (SNR) of the traditional design is small.
+
+\begin{figure}[htb]
+  %\vspace{-2.5ex}
+  \centering
+  \subfigure[1.05$f_0$,~SNR=38.3dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Online_T404.eps}
+  \end{minipage}%
+  }% This is important! use % to indicate same line, otherwise new line
+  \subfigure[1.05${f_0}'$,~SNR:21.5dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Trad_T426.eps}
+  \end{minipage}
+  }\vspace{-1ex}
+  \subfigure[1.15$f_0$,~SNR:36.2dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Online_T370.eps}
+  \end{minipage}
+  }%
+  \subfigure[1.15${f_0}'$,~SNR:9.0dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Trad_T390.eps}
+  \end{minipage}
+  }\vspace{-1ex}
+  \subfigure[1.25$f_0$,~SNR:26.7dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Online_T340.eps}
+  \end{minipage}%
+  }% same line
+  \subfigure[1.25${f_0}'$,~SNR:8.5dB]{
+  \begin{minipage}[c]{0.24\textwidth}
+    \centering
+    \includegraphics[width=1.3in]{./Figures/Exps/Lena/Trad_T358.eps}
+  \end{minipage}
+  }
+%\vspace{-2ex}
+\caption{Output images of image filter using online arithmetic (left column) and traditional arithmetic (right column), where $f_0$ and ${f_0}'$ denote the maximum error-free frequencies for each design.}
+\label{Fig:LenaImage}
+%\vspace{-1ex}
+\end{figure}
+
+\subsection{Potential Benefits in Circuit Design}
+In general, our results could be of interest to a circuit designers in two ways.
+By choosing different arithmetic and data representations, either a circuit can be designed to operate at a certain frequency with the minimum possible MRE, or a given error budget specified by the algorithm designer can be met with the fastest achievable frequency.
+For the first case, the experimental results obtained by UI inputs and 4 benchmark images are summarized in Table~\ref{Tab:MRE_Redu_Freq} in terms of the relative reduction of MRE as given by (\ref{Eq:MRE_Reduction}) where $MRE_{OL}$ and $MRE_{Trad}$ denote the value obtained with online arithmetic and with traditional arithmetic, respectively, and in Table \ref{Tab:SNR_Impro_Freq} for the differences of SNR.
+
+We also perform experiments using other benchmark images.
+The results are summarized in Table~\ref{Tab:MRE_Redu_Freq} and Table~\ref{Tab:SNR_Impro_Freq} in terms of the relative reduction of MRE and the improvements of SNR, respectively.
+In both tables the frequency is normalized to the maximum error-free frequency for each arithmetic.
+From Table~\ref{Tab:MRE_Redu_Freq}, a significant reduction of MRE can be observed using online arithmetic.
+The geometric mean reduction of MRE is $89.2\%$ using UI data.
+Even larger reductions of MRE can be achieved when testing with real image data, varying from $97.3\%$ to $98.2\%$, as expected given the results shown in Figure~\ref{Fig:MRE_ImageFilter}.
+Similarly from Table~\ref{Tab:SNR_Impro_Freq}, the improvements in SNR are $21.4dB\sim43.9dB$.
+%\vspace{-1ex}
+
+\begin{eqnarray}\label{Eq:MRE_Reduction}
+\scriptsize
+  \frac{MRE_{Trad}-MRE_{OL}}{MRE_{Trad}}\times100\%
+  %{(MRE_{Trad}-MRE_{OL})}/{MRE_{Trad}}\times100\%
+\normalsize
+\end{eqnarray}
+
+\begin{table}[tbh]
+\vspace{-1ex}
+\renewcommand{\arraystretch}{1.1}
+\setlength{\tabcolsep}{4.1pt}
+\caption{Relative Reduction of MRE with Online Arithmetic for Various Normalized Frequencies.}
+\vspace{1ex}
+\label{Tab:MRE_Redu_Freq}
+\small
+%\scriptsize
+\centering
+\begin{tabular}{|c|ccccc|c|}
+\hline
+\multirow{2}*{\textbf{Inputs}} & \multicolumn{5}{c|}{\textbf{Normalized Frequency}} &
+\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
+& 1.05 & 1.10 & 1.15 & 1.20 & 1.25 &\\
+\hline
+Uniform & 94.5\% & 89.1\% & 90.1\% & 88.3\% & 84.3\% & 89.2\%\\
+Lena    & 99.3\% & 99.2\% & 98.9\% & 97.7\% & 94.9\% & 97.9\%\\
+Pepper  & 99.7\% & 98.3\% & 98.1\% & 97.2\% & 95.1\% & 97.7\%\\
+Sailboat& 99.5\% & 97.9\% & 97.3\% & 96.8\% & 95.1\% & 97.3\%\\
+Tiffany & 99.9\% & 97.6\% & 98.4\% & 97.8\% & 97.2\% & 98.2\%\\
+\hline
+\end{tabular}
+%\vspace{-1ex}
+\normalsize
+\end{table}
+
+\begin{table}[thb]
+%\vspace{-1ex}
+\renewcommand{\arraystretch}{1.1}
+\setlength{\tabcolsep}{4.1pt}
+\caption{Improvement of SNR (dB) with Online Arithmetic for Various Normalized Frequencies.}
+\vspace{1ex}
+\label{Tab:SNR_Impro_Freq}
+%\scriptsize
+\small
+\centering
+\begin{tabular}{|c|ccccc|}
+\hline
+\multirow{2}*{\textbf{Inputs}} & \multicolumn{5}{c|}{\textbf{Normalized Frequency}} \\
+& 1.05 & 1.10 & 1.15 & 1.20 & 1.25\\
+\hline
+Lena    & 44.6 & 36.3 & 33.2 & 29.1 & 22.9\\
+Pepper  & 35.7 & 28.3 & 28.7 & 25.9 & 24.1\\
+Sailboat& 33.7 & 27.5 & 26.3 & 25.0 & 21.7\\
+Tiffany & 43.9 & 25.9 & 29.5 & 25.6 & 24.5\\
+\hline
+\end{tabular}
+\vspace{-2ex}
+\normalsize
+\end{table}
+
+For the second design perspective, Table~\ref{Tab:MRE_Reduc_Error} illustrates the frequency speedups with different input types when specific error budgets can be tolerated.
+We see that for all input types using online arithmetic still outperforms the traditional design for each MRE budget in terms of operating frequency.
+Likewise the geometric mean of frequency speed-ups is larger for real image inputs.\vspace{-1ex}
+
+\begin{table}[tbh]
+\vspace{-2ex}
+\renewcommand{\arraystretch}{1.1}
+\setlength{\tabcolsep}{4.1pt}
+\caption{Relative Improvement in Frequency with Online Arithmetic for Various Error Budgets.}
+\label{Tab:MRE_Reduc_Error}
+\small
+%\scriptsize
+\centering
+\begin{tabular}{|c|cccc|c|}
+\hline
+\multirow{2}*{\textbf{Inputs}} & \multicolumn{4}{c|}{\textbf{Error Budget}} &
+\multirow{2}*{\begin{tabular}{c}\textbf{Geo.}\\\textbf{Mean}\end{tabular}}\\
+& 0.01\% & 0.1\% & 1\% & 10\% &\\
+\hline
+Uniform & N/A & 4.59\%   & 8.78\%  & 12.83\% & 8.03\%\\
+Lena    & 7.96\% & 11.50\%  & 16.39\% & 13.71\% & 11.88\%\\
+Pepper  & 6.22\% & 8.87\%   & 18.68\% & 15.94\% & 11.32\%\\
+Sailboat& 5.71\% & 8.87\%   & 16.93\% & 15.29\% & 10.70\%\\
+Tiffany & 2.35\% & 6.90\%   & 18.58\% & 12.22\% & 7.79\% \\
+\hline
+\end{tabular}
+\label{Tab:}
+%\vspace{-2ex}
+\normalsize
+\end{table}
+
+\subsection{Area Overhead of Our Approach}
+The area comparison between two designs is illustrated in Table~\ref{Tab:AreaComparison}.
+While we notice that our approach comes at some increase in area, the FPGA architecture is optimized for conventional arithmetic.
+For instance, the Virtex series employs dedicated multiplexers and encoders for very fast ripple carry addition~\cite{Virtex6}.
+Besides, at least 2 orders of magnitude error reduction is obtained for a given frequency in our design, as shown in Figure \ref{Fig:MRE_ImageFilter}.
+Although the differences in both error and area can be compensated by using more digits with traditional arithmetic, this will result in longer delay and an even larger gap in frequency between two designs.
+
+\begin{table}[tbh]
+\vspace{-1ex}
+\small
+\caption{FPGA Resource Usage Comparison.}
+\vspace{.5ex}
+\centering
+\label{Tab:AreaComparison}
+\begin{tabular}{|c|cc|c|}
+\hline
+\multirow{2}*{\textbf{Metric}} & \multicolumn{2}{c|}{\textbf{Arithmetic Type}} &
+\multirow{2}*{\textbf{Overhead}}\\
+ & Traditional & Online &\\ \hline
+ Look-Up Tables   & 912 & 1896 & 2.08 \\ \hline
+ Slices & 324 & 525 & 1.62 \\ \hline
+
+\end{tabular}
+\vspace{-1ex}
+\normalsize
+\end{table}
 
@@
 
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
 %\vfill

### 2014-06-10 FPT2014/bare_conf.tex
Davids comments on abstract intro and performance analysis

--- 2014-05-29 FPT2014/bare_conf.tex
@@
 % author names and affiliations
-\author{Authors removed for blind review\\ \\ \\}
+%\author{Authors removed for blind review\\ \\ \\}
 %\author{\IEEEauthorblockN{Kan Shi, David Boland, and George A. Constantinides}
@@
 Online arithmetic has been widely studied for ASIC implementation.
-Online components are designed to perform computations most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
-Recent research also shows that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region, in comparison to operators with conventional arithmetic.
+Online components were originally designed to perform computations most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
+More recently, research has shown that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region in comparison to operators with conventional arithmetic.
 Unfortunately, the utilization of online arithmetic operators in the past has required a large area overhead for FPGA implementation.
 In this paper, we propose novel approaches to implement the key primitives of online arithmetic, adders and multipliers, efficiently on modern Xilinx FPGAs with 6-input LUTs and carry resources.
-We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve over $67\%$ slice savings and over $1.2\times$ speed-ups for adders, and more than $3\times$ area savings and $1.5\times$ speed-ups for multipliers.
-Furthermore in comparison to standard arithmetic primitives, the area overheads of online operators drop from $8.41\times$ to $1.88\times$ for adders, and $8.11\times$ to $0.54\times$ for multipliers using our approach.
+We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve slice savings of over $67\%$ and $69\%$, and speed-ups of over $1.2\times$ and $1.5\times$ for adders and multipliers, respectively.
+Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads of up to $8.41\times$ and $8.11\times$ for adders and multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approach.
 
@@
 Despite its attractiveness, the use of online arithmetic on existing FPGAs is still limited due to a large area overhead.
-Given for standard arithmetic, it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), the fundamental building blocks of FPGAs.
-As a result, both main commercial FPGA vendors introduced dedicated carry logic into the logic block to reduce carry propagation delay~\cite{Virtex6}.
+For standard arithmetic, because it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), both main commercial FPGA vendors introduced dedicated carry logic to reduce carry propagation delay~\cite{Virtex6}.
 Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
@@
 For online arithmetic, two major research directions have been investigated.
-First, although there has been previous research into FPGA implementations of online arithmetic, this work only focused on online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
-Second, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with two LUTs within a slice or a logic element (LE), such as the Xilinx Spartan~3 series \cite{XilinxSpartan} and the Altera Cyclone III \cite{AlteraCyclone}.
-However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGA with 6-input LUTs and four LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
-Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for efficient implementation.
+Firstly, there has been some research into FPGA implementations of online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
+Secondly, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with two LUTs within a slice or a logic element (LE), such as the Xilinx Spartan~3 series \cite{XilinxSpartan} and the Altera Cyclone III \cite{AlteraCyclone}.
+However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGAs, which typically have 6-input LUTs and four LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
+Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for further optimization.
 %However, the implementations of other key arithmetic primitives, such as online multipliers, lack exploration.
@@
 In this paper, both issues will be addressed.
-In Section~\ref{Sec:OA_FPGA}, we propose a novel approach to map the digit parallel online adders onto FPGAs with 6-LUTs.
-The mapping is based on the fast carry logic, and the available resources within a slice can be fully utilized.
-In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient FPGA implementation of a digit parallel online multiplier.
-The resource usage of both operators can be determined analytically.
+In Section~\ref{Sec:OA_FPGA}, we propose a novel approach to map digit parallel online adders onto FPGAs with 6-LUTs.
+The mapping is based on the fast carry logic and ensures the available resources within a slice are fully utilized.
+In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient digit parallel online multiplier for FPGAs.
 We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
-For online adders, our method achieves over $67\%$ slice savings and $1.2\times$ frequency speed-ups in comparison to a direct implementation.
-The area overhead drops from up to $8.41\times$ to $1.88\times$ using the proposed online adder in comparison to the standard ripple-carry adder.
-For online multipliers, the LUTs and slice utilization of the proposed new architecture drops over $2.4\times$ and $3.2\times$, with a frequency speed-up more than $1.5\times$ in comparison to a direct implementation.
-When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$.
-This value drops to $1.84\times$ when using the proposed online multiplier.
-Furthermore, using the proposed structure can even achieve area savings of up to $55\%$ for half precision results in comparison to the standard multiplier.
+For online adders, our method achieves  slice savings of over $67\%$ and  frequency speed-ups of over $1.2\times$ in comparison to a direct implementation.
+In comparison to the standard ripple-carry adder, the area overhead drops from up to $8.41\times$ to $1.88\times$ using the proposed online adder.
+For online multipliers, the slice utilization of the proposed architecture drops of over $69\%$, with a frequency speed-up over $1.5\times$ in comparison to a direct implementation.
+When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$, which drops to $1.84\times$ when using the proposed online multiplier.
 
-In summary, the main contributions of this paper are efficient methods to map online adders and multipliers to modern FPGAs. 
-% by fully utilizing the fast carry logic for .
+Our approach has the additional advantage of computing a correctly rounded multiplier with a reduced output precision, whereas a standard multiplier has to generate full precision output.
+Using our method, a programmable number of output precision can be obtained, offering the ability to trade silicon area for precision.
+As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves upto $56\%$ slice usage in comparison to a standard multiplier with truncated output.
 
-%\begin{enumerate}
-%    \item An efficient approach of mapping online adders onto modern FPGAs;
-%    \item Area efficient implementation of digit parallel online multiplication algorithm on FPGAs;
-%    \item Theoretical area models of the proposed architectures.
-%\end{enumerate}
+In summary, the main contributions of this paper are:
+\begin{enumerate}
+    \item Efficient methods to map online adders and multipliers to modern FPGAs;
+    \item Demonstration of the performance improvements of online operators in terms of silicon area and operating frequency. 
+\end{enumerate}
+
+%In summary, the main contributions of this paper are efficient methods to map online adders and multipliers to modern FPGAs.
+The performance improvements in terms of silicon area and operating frequency with these new architectures mean that using online operators is much more attractive for an end user.
+The benefits of these operators .
 
@@
 %
-\begin{figure}[tbp]
+\begin{figure}[htbp]
   \centering
@@
 The structure of an online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
-The module ``3:2'' denotes a 3:2 compressor, which takes 3 inputs and generates 2 outputs, and is logically equivalent to a full adder (FA).
+The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA).
 A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only 2 FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
+As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
 This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
@@
 \end{algorithm}
-
+%
 \begin{eqnarray}\label{Eq:SelFunc_OM}
-%\small
+\small
   sel(W_{[j]})=\begin{cases}
@@
   \end{cases}
-%\normalsize
+\normalsize
 \end{eqnarray}
@@
 Dotted circle indicates the logic block (LB) which can be mapped to the FPGA using the carry resources.}
+	\vspace{-1ex}
 	\label{Fig:PreviousWork}
@@
 	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork2.pdf}
+	\vspace{-1ex}
 	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
 	\label{Fig:PreWorkVirtex6}
-    %\vspace{-2ex}
+    \vspace{-1ex}
 \end{figure}
@@
 	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit2.pdf}
+	\vspace{-2ex}
 	\caption{Alternative structure of online adder.
 Left: an example of 4-digit online adder.
-The shaded part refers to the 2 logic blocks (LBs) that can be mapped onto 1 slice.
+The shaded part refers to the two logic blocks (LBs) that can be mapped onto one slice.
 Right: one LB.
 The dotted boxes outline the logic that can be mapped onto each LUT and the corresponding fast carry logic.}
-	\vspace{-1ex}	
+	\vspace{-2ex}	
 	\label{Fig:ModifiedOA}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDadder_FastCarry_New2.pdf}
-	\caption{Implementation of 2 logic blocks (LBs) in 1 FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
-	%\vspace{-1ex}	
+	\includegraphics[width=.49\textwidth]{./Figures/SDadder_FastCarry_New2.pdf}
+	\vspace{-5ex}
+	\caption{Implementation of two logic blocks (LBs) in one FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
+	\vspace{-2ex}	
 	\label{Fig:SliceNew}
@@
 
-In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) are given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) can be calculated as given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+
 \begin{eqnarray}\label{Eq:OAareaLUT}
+\scriptsize
 	OA\_LUT = 2N
@@
 	OA\_slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
+\normalsize
 \end{eqnarray}
@@
 In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using functional descriptions in Verilog based on 4:2 compressors (\texttt{OA\_behv}).
-In addition, we also include ripple carry adder (\texttt{RCA}) which uses conventional arithmetic, into the comparisons.
-While in our experiments all designs are targeting on Xilinx Virtex-6 FPGA with speed grade -1, our methods can also be applied on other FPGAs with same slice architecture such as the Xilinx 7 series FPGAs.
-Notice that in order to utilize the carry resources and to avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
+We also compare these architectures against a ripple carry adder (\texttt{RCA}), which uses conventional arithmetic.
+While our experiments are targeting on Xilinx Virtex-6 FPGAs with speed grade -1, our methods are applicable to any FPGAs with the same slice architecture such as all the Xilinx 7 series FPGAs.
+Notice that in order to utilize the carry resources and avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
 
@@
 	\includegraphics[width=.45\textwidth]{./Figures/Exp/Adder_Freq.eps}
-	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.1.}
+	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.7.}
 	\label{Fig:AdderFreq}
@@
 The results are shown in Fig.~\ref{Fig:AdderFreq}.
-The frequency values are obtained through Xilinx Timing Analyzer after placing and routing the designs in ISE 14.1.
-It can be seen that both designs with online arithmetic achieves relatively stable operating frequencies across a variety of operand word-lengths.
-This is as expected, because the critical path delay in the online adder is theoretically a fixed value independent of the operand precision.
+The frequency values are obtained through Xilinx Timing Analyzer after placing and routing the designs in ISE 14.7.
+It can be seen that both designs with online arithmetic achieve relatively stable operating frequencies across a variety of operand word-lengths.
+This is as expected, because the critical path delay of the online adder is theoretically independent of the operand precision.
 In comparison, the rated frequency of the \texttt{RCA} drops dramatically for larger word-lengths.
 It follows that both online adders outperform \texttt{RCA} for large word-lengths.
-Specifically, the frequency of \texttt{OA\_behv} is faster than \texttt{RCA} when $N\geqslant30$.
-In comparison, the proposed online adder is more efficient in performance, as it outperforms \texttt{RCA} for $N>16$.
-Furthermore, the speed-ups of \texttt{OA\_new} over \texttt{OA\_behv} are from $1.20\times$ to $1.26\times$.
+More specifically, the frequency of \texttt{OA\_behv} is faster than \texttt{RCA} when $N\geqslant30$, whereas the proposed online adder outperforms \texttt{RCA} for $N>16$.
+As a result, this makes the \texttt{OA\_new} more attractive for a wider range of applications.
+Furthermore, the speed-ups of \texttt{OA\_new} against \texttt{OA\_behv} are over $1.2\times$.
 
@@
 This is because the dedicated FPGA resources are fully utilized.
-However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of slices.
+These area savings reduce the overhead of an \texttt{OA} over an \texttt{RCA} from upto $2.95\times$ to $1.98\times$ for LUTs, and from $8.41\times$ to $1.88\times$ for slices.
+It is unlikely that the overhead can be completely avoided when using an \texttt{OA} because of the redundant number system.
+Nevertheless, with the reduced overhead, using \texttt{OA} to take advantage of the graceful degradation when operating beyond the deterministic clocking region may become more attractive for an FPGA developer.
+
+%However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of slices.
 This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
@@
   \end{minipage}%
-  }
+  }\vspace{-1ex}
   \subfigure[Usage of slices]{
@@
     \EndFor															\vspace{.5ex}
-    \State $Z_{[N+1:2N]} \leftarrow frac(W_{[N]})$
+    \State $Z_{[N+1:2N]} \leftarrow frac(W_{[N]})$					\vspace{.5ex}
   \end{algorithmic}
+  \vspace{-1ex}
 \end{algorithm}
@@
 Originally in order to generate one digit partial product, one digit of inputs $X$ and $Y$ are required respectively, as indicated in Fig.~\ref{Fig:PartialProduct}.
-Instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all six LUT inputs.
+Alternatively, instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all six LUT inputs, as shown on the right of Fig.\ref{Fig:PartialProduct}.
 Notice that this approach is only available for FPGAs with 6-LUTs.
@@
 Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and slices used by the first stage, which is built without online adders.
-
+%
 \begin{eqnarray}\label{Eq:OMareaLUT}
+\scriptsize
 	OM\_{LUT} = 2(N+2)(N-1) + {L}_{S1}
+\normalsize
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Eq:OMareaSlice}
+\scriptsize
 	OM\_{slice} = \left(1+\left\lceil{\frac{N}{2}}\right\rceil\right)(N-1)+S_{S1}
+\normalsize
 \end{eqnarray}
@@
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
-	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
-(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
-	\label{Fig:PMStructure_MSDhalf}
-	%\vspace{-2ex}
-\end{figure}
-
 In comparison, the \texttt{OM} offers the flexibility to simplify the structure corresponding to the required precision.
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
+	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
+(b) Structure diagram of stage $j$, with the word-lengths of all internal signals labelled.}
+	\label{Fig:PMStructure_MSDhalf}
+	\vspace{-1ex}
+\end{figure}
+
 \subsection{Performance Analysis}
@@
 The comparison of area in terms of the cost of LUTs and the cost of slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
-The results are obtained from ISE 14.1 after mapping the design to the Virtex-6 FPGA.
+The results are obtained from ISE 14.7 after mapping the design to the Virtex-6 FPGA.
 In comparison to \texttt{OM\_behv}, significant area savings have been obtained by the optimized design \texttt{OM\_full}.
-Specifically, the LUTs and slice utilization drops $2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
+Specifically, the LUTs and slice utilization reduces $59.0\%\sim70.1\%$ and $68.6\%\sim81.7\%$, respectively.
 
-In comparison to the \texttt{CoreGen} multiplier, the area overhead of online multipliers drops significantly when transferring to the proposed new structure.
-In order to generate full precision product, the area overheads of \texttt{OM\_behv} against \texttt{CoreGen} are $3.94\times\sim5.82\times$ for LUTs, and $3.58\times\sim8.11\times$ for slices, respectively.
+%$2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
+
+In comparison to the \texttt{CoreGen} multiplier, the area overhead of online multipliers drops significantly using the proposed new structure.
+In order to generate full precision product, the area overhead of \texttt{OM\_behv} against \texttt{CoreGen} are $3.94\times\sim5.82\times$ for LUTs, and $3.58\times\sim8.11\times$ for slices, respectively.
 Using the proposed structure \texttt{OM\_full} the area overheads drop to $1.48\times\sim1.83\times$ for LUTs and up to $1.84\times$ for slices.
-Furthermore, if only half precision result is required, \texttt{OM\_half} is more area efficient for all operand word-lengths when compared against the \texttt{CoreGen} multiplier.
-The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%$ to $55\%$ for slices.
+Furthermore, if only half of the output precision is required, \texttt{OM\_half} can save silicon area over the traditional \texttt{CoreGen} multiplier.
+The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim56\%$ for slices.
+Once again, the traditional multiplier is unable to compute this correctly rounded output using less silicon area.
+This is because for correct rounding, it must first compute the full precision output.
+In comparison, our approach offers the capability for the trade-off between area and precision.
 
@@
 
-Notice that there is an increasing gap between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
-This is because in the online multiplier, although the carry resources in the FPGA are efficiently used for area reduction, each 4-digit carry logic within a slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
+We comment that there remain a large gap in terms of frequency between the proposed online multipliers and the \texttt{CoreGen} multiplier, especially for large operand word-lengths.
+This is because in the online multiplier, even with the carry resources in the FPGA being used efficiently, each 4-digit carry logic within a slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
 Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is hyperbole for large operand word-lengths.
-This also explains the fact that \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, as the critical path of both designs are identical in theory.
+This also explains why \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, because the critical path of both designs are identical in theory.
 
@@
 	\caption{Rated frequencies of different types of binary multipliers for a variety of operand word-lengths.
-The results are obtained from the Xilinx Timing Analyzer in ISE 14.1 after placing and routing.}
+The results are obtained from the Xilinx Timing Analyzer in ISE 14.7 after placing and routing.}
 	\label{Fig:OM_Freq}
@@
 We examine the overclocking behavior of all 3 types of multipliers in terms of the mean relative error (\texttt{MRE}), which is given in (\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ refer to the mean value of error and the mean value of correct output, respectively.
-
+%
 \begin{eqnarray}\label{Eq:MRE}

### 2014-06-13 FPT2014/bare_conf.tex
Davids comments on abstract and intro

@@
 For standard arithmetic, because it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), both main commercial FPGA vendors introduced dedicated carry logic to reduce carry propagation delay~\cite{Virtex6}.
-Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain,Prefix_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
+Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
 Hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply accumulates~\cite{XilinxDSP}.
@@
 In Section~\ref{Sec:OA_FPGA}, we propose a novel approach to map digit parallel online adders onto FPGAs with 6-LUTs.
-The mapping is based on the fast carry logic and ensures the available resources within a slice are fully utilized.
+The mapping is based on the fast carry logic and ensures the available logic resources within a slice are fully utilized.
 In Section~\ref{Sec:OM_FPGA}, we optimize the online multiplication algorithm to yield an efficient digit parallel online multiplier for FPGAs.
@@
 For online multipliers, the slice utilization of the proposed architecture drops of over $69\%$, with a frequency speed-up over $1.5\times$ in comparison to a direct implementation.
-When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$, which drops to $1.84\times$ when using the proposed online multiplier.
+When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$, which drops to $1.84\times$ when using the proposed new architecture.
 
-Our approach has the additional advantage of computing a correctly rounded multiplier with a reduced output precision, whereas a standard multiplier has to generate full precision output.
+Our approach has the additional advantage of being able to create a correctly rounded multiplier with a reduced output precision using less hardware than a standard multiplier, which multiplies two $N$-digit numbers and produces an output of $2N$ digits.
+However, in many cases the full precision product is not required.
+In such cases, a reduced precision output is created either by truncating or rounding the LSDs.
+Although there has been research into saving area by avoiding the creation of unnecessary LSDs~\cite{TheoTC}, these techniques still require extensive simulation to guarantee correctness.
+In contract, since online multipliers compute the output from the MSD first, hardware can be saved by not generating the LSDs in the first place.
+As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves upto $56\%$ slice usage in comparison to a standard multiplier with truncated output.
+
+%computing a correctly rounded multiplier with a reduced output precision, whereas a standard multiplier has to generate full precision output.
 Using our method, a programmable number of output precision can be obtained, offering the ability to trade silicon area for precision.
@@
     \item Efficient methods to map online adders and multipliers to modern FPGAs;
+    \item Discussion of how to implement correctly-rounded online multipliers for a chosen output precision;
     \item Demonstration of the performance improvements of online operators in terms of silicon area and operating frequency.
@@
 	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
-    %\vspace{2ex}
+    \vspace{2ex}
 	\label{Fig:Radix2SD_adder}
@@
 In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$ \cite{Ercegovac_OnlineMult}.
-%
+
 \begin{algorithm}[tbp]
@@
 In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) can be calculated as given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
-
+%
 \begin{eqnarray}\label{Eq:OAareaLUT}
@@
 	OA\_LUT = 2N
+\normalsize
 \end{eqnarray}
@@
 \begin{eqnarray}\label{Eq:OAareaSlice}
+\footnotesize
 	OA\_slice = 1+\left\lceil\frac{N-2}{2}\right\rceil
@@
 
-The comparison of area in terms of the cost of LUTs and the cost of slices with respect to different operand word-lengths are illustrated in Fig.~\ref{Fig:OMArea}.
+The comparison of area in terms of the cost of LUTs and slices with respect to different operand word-lengths are shown in Fig.~\ref{Fig:OMArea}.
 The results are obtained from ISE 14.7 after mapping the design to the Virtex-6 FPGA.
@@
 Specifically, the LUTs and slice utilization reduces $59.0\%\sim70.1\%$ and $68.6\%\sim81.7\%$, respectively.
+In comparison to the \texttt{CoreGen} multiplier, the area overhead of online multipliers drops significantly using the proposed new structure.
+In order to generate full precision product, the area overhead of \texttt{OM\_behv} against \texttt{CoreGen} are $3.94\times\sim5.82\times$ for LUTs, and $3.58\times\sim8.11\times$ for slices.
+Using the proposed structure \texttt{OM\_full} the area overheads drop to $1.48\times\sim1.83\times$ for LUTs and up to $1.84\times$ for slices.
+Furthermore as mentioned in the introduction, a traditional multiplier is unable to compute this correctly rounded output using less silicon area without extensive simulation.
+In contrast, using our approach we can trade area for precision and tune output precision to be the minimum desired.
+As an example, if only half of the output precision is required, \texttt{OM\_half} can save silicon area over the traditional \texttt{CoreGen} multiplier.
+The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim56\%$ for slices.
 
-%$2.44\times\sim3.34\times$ and $3.19\times\sim5.45\times$, respectively.
-
-In comparison to the \texttt{CoreGen} multiplier, the area overhead of online multipliers drops significantly using the proposed new structure.
-In order to generate full precision product, the area overhead of \texttt{OM\_behv} against \texttt{CoreGen} are $3.94\times\sim5.82\times$ for LUTs, and $3.58\times\sim8.11\times$ for slices, respectively.
-Using the proposed structure \texttt{OM\_full} the area overheads drop to $1.48\times\sim1.83\times$ for LUTs and up to $1.84\times$ for slices.
-Furthermore, if only half of the output precision is required, \texttt{OM\_half} can save silicon area over the traditional \texttt{CoreGen} multiplier.
-The area saving varies from $40\%$ to $55\%$ for LUTs, and $46\%\sim56\%$ for slices.
-Once again, the traditional multiplier is unable to compute this correctly rounded output using less silicon area.
-This is because for correct rounding, it must first compute the full precision output.
-In comparison, our approach offers the capability for the trade-off between area and precision.
+%our approach offers the capability for the trade-off between area and precision.
 
@@
 	\includegraphics[width=.48\textwidth]{./Figures/Exp/OM_Freq2.eps}
+	\vspace{-3ex}
 	\caption{Rated frequencies of different types of binary multipliers for a variety of operand word-lengths.
 The results are obtained from the Xilinx Timing Analyzer in ISE 14.7 after placing and routing.}
+	\vspace{-2ex}
 	\label{Fig:OM_Freq}
-
 \end{figure}
@@
   MRE=\frac{E_{error}}{E_{out}}\times100\%
-  %\vspace{-1ex}
+  \vspace{-1.5ex}
 \end{eqnarray}
@@
   \includegraphics[width=.48\textwidth]{./Figures/Exp/MRE_PM.eps}
- % \vspace{-1ex}
+  \vspace{-3ex}
   \caption{Mean relative errors seen at the outputs of different types of 8-digit binary multipliers, when clocked with faster-than-rated frequencies.}
   \label{Fig:PM_MRE}
-  %\vspace{-1ex}
+  \vspace{-1ex}
 \end{figure}

### 2014-06-30 FPT2014/bare_conf.tex
Georges comment 3_1

@@
 Online arithmetic has been widely studied for ASIC implementation.
-Online components were originally designed to perform computations most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
+Online components were originally designed to perform computations in digit serial with most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
 More recently, research has shown that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region in comparison to operators with conventional arithmetic.
@@
 In this paper, we propose novel approaches to implement the key primitives of online arithmetic, adders and multipliers, efficiently on modern Xilinx FPGAs with 6-input LUTs and carry resources.
-We demonstrate experimentally that in comparison to a direct implementation, the proposed architectures achieve slice savings of over $67\%$ and $69\%$, and speed-ups of over $1.2\times$ and $1.5\times$ for adders and multipliers, respectively.
-Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads of up to $8.41\times$ and $8.11\times$ for adders and multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approach.
+We demonstrate experimentally that in comparison to a direct RTL synthesis, the proposed architectures achieve slice savings of over $67\%$ and $69\%$, and speed-ups of over $1.2\times$ and $1.5\times$ for adders and multipliers, respectively.
+As a result, the area overheads of using online adders and multipliers in place of traditional arithmtic primitives is reduced from
+% Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads from up to $8.41\times$ to $1.88\times$ for adders, and from $8.11\times$ to $1.84\times$ for multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approaches.
 
@@
 
-Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region, i.e.
-when overclocking \cite{SKDAC14_REVIEW}.
+Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region,  \textit{i.e.} when overclocking \cite{SKDAC14_REVIEW}.
 This theme of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
@@
 Despite its attractiveness, the use of online arithmetic on existing FPGAs is still limited due to a large area overhead.
-For standard arithmetic, because it is difficult to efficiently map arithmetic circuits solely onto look-up-tables (LUTs), both main commercial FPGA vendors introduced dedicated carry logic to reduce carry propagation delay~\cite{Virtex6}.
+For standard arithmetic, because it is inefficient and slow to map arithmetic circuits solely onto look-up-tables (LUTs), both main commercial FPGA vendors have introduced dedicated carry logic~\cite{Virtex6}.
 Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
@@
 For online arithmetic, two major research directions have been investigated.
-Firstly, there has been some research into FPGA implementations of online adders; a brief review of relevant works in this area is presented in Section~\ref{Sec:OA_FPGA}.
+Firstly, there has been some research into FPGA implementations of online adders; a brief review of relevant work in this area is presented in Section~\ref{Sec:OA_FPGA}.
 Secondly, there are existing approaches to build general purpose online adders specifically for FPGAs with 4-input LUTs and with two LUTs within a slice or a logic element (LE), such as the Xilinx Spartan~3 series \cite{XilinxSpartan} and the Altera Cyclone III \cite{AlteraCyclone}.
@@
 We demonstrate experimentally on Xilinx Virtex-6 FPGAs that the proposed designs achieve significant area reduction and performance gain over their original implementations.
-For online adders, our method achieves  slice savings of over $67\%$ and  frequency speed-ups of over $1.2\times$ in comparison to a direct implementation.
+For online adders, our method achieves  slice savings over $67\%$ and  frequency speed-ups of over $1.2\times$ in comparison to a direct implementation.
 In comparison to the standard ripple-carry adder, the area overhead drops from up to $8.41\times$ to $1.88\times$ using the proposed online adder.
@@
 
-Our approach has the additional advantage of being able to create a correctly rounded multiplier with a reduced output precision using less hardware than a standard multiplier, which multiplies two $N$-digit numbers and produces an output of $2N$ digits.
+Our approach has the additional advantage of being able to create a correctly rounded multiplier with a reduced output precision using less hardware than a full multiplier, which multiplies two $N$-digit numbers and produces an output of $2N$ digits.
 However, in many cases the full precision product is not required.
@@
 In contract, since online multipliers compute the output from the MSD first, hardware can be saved by not generating the LSDs in the first place.
-As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves upto $56\%$ slice usage in comparison to a standard multiplier with truncated output.
+As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves up to $56\%$ slice usage in comparison to a standard multiplier with truncated output.
 

### 2014-07-01 FPT2014/bare_conf.tex
Georges comment 3_2

@@
 Online arithmetic has been widely studied for ASIC implementation.
-Online components were originally designed to perform computations in digit serial with most significant digit first, resulting in the ability to chain arithmetic operators together for low latency.
+Online components were originally designed to perform computations in digit serial with most significant digit (MSD) first, resulting in the ability to chain arithmetic operators together for low latency.
 More recently, research has shown that digit parallel online operators can fail more gracefully when operating beyond the deterministic clocking region in comparison to operators with conventional arithmetic.
@@
 We demonstrate experimentally that in comparison to a direct RTL synthesis, the proposed architectures achieve slice savings of over $67\%$ and $69\%$, and speed-ups of over $1.2\times$ and $1.5\times$ for adders and multipliers, respectively.
-As a result, the area overheads of using online adders and multipliers in place of traditional arithmtic primitives is reduced from
+As a result, the area overheads of using online adders and multipliers in place of traditional arithmetic primitives is reduced from $8.41\times$ and $8.11\times$ to $1.88\times$ and $1.84\times$ respectively.
+Finally, because an online multiplier generates MSDs first, we also demonstrate the method to create an online multiplier with a reduced precision output that is smaller than a traditional multiplier producing the same result.
+We show that this can lead to silicon area savings of up to $56\%$.
 % Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads from up to $8.41\times$ to $1.88\times$ for adders, and from $8.11\times$ to $1.84\times$ for multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approaches.
@@
     \item Efficient methods to map online adders and multipliers to modern FPGAs;
-    \item Discussion of how to implement correctly-rounded online multipliers for a chosen output precision;
-    \item Demonstration of the performance improvements of online operators in terms of silicon area and operating frequency.
+    \item A method to implement correctly-rounded online multipliers for a chosen output precision;
+    \item Demonstration of the performance improvements of online operators in terms of area and frequency.
 \end{enumerate}
@@
 This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
-
+%
 \begin{figure}[tbp]
@@
 	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
-    \vspace{2ex}
+    \vspace{-2ex}
 	\label{Fig:Radix2SD_adder}
@@
 In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$ \cite{Ercegovac_OnlineMult}.
+%
+\begin{eqnarray}\label{Eq:SelFunc_OM}
+\small
+  sel(W_{[j]})=\begin{cases}
+    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
+    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
+    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
+  \end{cases}
+\normalsize
+\end{eqnarray}
 
@@
 \end{algorithm}
-%
-\begin{eqnarray}\label{Eq:SelFunc_OM}
-\small
-  sel(W_{[j]})=\begin{cases}
-    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
-    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
-    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
-  \end{cases}
-\normalsize
-\end{eqnarray}
+\vspace{-1ex}
 
@@
 In this case, the fast-carry logic in the FPGA can be employed, and the delay between the two 3:2 compressors can be greatly reduced.
-
+%
 \begin{figure}[tbp]
@@
 	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan2.pdf}
+	\vspace{-3ex}
 	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
@@
 Dotted circle indicates the logic block (LB) which can be mapped to the FPGA using the carry resources.}
-	\vspace{-1ex}
+	\vspace{-4ex}
 	\label{Fig:PreviousWork}
@@
 Due to the same reason, the output of \texttt{XORCY2} should not be used.
-
+%
 \begin{figure}[tbp]
@@
 	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork2.pdf}
-	\vspace{-1ex}
+	\vspace{-2ex}
 	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
 	\label{Fig:PreWorkVirtex6}
-    \vspace{-1ex}
+    \vspace{-2ex}
 \end{figure}
@@
 We also compare these architectures against a ripple carry adder (\texttt{RCA}), which uses conventional arithmetic.
-While our experiments are targeting on Xilinx Virtex-6 FPGAs with speed grade -1, our methods are applicable to any FPGAs with the same slice architecture such as all the Xilinx 7 series FPGAs.
+While our experiments target on Xilinx Virtex-6 FPGAs (speed grade -1), our methods are applicable to any FPGAs with the same slice architecture such as all the Xilinx 7 series FPGAs.
 Notice that in order to utilize the carry resources and avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
@@
 It follows that both online adders outperform \texttt{RCA} for large word-lengths.
-More specifically, the frequency of \texttt{OA\_behv} is faster than \texttt{RCA} when $N\geqslant30$, whereas the proposed online adder outperforms \texttt{RCA} for $N>16$.
+More specifically, the frequency of \texttt{OA\_behv} is faster than \texttt{RCA} when $N\geqslant30$, whereas our new online adder outperforms \texttt{RCA} for $N>16$.
 As a result, this makes the \texttt{OA\_new} more attractive for a wider range of applications.
@@
 We also compare the resource usage of all three adder designs with respect to a variety of operand word-lengths.
-The results are presented in Fig~\ref{Fig:AdderArea}.
+The results are presented in Fig.~\ref{Fig:AdderArea}.
 We can see that in comparison to the original \texttt{OA\_behv}, our implementation \texttt{OA\_new} achieves significant area savings: $25\%\sim 33\%$ in LUTs and $67\%\sim77\%$ in slices.
 This is because the dedicated FPGA resources are fully utilized.
-These area savings reduce the overhead of an \texttt{OA} over an \texttt{RCA} from upto $2.95\times$ to $1.98\times$ for LUTs, and from $8.41\times$ to $1.88\times$ for slices.
+These area savings reduce the overhead of an \texttt{OA} over an \texttt{RCA} from $2.95\times$ to $1.98\times$ for LUTs, and from $8.41\times$ to $1.88\times$ for slices.
 It is unlikely that the overhead can be completely avoided when using an \texttt{OA} because of the redundant number system.
@@
 \end{algorithm}
+\vspace{-1ex}
 
@@
 	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.pdf}
+	\vspace{-3ex}
 	\caption{(a) Structure of a 4-digit online multiplier using the proposed algorithm.
@@
 Using the proposed structure \texttt{OM\_full} the area overheads drop to $1.48\times\sim1.83\times$ for LUTs and up to $1.84\times$ for slices.
-Furthermore as mentioned in the introduction, a traditional multiplier is unable to compute this correctly rounded output using less silicon area without extensive simulation.
+Furthermore as mentioned in the introduction, a traditional multiplier is unable to compute this correctly rounded output using less silicon area.
 In contrast, using our approach we can trade area for precision and tune output precision to be the minimum desired.
@@
 This is because in the online multiplier, even with the carry resources in the FPGA being used efficiently, each 4-digit carry logic within a slice is divided into two parts, as shown previously in Section~\ref{Sec:OA_FPGA}.
-Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is hyperbole for large operand word-lengths.
+Therefore the critical path delay of an \texttt{OM} is determined by both the carry logic delays, and the net delay among different stages, which is huge for large operand word-lengths.
 This also explains why \texttt{OM\_full} and \texttt{OM\_half} run at similar frequencies, because the critical path of both designs are identical in theory.

### 2014-07-01 TCAD2014/TCAD14.tex
Model-errors-initial review

@@
 Notice that no carry chain will be generated under Case~1, because $P_{[\tau+1]}=0$.
-In other words, a chain could be generated if one of  the cases $C_2(\tau)$,...,$C_4(\tau)$ occur.
+In other words, a chain could be generated if one of  the cases $C_2(\tau),\cdots,C_4(\tau)$ occur.
 In this case we provide the following propositions which describe the probabilities of timing violations.
@@
 
-\subsection{Estimation of Timing Errors}
+\section{Estimation of Timing Errors}
+The presence of timing violations may result in overclocking errors generated from LSDs with online arithmetic.
+In this Section, we propose the modelling methods that quantify the overclocking error in terms of its statistic properties in Section~\ref{subsection:ErrorDistribution} and the magnitude of timing errors in Section~\ref{subsection:ErroeMagnitude}.
+Although we use the online multiplier as an example to illustrate the modelling process, our methods can be extended to other digit parallel online arithmetic operators.
 
-In the presence of timing violation, multiple chains might not be correctly propagated in the online multiplication, resulting in overclocking errors generated from LSDs.
-Let $z_i$ and ${z_i}'$ denote the correct value and the actual value of the output digit at the stage $S_i$, respectively.
-Then we have ${z_i}'=z_i+\varepsilon_i$ where $\varepsilon_i$ is referred to as the overclocking error.
-We now locate the first output digit $z_{\lambda}$ that contains error.
-For a given $T_S$ and a minimum value of $\tau$ such that $d(\tau)_{max}>b$, we have $\lambda=\tau+d(\tau)_{max}+1$ for chain annihilation.
-%
-%.
-Let us consider the first chain that timing violation may occur, i.e.
-$d(\tau)_{max}>b$, denote that it annihilates at $S_{\lambda}$ where $\lambda=\tau+d_{max}(\tau)-1$.
-Therefore overclocking errors may happen from digit $\lambda$ to digit $N-1$ of the result.
-%
-As such, the overclocking error can be expressed by (\ref{Eq:ErrorMagnitude})
+\subsection{Statistic Properties of Timing Errors}\label{subsection:ErrorDistribution}
 
-%, where $z_i$ and ${z_i}'$ denote the correct value and the actual value of the output digit of $S_i$, separately, and $\varepsilon_i\in\{\pm2^{-i},\pm2^{-i+1}\}$ since $z$ is represented using digit set $\{\overline{1},0,1\}$.
-%
-\begin{eqnarray}\label{Eq:ErrorMagnitude}
+In general, let $z_j$ and ${z_j}'$ denote the correct value and the actual value of the output digit at stage $S_j$, respectively.
+Then we have ${z_j}'=z_j+\varepsilon_j$ where $\varepsilon_j$ is referred to as the overclocking error at $S_j$.
+We initially determine the bound of variable $j$ for a given value of $T_S$.
+For the upper bound, we have $j\leqslant N$ because the overclocking error is generated from the LSD.
+For the lower bound, the minimum value of $\tau_{min}$ can be determined to satisfy $d(\tau_{min})>b$, which is required for timing violations.
+In this case we have $j>\tau_{min}+d(\tau_{min})$.
+In summary, the word-level representation of overclocking error ($\varepsilon$) is given in (\ref{Eq:ErrorRep}) where $\lambda=\tau_{min}+d(\tau_{min})$.
+
+\begin{eqnarray}\label{Eq:ErrorRep}
 \scriptsize
- \left| \varepsilon\right|= \left|\sum_{j=\lambda}^{N} r^{-j}\varepsilon_j\right|
+	\varepsilon = \sum_{j=\lambda+1}^{N} r^{-j}\varepsilon_j
 \normalsize
@@
 =\sum_{k=\lambda}^{N}r^{-2k} \left( r^{2(1-\delta)} \left(v\varepsilon^{in}    v\varepsilon^y_{k+1} +v\varepsilon^{in}   v\varepsilon^x_k\right)\right)
+\end{array}
+\end{equation}
+
+\subsection{Error Magnitude}\label{subsection:ErroeMagnitude}
+
+Let (\ref{Eq:VarianceDef}) be a definition of the variance of the error distribution, 
+\begin{eqnarray}\label{Eq:VarianceDef}
+\scriptsize
+	v\varepsilon=\frac{\sum_{j=\lambda}^{N} r^{-2j}(\varepsilon_j-\bar{\varepsilon})^2}{N-\lambda}
+\normalsize
+\end{eqnarray}
+
+by combining (\ref{Eq:VarianceDef}) and (\ref{Eq:VarianceErrorMagnitude}), since the mean value $\bar{\varepsilon}$ is zero, we obtain an estimation for the error $\varepsilon_j$ as in (\ref{Eq:ErrorEstimationj}).
+
+\begin{eqnarray}\label{Eq:ErrorEstimationj}
+\scriptsize
+	\varepsilon_j=(N-\lambda)^{\frac{1}{2}} v\varepsilon_j^{\frac{1}{2}}, \ \forall j=\lambda,\dots,N.
+\normalsize
+\end{eqnarray}
+
+By using the (\ref{Eq:VarInputUniform}), (\ref{Eq:var_XY}) and  (\ref{Eq:varerror_final}) into (\ref{Eq:ErrorEstimationj}) we have explicit in (\ref{Eq:value_ErrorUniform}) the dependence of the error $\varepsilon_j$ on the parameter $a$.
+
+\begin{eqnarray}\label{Eq:value_ErrorUniform}
+{\varepsilon}_j =& (N-\lambda)^{\frac{1}{2}} r  \left( r^{(1-\delta)} \left(\frac{(2a+1)^{2}-1}{12} \right. \right. \nonumber \\
+& \sum_{i=1}^{j+1+\delta} r^{-2i} \frac{(2a+1)^{2}-1}{12} + \nonumber \\
+&\left. \left. +\frac{(2a+1)^{2}-1}{12}   \sum_{i=1}^{j+\delta} r^{-2i} \frac{(2a+1)^{2}-1}{12}\right)^{\frac{1}{2}}\right)
+\end{eqnarray}
+
+Simplifing (\ref{Eq:value_ErrorUniform}) will give (\ref{Eq:value_ErrorUniformFinal})
+
+\begin{eqnarray}\label{Eq:value_ErrorUniformFinal}
+{\varepsilon}_j=    \frac{(2a+1)^2-1}{12r^{\delta-2} } \left[ (N-\lambda) (1+r^{-2(j+\delta -1})   \sum_{i=1}^{j+\delta} r^{-2i}\right]^\frac{1}{2}   
+\end{eqnarray}
+
+Finally, (\ref{Eq:value_ErrorUniformFinal}) can be used to derive the expression of $\varepsilon$ in (\ref{Eq:ErrorUniformFinal}) according to (\ref{Eq:ErrorMagnitude}).
+Notice that this expression forms the relationship between the value of overclocking error, the given input distribution, the number of the digit operands $N$, the online delay and the value of the sampling period whence depends the value of $\lambda$.
+
+\begin{equation}\label{Eq:ErrorUniformFinal}
+\begin{array}{l}
+{\varepsilon} =   \mathcal{G}(N,r, a, \delta,b)\\
+=\sum_{j=\lambda}^N    {\varepsilon}_j
 \end{array}

### 2014-10-05 FPT2014/bare_conf.tex
add authors and shrink to 8 pages

@@
 %\author{Authors removed for blind review\\ \\ \\}
-%\author{\IEEEauthorblockN{Kan Shi, David Boland, and George A. Constantinides}
-%\IEEEauthorblockA{Department of Electrical and Electronic Engineering\\
-%Imperial College London\\London, UK\\
+\author{
+\IEEEauthorblockN{Kan Shi}
+\IEEEauthorblockA{Department of Electrical and\\ Electronic Engineering\\
+Imperial College London\\London, SW7 2AZ, UK\\
+k.shi11@imperial.ac.uk}
+\and
+\IEEEauthorblockN{David Boland}
+\IEEEauthorblockA{Department of Electrical and\\ Computer Systems Engineering\\
+Monash University\\Clayton, VIC 3800, Australia\\
+david.boland@monash.edu
+}
+\and
+\IEEEauthorblockN{George A. Constantinides}
+\IEEEauthorblockA{Department of Electrical and\\ Electronic Engineering\\
+Imperial College London\\London, SW7 2AZ, UK\\
+g.constantinides@imperial.ac.uk}
 %\{k.shi11, david.boland03,g.constantinides\}@imperial.ac.uk}
-%}
+}
 
@@
 Finally, because an online multiplier generates MSDs first, we also demonstrate the method to create an online multiplier with a reduced precision output that is smaller than a traditional multiplier producing the same result.
-We show that this can lead to silicon area savings of up to $56\%$.
+We show that this can lead to silicon area savings of up to $56\%$.\vspace{-0.5ex}
 % Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads from up to $8.41\times$ to $1.88\times$ for adders, and from $8.11\times$ to $1.84\times$ for multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approaches.
@@
 
-\section{Introduction}\label{Sec:Intro}
+\section{Introduction}\label{Sec:Intro}\vspace{-0.5ex}
 In the conventional form of computer arithmetic, the computation results are generated either from the least significant digit (LSD), e.g.
@@
 This enables parallelism among multiple operations, and the overall computation latency can be significantly reduced.
-A brief overview of online arithmetic is given in Section~\ref{Sec:Background}.
+A brief overview of online arithmetic is given in Section~\ref{Sec:Background}.\vspace{-0.5ex}
 
-Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region,  \textit{i.e.} when overclocking \cite{SKDAC14_REVIEW}.
+Recent research has demonstrated another key advantage of online arithmetic: that it allows graceful degradation when operating beyond the deterministic clocking region,  \textit{i.e.} when overclocking \cite{SKDAC14}.
 This theme of research stems from the inspiration that for certain applications, releasing the absolute accuracy requirements could lead to significant performance improvements.
 However, traditional forms of computer arithmetic do not fail gracefully when timing violation happens, because timing errors tend to affect MSDs of the results.
-In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occur at LSDs of the results.
+In comparison, online arithmetic is more ``overclocking friendly'', as timing errors only occur at LSDs of the results.\vspace{-0.5ex}
 
@@
 Significant prior work explores methods that can effectively map circuits to the carry logic for performance improvements~\cite{FPL10_FPGA_CarryChain}, or proposes alternative carry logic for FPGAs~\cite{FPGA_CarryChain_New1,FPGA_CarryChain_New2}.
-Hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply accumulates~\cite{XilinxDSP}.
-However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.
+Hard DSP blocks are also included in modern architectures to improve the area and performance of multiplications and multiply accumulates.
+However, most of these approaches are designed to accelerate computations with the conventional form of arithmetic.\vspace{-0.5ex}
 
@@
 However, as will be discussed in Section~\ref{Sec:OA_FPGA}, these approaches cannot be directly applied on many modern FPGAs, which typically have 6-input LUTs and four LUTs in a slice, such as the Xilinx Virtex series FPGAs and all Xilinx 7 series FPGAs~\cite{Virtex7}.
-Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for further optimization.
+Moreover, the move to the 6-LUT on the basic architecture opens new opportunities for further optimization.\vspace{-0.5ex}
 %However, the implementations of other key arithmetic primitives, such as online multipliers, lack exploration.
@@
 For online multipliers, the slice utilization of the proposed architecture drops of over $69\%$, with a frequency speed-up over $1.5\times$ in comparison to a direct implementation.
-When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$, which drops to $1.84\times$ when using the proposed new architecture.
+When compared to the multiplier with standard arithmetic, the direct implementation has an area overhead up to $8.11\times$, which drops to $1.84\times$ when using the proposed new architecture.\vspace{-0.5ex}
 
@@
 In contract, since online multipliers compute the output from the MSD first, hardware can be saved by not generating the LSDs in the first place.
-As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves up to $56\%$ slice usage in comparison to a standard multiplier with truncated output.
+As an example, if we are only interested in the most significant half of the product, we can create a digit parallel online multiplier that saves up to $56\%$ slice usage in comparison to a standard multiplier with truncated output.\vspace{-0.5ex}
 
@@
 
-In summary, the main contributions of this paper are:
+In summary, the main contributions of this paper are:\vspace{-0.5ex}
 \begin{enumerate}
@@
     \item Demonstration of the performance improvements of online operators in terms of area and frequency.
-\end{enumerate}
+\end{enumerate}\vspace{-1ex}
 
@@
 
-\section{Background: Online Arithmetic}\label{Sec:Background}
-\subsection{Key Features of Online Arithmetic}
+\section{Background: Online Arithmetic}\label{Sec:Background}\vspace{-0.5ex}
+\subsection{Key Features of Online Arithmetic}\vspace{-0.5ex}
 
@@
 For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$.
-Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
+Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.\vspace{-0.5ex}
 %
-\begin{figure}[htbp]
+\begin{figure}[tbp]
   \centering
@@
 Thus a standard number corresponds to several possible redundant representations.
-For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.
+For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.\vspace{-0.5ex}
+%
+\vspace{-.5ex}
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./Figures/SDAdder2.pdf}
+    \vspace{-7ex}
+  \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
+    \vspace{-2ex}
+  \label{Fig:Radix2SD_adder}
+\end{figure}
 
 Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
-Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.
+Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.\vspace{-0.5ex}
 
-\subsection{Binary Online Addition}
+\subsection{Binary Online Addition}\vspace{-0.5ex}
 Adders serve as a critical building block for arithmetic operations.
@@
 As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
-This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
+This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.\vspace{-0.5ex}
 %
-\begin{figure}[tbp]
-	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDAdder2.pdf}
-    \vspace{-6ex}
-	\caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
-    \vspace{-2ex}
-	\label{Fig:Radix2SD_adder}
-\end{figure}
 
@@
 
-\subsection{Binary Online Multiplication}
+\subsection{Binary Online Multiplication}\vspace{-0.5ex}
 Multiplication is another key arithmetic operator.
@@
 As the binary radix is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
-In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$ \cite{Ercegovac_OnlineMult}.
+In this case $sel()$ is given by (\ref{Eq:SelFunc_OM}), and the selection is based on two integer digits and one fractional digit of $W_{[j]}$ \cite{Ercegovac_OnlineMult}.\vspace{-0.5ex}
 %
@@
 \end{algorithm}
-\vspace{-1ex}
+\vspace{-1.5ex}
 
@@
 Hence the successive operations cannot commence until the result with full-precision is generated.
-This feature of online arithmetic has inspired research about dynamically control of computation precision in numerous applications~\cite{Online_Truncation}.
+This feature of online arithmetic has inspired research about dynamically control of computation precision in numerous applications~\cite{Online_Truncation}.\vspace{-0.5ex}
 
@@
 In Section~\ref{Sec:OM_FPGA}, we will first describe an optimized online multiplication algorithm and its FPGA implementation, which are designed specifically targeting digit parallel operations.
-Then we provide a modified structure which only generates the most significant half of the product in order to achieve extra area savings.
+Then we provide a modified structure which only generates the most significant half of the product in order to achieve extra area savings.\vspace{-0.5ex}
 
@@
 \section{Digit Parallel Online Adder for FPGAs}\label{Sec:OA_FPGA}
-\subsection{Related Works}
-There have been previous works about FPGA implementation of digit parallel online adders. From the literature, the existing approaches can be classified into three types:
+\subsection{Related Works}\vspace{-0.5ex}
+There have been previous works about FPGA implementation of digit parallel online adders. From the literature, the existing approaches can be classified into three types:\vspace{-0.5ex}
 
@@
 Instead, we focus on two-operand online addition that performs $Z=X+Y$, as shown in Fig.~\ref{Fig:Radix2SD_adder}.
-In comparison to type 3, this paper attempts to obtain the best performance from mainstream FPGAs instead of suggesting ways to modify the FPGA fabric.
+In comparison to type 3, this paper attempts to obtain the best performance from mainstream FPGAs instead of suggesting ways to modify the FPGA fabric.\vspace{-0.5ex}
 
@@
 	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan2.pdf}
-	\vspace{-3ex}
+	\vspace{-4ex}
 	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
@@
 Nevertheless, for FPGAs with 6-input LUTs (6-LUT) and four LUTs in a slice, such as the Xilinx Virtex series and all Xilinx 7 series FPGAs, directly applying these approaches will result in either resource waste or wrong results.
-For instance, if two \texttt{LB}s are mapped to a slice with four LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} should not be used because the its carry input cannot be explicitly initialized.
-Due to the same reason, the output of \texttt{XORCY2} should not be used.
+For instance, if two \texttt{LB}s are mapped to a slice with four LUTs as seen in Fig.~\ref{Fig:PreWorkVirtex6}, the outputs of \texttt{LB1} should not be used because its carry input cannot be explicitly initialized.
+Due to the same reason, the output of \texttt{XORCY2} should not be used.\vspace{-0.5ex}
 %
@@
 	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork2.pdf}
-	\vspace{-2ex}
+	\vspace{-3ex}
 	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
 	\label{Fig:PreWorkVirtex6}
-    \vspace{-2ex}
+    \vspace{-2.5ex}
 \end{figure}
 
-\subsection{Proposed Mapping Method}
+\subsection{Proposed Mapping Method}\vspace{-0.5ex}
 To tackle this problem, we first present an alternative structure of the online adder to enable an efficient FPGA mapping.
@@
 In this case they can be mapped individually on two LUTs.
-The second FA, which generates the outputs, is unchanged and can be implemented using the fast carry logic.
+The second FA, which generates the outputs, is unchanged and can be implemented using the fast carry logic.\vspace{-0.5ex}
 
@@
 	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit2.pdf}
-	\vspace{-2ex}
+	\vspace{-3ex}
 	\caption{Alternative structure of online adder.
@@
 The logic to generate the MSD and the LSD can be combined into one slice as observed from Fig.~\ref{Fig:ModifiedOA}.
-Therefore using this mapping method the resources within one slice can be fully utilized, leading to a significant area reduction.
+Therefore using this mapping method the resources within one slice can be fully utilized, leading to a significant area reduction.\vspace{-0.5ex}
 
@@
 
-In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) can be calculated as given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.
+In this mapping approach, the area figures of the online adder in terms of the number of LUTs and slices with respect to the operand word-lengths ($N$) can be calculated as given in (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), respectively.\vspace{-0.5ex}
 %
@@
 \normalsize
+\vspace{-0.5ex}
 \end{eqnarray}
@@
 
-\subsection{Performance Analysis}\label{subsec:OA_Performance}
+\subsection{Performance Analysis}\label{subsec:OA_Performance}\vspace{-0.5ex}
 In our experiments, we compare the proposed online adder (\texttt{OA\_new}) against the original design which is implemented using functional descriptions in Verilog based on 4:2 compressors (\texttt{OA\_behv}).
@@
 While our experiments target on Xilinx Virtex-6 FPGAs (speed grade -1), our methods are applicable to any FPGAs with the same slice architecture such as all the Xilinx 7 series FPGAs.
-Notice that in order to utilize the carry resources and avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.
+Notice that in order to utilize the carry resources and avoid logic optimizations by the synthesis tool, the Xilinx primitive component ``\texttt{Carry4}" is used to create \texttt{OA\_new}.\vspace{-0.5ex}
 
@@
 Algorithm \ref{Algorithm:OnlineMult} as described in Section~\ref{Sec:Background} can be synthesized into a unrolled digit parallel structure.
-A recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14_REVIEW}.
+A recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14}.
 %This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
@@
 In addition, we also compare the \texttt{OM} with the conventional binary arithmetic multiplier.
-The conventional multiplier is created using the Xilinx Core Generator with speed optimization~\cite{XilinxMult}, and it is implemented based on LUTs without DSPs for a fairer comparison.
+The conventional multiplier is created using the Xilinx Core Generator with speed optimization, and it is implemented based on LUTs without DSPs for a fairer comparison.
 
@@
 We see that although the Timing Analyzer predicts slower frequencies for the \texttt{OM}s, they actually operate faster than \texttt{CoreGen} without the occurrence of timing errors.
-This is in accordance with the results seen in the previous work \cite{SKDAC14_REVIEW}.
+This is in accordance with the results seen in the previous work \cite{SKDAC14}.
 

### 2014-10-12 FPT2014/bare_conf.tex
add acknowledgement and change format again

@@
 As a result, this makes the \texttt{OA\_new} more attractive for a wider range of applications.
-Furthermore, the speed-ups of \texttt{OA\_new} against \texttt{OA\_behv} are over $1.2\times$.
+Furthermore, the speed-ups of \texttt{OA\_new} against \texttt{OA\_behv} are over $1.2\times$.\vspace{-0.5ex}
 
@@
 It is unlikely that the overhead can be completely avoided when using an \texttt{OA} because of the redundant number system.
-Nevertheless, with the reduced overhead, using \texttt{OA} to take advantage of the graceful degradation when operating beyond the deterministic clocking region may become more attractive for an FPGA developer.
-
-%However, our design still costs more area than an \texttt{RCA}, with an area overhead of $80\%\sim98\%$ in terms of LUTs, and up to $88\%$ in terms of slices.
-This is because for a single adder, the area overhead brought by the redundant number representations cannot be removed.
-%However research has shown that this overhead can be reduced for multiple-operand adders or adder trees [xxx].
+Nevertheless, with the reduced overhead, using \texttt{OA} to take advantage of the graceful degradation when operating beyond the deterministic clocking region may become more attractive for an FPGA developer.\vspace{-0.5ex}
 
@@
 A recent study has shown that the digit-parallel online multiplier (\texttt{OM}) is also more tolerant to timing violations in comparison to the conventional arithmetic, because timing errors initially affect the LSDs and this will lead to smaller error magnitude~\cite{SKDAC14}.
-%This implementation method is straightforward and can be directly utilized to design other digit parallel online operators.
+\vspace{-0.5ex}
 
@@
 Also, the word-length of signals $H_{[j]}$, $W_{[j]}$ and $P_{[j]}$ is $(N+2+\delta)$, because the selection function needs two integer digits and one fractional digit to generate $z_j$, as described in Section~\ref{Sec:Background}.
-Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.
+Third, this \texttt{OM} architecture is not optimized specifically for FPGA technology.\vspace{-0.5ex}
 %In comparison, an $N$-digit array multiplier, there are only $(N-1)$ rows, each of which is basically an $N$-digit ripple-carry adder.
@@
 For the same reason, $H[j]$, which takes one digit of each input per stage as shown in the original algorithm, can be optimized to take one partial product $Xy_j$ or $Yx_j$ per stage.
-To summarize, the modified algorithm for digit parallel online multiplication is described in Algorithm~\ref{Algorithm:OM_DigitParallel}, where $N$ denotes the operand word-length, function $frac(W_{[N]})$ refers to select the fractional digits of $W_{[N]}$, and the selection function $sel()$ is given previously in (\ref{Eq:SelFunc_OM}).
+To summarize, the modified algorithm for digit parallel online multiplication is described in Algorithm~\ref{Algorithm:OM_DigitParallel}, where $N$ denotes the operand word-length, function $frac(W_{[N]})$ refers to select the fractional digits of $W_{[N]}$, and the selection function $sel()$ is given previously in (\ref{Eq:SelFunc_OM}).\vspace{-0.5ex}
 
@@
 
-\subsection{FPGA Implementation}
+\subsection{FPGA Implementation}\vspace{-0.5ex}
 We now present an area efficient implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} on FPGAs.
@@
 Similarly the generation of $P_{[j]}$ can also be implemented using one 6-LUT, since only the integer digits of $W_{[j]}$ need to be modified due to the selection of $Z_{[j]}$.
-In addition, the structure of Stage 1 in Fig~\ref{Fig:PMStructure}(a) can be further optimized by removing the online adder, because $P_{[0]}=0$.
+In addition, the structure of Stage 1 in Fig~\ref{Fig:PMStructure}(a) can be further optimized by removing the online adder, because $P_{[0]}=0$.\vspace{-0.5ex}
 %
@@
 	\label{Fig:PMStructure}
-	\vspace{-1ex}
+	\vspace{-2ex}
 \end{figure}
@@
 Alternatively, instead of using extra logic to generate $Xy_j$, it can be merged into the corresponding LUTs in the online adder by fully utilizing all six LUT inputs, as shown on the right of Fig.\ref{Fig:PartialProduct}.
-Notice that this approach is only available for FPGAs with 6-LUTs.
+Notice that this approach is only available for FPGAs with 6-LUTs.\vspace{-0.5ex}
 %
@@
 	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.pdf}
-	\vspace{-1ex}
+	\vspace{-2.5ex}
 	\caption{Left: Direct implementation with extra logic to generate partial products.
@@
 	\label{Fig:PartialProduct}
-	\vspace{-1ex}
+	\vspace{-1.5ex}
 \end{figure}
@@
 Therefore based on (\ref{Eq:OAareaLUT}) and (\ref{Eq:OAareaSlice}), the number of LUTs and the number of slices used by the \texttt{OM} is given in (\ref{Eq:OMareaLUT}) and (\ref{Eq:OMareaSlice}), respectively.
-Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and slices used by the first stage, which is built without online adders.
+Note that $L_{S1}$ and $S_{S1}$ denote the number of LUTs and slices used by the first stage, which is built without online adders.\vspace{-0.5ex}
 %
@@
 
-\subsection{Structure Optimization for Half Precision Results}
+\subsection{Structure Optimization for Half Precision Results}\vspace{-0.5ex}
 As discussed before, normally the multiplier is connected with other arithmetic operators in real applications.
@@
 In a conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
-However, both the computation time and the structure remains unchanged, because the results are generated from LSDs.
+However, both the computation time and the structure remains unchanged, because the results are generated from LSDs.\vspace{-0.5ex}
 
@@
 The word-length of signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PMStructure_MSDhalf}(b).
-It can be seen that instead of keeping identical word-length throughout the stages (in Fig.~\ref{Fig:PMStructure}), in the modified structure the signal word-lengths depend on the stage number $j$ and fewer bits of signals are needed for LSD stages.
-
+It can be seen that instead of keeping identical word-length throughout the stages (in Fig.~\ref{Fig:PMStructure}), in the modified structure the signal word-lengths depend on the stage number $j$ and fewer bits of signals are needed for LSD stages.\vspace{-3ex}
+%
 \begin{figure}[tbp]
@@
 	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
+  \vspace{-2ex}
 	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.
@@
 	\label{Fig:PMStructure_MSDhalf}
-	\vspace{-1ex}
+	\vspace{-2ex}
 \end{figure}
@@
 %\section*{Acknowledgment}
+\section*{Acknowledgment}
+%\vspace{-0.5ex}
+This work is supported by the EPSRC (Grants EP/I020557/1 and EP/I012036/1).
 

### 2014-10-15 FPT2014/bare_conf.tex
change file format for figures

@@
 % Graph package
-\ifx\pdfoutput\undefined
+%\ifx\pdfoutput\undefined
 \usepackage{graphicx}
-\else
-\usepackage[pdftex]{graphicx}
-\fi
-\usepackage{epstopdf}
+%\else
+%\usepackage[pdftex]{graphicx}
+%\fi
+%\usepackage{epstopdf}
 
@@
 
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
 \usepackage[caption=false,font=footnotesize]{subfig}
@@
 
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-%\IEEEpeerreviewmaketitle
+f
 
@@
 
-%In summary, the main contributions of this paper are efficient methods to map online adders and multipliers to modern FPGAs.
-The performance improvements in terms of silicon area and operating frequency with these new architectures mean that using online operators is much more attractive for an end user.
-The benefits of these operators .
-
 \section{Background: Online Arithmetic}\label{Sec:Background}\vspace{-0.5ex}
@@
   %\vspace{-2.5ex}
-  \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.pdf}
+  \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.eps}
   \vspace{-4ex}
@@
   \centering
-  \includegraphics[width=.5\textwidth]{./Figures/SDAdder2.pdf}
+  \includegraphics[width=.5\textwidth]{./Figures/SDAdder.eps}
     \vspace{-7ex}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan2.pdf}
+	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan.eps}
 	\vspace{-4ex}
@@
 	\centering
-	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit2.pdf}
+	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit.eps}
 	\vspace{-3ex}
@@
 	\centering
-	\includegraphics[width=.49\textwidth]{./Figures/SDadder_FastCarry_New2.pdf}
+	\includegraphics[width=.49\textwidth]{./Figures/SDadder_FastCarry_New.eps}
 	\vspace{-5ex}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.pdf}
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.eps}
 	\vspace{-3ex}
@@
 	\centering
-	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.pdf}
+	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.eps}
 	\vspace{-2.5ex}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.pdf}
+	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.eps}
   \vspace{-2ex}
@@
 
-%\section{Results}
-
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
 \section{Conclusion}
@@
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
 \bibliographystyle{./IEEEtran}

### 2014-11-10 WAP2015/wap2015.tex
some paragraphs

\documentclass[10pt, conference, compsocconf]{IEEEtran}
% Add the compsocconf option for Computer Society conferences.
%
% If IEEEtran.cls has not been installed into the LaTeX system files,
% manually specify the path to it like:
% \documentclass[conference]{../sty/IEEEtran}
\usepackage{cite}

\usepackage[cmex10]{amsmath}
\usepackage{amssymb}

\usepackage{algorithm}
\usepackage{array}
\usepackage{algpseudocode}
\usepackage{indentfirst}
\usepackage[pdftex]{graphicx}
\usepackage[tight,footnotesize]{subfigure}

%\usepackage{algorithmic}

\begin{document}

\title{Evaluation of Optimum Arithmetic Operators For Approximate Datapath Design}

\author{\IEEEauthorblockN{Kan Shi and George A. Constantinides}
\IEEEauthorblockA{Department of Electrical and Electronic Engineering\\
Imperial College London\\
London, UK\\
Email: {k.shi11, g.contantinides}@imperial.ac.uk}
%\and
%\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
%\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
%line 2: name of organization, acronyms acceptable\\
%line 3: City, Country\\
%line 4: Email: name@xyz.com}
}

\maketitle

\begin{abstract}
The abstract goes here.

\end{abstract}

\begin{IEEEkeywords}
approximate computing; datapath; computer arithmetic;

\end{IEEEkeywords}

\section{Introduction}

\section{Background}
\subsection{Approximate Datapath Design}

\subsection{Online Arithmetic}

Online arithmetic has been found using in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}. Online arithmetic was originally designed for digit-serial operation, as illustrated in Fig~\ref{Fig:OnlineDataFlow}. It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required, where $\delta$ is called the ``online delay''. $\delta$ is normally a small constant, which is independent of the precision. For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$. Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
%
\begin{figure}[tbp]
  \centering
  %\vspace{-2.5ex}
  \includegraphics[width=.42\textwidth]{./figures/OnlineArithmetic_DataFlow.eps}
  %\vspace{-1ex}
  \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
  \vspace{-2ex}
  \label{Fig:OnlineDataFlow}
\end{figure}
%
\begin{eqnarray}\label{Eq:Online_Operands}
\footnotesize
  X_{[j]}=\sum_{i=1}^{j+\delta}x_ir^{-i},~Y_{[j]}=\sum_{i=1}^{j+\delta}y_ir^{-i},~Z_{[j]}=\sum_{i=1}^{j}z_ir^{-i}
\normalsize
\end{eqnarray}

MSD-first operation is possible only if a redundant number system is used. Normally there are two most commonly used redundant number representations: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}. With SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$. In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots,r-1\}$. Thus a standard number corresponds to several possible redundant representations. For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.

Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs. Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.

\section{Comparison of Different Adder Structures}
\subsection{Ripple Carry Adder}
Adders serve as a key building block for arithmetic operations. In general, the ripple carry adder (RCA) is the most straightforward and widely used adder structure. As such, in our previous work we proposed probabilistic models of overclocking errors for RCA.

For an $n$-bit RCA, it is composed of $n$ serial-connected full adders (FA). Typically the maximum frequency of RCA is determined by the longest carry propagation. Under the assumption that the carry propagation delay of each FA is a constant value $\mu$, the critical path of the RCA is: $\mu_{RCA}=n\mu$. For the sampling period $T_S$, it follows that if $T_S\geqslant\mu_{RCA}$, correct result will always be sampled; otherwise if $T_S<\mu_{RCA}$, intermediate be sampled and potentially generating errors. In the previous work, the mean value of overclocking error is modeled as given in (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation in bits.
%
\begin{eqnarray}\label{Eq:MeanError_RCA}
    E_O=\left\{
        \begin{matrix}
            2^{-b}-2^{-n-1}, & \textrm{if $b\leq n$}\\
            0, & \textrm{otherwise}
        \end{matrix}
        \right.
\end{eqnarray}
%
\begin{eqnarray}\label{Eq:b}
    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
\end{eqnarray}

On the other hand, a specific timing target can be met by truncating the word-length of RCA while timing violation is not permitted. This will result in truncation error for most data.  The mean value of truncation error is also modeled as given in~(\ref{Eq:MeanTruncError_RCA}) [xxx], where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively. 
%
\begin{eqnarray}\label{Eq:MeanTruncError_RCA}
    E_O=\left\{
        \begin{matrix}
            2^{-n}-2^{-k}, & \textrm{if $n<k$}\\
            0, & \textrm{otherwise}
        \end{matrix}
        \right.
\end{eqnarray}

In this paper we consider two design scenarios for RCA: one is the overclocking scenario where timing violation is allowed to happen while maintaining the original word-length; the other is the trad scenario by truncating RCA word-length to meet timing. For a given $f_S$, in the first design scenario we have $n=k$. In the second design scenario we have $n=b-1$ to prevent timing violation while minimizing the value of $E_O$. Therefore the comparison between the two scenarios in mean error value is given in (\ref{Eq:ErrorCompare_RCA}) by updating (\ref{Eq:MeanError_RCA}) and (\ref{Eq:MeanTruncError_RCA}) respectively. As seen in (\ref{Eq:ErrorCompare_RCA}), in theory the mean value of error in the overclocking scenario ($E_{oc}$) is two times smaller than that in the traditional scenario ($E_{trad}$).
%
\begin{eqnarray}\label{Eq:ErrorCompare_RCA}
    \frac{E_{oc}}{E_{trad}} = \frac{2^{-b}-2^{-n-1}|_{n=k}}{2^{-n}-2^{-k}|_{n=b-1}}=\frac{1}{2}
\end{eqnarray}

\subsection{Carry Select Adder}

\subsection{Online Adder}
\subsubsection{Algorithm}
The structure of a digit-parallel online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}. The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA). A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition. As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands. This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
%
\begin{figure}[tbp]
  \centering
  \includegraphics[width=.45\textwidth]{./figures/SDAdder.eps}
  %\vspace{-7ex}
  %\vspace{-2ex}
  \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
    \vspace{-2ex}
  \label{Fig:Radix2SD_adder}
\end{figure}

\begin{eqnarray}\label{Eq:b}
    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
\end{eqnarray}

\section{Comparison of Different Multiplier Structures}
\subsection{Standard Binary Multiplier}

\subsection{Online Multiplier}
\subsubsection{Algorithm}
Similar to online addition, online multiplication can also be implemented in a unrolled digit-parallel manner, of which the optimized algorithm is shown in Algorithm~\ref{Algorithm:OM_DigitParallel} [xxx]. In this algorithm, both inputs and outputs are $N$-digit numbers as given in (\ref{Eq:Online_Operands}). For a given iteration $j$, the product digit $z_j$ is generated MSD-first through a selection function $sel()$. For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence. As the binary radix is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$. In this case $sel()$ is given by (\ref{Eq:SelFunc_OM})~\cite{Ercegovac_OnlineMult}.

\begin{algorithm}[tbp]
  \caption{Digit Parallel Online Multiplication}\label{Algorithm:OM_DigitParallel}
  \begin{algorithmic}[1]
    \State \textbf{Initialization:} $P_{[0]}=0$                     \vspace{.5ex}
    \For{$j=1,~2,~\cdots,~N$}                                       \vspace{.5ex}
        \State $Xy_j \leftarrow X \cdot y_j$                        \vspace{.5ex}
        \State $W_{[j]}    \leftarrow  P_{[j-1]} + Xy_j$            \vspace{.5ex}
        \State $z_{j}  ~~      \leftarrow  sel(W_{[j]})$            \vspace{.5ex}
        \State $P_{[j+1]}  \leftarrow  r\left(W_{[j]}-Z_{[j]}\right)$   \vspace{.5ex}
    \EndFor                                                         \vspace{.5ex}
    \State $Z_{[N+1:2N]} \leftarrow frac(W_{[N]})$                  \vspace{.5ex}
  \end{algorithmic}
  \vspace{-1ex}
\end{algorithm}

\begin{eqnarray}\label{Eq:SelFunc_OM}
\small
  sel(W_{[j]})=\begin{cases}
    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
  \end{cases}
\normalsize
\end{eqnarray}

In our previous work, an area efficient implementation

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.42\textwidth]{./figures/ParallelMult_Structure.eps}
  \caption{(a) Structure of a 4-digit online multiplier. (b) Structure of one stage. The word-length of all signals are labeled in digits, $N$ is the word-length of input signals.}
    \vspace{-2ex}
  \label{Fig:PM}
\end{figure}

\subsubsection{Structure Optimization for Half Precision Results}
In actual applications, normally the multiplier is connected with other arithmetic operators. If the multiplication result is utilized for subsequent operations, and a consistent word-length is used throughout the system, then only the most significant half of the product is required. In a conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products. However, both the computation time and the structure remains unchanged, because results are generated from LSDs.

In comparison, OM offers the flexibility to simplify the structure corresponding to the required precision. This is possible because in an OM, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system. This will potentially lead to a more area efficient design. For example, the modified structure diagram of a 4-digit OM is illustrated in Fig.~\ref{Fig:PM_half}(a). The word-length of signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PM_half}(b). Notice that instead of keeping identical word-length throughout the stages (in Fig.~\ref{Fig:PM}), in the modified structure the signal word-lengths depend on the stage number $j$ and hence fewer bits of signals are needed for LSD stages.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=.42\textwidth]{./figures/ParallelMult_MSDhalf.eps}
  \caption{(a) A 4-digit online multiplier with half precision results. (b) Structure of stage $j$, with the word-length of all signals labeled.}
    \vspace{-2ex}
  \label{Fig:PM_half}
\end{figure}

\section{Conclusion}

\section*{Acknowledgment}

\bibliographystyle{./IEEEtran}

\bibliography{./IEEEabrv,./Reference}

\end{document}

### 2014-11-11 WAP2015/wap2015.tex
add some adder sections

@@
 \subsection{Carry Select Adder}
+Although smaller value of mean error can be achieved in the overclocking scenario, it costs extra area because the full precision is maintained.
+Instead, alternative adder structures, such as carry select adder (CSA), are originally designed to trade silicon area for low latency.
+In a CSA, the carry chain is divided into multiple overlapped stages, and each stage contains two RCAs and two multiplexers, as shown in Fig.
+xxx(a) and Fig.
+xxx(b).
+For a given input, two additions are performed simultaneously within a single stage where the carry input is zero and one separately.
+One of these two results is then selected according to the actual carry input.
+Although this structure brings performance benefits, it costs extra hardware resources compared to a standard RCA because the carry chain is duplicated.
+Furthermore, multiplexers are area-expensive to implement with FPGA technology.
 
-\subsection{Online Adder}
-\subsubsection{Algorithm}
-The structure of a digit-parallel online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
+In this paper, we take CSA with different stages into comparison when considering a variety of accuracy, performance and area trade-offs. The results are shown in Section.xxx.
+
+\subsection{Online Adder}\label{subsec:online_adder}
+%\subsubsection{Structure}
+In addition to standard binary arithmetic, alternative forms of computer arithmetic was studied to boost performance.
+For example, adder with online arithmetic is also designed for low latency at the cost of more silicon area.
+The structure of a digit-parallel online adder (OA) where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
 The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA).
 A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
-This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
+As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, at the expenses of one extra FA for each digit of operands.
 %
@@
 
-\begin{eqnarray}\label{Eq:b}
-    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
-\end{eqnarray}
+\subsection{Comparison of Adders}
+In this section, we initially demonstrate the benefits of CSA and OA in accuracy and performance, as well as the area overhead in comparison to RCA.
+As an example, the maximum word-length with respect to a variety of operating frequencies for RCA, CSA and OA is illustrated in Fig.~xxx.
+Notice that in this case, overclocking error is not allowed to happen and the conventional design scenario is evaluated for all structures.
+
+Correspondingly, the area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA is depicted in Fig.~xxx.
+Clearly we see that for a given frequency, CSA costs xxx (4 stages) and xxx (2 stages) area than RCA, and OA is almost constantly two times larger than RCA as predicted in Section~\ref{subsec:online_adder}.
+Therefore, we incorporate silicon area as another design metric besides accuracy and performance, and evaluate the optimum adder structure under various design trade-offs.
 

### 2014-11-12 WAP2015/wap2015.tex
add some figures for adders

@@
 
-\title{Evaluation of Optimum Arithmetic Operators For Approximate Datapath Design}
+\title{Evaluation of Design Trade-offs for Approximate Arithmetic Operators}
+
+%Evaluation of Optimum Arithmetic Operators For Approximate Datapath Design
 
@@
 
-Online arithmetic has been found using in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
+As an alternative form of computer arithmetic, online arithmetic has been used in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
 Online arithmetic was originally designed for digit-serial operation, as illustrated in Fig~\ref{Fig:OnlineDataFlow}.
@@
 
-In this paper, we take CSA with different stages into comparison when considering a variety of accuracy, performance and area trade-offs. The results are shown in Section.xxx.
+%In this paper, we take CSA with different stages into comparison when considering a variety of accuracy, performance and area trade-offs. The results are shown in Section.xxx.
 
@@
   \includegraphics[width=.45\textwidth]{./figures/SDAdder.eps}
-  %\vspace{-7ex}
-  %\vspace{-2ex}
   \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
-    \vspace{-2ex}
   \label{Fig:Radix2SD_adder}
@@
 
-\subsection{Comparison of Adders}
+\subsection{Design Trade-offs for Adders}
 In this section, we initially demonstrate the benefits of CSA and OA in accuracy and performance, as well as the area overhead in comparison to RCA.
-As an example, the maximum word-length with respect to a variety of operating frequencies for RCA, CSA and OA is illustrated in Fig.~xxx.
+As an example, the maximum word-length with respect to a variety of operating frequencies for RCA, CSA and OA is illustrated in Fig.~\ref{Fig:max_wl_adder}.
 Notice that in this case, overclocking error is not allowed to happen and the conventional design scenario is evaluated for all structures.
+%
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./figures/exp/max_wl.eps}
+  \caption{The maximum word-length of different adder structures.}
+  \label{Fig:max_wl_adder}
+\end{figure}
 
-Correspondingly, the area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA is depicted in Fig.~xxx.
-Clearly we see that for a given frequency, CSA costs xxx (4 stages) and xxx (2 stages) area than RCA, and OA is almost constantly two times larger than RCA as predicted in Section~\ref{subsec:online_adder}.
+Correspondingly, the area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA is depicted in Fig.~\ref{Fig:area_adder}.
+Clearly we see that for a given frequency, CSA costs up to $4.5\times$ (4 stages) and $3.1\times$ (2 stages) area than RCA, and OA is up to $3.8\times$ larger than RCA for some frequency values.
 Therefore, we incorporate silicon area as another design metric besides accuracy and performance, and evaluate the optimum adder structure under various design trade-offs.
+In this paper, we examine both the overclocking scenario and the conventional scenario for RCA, while only considering the conventional scenario for other adder structures.
+%the considered design scenarios and adder structures are summarized in Table.xxx.
+% some figure goes here
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./figures/exp/area_adders.eps}
+  \caption{The maximum word-length of different adder structures.}
+  \label{Fig:area_adder}
+\end{figure}
+
+In general, the evaluation could be of interest to a circuit designer in several ways.
+First, suppose the algorithm designer wish the circuit to run at a given frequency within a given area budget, while achieving the minimum output error.
+Decisions must then be made on which adder structure achieves this minimum, and whether the circuit should be overclocked.
+
+As an example slice through the design space, we record the mean relative error (MRE) with respect to a range of operating frequencies for different design scenarios when the area budget is set to xxx.
+MRE can be calculated as given in (xxx).
+Notice that in Fig.~xxx, the optimum adder structure is labeled.
+
+Under this given area budget, both CSA and OA cannot be implemented with full precision, and this leads to large truncation errors
 
@@
 
-In our previous work, an area efficient implementation
+The parallel implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} is illustrated in Fig.~\ref{Fig:PM} where $N=4$. The details of implementation are addressed in our previous work [xxx].
 

### 2014-11-18 WAP2015/mult.tex
add main result graphs, abstract and some introductions

--- 2014-11-10 WAP2015/wap2015.tex
@@
-\documentclass[10pt, conference, compsocconf]{IEEEtran}
-% Add the compsocconf option for Computer Society conferences.
-%
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-\usepackage{cite}
-
-\usepackage[cmex10]{amsmath}
-\usepackage{amssymb}
-
-\usepackage{algorithm}
-\usepackage{array}
-\usepackage{algpseudocode}
-\usepackage{indentfirst}
-\usepackage[pdftex]{graphicx}
-\usepackage[tight,footnotesize]{subfigure}
-
-%\usepackage{algorithmic}
-
-\begin{document}
-
-\title{Evaluation of Optimum Arithmetic Operators For Approximate Datapath Design}
-
-\author{\IEEEauthorblockN{Kan Shi and George A. Constantinides}
-\IEEEauthorblockA{Department of Electrical and Electronic Engineering\\
-Imperial College London\\
-London, UK\\
-Email: {k.shi11, g.contantinides}@imperial.ac.uk}
-%\and
-%\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
-%\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
-%line 2: name of organization, acronyms acceptable\\
-%line 3: City, Country\\
-%line 4: Email: name@xyz.com}
-}
-
-\maketitle
-
-\begin{abstract}
-The abstract goes here.
-
-\end{abstract}
-
-\begin{IEEEkeywords}
-approximate computing; datapath; computer arithmetic;
-
-\end{IEEEkeywords}
-
-\section{Introduction}
-
-\section{Background}
-\subsection{Approximate Datapath Design}
-
-\subsection{Online Arithmetic}
-
-Online arithmetic has been found using in numerous applications such as signal processing and control algorithms~\cite{Online_FPGADSP,Online_Control}.
-Online arithmetic was originally designed for digit-serial operation, as illustrated in Fig~\ref{Fig:OnlineDataFlow}.
-It can be seen that in order to generate the first output digit, $\delta$ digits of inputs are required, where $\delta$ is called the ``online delay''.
-$\delta$ is normally a small constant, which is independent of the precision.
-For ease of discussion, for the rest of this paper, the input data is assumed to be fixed point numbers in the range $(-1,1)$.
-Based on this premise, the online representation of $N$-digit operands and result at iteration $j$ are given by (\ref{Eq:Online_Operands}), where $j\in[-\delta,N-1]$ and $r$ denotes the radix \cite{Ercegovac_Book}.
-%
-\begin{figure}[tbp]
-  \centering
-  %\vspace{-2.5ex}
-  \includegraphics[width=.42\textwidth]{./figures/OnlineArithmetic_DataFlow.eps}
-  %\vspace{-1ex}
-  \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
-  \vspace{-2ex}
-  \label{Fig:OnlineDataFlow}
-\end{figure}
-%
-\begin{eqnarray}\label{Eq:Online_Operands}
-\footnotesize
-  X_{[j]}=\sum_{i=1}^{j+\delta}x_ir^{-i},~Y_{[j]}=\sum_{i=1}^{j+\delta}y_ir^{-i},~Z_{[j]}=\sum_{i=1}^{j}z_ir^{-i}
-\normalsize
-\end{eqnarray}
-
-MSD-first operation is possible only if a redundant number system is used.
-Normally there are two most commonly used redundant number representations: carry-save (CS) \cite{CSadder} and signed-digit (SD) \cite{RedundantNumber}.
-With SD representation, each digit is represented using a redundant digit set $\{-a, \cdots,-1,0, 1, \cdots, a\}$, where $a\in[r/2,r-1]$.
-In comparison, the standard non-redundant representation only uses a digit set $\{0,\cdots,r-1\}$.
-Thus a standard number corresponds to several possible redundant representations.
-For example, the binary number $0.011$ can be represented in SD form as $0.1\overline{1}1$, $0.10\overline{1}$ or $0.011$ among many other possible representations.
-
-Due to the redundancy, the MSDs of the result can be calculated using partial information from both inputs.
-Then the value of the number can be revised using the subsequent digits, because each number has multiple representations.
-
-\section{Comparison of Different Adder Structures}
-\subsection{Ripple Carry Adder}
-Adders serve as a key building block for arithmetic operations.
-In general, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
-As such, in our previous work we proposed probabilistic models of overclocking errors for RCA.
-
-For an $n$-bit RCA, it is composed of $n$ serial-connected full adders (FA).
-Typically the maximum frequency of RCA is determined by the longest carry propagation.
-Under the assumption that the carry propagation delay of each FA is a constant value $\mu$, the critical path of the RCA is: $\mu_{RCA}=n\mu$.
-For the sampling period $T_S$, it follows that if $T_S\geqslant\mu_{RCA}$, correct result will always be sampled; otherwise if $T_S<\mu_{RCA}$, intermediate be sampled and potentially generating errors.
-In the previous work, the mean value of overclocking error is modeled as given in (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation in bits.
-%
-\begin{eqnarray}\label{Eq:MeanError_RCA}
-    E_O=\left\{
-        \begin{matrix}
-            2^{-b}-2^{-n-1}, & \textrm{if $b\leq n$}\\
-            0, & \textrm{otherwise}
-        \end{matrix}
-        \right.
-\end{eqnarray}
-%
-\begin{eqnarray}\label{Eq:b}
-    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
-\end{eqnarray}
-
-On the other hand, a specific timing target can be met by truncating the word-length of RCA while timing violation is not permitted.
-This will result in truncation error for most data.
-The mean value of truncation error is also modeled as given in~(\ref{Eq:MeanTruncError_RCA}) [xxx], where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively.
-%
-\begin{eqnarray}\label{Eq:MeanTruncError_RCA}
-    E_O=\left\{
-        \begin{matrix}
-            2^{-n}-2^{-k}, & \textrm{if $n<k$}\\
-            0, & \textrm{otherwise}
-        \end{matrix}
-        \right.
-\end{eqnarray}
-
-In this paper we consider two design scenarios for RCA: one is the overclocking scenario where timing violation is allowed to happen while maintaining the original word-length; the other is the trad scenario by truncating RCA word-length to meet timing.
-For a given $f_S$, in the first design scenario we have $n=k$.
-In the second design scenario we have $n=b-1$ to prevent timing violation while minimizing the value of $E_O$.
-Therefore the comparison between the two scenarios in mean error value is given in (\ref{Eq:ErrorCompare_RCA}) by updating (\ref{Eq:MeanError_RCA}) and (\ref{Eq:MeanTruncError_RCA}) respectively.
-As seen in (\ref{Eq:ErrorCompare_RCA}), in theory the mean value of error in the overclocking scenario ($E_{oc}$) is two times smaller than that in the traditional scenario ($E_{trad}$).
-%
-\begin{eqnarray}\label{Eq:ErrorCompare_RCA}
-    \frac{E_{oc}}{E_{trad}} = \frac{2^{-b}-2^{-n-1}|_{n=k}}{2^{-n}-2^{-k}|_{n=b-1}}=\frac{1}{2}
-\end{eqnarray}
-
-\subsection{Carry Select Adder}
-
-\subsection{Online Adder}
-\subsubsection{Algorithm}
-The structure of a digit-parallel online adder where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
-The module ``3:2'' denotes a 3:2 compressor, which takes three inputs and generates two outputs, and is logically equivalent to a full adder (FA).
-A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, with the cost of one extra FA for each digit of operands.
-This makes the online adder suitable for building up more complex arithmetic operators such as multipliers to accelerate the sum of partial products \cite{RedundantMult_1987}.
-%
-\begin{figure}[tbp]
-  \centering
-  \includegraphics[width=.45\textwidth]{./figures/SDAdder.eps}
-  %\vspace{-7ex}
-  %\vspace{-2ex}
-  \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
-    \vspace{-2ex}
-  \label{Fig:Radix2SD_adder}
-\end{figure}
-
-\begin{eqnarray}\label{Eq:b}
-    b:=\left\lceil \frac{T_S}{\mu} \right\rceil=\left\lceil \frac{1}{\mu\cdot f_S}\right\rceil
-\end{eqnarray}
-
 \section{Comparison of Different Multiplier Structures}
@@
 \end{figure}
-
-\section{Conclusion}
-
-\section*{Acknowledgment}
-
-\bibliographystyle{./IEEEtran}
-
-\bibliography{./IEEEabrv,./Reference}
-
-\end{document}

### 2014-11-18 WAP2015/wap2015.tex
add main result graphs, abstract and some introductions

@@
 
-\title{Evaluation of Design Trade-offs for Approximate Arithmetic Operators}
-
+\title{Evaluation of Design Trade-offs for Adders\\ in Approximate Datapath}
+%Evaluation of Design Trade-offs for Approximate Arithmetic Operators
 %Evaluation of Optimum Arithmetic Operators For Approximate Datapath Design
@@
 London, UK\\
-Email: {k.shi11, g.contantinides}@imperial.ac.uk}
+Email: \{k.shi11, g.contantinides\}@imperial.ac.uk}
 %\and
@@
 \begin{abstract}
-The abstract goes here.
+Releasing the stringent accuracy requirement would potentially offer greater freedom to create a design with better performance or energy efficiency.
+In this paper, we evaluate the design trade-offs for adders, which are key building blocks for many applications.
+We demonstrate the optimum design metric for adders, under the consideration of various design constraints, such as accuracy, operating frequency, silicon area, different types of adder structure and even alternative form of computer arithmetic for adder implementation.
+Two design scenarios are compared: one is the conventional design scenario where timing closure is met by adjusting operand word-lengths.
+The other is an overclocking scenario where timing violations are allowed to occur.
+We show that applying the overclocking approach to ripple carry adders can be more beneficial than using fast adders to achieve similar latency, because the worst cases only happen with very small probabilities.
+We also show that using the conventional approach on adders with new form of computer arithmetic is optimal for a wide range of design constraints.
+
+%We show that instead of losing precision to ensure timing closure, allowing timing violations to happen can be beneficial, because the worst case scenario only happens with a very small probability.
 
@@
 \begin{IEEEkeywords}
-approximate computing; datapath; computer arithmetic;
+approximate computing; adder; overclocking; online arithmetic;
 
@@
 \section{Introduction}
+Circuit performance has been increased tremendously over the past decades.
+However, in recent years people have observed an end of performance improvement [xx] due to the scaling of CMOS technology to the nanometer regime.
+In order to boost circuit performance, two standard design techniques are commonly adopted: one is to heavily pipeline the datapath, the other is to reduce the design precision.
+For the first technique, pipelining can be used to increase operating frequency, whereas the overall computational latency will not be affected.
+Therefore the application of this technique is limited in many embedded applications, which are often designed with strict latency specifications.
+The second technique is common especially with FPGA technology, which embodies the flexibility to implement customized variable representation and is able to optimize the operand word-length across the entire datapath to meet a given performance and area constraint.
+However, the precision loss will inevitably introduce quantization errors into the design.
 
-\section{Background}
+Unfortunately, in both cases circuits are designed for the worst cases.
+In order to avoid potential timing violations, timing analysis tools tend to provide a more conservative path delay by adding guard bands and timing margins.
+However, continuing with this approach will become increasing expensive and difficult as technology shrinks.
+
+To tackle this problem, a large volume of research activities were focused on the design methodology of relaxing the $100\%$ accuracy requirements and design constraints, while evaluating the corresponding design benefits and costs.
+Studies have shown that computing approximately provides extra opportunities to design circuits with better performance and less energy consumption.
+A brief discussion of the work in this area is given in Section~\ref{sec:Background}.
+
+In this paper, we provide a detailed evaluation of design trade-offs for adders, which are key arithmetic primitives for a broad range of applications.
+
+\section{Background}\label{sec:Background}
 \subsection{Approximate Datapath Design}
+Typically this can be achieved by either reducing the supply voltage [xxx] or increasing the operating frequency beyond the rated value [xxx].
 
@@
 
-\section{Comparison of Different Adder Structures}
+\section{Design Trade-offs of Different Adder Structures}
 \subsection{Ripple Carry Adder}
@@
 In this section, we initially demonstrate the benefits of CSA and OA in accuracy and performance, as well as the area overhead in comparison to RCA.
-As an example, the maximum word-length with respect to a variety of operating frequencies for RCA, CSA and OA is illustrated in Fig.~\ref{Fig:max_wl_adder}.
-Notice that in this case, overclocking error is not allowed to happen and the conventional design scenario is evaluated for all structures.
+As an example, the maximum word-lengths with respect to a variety of operating frequencies for RCA, CSA and OA are illustrated in Fig.~\ref{Fig:max_wl_adder}, where overclocking error is not allowed to happen and the conventional design scenario is evaluated for all structures.
+Also notice that in the experiment we consider the word-length of adders from 4-bit to 32-bit with a step of 4-bit.
+For a finer grain experiment, the trend will be similar to that in Fig.~\ref{Fig:max_wl_adder}.
 %
@@
   \includegraphics[width=.5\textwidth]{./figures/exp/max_wl.eps}
-  \caption{The maximum word-length of different adder structures.}
+  \vspace{-4ex}
+  \caption{The maximum word-lengths of different adder structures with respect to a variety of frequencies. The results are obtained from Xilinx ISE 14.7.}
   \label{Fig:max_wl_adder}
@@
 
-Correspondingly, the area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA is depicted in Fig.~\ref{Fig:area_adder}.
-Clearly we see that for a given frequency, CSA costs up to $4.5\times$ (4 stages) and $3.1\times$ (2 stages) area than RCA, and OA is up to $3.8\times$ larger than RCA for some frequency values.
+As can be seen in Fig.~\ref{Fig:max_wl_adder}, for a relatively relaxed frequency requirement, both CSA and OA can be implemented with greater word-lengths than RCA.
+For CSA, this is because the stage parallelism enables a larger word-length, even though the multiplexer delay limits the word-length of each stage in the CSA in comparison to RCA.
+For OA, an even larger gap in word-length can be observed when compared to RCA.
+Additionally, unlike RCA and CSA of which the word-length drops gradually with the increment of frequency, OA maintains the full precision across a large rang of frequencies.
+This is expected, because the critical path delay of OA is theoretically irrelevant to the operand word-length.
+However, we also observe that for a large frequency requirement, the word-length of OA drops drastically, while RCA and CSA with 2 stages outperform.
+This is because the multiplexer delay becomes comparable to the delay of the carry chain for CSA, and it inhibits the benefits of parallelism.
+
+We also record the corresponding area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA as depicted in Fig.~\ref{Fig:area_adder}.
+It can be seen that for a given frequency, CSA costs up to $4.5\times$ (4 stages) and $3.1\times$ (2 stages) area than RCA, and OA is up to $3.8\times$ larger than RCA for some frequency values.
 Therefore, we incorporate silicon area as another design metric besides accuracy and performance, and evaluate the optimum adder structure under various design trade-offs.
 In this paper, we examine both the overclocking scenario and the conventional scenario for RCA, while only considering the conventional scenario for other adder structures.
-%the considered design scenarios and adder structures are summarized in Table.xxx.
-% some figure goes here
+%
 \begin{figure}[tbp]
@@
 
+\section{Evaluation of Optimum Adder Structure}
 In general, the evaluation could be of interest to a circuit designer in several ways.
-First, suppose the algorithm designer wish the circuit to run at a given frequency within a given area budget, while achieving the minimum output error.
-Decisions must then be made on which adder structure achieves this minimum, and whether the circuit should be overclocked.
+For example, suppose the algorithm designer wish the circuit to run at a given frequency within a given area budget, while achieving the minimum output error.
+Besides, for many applications, the circuit design would wish the circuit to operate as fast as possible with the minimum resource usage, whilst a certain error budget can be tolerated.
+In both cases, decisions must then be made on which adder structure achieves this minimum, and whether the circuit should be overclocked.
 
-As an example slice through the design space, we record the mean relative error (MRE) with respect to a range of operating frequencies for different design scenarios when the area budget is set to xxx.
-MRE can be calculated as given in (xxx).
-Notice that in Fig.~xxx, the optimum adder structure is labeled.
-
-Under this given area budget, both CSA and OA cannot be implemented with full precision, and this leads to large truncation errors
-
-\section{Comparison of Different Multiplier Structures}
-\subsection{Standard Binary Multiplier}
-
-\subsection{Online Multiplier}
-\subsubsection{Algorithm}
-Similar to online addition, online multiplication can also be implemented in a unrolled digit-parallel manner, of which the optimized algorithm is shown in Algorithm~\ref{Algorithm:OM_DigitParallel} [xxx].
-In this algorithm, both inputs and outputs are $N$-digit numbers as given in (\ref{Eq:Online_Operands}).
-For a given iteration $j$, the product digit $z_j$ is generated MSD-first through a selection function $sel()$.
-For any radix $r$ and chosen digit set, there exits an appropriate selection method and a value of $\delta$ which ensure convergence.
-As the binary radix is used most commonly in computer arithmetic, we keep $r=2$ throughout this paper with the corresponding redundant digit set $\{\overline{1},0,1\}$.
-In this case $sel()$ is given by (\ref{Eq:SelFunc_OM})~\cite{Ercegovac_OnlineMult}.
-
-\begin{algorithm}[tbp]
-  \caption{Digit Parallel Online Multiplication}\label{Algorithm:OM_DigitParallel}
-  \begin{algorithmic}[1]
-    \State \textbf{Initialization:} $P_{[0]}=0$                     \vspace{.5ex}
-    \For{$j=1,~2,~\cdots,~N$}                                       \vspace{.5ex}
-        \State $Xy_j \leftarrow X \cdot y_j$                        \vspace{.5ex}
-        \State $W_{[j]}    \leftarrow  P_{[j-1]} + Xy_j$            \vspace{.5ex}
-        \State $z_{j}  ~~      \leftarrow  sel(W_{[j]})$            \vspace{.5ex}
-        \State $P_{[j+1]}  \leftarrow  r\left(W_{[j]}-Z_{[j]}\right)$   \vspace{.5ex}
-    \EndFor                                                         \vspace{.5ex}
-    \State $Z_{[N+1:2N]} \leftarrow frac(W_{[N]})$                  \vspace{.5ex}
-  \end{algorithmic}
-  \vspace{-1ex}
-\end{algorithm}
-
-\begin{eqnarray}\label{Eq:SelFunc_OM}
-\small
-  sel(W_{[j]})=\begin{cases}
-    1 & \text{ if } W_{[j]} \geqslant \frac{1}{2} \\
-    0 & \text{ if } -\frac{1}{2}\leqslant W_{[j]}<\frac{1}{2} \\
-    \overline{1} & \text{ if } W_{[j]}<-\frac{1}{2}
-  \end{cases}
-\normalsize
+\subsection{Optimum Adder Design Metric with Given Frequency and Area Requirements}
+For this type of applications, the available area and expected operating frequency are given at the design time.
+As an example slice through the design space, in Fig.~\ref{Fig:Error_Area} we record the mean relative error (MRE) with respect to a range of operating frequencies for different design scenarios, when the area budget is set to 35 LUTs and 55 LUTs separately.
+MRE can be calculated as given by (\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ denote the mean value of error and the mean value of correct outputs, respectively.
+Notice that the optimum adder design metric that achieves the minimum error at outputs is labeled.
+%
+\begin{eqnarray}\label{Eq:MRE}
+  MRE=\frac{E_{error}}{E_{out}}\times100\%
 \end{eqnarray}
 
-The parallel implementation of Algorithm~\ref{Algorithm:OM_DigitParallel} is illustrated in Fig.~\ref{Fig:PM} where $N=4$. The details of implementation are addressed in our previous work [xxx].
-
 \begin{figure}[tbp]
+  %\vspace{-2ex}
   \centering
-  \includegraphics[width=.42\textwidth]{./figures/ParallelMult_Structure.eps}
-  \caption{(a) Structure of a 4-digit online multiplier. (b) Structure of one stage. The word-length of all signals are labeled in digits, $N$ is the word-length of input signals.}
+  \subfigure[Available LUT=35.]{
+  \begin{minipage}[c]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{./figures/exp/Error_LUT35.eps}
+    \label{subfig:error_area_lut35}
     \vspace{-2ex}
-  \label{Fig:PM}
+  \end{minipage}%
+  }
+  \subfigure[Available LUT=55.]{
+  \begin{minipage}[c]{0.5\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{./figures/exp/Error_LUT55.eps}
+    \label{subfig:error_area_lut55}
+    \vspace{-2ex}
+  \end{minipage}
+  }
+\caption{Two examples of comparisons between different design scenarios and adder implementations with limited area budget.
+RCA is evaluated with both overclocking and truncation scenario, whereas CSA and OA are evaluated with truncation scenario only.
+Design scenario with minimum error is labeled.}
+\label{Fig:Error_Area}
+%\vspace{-2ex}
 \end{figure}
 
-\subsubsection{Structure Optimization for Half Precision Results}
-In actual applications, normally the multiplier is connected with other arithmetic operators.
-If the multiplication result is utilized for subsequent operations, and a consistent word-length is used throughout the system, then only the most significant half of the product is required.
-In a conventional multiplier with standard binary arithmetic, this is achieved by either truncating or rounding the least significant half of the products.
-However, both the computation time and the structure remains unchanged, because results are generated from LSDs.
+If the area budget is 35 LUTs, as seen in Fig.~\ref{subfig:error_area_lut35}, it can be noticed that for all frequency values, the overcloced RCA achieves no larger mean error than the RCA with truncated operand word-lengths.
+This is in accordance with the analysis in Section~xxx.
+We also notice that both CSA and OA cannot be implemented with full precision due to the limited area budget, and this leads to large truncation errors.
+Despite that the CSA with 4 stages is best for some frequencies, in general the overclocked RCA is still the optimum design for most frequency requirements.
 
-In comparison, OM offers the flexibility to simplify the structure corresponding to the required precision.
-This is possible because in an OM, the product digits are generated initially from the MSD, and there is no carry propagation from the LSD to the MSD with the employment of the redundant number system.
-This will potentially lead to a more area efficient design.
-For example, the modified structure diagram of a 4-digit OM is illustrated in Fig.~\ref{Fig:PM_half}(a).
-The word-length of signals within each stage can be correspondingly reduced, as shown in Fig.~\ref{Fig:PM_half}(b).
-Notice that instead of keeping identical word-length throughout the stages (in Fig.~\ref{Fig:PM}), in the modified structure the signal word-lengths depend on the stage number $j$ and hence fewer bits of signals are needed for LSD stages.
+However if the area budget is released to 55 LUTs, OA can be implemented with original word-length.
+Additionally CSA can be implemented with larger precision, but still not the full precision.
+Therefore as shown in Fig.~\ref{subfig:error_area_lut55}, OA serves as the optimum design choice with respect to a wide range of frequencies.
+For higher frequencies, the MRE of OA increases rapidly, and CSA with 4 stages outperforms for higher frequencies.
+Similar to Fig.~\ref{subfig:error_area_lut35}, the overclocked RCA is the optimum design choice for even higher frequencies, because in this case the CSA can only be implemented with small precisions, and the multiplexer delay limits the benefits of parallelism.
 
-\begin{figure}[tbp]
+The results shown in Fig.~\ref{Fig:Error_Area} can be generalized with a variety of area constraints.
+In this case, the optimum design methods with respect to different operating frequencies and area consumptions are illustrated in Fig.~\ref{Fig:adder_3d_FreqArea}.
+%
+\begin{figure*}[tbp]
   \centering
-  \includegraphics[width=.42\textwidth]{./figures/ParallelMult_MSDhalf.eps}
-  \caption{(a) A 4-digit online multiplier with half precision results. (b) Structure of stage $j$, with the word-length of all signals labeled.}
-    \vspace{-2ex}
-  \label{Fig:PM_half}
-\end{figure}
+  \includegraphics[width=.8\textwidth]{./figures/exp/3d_FreqArea.eps}
+  \caption{The maximum word-length of different adder structures.}
+  \label{Fig:adder_3d_FreqArea}
+\end{figure*}
+
+\subsection{Optimum Adder Design Metric with Given Accuracy and Area Requirements}
+%
+\begin{figure*}[tbp]
+  \centering
+  \includegraphics[width=.8\textwidth]{./figures/exp/3d_ErrorArea.eps}
+  \caption{The maximum word-length of different adder structures.}
+  \label{Fig:adder_3d_ErrorArea}
+\end{figure*}
 

### 2014-11-18 WAP2015/wap2015.tex
add initial introduction

@@
 Email: \{k.shi11, g.contantinides\}@imperial.ac.uk}
+\vspace{2ex}
 %\and
@@
 
-In this paper, we provide a detailed evaluation of design trade-offs for adders, which are key arithmetic primitives for a broad range of applications.
+In this paper, we provide detailed evaluations of design trade-offs for adders, which are key arithmetic primitives for a broad range of applications.
+In order to provide the optimum design choice for adders, we examine several design constrains and options, such as accuracy, operating frequency, silicon area, different types of adder structure, as well as different forms of computer arithmetic for adder implementation.
+In comparison to the conventional design scenario that timing closure is achieved by truncating the word-length of operands, we take a radical step forward by adopting an alternative design scenario, which is named ``overclockign scenario''.
+In this scenario, circuits are operated far beyond the conservation region with full precision, while timing violation can be tolerated.
+Previous work has shown that for many applications, it is preferable to follow the overclocking scenario because the worst case is triggered by certain input patterns and hence it happens rarely [xxx].
+In addition to the adder structures that are created based on standard binary arithmetic, such as ripple carry adder and carry select adder, we also evaluate adder with ``online arithmetic'' [xxx], which employs different style of data representation to eliminate carry propagation in conventional adders.
+We demonstrate experimentally on FPGAs that for limited area budgets, applying the overclocking approach to ripple carry adders can be more beneficial than using fast adders to achieve similar latency.
+With more relaxed area constraints, the online adder outperforms in terms of accuracy or performance.
+Potentially our study will provide circuit designers with guidance and extra options when balancing between various design trade-offs.
+
+In summary, the main contributions of this paper are:
+\begin{enumerate}
+  \item Detailed evaluation of three adder structures: ripple carry adder, carry select adder and online adder; 
+  \item Evaluation of design scenarios by demonstrating the optimum design choice under the consideration of accuracy-performance-area trade-offs.
+\end{enumerate}
+
+The rest of this paper is organized as below: we first provide a brief overview of the relevant work in this area, together with the background knowledge of online arithmetic in Section~\ref{sec:Background}.
+The comparison between different adder structures and design trade-offs are described in detail in Section~\ref{sec:diff_adder}.
+This is followed by the evaluation of optimum design choices when considering trade-offs between accuracy, performance and area in Section~\ref{sec:optimum_adder}.
+The conclusion and identification of possible future work is given in Section~\ref{sec:conclusion}.
 
@@
 
-\section{Design Trade-offs of Different Adder Structures}
+\section{Design Trade-offs of Different Adder Structures}\label{sec:diff_adder}
 \subsection{Ripple Carry Adder}
@@
 
-\section{Evaluation of Optimum Adder Structure}
+\section{Evaluation of Optimum Adder Structure}\label{sec:optimum_adder}
 In general, the evaluation could be of interest to a circuit designer in several ways.
@@
 
-\section{Conclusion}
+\section{Conclusion}\label{sec:conclusion}
 
-\section*{Acknowledgment}
+%\section*{Acknowledgment}
 

### 2014-11-19 WAP2015/wap2015.tex
add relevant work

@@
 Circuit performance has been increased tremendously over the past decades.
-However, in recent years people have observed an end of performance improvement [xx] due to the scaling of CMOS technology to the nanometer regime.
+However, in recent years people have observed an end of performance improvement~\cite{DarkSilicon2011} due to the scaling of CMOS technology to the nanometer regime.
 In order to boost circuit performance, two standard design techniques are commonly adopted: one is to heavily pipeline the datapath, the other is to reduce the design precision.
@@
 In this scenario, circuits are operated far beyond the conservation region with full precision, while timing violation can be tolerated.
-Previous work has shown that for many applications, it is preferable to follow the overclocking scenario because the worst case is triggered by certain input patterns and hence it happens rarely [xxx].
-In addition to the adder structures that are created based on standard binary arithmetic, such as ripple carry adder and carry select adder, we also evaluate adder with ``online arithmetic'' [xxx], which employs different style of data representation to eliminate carry propagation in conventional adders.
+Previous work has shown that for many applications, it is preferable to follow the overclocking scenario because the worst case is triggered by certain input patterns and hence it happens rarely~\cite{SKfccm13}.
+In addition to the adder structures that are created based on standard binary arithmetic, such as ripple carry adder and carry select adder, we also evaluate adder with ``online arithmetic''~\cite{Ercegovac_OnlineOverview}, which employs different style of data representation to eliminate carry propagation in conventional adders.
 We demonstrate experimentally on FPGAs that for limited area budgets, applying the overclocking approach to ripple carry adders can be more beneficial than using fast adders to achieve similar latency.
@@
   \item Detailed evaluation of three adder structures: ripple carry adder, carry select adder and online adder; 
-  \item Evaluation of design scenarios by demonstrating the optimum design choice under the consideration of accuracy-performance-area trade-offs.
+  \item Evaluation of design scenarios and identification of the optimum design choice under the consideration of accuracy-performance-area trade-offs.
 \end{enumerate}
@@
 \subsection{Approximate Datapath Design}
-Typically this can be achieved by either reducing the supply voltage [xxx] or increasing the operating frequency beyond the rated value [xxx].
+The International Technology Roadmap for Semiconductors (ITRS) has identified that additional benefits of manufacturing, test, power and timing can be achieved by releasing the requirement of absolute correctness~\cite{semiconductor2007international}.
+A series of studies in this area called ``Better Than Worst-Case Design'' focused on creating circuits by operating beyond the safety margins.
+Typically this can be achieved by either reducing the supply voltage~\cite{NonUniformScaling} or increasing the operating frequency beyond the rated value~\cite{SKfccm13,JoshFCCM2012}.
+The Razor project~\cite{Razor2004} served as one of the exemplary designs, in which both supply voltage and clock frequency were scaled over the most conservative value, while the error rate was monitored by using a self-checking circuit.
+It was shown that over $30\%$ power saving can be obtained at the cost of around $1\%$ error rates.
+
+Another stream of research was focus on proposing either approximate circuit structures or design tools by trading accuracy to performance and/or energy benefits.
+Work in this area was inspired by the fact that many applications, e.g.
+image processing and machine learning, were naturally error resilient.
+For example, code analysis tools~\cite{Truffle2012Uwash,EnerJ2011Uwash} were developed to divide the program into precise parts and approximate parts, which can then be mapped to hardware components with different speed-grades and supply voltages.
+As for the approximate hardware, numerous forms of architectures were designed for basic arithmetic operators such as adders [xxx] and multipliers [xxx].
+For example, a under-designed multiplier unit was proposed, of which the worst case was replaced by a normal case based on straightforward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
+However, many of these techniques are designed at gate-level or transistor-level, and they cannot be directly applied onto existing hardware platforms such as FPGAs.
+
+In this paper, we overcome the previous limitations by comparing three adder structures: ripple carry adder and carry select adder, which are widely employed in mainstream hardware platforms, together with online adder which can be also found when designing fast multipliers and embedded processors~\cite{RedundantMult_1987}.
+It is argued that our approach can be efficiently applied to existing designs, and we back up this hypothesis based on FPGA experiments.
 
@@
 %
-\begin{figure}[htbp]
+\begin{figure}[tbp]
   \centering
@@
 For the sampling period $T_S$, it follows that if $T_S\geqslant\mu_{RCA}$, correct result will always be sampled; otherwise if $T_S<\mu_{RCA}$, intermediate be sampled and potentially generating errors.
-In the previous work, the mean value of overclocking error is modeled as given in (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation in bits.
+In the previous work~\cite{SKfccm13}, the mean value of overclocking error is modeled as given in (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation in bits.
 %
@@
 This will result in truncation error for most data.
-The mean value of truncation error is also modeled as given in~(\ref{Eq:MeanTruncError_RCA}) [xxx], where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively.
+The mean value of truncation error is also modeled as given in~(\ref{Eq:MeanTruncError_RCA})~\cite{SKfccm13}, where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively.
 %
@@
 
-%In this paper, we take CSA with different stages into comparison when considering a variety of accuracy, performance and area trade-offs. The results are shown in Section.xxx.
-
 \subsection{Online Adder}\label{subsec:online_adder}
-%\subsubsection{Structure}
 In addition to standard binary arithmetic, alternative forms of computer arithmetic was studied to boost performance.
@@
 Similar to Fig.~\ref{subfig:error_area_lut35}, the overclocked RCA is the optimum design choice for even higher frequencies, because in this case the CSA can only be implemented with small precisions, and the multiplexer delay limits the benefits of parallelism.
-
-The results shown in Fig.~\ref{Fig:Error_Area} can be generalized with a variety of area constraints.
-In this case, the optimum design methods with respect to different operating frequencies and area consumptions are illustrated in Fig.~\ref{Fig:adder_3d_FreqArea}.
 %
@@
 
+The results shown in Fig.~\ref{Fig:Error_Area} can be further extended by testing with a variety of area constraints.
+In this case, we can map the optimum design scenarios into the design space of different operating frequencies and area consumptions, as shown in Fig.~\ref{Fig:adder_3d_FreqArea}.
+It can be seen that in general the graph is divided into several regions.
+Firstly, if the frequency requirement is moderate whilst the area budget is large enough to implement an OA in full precision, it will be the optimum design.
+This is because long carry chains are eliminated from OA such that it can maintain full precision for a wide range of frequency values.
+Also this is in accordance with the results in Fig.~\ref{subfig:error_area_lut55}.
+Secondly, CSA is a better design choice for high frequency requirement and large area budget, because it is originally designed with high speed operation.
+Besides, each stage of CSA is implemented in the FPGA with fast carry logic [xxx], hence it runs even faster than OA.
+Thirdly, for a tighter area budget only part of OA and CSA can be implemented, whereas RCA still keeps original precision.
+In this situation, area becomes the limitation factor.
+Truncation errors occur for both OA and CSA and they are greater than the overclocking error of RCA.
+Therefore, the overclocked RCA is the optimum design option across almost the entire frequency domain.
+Furthermore, the precision of RCA is also limited for very stringent area constraints.
+This causes truncation errors for every design option.
+Nevertheless, RCA with either overclocking or truncation scenario equally serves to be optimal, because it maintains more precision than OA and CSA for a specific area budget.
+
 \subsection{Optimum Adder Design Metric with Given Accuracy and Area Requirements}
@@
   \includegraphics[width=.8\textwidth]{./figures/exp/3d_ErrorArea.eps}
-  \caption{The maximum word-length of different adder structures.}
+  \caption{.The original word-length for all adders is 32-bit.}
   \label{Fig:adder_3d_ErrorArea}

### 2014-11-23 WAP2015/wap2015.tex
submitted version

@@
 \usepackage[tight,footnotesize]{subfigure}
+\usepackage{multirow}
 
@@
 Email: \{k.shi11, g.contantinides\}@imperial.ac.uk}
-\vspace{2ex}
+\vspace{1ex}
 %\and
@@
 In this paper, we evaluate the design trade-offs for adders, which are key building blocks for many applications.
-We demonstrate the optimum design metric for adders, under the consideration of various design constraints, such as accuracy, operating frequency, silicon area, different types of adder structure and even alternative form of computer arithmetic for adder implementation.
+We demonstrate the optimum design metric for adders, under the consideration of various design constraints, such as accuracy, operating frequency, silicon area, different types of adder structure and alternative form of computer arithmetic for adder implementation.
 Two design scenarios are compared: one is the conventional design scenario where timing closure is met by adjusting operand word-lengths.
@@
 \section{Introduction}
-Circuit performance has been increased tremendously over the past decades.
-However, in recent years people have observed an end of performance improvement~\cite{DarkSilicon2011} due to the scaling of CMOS technology to the nanometer regime.
+Circuit performance has increased tremendously over the past decades.
+However, in recent years people have observed an end of performance scaling~\cite{DarkSilicon2011} due to the improvement of CMOS technology to the nanometer regime.
 In order to boost circuit performance, two standard design techniques are commonly adopted: one is to heavily pipeline the datapath, the other is to reduce the design precision.
 For the first technique, pipelining can be used to increase operating frequency, whereas the overall computational latency will not be affected.
-Therefore the application of this technique is limited in many embedded applications, which are often designed with strict latency specifications.
-The second technique is common especially with FPGA technology, which embodies the flexibility to implement customized variable representation and is able to optimize the operand word-length across the entire datapath to meet a given performance and area constraint.
+Therefore the utilization of this technique is limited in many embedded applications, which are often designed with strict latency specifications.
+The second technique is common especially with FPGA technology, which embodies the flexibility to implement customized variable representation and is able to optimize the operand word-length across the entire datapath to meet a given performance and area constraint~\cite{GeorgeDT11}.
 However, the precision loss will inevitably introduce quantization errors into the design.
 
-Unfortunately, in both cases circuits are designed for the worst cases.
-In order to avoid potential timing violations, timing analysis tools tend to provide a more conservative path delay by adding guard bands and timing margins.
-However, continuing with this approach will become increasing expensive and difficult as technology shrinks.
+Unfortunately, in both situations circuits are designed for the worst cases.
+In order to avoid potential timing violations, timing analysis tools tend to provide a conservative critical path delay by adding guard bands and timing margins.
+However, continuing with this approach will become increasingly expensive and difficult as technology shrinks.
 
-To tackle this problem, a large volume of research activities were focused on the design methodology of relaxing the $100\%$ accuracy requirements and design constraints, while evaluating the corresponding design benefits and costs.
+To tackle this problem, a large volume of research activities were focused on the design methodology of relaxing the $100\%$ accuracy requirements and design constraints, while reasoning about the corresponding benefits and costs.
 Studies have shown that computing approximately provides extra opportunities to design circuits with better performance and less energy consumption.
-A brief discussion of the work in this area is given in Section~\ref{sec:Background}.
+A brief review of the work in this area is given in Section~\ref{sec:Background}.
 
@@
 In order to provide the optimum design choice for adders, we examine several design constrains and options, such as accuracy, operating frequency, silicon area, different types of adder structure, as well as different forms of computer arithmetic for adder implementation.
-In comparison to the conventional design scenario that timing closure is achieved by truncating the word-length of operands, we take a radical step forward by adopting an alternative design scenario, which is named ``overclockign scenario''.
-In this scenario, circuits are operated far beyond the conservation region with full precision, while timing violation can be tolerated.
-Previous work has shown that for many applications, it is preferable to follow the overclocking scenario because the worst case is triggered by certain input patterns and hence it happens rarely~\cite{SKfccm13}.
-In addition to the adder structures that are created based on standard binary arithmetic, such as ripple carry adder and carry select adder, we also evaluate adder with ``online arithmetic''~\cite{Ercegovac_OnlineOverview}, which employs different style of data representation to eliminate carry propagation in conventional adders.
+In comparison to the conventional design scenario that timing closure is achieved by truncating the operand word-length, we take a radical step forward by adopting an alternative design scenario, which is named ``overclockign scenario''.
+In this case, circuits are operated far beyond the conservation region with full precision, while timing violation can be tolerated.
+Previous work has shown that for many applications, it is preferable to follow the overclocking scenario because the worst case is triggered only by certain input patterns and hence it happens rarely~\cite{SKfccm13}.
+In addition to the adder structures that are created based on standard binary arithmetic, such as ripple carry adder and carry select adder, we also evaluate adder with ``online arithmetic''~\cite{Ercegovac_OnlineOverview}, which employs different style of data representation to eliminate carry propagation.
 We demonstrate experimentally on FPGAs that for limited area budgets, applying the overclocking approach to ripple carry adders can be more beneficial than using fast adders to achieve similar latency.
@@
   \item Detailed evaluation of three adder structures: ripple carry adder, carry select adder and online adder; 
-  \item Evaluation of design scenarios and identification of the optimum design choice under the consideration of accuracy-performance-area trade-offs.
+  \item Comparison of design scenarios and demonstration of the optimum design choice under the consideration of trade-offs between accuracy, performance and area.
 \end{enumerate}
 
-The rest of this paper is organized as below: we first provide a brief overview of the relevant work in this area, together with the background knowledge of online arithmetic in Section~\ref{sec:Background}.
-The comparison between different adder structures and design trade-offs are described in detail in Section~\ref{sec:diff_adder}.
+The rest of this paper is organized as follows: we first provide a brief overview of the relevant work in this area, together with the background knowledge of online arithmetic in Section~\ref{sec:Background}.
+The comparison between different adder structures and design trade-offs are detailed in Section~\ref{sec:diff_adder}.
 This is followed by the evaluation of optimum design choices when considering trade-offs between accuracy, performance and area in Section~\ref{sec:optimum_adder}.
-The conclusion and identification of possible future work is given in Section~\ref{sec:conclusion}.
+The conclusion and suggestions of possible future work is given in Section~\ref{sec:conclusion}.
 
@@
 The International Technology Roadmap for Semiconductors (ITRS) has identified that additional benefits of manufacturing, test, power and timing can be achieved by releasing the requirement of absolute correctness~\cite{semiconductor2007international}.
-A series of studies in this area called ``Better Than Worst-Case Design'' focused on creating circuits by operating beyond the safety margins.
+This fact has inspired a series of studies to create circuits operating beyond the worst cases and the safety margins.
 Typically this can be achieved by either reducing the supply voltage~\cite{NonUniformScaling} or increasing the operating frequency beyond the rated value~\cite{SKfccm13,JoshFCCM2012}.
 The Razor project~\cite{Razor2004} served as one of the exemplary designs, in which both supply voltage and clock frequency were scaled over the most conservative value, while the error rate was monitored by using a self-checking circuit.
-It was shown that over $30\%$ power saving can be obtained at the cost of around $1\%$ error rates.
+It was shown that over $30\%$ power saving can be obtained at the cost of around $1\%$ errors.
 
-Another stream of research was focus on proposing either approximate circuit structures or design tools by trading accuracy to performance and/or energy benefits.
+Another stream of research was focusing on proposing either approximate circuit structures or design tools to trade accuracy for performance and/or energy benefits.
 Work in this area was inspired by the fact that many applications, e.g.
 image processing and machine learning, were naturally error resilient.
-For example, code analysis tools~\cite{Truffle2012Uwash,EnerJ2011Uwash} were developed to divide the program into precise parts and approximate parts, which can then be mapped to hardware components with different speed-grades and supply voltages.
-As for the approximate hardware, numerous forms of architectures were designed for basic arithmetic operators such as adders [xxx] and multipliers [xxx].
+For example, code analysis tools~\cite{Truffle2012Uwash,EnerJ2011Uwash} were developed to divide a program into precise parts and approximate parts, which can then be mapped to hardware components with different speed-grades and supply voltages.
+As for the approximate hardware, numerous forms of architectures were designed for basic arithmetic operators such as adders~\cite{ApproximateAdderTC} and multipliers~\cite{ApproximateMultDATE}.
 For example, a under-designed multiplier unit was proposed, of which the worst case was replaced by a normal case based on straightforward Karnaugh-Map analysis~\cite{Undersigned2x2multiplier}.
@@
 
-In this paper, we overcome the previous limitations by comparing three adder structures: ripple carry adder and carry select adder, which are widely employed in mainstream hardware platforms, together with online adder which can be also found when designing fast multipliers and embedded processors~\cite{RedundantMult_1987}.
+In this paper, we overcome the previous limitations by comparing two standard adder structures: ripple carry adder and carry select adder, which are widely employed in mainstream hardware platforms.
+We also compare a type of adder with ``online arithmetic'', which can be also found when designing fast multipliers and embedded processors~\cite{RedundantMult_1987}.
 It is argued that our approach can be efficiently applied to existing designs, and we back up this hypothesis based on FPGA experiments.
@@
   \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
-  \vspace{-2ex}
+  %\vspace{-2ex}
   \label{Fig:OnlineDataFlow}
@@
 \section{Design Trade-offs of Different Adder Structures}\label{sec:diff_adder}
-\subsection{Ripple Carry Adder}
+\subsection{Ripple Carry Adder}\label{subsec:rca}
 Adders serve as a key building block for arithmetic operations.
 In general, the ripple carry adder (RCA) is the most straightforward and widely used adder structure.
-As such, in our previous work we proposed probabilistic models of overclocking errors for RCA.
+As such, in our previous work we proposed probabilistic models of overclocking errors for RCA~\cite{SKfccm13}.
+A brief summary of the models is described below.
+%
+\begin{figure}[tbp]
+  \centering
+  \includegraphics[width=.5\textwidth]{./figures/RCA.pdf}
+  \vspace{-4ex}
+  \caption{An $n$-bit ripple carry adder. $\mu_i$ and $\mu_{RCA}$ denote the propagation delay of a full adder and the overall delay of RCA, respectively.}
+  \vspace{-2ex}
+  \label{Fig:rca}
+\end{figure}
 
-For an $n$-bit RCA, it is composed of $n$ serial-connected full adders (FA).
+For an $n$-bit RCA, it is composed of $n$ serial-connected full adders (FA) as shown in Fig.~\ref{Fig:rca}.
 Typically the maximum frequency of RCA is determined by the longest carry propagation.
-Under the assumption that the carry propagation delay of each FA is a constant value $\mu$, the critical path of the RCA is: $\mu_{RCA}=n\mu$.
-For the sampling period $T_S$, it follows that if $T_S\geqslant\mu_{RCA}$, correct result will always be sampled; otherwise if $T_S<\mu_{RCA}$, intermediate be sampled and potentially generating errors.
-In the previous work~\cite{SKfccm13}, the mean value of overclocking error is modeled as given in (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation in bits.
+Under the assumption that the carry propagation delay of each FA is a constant value $\mu_i=\mu$, the critical path of the RCA is: $\mu_{RCA}=n\mu$.
+For the sampling period $T_S$, it follows that if $T_S\geqslant\mu_{RCA}$, correct result will always be sampled.
+Otherwise, intermediate result will be sampled and potentially generating overclocking errors.
+The mean value of overclocking error is modeled~\cite{SKfccm13} as given by (\ref{Eq:MeanError_RCA}), where coefficient $b$ is given in (\ref{Eq:b}) and it determines the maximum length of error-free carry propagation.
 %
@@
 \end{eqnarray}
+\vspace{-1.5ex}
 %
@@
 \end{eqnarray}
+\vspace{-1ex}
+\normalsize
 
-On the other hand, a specific timing target can be met by truncating the word-length of RCA while timing violation is not permitted.
+In the conventional scenario, a specific timing target can be met by truncating the word-length of RCA while timing violation is not permitted.
 This will result in truncation error for most data.
-The mean value of truncation error is also modeled as given in~(\ref{Eq:MeanTruncError_RCA})~\cite{SKfccm13}, where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively.
+The mean value of truncation error is also modeled~\cite{SKfccm13} as given by~(\ref{Eq:MeanTruncError_RCA}), where parameters $k$ and $n$ denote the word-length of RCA before and after truncation, respectively.
 %
@@
 \end{eqnarray}
+\vspace{-2ex}
 
-In this paper we consider two design scenarios for RCA: one is the overclocking scenario where timing violation is allowed to happen while maintaining the original word-length; the other is the trad scenario by truncating RCA word-length to meet timing.
+In this paper we consider two design scenarios for RCA: one is the overclocking scenario where timing violation is allowed to happen while maintaining the original word-length; the other is the traditional scenario by truncating RCA word-length to meet timing.
 For a given $f_S$, in the first design scenario we have $n=k$.
@@
 Therefore the comparison between the two scenarios in mean error value is given in (\ref{Eq:ErrorCompare_RCA}) by updating (\ref{Eq:MeanError_RCA}) and (\ref{Eq:MeanTruncError_RCA}) respectively.
-As seen in (\ref{Eq:ErrorCompare_RCA}), in theory the mean value of error in the overclocking scenario ($E_{oc}$) is two times smaller than that in the traditional scenario ($E_{trad}$).
+As seen in (\ref{Eq:ErrorCompare_RCA}), in theory the mean value of error in the overclocking scenario ($E_{oc}$) is constantly two times smaller than that in the traditional scenario ($E_{trad}$).
 %
@@
 Instead, alternative adder structures, such as carry select adder (CSA), are originally designed to trade silicon area for low latency.
-In a CSA, the carry chain is divided into multiple overlapped stages, and each stage contains two RCAs and two multiplexers, as shown in Fig.
-xxx(a) and Fig.
-xxx(b).
+In a CSA, the carry chain is divided into multiple overlapped stages, and each stage contains two RCAs and two multiplexers.
 For a given input, two additions are performed simultaneously within a single stage where the carry input is zero and one separately.
@@
 In addition to standard binary arithmetic, alternative forms of computer arithmetic was studied to boost performance.
-For example, adder with online arithmetic is also designed for low latency at the cost of more silicon area.
+For example, adder with online arithmetic is also designed for low latency at the cost of extra silicon area.
 The structure of a digit-parallel online adder (OA) where all signals represented with SD numbers of digit set $\{-1,0,1\}$ is shown in Fig.~\ref{Fig:Radix2SD_adder}.
@@
 A major advantage of the redundant number system over the standard ripple-carry based arithmetic is that the propagation of carry is eliminated, resulting in a precision-independent computation time for addition.
-As labelled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, at the expenses of one extra FA for each digit of operands.
+As labeled in Fig.~\ref{Fig:Radix2SD_adder}, ideally the computation delay of this adder is only two FA delays for any operand word-length, at the expenses of one extra FA for each digit of operands.
 %
@@
   \includegraphics[width=.45\textwidth]{./figures/SDAdder.eps}
+  \vspace{-1ex}
   \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
   \label{Fig:Radix2SD_adder}
+  \vspace{-2ex}
 \end{figure}
@@
 \subsection{Design Trade-offs for Adders}
-In this section, we initially demonstrate the benefits of CSA and OA in accuracy and performance, as well as the area overhead in comparison to RCA.
-As an example, the maximum word-lengths with respect to a variety of operating frequencies for RCA, CSA and OA are illustrated in Fig.~\ref{Fig:max_wl_adder}, where overclocking error is not allowed to happen and the conventional design scenario is evaluated for all structures.
-Also notice that in the experiment we consider the word-length of adders from 4-bit to 32-bit with a step of 4-bit.
-For a finer grain experiment, the trend will be similar to that in Fig.~\ref{Fig:max_wl_adder}.
+In this section, we demonstrate the benefits of CSA and OA in accuracy and performance, as well as the area overhead in comparison to RCA.
+As an example, the maximum word-lengths with respect to a variety of operating frequencies for RCA, CSA and OA are illustrated in Fig.~\ref{Fig:max_wl_adder}.
+In this experiment, circuits are operated with timing closure, i.e.
+the conventional design scenario is evaluated for all structures.
+We consider the operand word-length of adders ranging from 32-bit to 4-bit.
 %
@@
   \label{Fig:max_wl_adder}
+  \vspace{-2ex}
 \end{figure}
 
-As can be seen in Fig.~\ref{Fig:max_wl_adder}, for a relatively relaxed frequency requirement, both CSA and OA can be implemented with greater word-lengths than RCA.
-For CSA, this is because the stage parallelism enables a larger word-length, even though the multiplexer delay limits the word-length of each stage in the CSA in comparison to RCA.
+As can be seen in Fig.~\ref{Fig:max_wl_adder}, for a relatively relaxed frequency requirement (e.g.
+470 MHz), both CSA and OA can be implemented with greater word-lengths than RCA.
+For CSA, this is because the stage parallelism enables a larger word-length, even though the multiplexer delay limits the precision of each CSA stage in comparison to RCA.
 For OA, an even larger gap in word-length can be observed when compared to RCA.
-Additionally, unlike RCA and CSA of which the word-length drops gradually with the increment of frequency, OA maintains the full precision across a large rang of frequencies.
-This is expected, because the critical path delay of OA is theoretically irrelevant to the operand word-length.
-However, we also observe that for a large frequency requirement, the word-length of OA drops drastically, while RCA and CSA with 2 stages outperform.
-This is because the multiplexer delay becomes comparable to the delay of the carry chain for CSA, and it inhibits the benefits of parallelism.
-
-We also record the corresponding area consumed by each adder structure in terms of look-up-tables (LUTs) in FPGA as depicted in Fig.~\ref{Fig:area_adder}.
-It can be seen that for a given frequency, CSA costs up to $4.5\times$ (4 stages) and $3.1\times$ (2 stages) area than RCA, and OA is up to $3.8\times$ larger than RCA for some frequency values.
-Therefore, we incorporate silicon area as another design metric besides accuracy and performance, and evaluate the optimum adder structure under various design trade-offs.
-In this paper, we examine both the overclocking scenario and the conventional scenario for RCA, while only considering the conventional scenario for other adder structures.
+Additionally, unlike RCA and CSA of which the maximum word-length drops gradually with the increment of frequency, OA maintains full precision across a large range of frequencies.
+This is expected, because the critical path delay of OA is theoretically irrelevant to the operand word-length as discussed in Section~\ref{subsec:online_adder}.
+However, we also observe that given a large frequency requirement, the word-length of OA drops drastically.
+Besides, CSA cannot be implemented with larger precision than RCA either, because in this case the multiplexer delay becomes comparable to the delay of the carry chain for CSA, and it inhibits the benefits of parallelism.
 %
@@
   \includegraphics[width=.5\textwidth]{./figures/exp/area_adders.eps}
+  \vspace{-4ex}
   \caption{The maximum word-length of different adder structures.}
+  %\vspace{-2ex}
   \label{Fig:area_adder}
@@
 
+We also record the corresponding area consumption of each adder structure in terms of look-up-tables (LUTs) in FPGA as depicted in Fig.~\ref{Fig:area_adder}.
+It can be seen that the CSA with 4 stages and 2 stages costs up to $4.5\times$ and $3.1\times$ area than RCA, respectively.
+OA is also up to $3.8\times$ larger than RCA.
+Therefore, it is necessary to provide comprehensive evaluations of different adders by considering the trade-offs between accuracy, performance and area consumption.
+In summary, the evaluated adder structures as well as design scenarios are summarized in Table~\ref{Table:comparison}.
+
+\begin{table}[tbp]
+\renewcommand{\arraystretch}{1.1}
+\caption{Adder Structures and Design Scenarios Considered in this Paper.}
+\vspace{-1.5ex}
+\label{Table:comparison}
+\begin{center}
+\small
+\begin{tabular}{c|cc}
+\hline
+\hline
+\multirow{2}*{\textbf{Adders}} & \multicolumn{2}{c}{\textbf{Design Scenarios}} \\
+& Overclocking & Traditional \\
+\hline
+Ripple Carry Adder & $\surd$ & $\surd$ \\
+Carry Select Adder &       & $\surd$ \\
+Online Arithmetic Adder  &       & $\surd$ \\
+\hline
+\hline
+\end{tabular}
+\end{center}
+\vspace{-2ex}
+\end{table}
+\normalsize
+
 \section{Evaluation of Optimum Adder Structure}\label{sec:optimum_adder}
-In general, the evaluation could be of interest to a circuit designer in several ways.
-For example, suppose the algorithm designer wish the circuit to run at a given frequency within a given area budget, while achieving the minimum output error.
-Besides, for many applications, the circuit design would wish the circuit to operate as fast as possible with the minimum resource usage, whilst a certain error budget can be tolerated.
-In both cases, decisions must then be made on which adder structure achieves this minimum, and whether the circuit should be overclocked.
+Generally, our evaluation could be of interest to a circuit designer in several ways.
+For example, suppose the algorithm designer wish the circuit to run at a given frequency within a specific area budget, while achieving the minimum output error.
+Besides, for many applications, the circuit designer would wish the circuit to operate as fast as possible with the minimum resource usage, whilst a certain error budget can be tolerated.
+In both cases, decisions must be made on which adder structure achieves this minimum, and which design scenario should be adopted.
+%whether the circuit should be overclocked.
 
-\subsection{Optimum Adder Design Metric with Given Frequency and Area Requirements}
+\subsection{Optimum Adder with Given Frequency and Area Requirements}\label{subsec:adder_freq_area}
+
 For this type of applications, the available area and expected operating frequency are given at the design time.
@@
 MRE can be calculated as given by (\ref{Eq:MRE}), where $E_{error}$ and $E_{out}$ denote the mean value of error and the mean value of correct outputs, respectively.
-Notice that the optimum adder design metric that achieves the minimum error at outputs is labeled.
+Notice that the optimum adder design metric that achieves the minimum MRE is labeled.
 %
@@
 \end{eqnarray}
+
+In Fig.~\ref{subfig:error_area_lut35}, the area budget is set to 35 LUTs.
+For all frequency values, the overcloced RCA achieves no larger MRE than the RCA with truncated operand word-lengths.
+This is in accordance with the analysis in Section~\ref{subsec:rca}.
+We also notice that both CSA and OA cannot be implemented with full precision due to area limitation, and this leads to large truncation errors.
+Despite that the CSA with 4 stages is best for some frequencies, in general the overclocked RCA is the optimum design for most frequency requirements.
+
+However if the area budget is released to 55 LUTs, OA can be implemented with original word-length.
+Additionally CSA can also be implemented with larger precision, but still with truncation errors.
+Therefore as shown in Fig.~\ref{subfig:error_area_lut55}, OA serves as the optimum design with respect to a wide range of frequency requirements.
+For higher frequencies, the MRE of OA increases rapidly, and CSA with 4 stages outperforms for higher frequencies.
+Similar to Fig.~\ref{subfig:error_area_lut35}, the overclocked RCA is the optimum design for even higher frequencies, because in this case the CSA can only be implemented with small precisions, and the multiplexer delay limits the benefits of parallelism.
 
@@
     \label{subfig:error_area_lut35}
-    \vspace{-2ex}
+    \vspace{-2.5ex}
   \end{minipage}%
@@
     \label{subfig:error_area_lut55}
-    \vspace{-2ex}
+    \vspace{-2.5ex}
   \end{minipage}
   }
+  \vspace{-2.5ex}
 \caption{Two examples of comparisons between different design scenarios and adder implementations with limited area budget.
@@
 \label{Fig:Error_Area}
-%\vspace{-2ex}
+\vspace{-2ex}
 \end{figure}
 
-If the area budget is 35 LUTs, as seen in Fig.~\ref{subfig:error_area_lut35}, it can be noticed that for all frequency values, the overcloced RCA achieves no larger mean error than the RCA with truncated operand word-lengths.
-This is in accordance with the analysis in Section~xxx.
-We also notice that both CSA and OA cannot be implemented with full precision due to the limited area budget, and this leads to large truncation errors.
-Despite that the CSA with 4 stages is best for some frequencies, in general the overclocked RCA is still the optimum design for most frequency requirements.
+The results shown in Fig.~\ref{Fig:Error_Area} can be further extended by testing with a variety of area constraints.
+In this case, we can map the optimum design scenarios into the design space of different operating frequencies and area consumptions, as shown in Fig.~\ref{Fig:adder_3d_FreqArea}.
+In general this graph can be divided into several regions.
+Firstly, if the frequency requirement is moderate whilst the area budget is large enough to implement an OA in full precision, it will be the optimum design.
+This is because long carry chains are eliminated from OA such that it can maintain full precision for a wide range of frequency values.
+Also this is in accordance with the results in Fig.~\ref{subfig:error_area_lut55}.
+Secondly, CSA is a better design choice for high frequency requirements and large area budget, because it is originally designed with high speed operation.
+Besides, each stage of CSA is implemented in the FPGA with fast carry logic~\cite{Virtex6}, hence it runs even faster than OA.
+Thirdly, for a tighter area budget only part of OA and CSA can be implemented, whereas RCA still keeps original precision.
+In this situation, area becomes the limitation factor.
+Both OA and CSA generate truncation errors, which are greater than the overclocking error of RCA.
+Therefore, the overclocked RCA is the optimum design option across almost the entire frequency domain.
+Furthermore, the precision of RCA is also limited under very stringent area constraints.
+This causes truncation errors for every design option.
+Nevertheless, RCA with either overclocking or truncation scenario equally serves to be optimal, because it maintains more precision than OA and CSA for a specific area budget.
 
-However if the area budget is released to 55 LUTs, OA can be implemented with original word-length.
-Additionally CSA can be implemented with larger precision, but still not the full precision.
-Therefore as shown in Fig.~\ref{subfig:error_area_lut55}, OA serves as the optimum design choice with respect to a wide range of frequencies.
-For higher frequencies, the MRE of OA increases rapidly, and CSA with 4 stages outperforms for higher frequencies.
-Similar to Fig.~\ref{subfig:error_area_lut35}, the overclocked RCA is the optimum design choice for even higher frequencies, because in this case the CSA can only be implemented with small precisions, and the multiplexer delay limits the benefits of parallelism.
+\begin{figure*}[tbp]
+  \centering
+  \includegraphics[width=.7\textwidth]{./figures/exp/3d_FreqArea.eps}
+  \vspace{-3ex}
+  \caption{Mapping of optimum design metric of adders, which achieves minimum error with respect to a variety of frequency and area constraints.
+The original word-length of all adders is 32-bit.
+The results are obtained from Xilinx ISE 14.7.}
+  \label{Fig:adder_3d_FreqArea}
+\end{figure*}
+
+\subsection{Optimum Adder with Given Accuracy and Area Budgets}\label{subsec:adder_accuracy_area}
+If the circuit is designed to operate as fast as possible with minimum area, whilst a certain amount of imprecision can be tolerated, the optimum adder design metric can also be determined as illustrated in Fig.~\ref{Fig:adder_3d_ErrorArea}.
+In this set of experiments, the error budget is evaluated in terms of MRE, which varies from $10^{-6}\%$ to $10\%$.
+For a given MRE, the optimum adder is selected with maximum operating frequency.
+In this case, if multiple designs can operate with the same frequency, the optimum design is then selected based on actual area consumption within the area constraint.
 %
@@
   \centering
-  \includegraphics[width=.8\textwidth]{./figures/exp/3d_FreqArea.eps}
-  \caption{The maximum word-length of different adder structures.}
-  \label{Fig:adder_3d_FreqArea}
-\end{figure*}
-
-The results shown in Fig.~\ref{Fig:Error_Area} can be further extended by testing with a variety of area constraints.
-In this case, we can map the optimum design scenarios into the design space of different operating frequencies and area consumptions, as shown in Fig.~\ref{Fig:adder_3d_FreqArea}.
-It can be seen that in general the graph is divided into several regions.
-Firstly, if the frequency requirement is moderate whilst the area budget is large enough to implement an OA in full precision, it will be the optimum design.
-This is because long carry chains are eliminated from OA such that it can maintain full precision for a wide range of frequency values.
-Also this is in accordance with the results in Fig.~\ref{subfig:error_area_lut55}.
-Secondly, CSA is a better design choice for high frequency requirement and large area budget, because it is originally designed with high speed operation.
-Besides, each stage of CSA is implemented in the FPGA with fast carry logic [xxx], hence it runs even faster than OA.
-Thirdly, for a tighter area budget only part of OA and CSA can be implemented, whereas RCA still keeps original precision.
-In this situation, area becomes the limitation factor.
-Truncation errors occur for both OA and CSA and they are greater than the overclocking error of RCA.
-Therefore, the overclocked RCA is the optimum design option across almost the entire frequency domain.
-Furthermore, the precision of RCA is also limited for very stringent area constraints.
-This causes truncation errors for every design option.
-Nevertheless, RCA with either overclocking or truncation scenario equally serves to be optimal, because it maintains more precision than OA and CSA for a specific area budget.
-
-\subsection{Optimum Adder Design Metric with Given Accuracy and Area Requirements}
-%
-\begin{figure*}[tbp]
-  \centering
-  \includegraphics[width=.8\textwidth]{./figures/exp/3d_ErrorArea.eps}
-  \caption{.The original word-length for all adders is 32-bit.}
+  \includegraphics[width=.7\textwidth]{./figures/exp/3d_ErrorArea.eps}
+  \vspace{-3ex}
+  \caption{Mapping of optimum design metric of adders, which achieves highest frequency with respect to a variety of accuracy and area constraints.
+The original word-length of all adders is 32-bit.
+The results are obtained from Xilinx ISE 14.7.}
   \label{Fig:adder_3d_ErrorArea}
@@
 
+Similar to the analysis in Section~\ref{subsec:adder_freq_area}, for tight accuracy requirement and large area budget, OA is the optimum design choice because it keeps full precision while running at high frequencies.
+If relaxing the accuracy requirement (e.g.
+$0.01\%$), CSA gradually outperforms because its precision loss is less than that of OA.
+Once again, if area budget is tightened, the RCA becomes the best design choice, because the precision of OA and CSA is largely limited.
+Furthermore, when the accuracy requirement is released (e.g.
+over $1\%$), RCA can operate with the fastest frequency across most area constraints.
+
 \section{Conclusion}\label{sec:conclusion}
+In this paper, we have quantified design trade-offs for three different adder structures: ripple carry adder, carry select adder and online adder.
+Two design scenarios that can sacrifice accuracy for better performance have been evaluated: one is the conventional design scenario in which timing closure is achieved by truncating precision, the other is the overclocking scenario where timing violations are allowed to occur.
+By combining both adder structures and design scenarios, we have demonstrated experimentally the optimum design option when considering a variety of frequency-accuracy-area trade-offs.
+We have shown that applying the overclocking scenario to RCA can be beneficial with limited area budget, whilst applying the conventional scenario to online adder is an optimal design choice with relaxed area requirements.
+
+In the future we wish to provide similar evaluation to other arithmetic primitives, such as multipliers.
+Other evaluation metrics, such as energy consumption and throughput, can also be included in the future.
+
+% and more complex designs and applications.
 

### 2014-11-23 FPT2014/final/bare_conf.tex

--- 2014-10-15 FPT2014/bare_conf.tex
@@
 % Furthermore in comparison to standard arithmetic primitives, this translates to reduction of the area overheads from up to $8.41\times$ to $1.88\times$ for adders, and from $8.11\times$ to $1.84\times$ for multipliers using direct implementation, to $1.88\times$ and $0.54\times$ using our approaches.
-
 \end{abstract}
-
-f
 
@@
   %\vspace{-2.5ex}
-  \includegraphics[width=.48\textwidth]{./Figures/OnlineArithmetic_DataFlow.eps}
-  \vspace{-4ex}
+  \includegraphics[width=.45\textwidth]{./Figures/OnlineArithmetic_DataFlow.eps}
+  %\vspace{-3ex}
+  \vspace{-1ex}
   \caption{Dataflow in digit-serial online arithmetic, in which both inputs and outputs are processed from the MSD to the LSD. $\delta$ denotes the online delay.}
-  \vspace{-1ex}
+  \vspace{-2ex}
   \label{Fig:OnlineDataFlow}
@@
   \centering
-  \includegraphics[width=.5\textwidth]{./Figures/SDAdder.eps}
-    \vspace{-7ex}
+  \includegraphics[width=.45\textwidth]{./Figures/SDAdder.eps}
+  %\vspace{-7ex}
+  \vspace{-2ex}
   \caption{An $N$-digit binary digit-parallel online adder. Both inputs and outputs are represented using SD representation. ``3:2'' denotes a 3:2 compressor.}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/SDAdder_42comp_Spartan.eps}
-	\vspace{-4ex}
+	\includegraphics[width=.47\textwidth]{./Figures/SDAdder_42comp_Spartan.eps}
+	%\vspace{-4ex}
+  \vspace{-1ex}
 	\caption{Map the online adder onto Spartan FPGAs using the fast-carry resources.
@@
 Dotted circle indicates the logic block (LB) which can be mapped to the FPGA using the carry resources.}
-	\vspace{-4ex}
+	%\vspace{-2ex}
 	\label{Fig:PreviousWork}
@@
 	\centering
-	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork2.pdf}
-	\vspace{-3ex}
+	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_PreviousWork.eps}
+	\vspace{-1ex}
 	\caption{An example illustrating that direct applying approaches in \cite{FPT09RA} on a Virtex-6 FPGA will results in faulty outputs, because the carry input of \texttt{LB1} cannot be explicitly initialized.}
 	\label{Fig:PreWorkVirtex6}
-    \vspace{-2.5ex}
+   % \vspace{-2.5ex}
 \end{figure}
@@
 	\includegraphics[width=.85\textwidth]{./Figures/SDadder_FPGA_New_4digit.eps}
-	\vspace{-3ex}
+	\vspace{-1ex}
 	\caption{Alternative structure of online adder.
@@
 The dotted boxes outline the logic that can be mapped onto each LUT and the corresponding fast carry logic.}
-	\vspace{-2ex}	
+	\vspace{-1ex}	
 	\label{Fig:ModifiedOA}
@@
 	\centering
-	\includegraphics[width=.49\textwidth]{./Figures/SDadder_FastCarry_New.eps}
-	\vspace{-5ex}
+	\includegraphics[width=.45\textwidth]{./Figures/SDadder_FastCarry_New.eps}
+	%\vspace{-1.5ex}
 	\caption{Implementation of two logic blocks (LBs) in one FPGA slice which contains four 6-LUTs. NC stands for ``Not Care''.}
-	\vspace{-2ex}	
+	%\vspace{-2ex}	
 	\label{Fig:SliceNew}
@@
 	\includegraphics[width=.45\textwidth]{./Figures/Exp/Adder_Freq.eps}
+  \vspace{-1ex}
 	\caption{Rated frequencies of the RCA and the online adder with different implementation methods. The results are obtained from post place and route timing reports in ISE 14.7.}
 	\label{Fig:AdderFreq}
-	\vspace{-1ex}
+	\vspace{-3ex}
 \end{figure}
@@
 \end{algorithm}
-\vspace{-1ex}
 
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_Structure.eps}
-	\vspace{-3ex}
+	\includegraphics[width=.45\textwidth]{./Figures/ParallelMult_Structure.eps}
+	\vspace{-1ex}
 	\caption{(a) Structure of a 4-digit online multiplier using the proposed algorithm.
@@
 	\includegraphics[width=.4\textwidth]{./Figures/PartialProduct.eps}
-	\vspace{-2.5ex}
+	\vspace{-1.5ex}
 	\caption{Left: Direct implementation with extra logic to generate partial products.
@@
 	\label{Fig:PartialProduct}
-	\vspace{-1.5ex}
+	\vspace{-2ex}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=.5\textwidth]{./Figures/ParallelMult_MSDhalf.eps}
-  \vspace{-2ex}
+	\includegraphics[width=.45\textwidth]{./Figures/ParallelMult_MSDhalf.eps}
+  \vspace{-1ex}
 	\caption{(a) Modified structure of a 4-digit online multiplier which only generates the most significant 4-digit result.

### 2015-01-07 WAP2015/wap2015.tex
WAPCO15 paper final version

@@
 \usepackage{indentfirst}
+
+\ifx\pdfoutput\undefined
+\usepackage{graphicx}
+\else
 \usepackage[pdftex]{graphicx}
+\fi
+\usepackage{epstopdf}
+
+%\usepackage[pdftex]{graphicx}
 \usepackage[tight,footnotesize]{subfigure}
@@
 In order to provide the optimum design choice for adders, we examine several design constrains and options, such as accuracy, operating frequency, silicon area, different types of adder structure, as well as different forms of computer arithmetic for adder implementation.
-In comparison to the conventional design scenario that timing closure is achieved by truncating the operand word-length, we take a radical step forward by adopting an alternative design scenario, which is named ``overclockign scenario''.
+In comparison to the conventional design scenario that timing closure is achieved by truncating the operand word-length, we take a radical step forward by adopting an alternative design scenario, which is named ``overclocking scenario''.
 In this case, circuits are operated far beyond the conservation region with full precision, while timing violation can be tolerated.
@@
 \begin{eqnarray}\label{Eq:MeanError_RCA}
-    E_O=\left\{
+    E_{oc}=\left\{
         \begin{matrix}
@@
 \begin{eqnarray}\label{Eq:MeanTruncError_RCA}
-    E_O=\left\{
+    E_{trad}=\left\{
         \begin{matrix}
@@
 \subsection{Online Adder}\label{subsec:online_adder}
-In addition to standard binary arithmetic, alternative forms of computer arithmetic was studied to boost performance.
+In addition to standard binary arithmetic, alternative forms of computer arithmetic were studied to boost performance.
 For example, adder with online arithmetic is also designed for low latency at the cost of extra silicon area.
@@
   \vspace{-4ex}
-  \caption{The maximum word-length of different adder structures.}
+  \caption{The maximum area of different adder structures.}
   %\vspace{-2ex}
@@
 In both cases, decisions must be made on which adder structure achieves this minimum, and which design scenario should be adopted.
+In our experiments, the inputs are set to randomly generated data following uniform distribution.
 %whether the circuit should be overclocked.
